### 2017-06-01 O2_fig.Rnw
version 0.1

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(warning=F, message = FALSE,echo=F,results='asis',error=FALSE,fig.lp='fig:',fig.path='images/')
@

<<O2_fig,fig.cap='Maximum metabolic rate, determined by oxygen supply, as a function of temperature, for four different optimal temperatures (panels---see panel label for optimal temperature in degrees celsius), and increasing values of $\\eta$.', fig.width=8, fig.height=4, echo=FALSE, out.width='\\linewidth'>>=

grid <- expand.grid(eta = c(0.1,0.5,2,5),
                    Topt = c(10,15,20,29))

O2fun <- function(x) {
  ts = with(x,((30-seq(1,30,l=1000))/(30-Topt))^eta*exp(-eta*(30-seq(1,30,l=1000))/(30-Topt)))
  ts = ts/max(ts)
}

require(dplyr)
require(purrr)
require(ggplot2)
#require(cowplot)

g <- grid %>% 
  by_row(~O2fun(.x), .collate='rows') %>%
  group_by(.row) %>%
  mutate(Temperature=seq(1,30,l=1000))

  ggplot(g) + 
  geom_line(aes(x = Temperature, 
                y = .out,
                linetype=factor(eta))) + 
  theme_bw() + 
  facet_grid(Topt~.) +
  scale_linetype_discrete(bquote(eta)) + 
  ylab(expression(Relative~O[2]~supply)) # + 
  #scale_color_discrete(bquote(T[opt]), h.start = 180)

@

### 2017-06-01 draft.Rnw
version 0.1

\documentclass{article}
\usepackage{amsmath}
\usepackage{caption} 
\usepackage{array} 
\usepackage{breqn}
\usepackage[backend=biber]{biblatex}
\addbibresource{Sizing-fx-of-temperature.bib}
\captionsetup[table]{singlelinecheck=false}

\title{Sizing the effects of temperature on ectotherms - from physiology to ecology}
\author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
        Ken H. Andersen\\Centre for Ocean Life
        Danish Technical University, Lyngby, Denmark}

\begin{document}

\maketitle

\section*{Abstract}

Increasing temperatures under climate change are thought to affect individual physiology of ectotherms through increases in metabolic demands, leading to decreases in body-size with concomitant effects on species ecology. Although intuitively appealing, the magnitude, as well as when and where such changes are expected in an ecosystem context remains unclear. We develop a general trait-based model of carbon and oxygen budgets to determine the relative influence of thermal sensitivity, oxygen limitation, and environmental conditions on ectotherm body size.  Our model provides a physiological basis for changes in species size and observed ecological consequences of temperature, and ties together various strands of thought about the ecological consequences of increased temperatures.

\section{Introduction}

Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\cite{deutsch_climate_2015,pinsky_marine_2013,brown_toward_2004}). As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\cite{deutsch_climate_2015, stuart-smith_thermal_2015}). However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems. Through this cascade of scales, incorrect or approxiamte model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\cite{brander_overconfidence_2013, lefevre_models_2017}). In marine fish, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017}). While it is not disputed that organism size can change as a result of changing temperatures, the question is when, where and why this is so.

Empirically, most ectotherms are found to grow larger at colder temperatures - a phenomenon called the temperature-size rule. Models of ectotherm growth can reproduce this pattern (under assumptions of optimal energy allocation between growth and reproduction) if increases in metabolic costs (metabolism) with temperature outpace increases in energy acquisition (\cite{kozlowski_can_2004}). While increasing metabolic costs are real, energy acquisition is an abstract, phenomenological description that lumps ecological aspects of foraging activity and prey availability. At this more mechanistic level of energy acquisition, consistent temperature patterns have remained elusive (\cite{englund_temperature_2011,rall_universal_2012}), with highly variable responses across habitats and taxa.

Physiologically, a long held view has been that temperature is a controlling factor while oxygen supply sets the physiological limits (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016}). Other factors, such as salinity and pH are masking factors that influence physiology via their effects on oxygen availability and temperature sensitivity. How exactly temperature influences physiological rates and limits, however, has been a matter of debate, not least because of the variable responses observed among different species.

In most species, the standard metabolism (i.e., the metabolic cost of maintenance and routine activity such as ventilation) increases steadily with temperature. A prevalent view is that the maximum metabolic rate (i.e., the metabolic rate at maximum sustained exercise) has a  dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}). This leads to the view of a modal curve for metabolic scope, the available oxygen/energy for activity, and suggests that towards the upper end of the curve. This view was formalized in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species limits their ability to sustain core functions such as foraging and growth. In some species, however, maximum metabolic rate may be steadily increasing (\cite{lefevre_are_2016}), suggesting that oxygen may not be the limiting factor. Consequently, the difference in observed physiological responses will at least partially determine temperature effects on body size for individual species. In addition to physiological differences, the assumed coefficients for temperature sensitivity of metabolism and size scaling exponents are different between species, and can disproportionately affect inferences about future organism size.

A general framework for understanding temperature effects on size should reflect physiology, and also allow exploring effects of physiological traits on temperature dependence of body size. Here, we develop a trait based framework to investigate temperature on ectotherm physiology, growth and body size. We discuss traits that have large effects on body size, and discuss expectations under climate change.

\section{Setting up the model}

\subsection{Key assumptions}

Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets. In setting up the model we make a number of key assumptions, which are similar to those made in Holt \& Jorgensen. At a high level, we assume that animals will adapt activity levels to optimise available energy for growth and reproduction. Growth is limited either by food capture, food processing capacity, or by available oxygen. We further assume that temperature acts directly on rates that are determined by enzymatic activity: digestive activity (via maximum consumption) and metabolic costs. The scaling with temperature (determined by the activation energy $E_a$) is assumed the same for these processes. Consequently, temperature only acts on ecological rates (food acquisition) via optimisation given temperature driven changes in enzymatic rates.

\subsection{Metabolically constrained activity model}

In the constrained activity model, ectotherms adjust the relative amounts of time ($\tau$) spent foraging and resting/hiding to optimise the net energy/mass gain $P_C$ relative to natural mortality. Since both energy gain and loss are sensitive to temperature and oxygen limitations, both the activity level and the net energy gain will be subject to these environmental constraints. Their interplay thus determines available energy for growth, reproduction, and, ultimately, organisms final size.

The model is written in terms of carbon (or energy) and oxygen balance equations:

\begin{align}
f_C &= \frac{\tau }{\tau  + \frac{h c_T w^{q-p}}{\gamma\Theta} } \label{eq:f} \\
P_C &= S_C - D_C \\
  &=(1-\beta-\phi)f_C h c_T w^q  -(1+\tau \delta)c_T k w^n \\
P_{0_2} &= S_{O_2} - D_{O_2} \\
        &= f_{O_2}w^n - \omega \left( \beta f_C h c_T w^q +(1+\tau \delta) c_T k w^n \right)
\end{align}

where $f$ is the feeding level ([0,1]) at weight $w$, determined by the fraction of time spent foraging (or proportion of maximum attack rate) $\tau$, consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h w^q$. In the following, we will refer to $\tau$ as the activity fraction for sake of generality. Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke2002predator, sentis2013parsing}), is assumed to scale with temperature as $c_T = e^{E_a(T-T_0)/kTT_0}$. Available carbon $P_C$ is determined by supply ($S_C$) from prey consumption ($f_C h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested. Metabolic costs ($D_C$) are those of standard metabolism ($k w^n$), as well as active metabolism (scaled in units of standard metabolism as $\delta k w^n$), with the activity fraction $\tau$ determining the fraction of time that the active metabolism cost applies.

The oxygen budget determines the metabolic scope $P_{0_2}$. Metabolic scope is the difference between oxygen supply $S_{O_2}/w^n=f_{O_2}$, the amount of oxygen supplied per unit weight, and oxygen demand. Demand ($D_{O_2}$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy and growth - $\beta f_C h c_T w^q$) and catabolism ($[1+\tau \delta] c_T k w^n$), with $\omega$ determining amount of oxygen required per unit of metabolised carbon (note: oxygen is measured in the same units as the carbon. To find the actual amount of oxygen used multiply by the amount of oxygen used to respire one unit of carbon).

The maximum oxygen consumption---usually assumed to occur at the maximum metabolic rate (MMR), or active metbolic rate---is the oxygen consumption during maximal activity level that can be sustained over some time. This level is determined by oxygen delivery to organs and muscles. At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function \cite[e.g.,][]{lefrancois_influence_2003}. We specify $P_{50}$ as the point where the MMR (or oxygen supply) has dropped by 50\% relative to the saturation level $l$ \footnote{Could also use the same functional form as the consumption of food for simplicity: $f_{O_2} = \Gamma \Theta_{O_2}/\Gamma \Theta_{O_2} + h_{O_2} = \Theta_{O_2}/(\Theta_{O_2} + P_{50}).$}. Oxygen supply, and hence the MMR, are usually found to be temperature dependent \cite{lefelefevre_are_2016}. We follow \cite{gnauck2013freshwater, lefrancois_influence_2003} and use a dome shaped function that peaks at the optimal temperature (optimal in the sense of maximising the MMR). Thus:

\begin{align}
f_{O_2}&=\lambda(1-e^{O_2\log(0.5)/P50}),\\
\lambda&=\zeta(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}})^\eta \times \exp(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}),
\end{align}

with $f_{O_2}$ the oxygen supply (MMR), $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which the MMR is optimised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (Figure \ref{fig:O2_fig}). Note that we can emulate a MMR that increases up to the lethal temperature by setting the optimal temperature for MMR close to the maximum temperature.

\input{O2_fig}

We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness (I \emph{think} this amounts to maximizing R0, but can't find the reference where this came from). We further assume here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M_{\tau,w} = \tau^\eta \rho w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=1$, that is, at constant maximum activity and $M$ is the effective mortality at realised levels of activity at weight $w$.

\input{m}

The optimal activity level ($\tau_{\text{opt}}$) is found at $\frac{dF}{d\tau}=0$. We assume that the metabolic scope dictates the upper limit of this activity, such that at $\tau_{\text{max}}$, oxygen demand $D_{0_2}$ equals total supply $S_{0_2}$. Both temperature and oxygen will influence $\tau$, such that at a given temperature and oxygen concentration, $\tau_{T,O_2} = \text{min}\left( \tau_{\text{opt}},\tau_{\text{max}} \right)$, meaning we assume that animals will adapt their effort to optimise fitness $F$ given temperature and oxygen constraints.

Life history theory suggests that the maximum\/asymptotic weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity; CITE Taylor, PErrin,Kozlovski). Note that $W_{\infty}$ depends on temperature only through $\tau$ and changes in $P_C$ as temperature changes metabolic and enzymatic rates. We thus impose no direct constraint on $W_{\infty}$.

\begin{table}
\caption{Parameters}
\begin{tabular}{ll}
Description & Value \\
\hline
Specific dynamic action & $\beta = 0.15$ \\
Egestion and excretion & $\phi = 0.25$ \\
Consumption rate$^1$ & $\Theta \gamma \approx h w^{p-q}$ (g$_C$/time) \\
Coef.~for maximum consumption rate & $h \approx 20 $g$_{WW}^{1-n}$/yr \\
Activity coefficient & $\delta \approx 3$ \\
Exponent for max.~consumption & $q=0.75$ \\
Exponent for clearance rate & $p=0.8$ \\
Exponent for std.~metabolism & $n=0.88$ \\
\hline
\multicolumn{2}{p{\textwidth}}{$^1$ This is under the assumption that the amount of encountered food $\Theta$ is roughly independent of body size.  This gives and order-of-magnitude estimate of the product $\Theta \gamma $.}
\end{tabular}
\end{table}

\section{Model results}

\begin{figure}
\includegraphics[width=\linewidth]{activity} 
\caption[Activity, feeding and maximum length as a function of temperature]{Consequences of increasing temperature on activity levels, feeding and maximum weight. (a) Optimal (dashed line), limiting (dotted line) and realised (solid line) activity as a function of temperature. Realised activity is the smaller of the limiting and optimal levels at each temperature, with activity limited by O2 supply as pictured by dashed lines in b). Optimal acitivity steadily increases to compensate for rising metabolic costs (dotted line in b) with temperature until limited by oxygen (overlapping supply (dashed) and demand (solid) curves in b). (c) Rising activity lelves keeps feeding levels constant (solid line in c).  Mortality levels (dashed) increase as activity increases with temperature, while available energy (carbon, dotted line) for growth and reproduction peaks and decreases. Note that energy is only limited by oxygen-limited activity levels at low temperatures in scenario 3. }
\label{fig:act_fig}
\end{figure}

\section{Discussion}

\printbibliography 
\end{document}

### 2017-06-01 m.Rnw
version 0.1

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(warning=F, message = FALSE,echo=F,results='asis',error=FALSE,fig.lp='fig:',fig.path='images/')
@

<<mortality,fig.cap='Mortality as a function of activity $\\tau$ for three levels of the mortality scaler $\\eta$',fig.width=5, fig.height=4,>>=
  require(ggplot2)
mframe <- data.frame(tau = rep(c(0,exp(seq(log(0.001),log(1),l=100))),each=3),
                     etalab = as.character(c(0.33,1,3)),
                     M=rep(c(0,exp(seq(log(0.001),log(1),l=100))),each=3)^c(0.33,1,3)*1)

ggplot(mframe) + 
  geom_line(aes(x=tau,y=M,linetype=etalab)) + 
  theme_bw() +
  xlab(bquote(tau)) +
  scale_linetype(expression(eta))
@

### 2017-06-01 model.R

@@ -1,0 +1,675 @@
+O2_plotfun <- function(etas,Tops){
+  grid <- expand.grid(eta = etas,
+                      Topt = Tops)
+  
+  O2fun <- function(x) {
+    ts = with(x,((30-seq(1,30,l=1000))/(30-Topt))^eta*exp(-eta*(30-seq(1,30,l=1000))/(30-Topt)))
+    ts = ts/max(ts)
+  }
+  
+  
+  
+  require(dplyr)
+  require(purrr)
+  require(ggplot2)
+  g <- grid %>% 
+    by_row(~O2fun(.x), .collate='rows') %>%
+    group_by(.row) %>%
+    mutate(Temperature=seq(1,30,l=1000)) 
+  
+  ggplot(g) + 
+    geom_line(aes(x = Temperature, 
+                  y = .out,
+                  linetype=factor(eta))) + 
+    theme_bw() + 
+    facet_grid(Topt~.) +
+    scale_linetype_discrete(bquote(eta)) + 
+    ylab(paste(expression(O_2, supply))) # + 
+  #scale_color_discrete(bquote(T[opt]), h.start = 180)
+  
+}
+
+plot_data_temp <- function(v){
+  
+  out = eval_tau_eq(gamma=v$gamma,
+                    delta=v$delta,
+                    phi=v$phi,
+                    h=v$h,
+                    beta=v$beta,
+                    k=v$k,
+                    p=v$p,
+                    q=v$q,
+                    n=v$n,
+                    m=10^seq(-1,5,l=100),
+                    M=v$M,
+                    v=v$v)
+  
+  pd <- data_frame(m=10^seq(-1,5,l=100))
+  pd$tau_uc <- out
+  
+  #browser()
+  O2 = O2_supply(O2=seq(1,10,l=length(v$temp)),Topt=v$Topt,O2crit=v$O2crit,Tmax=v$temp[length(v$temp)],T=v$Topt,delta=v$lO,omega=v$shape,P50=v$P50,n=v$n)
+  tau_o2 = sapply(eval_tau_max_o2(f=O2,omega = v$omega,
+                                  gamma=v$gamma,
+                                  delta=v$delta,
+                                  phi=v$phi,
+                                  h=v$h,
+                                  beta=v$beta,
+                                  k=v$k,
+                                  p=v$p,
+                                  q=v$q,
+                                  n=v$n,
[…]

### 2017-06-01 run.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+set -ex
+
+#docker build -t docker.dragonfly.co.nz/adaptive_activity .
+
+#docker push docker.dragonfly.co.nz/adaptive_activity
+
+docker run --rm  -v $PWD:/work -w /work \
+  docker.dragonfly.co.nz/adaptive_activity ./build.sh

### 2017-06-01 script.R

@@ -1,0 +1,403 @@
+#Scenarios
+require(tidyr)
+require(dplyr)
+require(ggplot2)
+require(cowplot)
+require(viridis)
+
+source('model.R')
+
+sc1 <- list(beta=0.15,
+            delta=4,
+            Ea=0.52, 
+            gamma=40, 
+            h=20, 
+            k=1.2,
+            lO=1, 
+            m=100, 
+            M=2 ,
+            n=0.88, 
+            O2crit=2, 
+            omega=0.03, 
+            p=0.8 ,
+            P50=4.2, 
+            phi=0.25, 
+            q=0.75 ,
+            shape=0.1,
+            temp=seq(8,26,l=100),
+            Topt=20, 
+            Tref=15 ,
+            v=1)
+
+sc2 <- list(beta=0.15,
+            delta=4,
+            Ea=0.52, 
+            gamma=40, 
+            h=20, 
+            k=1.2,
+            lO=1, 
+            m=100, 
+            M=2 ,
+            n=0.88, 
+            O2crit=2, 
+            omega=0.03, 
+            p=0.8 ,
+            P50=4.2, 
+            phi=0.25, 
+            q=0.75 ,
+            shape=1,
+            temp=seq(8,26,l=100),
+            Topt=20, 
+            Tref=15 ,
+            v=1)
+
+sc3 <- list(beta=0.15,
+            delta=4,
+            Ea=0.52, 
+            gamma=40, 
+            h=20, 
+            k=1.2,
+            lO=1, 
+            m=100,  
+            M=2 ,
+            n=0.88, 
+            O2crit=2, 
+            omega=0.03, 
+            p=0.8 ,
+            P50=4.2, 
+            phi=0.25, 
+            q=0.75 ,
+            shape=5,
+            temp=seq(8,26,l=100),
+            Topt=20, 
+            Tref=15 ,
+            v=1)
+
+scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(1:3,each=100))),
+                       bind_rows(plot_data_temp(sc1),
+                       plot_data_temp(sc2),
+                       plot_data_temp(sc3)))
+
+ggp <-lst()
+
+sc_act <- tidyr::gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
+  mutate(Activity = relevel(as.factor(Activity), "Realised"))
+
+ggp[['Activity']] <- ggplot(sc_act) + 
[…]

### 2017-06-29 O2_fig.Rnw
drafting

@@
 opts_chunk$set(warning=F, message = FALSE,echo=F,results='asis',error=FALSE,fig.lp='fig:',fig.path='images/')
+install.packages("purrrlyr",repo="http://cloud.r-project.org/")
+library("purrrlyr")
 @

### 2017-06-29 draft.Rnw
drafting

@@
-\documentclass{article}
+\documentclass[a4paper, toc=index,abstract=true]{scrartcl}
+\usepackage{geometry}
+\usepackage{enumitem}
+\usepackage{setspace}
+\usepackage{subfig}
+\usepackage{placeins}
 \usepackage{amsmath}
-\usepackage{caption} 
-\usepackage{array} 
-\usepackage{breqn}
-\usepackage[backend=biber]{biblatex}
+\usepackage{pdflscape}
+\usepackage{longtable}
+\usepackage[toc,page]{appendix}
+\usepackage{array,booktabs}
+\usepackage[american]{babel}
+\usepackage[backend=biber,style=apa,language=american, labeldate=year,
+uniquename=false, maxcitenames=2,maxbibnames=200,uniquelist=false,mincitenames=1]{biblatex}
+\usepackage{lineno, blindtext}
+\DeclareLanguageMapping{american}{american-apa}
 \addbibresource{Sizing-fx-of-temperature.bib}
@@
 
-\title{Sizing the effects of temperature on ectotherms - from physiology to ecology}
+\title{Sizing the effects of temperature on fish - from physiology to ecology}
 \author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
@@
 
-\section*{Abstract}
+\begin{spacing}{1.9}
+
+\pagenumbering{gobble}
+\begin{abstract}
 
@@
 Our model provides a physiological basis for changes in species size and observed ecological consequences of temperature, and ties together various strands of thought about the ecological consequences of increased temperatures.
+
+\end{abstract}
+{\large Keywords:} stock assessment, fisheries meta-analysis, fishery development, time-to-event analysis, marine conservation, catch-only methods
+
+\newpage
 
@@
 In marine fish, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017}).
-While it is not disputed that organism size can change as a result of changing temperatures, the question is when, where and why this is so.
+While it is not disputed that organism size can change as a result of changing temperatures, the question remains when, where and why this is so.
 
-Empirically, most ectotherms are found to grow larger at colder temperatures - a phenomenon called the temperature-size rule.
-Models of ectotherm growth can reproduce this pattern (under assumptions of optimal energy allocation between growth and reproduction) if increases in metabolic costs (metabolism) with temperature outpace increases in energy acquisition (\cite{kozlowski_can_2004}).
-While increasing metabolic costs are real, energy acquisition is an abstract, phenomenological description that lumps ecological aspects of foraging activity and prey availability.
-At this more mechanistic level of energy acquisition, consistent temperature patterns have remained elusive (\cite{englund_temperature_2011,rall_universal_2012}), with highly variable responses across habitats and taxa.
+Empirically, most ectotherms are found to grow larger in colder temperatures - a phenomenon called the temperature-size rule (\cite{atkinson_cells_2006}).
+Models of ectotherm growth can reproduce this pattern (under assumptions of optimal energy allocation between growth and reproduction) if increases in metabolic costs (in terms of energy) with temperature outpace increases in energy acquisition (\cite{kozlowski_can_2004}).
+However, while increasing metabolic costs are real, energy acquisition is an abstract, phenomenological description that lumps ecological aspects of foraging activity and prey availability.
+At a more mechanistic level of energy acquisition, consistent responses of foraging and energy aquisition with temperature have remained elusive (\cite{englund_temperature_2011,rall_universal_2012}), with variable responses across habitats and taxa.
+This is perhaps not surprising given variable foraging ecologies, but it remains unclear how temperature dependant feeding ecology impacts growth and adult size.
 
 Physiologically, a long held view has been that temperature is a controlling factor while oxygen supply sets the physiological limits (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016}).
-Other factors, such as salinity and pH are masking factors that influence physiology via their effects on oxygen availability and temperature sensitivity.
 How exactly temperature influences physiological rates and limits, however, has been a matter of debate, not least because of the variable responses observed among different species.
+In most species, the standard metabolism (i.e., the metabolic cost of maintenance and routine activity such as ventilation) increases near exponentially with temperature.
+A prevalent view is that the maximum metabolic rate (i.e., the metabolic rate at maximum sustained exercise) has a  dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
+This leads to the view of a modal curve for metabolic scope (the available oxygen/energy for activity), and suggests that towards the upper end of this curve, organisms will run out of oxygen.
 
-In most species, the standard metabolism (i.e., the metabolic cost of maintenance and routine activity such as ventilation) increases steadily with temperature.
-A prevalent view is that the maximum metabolic rate (i.e., the metabolic rate at maximum sustained exercise) has a  dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
-This leads to the view of a modal curve for metabolic scope, the available oxygen/energy for activity, and suggests that towards the upper end of the curve.
-This view was formalized in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species limits their ability to sustain core functions such as foraging and growth.
-In some species, however, maximum metabolic rate may be steadily increasing (\cite{lefevre_are_2016}), suggesting that oxygen may not be the limiting factor.
-Consequently, the difference in observed physiological responses will at least partially determine temperature effects on body size for individual species.
-In addition to physiological differences, the assumed coefficients for temperature sensitivity of metabolism and size scaling exponents are different between species, and can disproportionately affect inferences about future organism size.
+This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth.
+In some species, however, maximum metabolic rate may be steadily increasing (\cite{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor.
+Consequently, the difference in observed physiological responses may at least partially determine temperature effects on body size for individual species.
+In addition to physiological differences, the assumed coefficients for temperature sensitivity of metabolism and size scaling exponents are different between species, and can disproportionately affect inferences about future organism size \cite{lefevre_models_2017, kozlowski_can_2004}.
 
-A general framework for understanding temperature effects on size should reflect physiology, and also allow exploring effects of physiological traits on temperature dependence of body size.
 Here, we develop a trait based framework to investigate temperature on ectotherm physiology, growth and body size.
-We discuss traits that have large effects on body size, and discuss expectations under climate change.
+We discuss physiological traits that have large effects on body size changes, and discuss expectations under climate change.
 
@@
 Available carbon $P_C$ is determined by supply ($S_C$) from prey consumption ($f_C h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
-Metabolic costs ($D_C$) are those of standard metabolism ($k w^n$), as well as active metabolism (scaled in units of standard metabolism as $\delta k w^n$), with the activity fraction $\tau$ determining the fraction of time that the active metabolism cost applies.
+Metabolic costs ($D_C$) are those of standard metabolism ($k w^n$), as well as active metabolism (scaled in units of standard metabolism as $\delta k w^n$, with $\delta$ the factorial aerobic scope (FAS)), with the activity fraction $\tau$ determining the fraction of time that the active metabolism cost applies.
 
-The oxygen budget determines the metabolic scope $P_{0_2}$.
-Metabolic scope is the difference between oxygen supply $S_{O_2}/w^n=f_{O_2}$, the amount of oxygen supplied per unit weight, and oxygen demand.
-Demand ($D_{O_2}$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy and growth - $\beta f_C h c_T w^q$) and catabolism ($[1+\tau \delta] c_T k w^n$), with $\omega$ determining amount of oxygen required per unit of metabolised carbon (note: oxygen is measured in the same units as the carbon.
-To find the actual amount of oxygen used multiply by the amount of oxygen used to respire one unit of carbon).
+The oxygen budget $P_{0_2}$, determines physiological limits to aerobic acitivity.
+Demand ($D_{O_2}$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy and growth - $\beta f_C h c_T w^q$) and ``active metabolism", the sum of standard (or resting) metabolism and the metabolic costs of foraging ($[1+\tau \delta] c_T k w^n$), with $\omega$ determining amount of oxygen required per unit of metabolised carbon.
+Metabolic scope is the difference between $S_{O_2}/w^n=f_{O_2}$, the amount of oxygen supplied per unit weight, and oxygen demand due to standard metabolism ($c_T k w^n$).
 
-The maximum oxygen consumption---usually assumed to occur at the maximum metabolic rate (MMR), or active metbolic rate---is the oxygen consumption during maximal activity level that can be sustained over some time.
+The maximum oxygen consumption---usually assumed to occur at the maximum metabolic rate (MMR)---is the oxygen consumption during maximal activity level that can be sustained over some time.
 This level is determined by oxygen delivery to organs and muscles.
@@
 We specify $P_{50}$ as the point where the MMR (or oxygen supply) has dropped by 50\% relative to the saturation level $l$ \footnote{Could also use the same functional form as the consumption of food for simplicity: $f_{O_2} = \Gamma \Theta_{O_2}/\Gamma \Theta_{O_2} + h_{O_2} = \Theta_{O_2}/(\Theta_{O_2} + P_{50}).$}.
-Oxygen supply, and hence the MMR, are usually found to be temperature dependent \cite{lefelefevre_are_2016}.
+Oxygen supply, and hence the MMR, are usually found to be temperature dependent \cite{lefevre_are_2016}.
 We follow \cite{gnauck2013freshwater, lefrancois_influence_2003} and use a dome shaped function that peaks at the optimal temperature (optimal in the sense of maximising the MMR).
@@
 
-We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness (I \emph{think} this amounts to maximizing R0, but can't find the reference where this came from).
+We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness \footnote{I \emph{think} this amounts to maximizing R0 if no more growth occurs: life expectancy is 1/M and reporoductive output is proportional to energy}.
 We further assume here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M_{\tau,w} = \tau^\eta \rho w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=1$, that is, at constant maximum activity and $M$ is the effective mortality at realised levels of activity at weight $w$.
 
+\begin{center}
 \input{m}
+\end{center}
 
@@
 
-Life history theory suggests that the maximum\/asymptotic weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity; CITE Taylor, PErrin,Kozlovski).
+Life history theory suggests that the maximum\/asymptotic weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity).
 Note that $W_{\infty}$ depends on temperature only through $\tau$ and changes in $P_C$ as temperature changes metabolic and enzymatic rates.
@@
 
-\begin{figure}
+\begin{figure}[ht!]
 \includegraphics[width=\linewidth]{activity} 
-\caption[Activity, feeding and maximum length as a function of temperature]{Consequences of increasing temperature on activity levels, feeding and maximum weight.
+\caption[Activity, feeding and maximum length as a function of temperature]{Consequences of increasing temperature on activity levels, feeding and maximum weight for an individual weighing 100g.
 (a) Optimal (dashed line), limiting (dotted line) and realised (solid line) activity as a function of temperature.
@@
 Note that energy is only limited by oxygen-limited activity levels at low temperatures in scenario 3.
-}
+The rate of change of available energy relative to mortality drives the adult size, which delines near linearly in log-space without oxygen limitations, and lower and upper limits imposed as oxygen limits activity and energy aquisition.}
 \label{fig:act_fig}
+\end{figure}
+
+Higher temperature have cascading effects through their influence on both metabolic and ecological rates (Figure \ref{fig:act_fig}).
+To maintain optimal energy aquisition for growth and reproduction relative to mortality, activity levels generally increase, until they reach limitations imposed by oxygen supply (Figure \ref{fig:act_fig}a).
+This limit occurs when active metabolic costs equal oxygen supply (Figure \ref{fig:act_fig}b), and are therefore more pronounced for species with strongly dome-shaped maximum-metabolic rates (scenario 3 in Figure \ref{fig:act_fig}).
+
+Although increasing energy levels maintain a constant feeding level, increased maximum consumption with temperature leads to a dome-shaped response in available energy (Figure \ref{fig:act_fig}c).
+Since the rate of change of available energy relative to mortality determines adult size,
+
+\begin{figure}[ht!]
+\includegraphics[width=\linewidth]{winf} 
+\caption[Influence of ecological and physiological variables on $W_\infty$]{Influence of scaling of mortality with activity (a), consumption rate (b), factorial aerobic scope (FAR; c), and exponent of metabolic rate on adult size $W\infty$.}
+\label{fig:winf_fig}
 \end{figure}
@@
 
+\end{spacing}
+
 \printbibliography 

### 2017-06-29 m.Rnw
drafting

@@
 
-<<mortality,fig.cap='Mortality as a function of activity $\\tau$ for three levels of the mortality scaler $\\eta$',fig.width=5, fig.height=4,>>=
+<<mortality,fig.align='center',fig.cap='Mortality as a function of activity $\\tau$ for three levels of the mortality scaler $\\eta$',fig.width=4, fig.height=3,out.height=4,out.width=3>>=
   require(ggplot2)

### 2017-06-29 build.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+set -ex
+
+#Rscript -e 'install.packages("purrr",repo="http://cloud.r-project.org/")'
+make
+
+cp draft.pdf /output/

### 2017-06-29 model.R

@@ -132,9 +132,9 @@ plot_data_temp <- function(v){
                     M = tau_max^v$v*v$M*v$m^(v$q-1),
                     Optimum = sapply(sapply(tau,max,0),min,1),
                     Scope=ifelse(scope<0.0001,0,scope),
-                    Supply = f*v$m^v$n,
-                    Demand = model_frame$Metabolism*v$omega,
-                    `Std Metabolism` = model_frame$Std*v$omega,
+                    `MMR` = f*v$m^v$n,
+                    `Active M.` = model_frame$Metabolism*v$omega,
+                    `Std M.` = model_frame$Std*v$omega,
                     Viable = as.numeric(tau_max>0.0001 & model_frame[['C for growth']]>0.0001))
   )
   return(bc)

### 2017-06-29 run.sh

@@ -7,4 +7,4 @@ set -ex
 #docker push docker.dragonfly.co.nz/adaptive_activity
 
 docker run --rm  -v $PWD:/work -w /work \
-  docker.dragonfly.co.nz/adaptive_activity ./build.sh
+  docker.dragonfly.co.nz/dragonverse-17.04:2017-06-28 ./build.sh

### 2017-06-29 script.R

@@ -89,7 +89,8 @@ ggp[['Activity']] <- ggplot(sc_act) +
   theme_cowplot()+
   #scale_size_discrete(guide='none',range = c(1.2,0.6))+
   theme(legend.justification=c(0,1), 
-        legend.position=c(0.05,0.95),
+        legend.position=c(0.55,1),
+        legend.box = "horizontal",
         legend.text  = element_text(size=8),
         legend.title = element_text(size=10),
         legend.spacing = unit(0.005,'npc'),
@@ -97,7 +98,7 @@ ggp[['Activity']] <- ggplot(sc_act) +
   labs(x = expression("Mean temperature " ( degree*C)),
        y=expression('Activity ' (tau)))
 
-sco <- tidyr::gather(scenarios,Rate,value,Supply, Demand, `Std Metabolism`)
+sco <- tidyr::gather(scenarios,Rate,value,MMR, `Active M.`, `Std M.`)
 
 ggp[['Oxygen']] <- sco %>%
   ggplot() + 
@@ -117,21 +118,21 @@ ggp[['Oxygen']] <- sco %>%
 
 sc <- function(x) x/max(x)
 sc_feed <- scenarios %>% 
-  #group_by(Scenario) %>% 
   mutate(Consumption=sc(Consumption),
          Efficiency=sc(Efficiency),
-         `Available C` = sc(`C for growth`)) %>% 
-  tidyr::gather(Rate,value,`Feeding level`,`Available C`,M) %>%
+         `Available Energy` = sc(`C for growth`),
+         `Available Energy` = ifelse(`Available Energy`<0,0,`Available Energy`)) %>% 
+  tidyr::gather(Rate,value,`Feeding level`,`Available Energy`,M) %>%
   mutate(Rate = relevel(as.factor(Rate),'Feeding level'))
 
-ggp[['Feeding']] <-sc_feed  %>% 
+ggp[['Feeding']] <- sc_feed  %>% 
   ggplot() + 
   geom_line(aes(x=Temperature, y=value, linetype=Rate, col=Scenario),alpha=0.7) +
   geom_point(data=sc_feed[seq.int(1,nrow(sc_feed),by = 5),],aes(x=Temperature, y=value, group=Rate, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
   theme_cowplot()+
   lims(y=c(0,1))+
   theme(legend.justification=c(1,1), 
-        legend.position=c(0.6,0.3),
+        legend.position=c(0.8,0.8),
[…]

### 2017-06-30 figures/O2_fig.tex
arg

\begin{figure}
\includegraphics[width=\linewidth]{images/O2_fig-1} \caption[Maximum metabolic rate, determined by oxygen supply, as a function of temperature, for four different optimal temperatures (panels---see panel label for optimal temperature in degrees celsius), and increasing values of $\eta$]{Maximum metabolic rate, determined by oxygen supply, as a function of temperature, for four different optimal temperatures (panels---see panel label for optimal temperature in degrees celsius), and increasing values of $\eta$.}\label{fig:O2_fig}
\end{figure}

### 2017-06-30 figures/m.Rnw
arg

--- 2017-06-01 m.Rnw
@@
 
-<<mortality,fig.cap='Mortality as a function of activity $\\tau$ for three levels of the mortality scaler $\\eta$',fig.width=5, fig.height=4,>>=
+<<mortality,fig.align='center',fig.cap='Mortality as a function of activity $\\tau$ for three levels of the mortality scaler $\\eta$',fig.width=4, fig.height=3,out.height='0.4\\textwidth'>>=
   require(ggplot2)

### 2017-08-18 poster/poster.Rmd
commit before changing poster to norm-based

---
title: "Sizing the effects of temperature on fish"

author: ['<span class=\"presenter\">Philipp Neubauer<sup>1</sup></span>, Ken H. Andersen<sup>2</sup><ol class=\"affiliations\"><li> Dragonfly Data Science, Wellington, New Zealand</li><li>Centre for Ocean Life, National Institute of Aquatic Resources, Technical University of Denmark, Denmark</li></ol>']

output: drposter::revealjs_poster

bibliography: ../Sizing-fx-of-temperature.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = F,message = F,
                      cache=T,autodep = T,dev = "svg")  # Hide code by default. Can override chunk-by-chunk
```

# {.col-1}

## Introduction

Size-at-maturation and maximum size are key traits, defining ecoloical niches and driving ecological interactions [@andersen_asymptotic_2006]. Temperature has been identified in various contexts as a key driver of organism size (Bergman's rule, Temperature size rule...) [@atkinson_temperature_1994]. Climate change may therefore have strong effects on organism size and follow on effects at population and ecosystem levels, but no clear framework to understand effects of temperature.

**Aim: Develop a eco-physiological model to predict effects of changing temperatures on organism size over ecological and evolutionary time-scales**

# {.col-2}

## Model

We set up a weight ($w$) based model consisting of mass and oxygen balance equations:

Feeding - type 2 response with parameters for maximum consumption rate $\gamma$ and maximum intake $h$, modulated by feeding activity $\tau$:
$$ f = \frac{{\color{uclagold}\tau} \gamma w^{p}\Theta}{{\color{uclagold}\tau}\gamma w^{p}\Theta  + {\color{bondiblue} T^c_{h} h w^{q}}} $$

Mass balance: Intake is assimilated with loss from heat increment $\phi$ and absorbtion $\beta$. Metabolic loss due to standard and feeding activity ($\tau$) metabolic costs
$$ P =(1-\beta-\phi)f {\color{bondiblue} T^c_{h} h w^{q}}-{\color{sinopia}k(1+{\color{uclagold}\tau\delta}) T^c_{M} w^n} $$

Oxygen balance: Oxygen sets the limit for metabolism via the cost of metabolising one gram of feed $\omega$ relative to the potential oxygen supply $f_{O_2}w^n$:
$$P_{0_2} = f_{O_2}w^n - \omega(\beta f_C {\color{bondiblue} T^c_{h} h w^{q}} +{\color{sinopia}k(1+{\color{uclagold}\tau\delta}) T^c_{M} w^n})$$

Mortality: Weight based with base mortality $m_0$ and activity related mortality $m_\tau$.

$$M = (m_0 + {\color{uclagold}\tau}m_{\color{uclagold}\tau})w^{1-p}$$
${\bf \tau}$ **is optimised at any temperature via Gilliam's rule (argmax${\bf _\tau\{P/M\}}$)**

## Ecological dynamics
With increasing temperature, most organisms will increase activity $\tau$ to offset increased metabolic costs.

Feeding level, available energy and mortality are impacted by response to temperature

Oxygen sets metabolic limits at extreme temperatures

```{r}

require(dplyr)
source('../model.R')

# Sluggish small
ss <- list(beta=0.15,
           delta=4,
           Ea=0.52, 
           gamma=40, 
           h=20, 
           k=1.2,
           lO=1, 
           m=100, 
           M=0.1 ,
           n=0.88, 
           O2crit=2, 
           omega=0.25, 
           p=0.8,
           P50=4.2, 
           phi=0.25, 
           q=0.8 ,
           shape=3,
           temp=seq(5,26,l=100),
           Topt=20, 
           temp_ref=15,
           slope=-0.2,
           tmax=30,
           tr=0.3,
           v=6,
           lm=5000,
           nu=-0.2
)

# sluggish large
sl <- ss
sl$nu <- -0.3

# fast large
fl <- sl
fl$lO <- 2
fl$k <- 1.5
fl$h <- 40
fl$v <- 1
fl$M <- 0.3

# fast large
fs <- fl
fs$nu <- -0.2

scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('Sluggish small','Sluggish large','Active small','Active large'),each=100))),
                       bind_rows(plot_data_temp(ss),
                                 plot_data_temp(sl),
                                 plot_data_temp(fs),
                                 plot_data_temp(fl)))

ggp <-lst()

```

```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=2}

require(ggplot2)
require(cowplot)

sc_act <- tidyr::gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
  mutate(Activity = relevel(as.factor(Activity), "Realised")) %>%
  filter(!grepl('large',Scenario))

ggplot(sc_act) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity),alpha=0.7) +
  theme_cowplot()+
  facet_wrap(~Scenario)+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

```
\newline
```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=2}

sc <- function(x) x/max(x,na.rm=T)

sc_feed <- scenarios %>%
  filter(!grepl('large',Scenario)) %>% 
  group_by(Scenario) %>%
  mutate(Consumption=sc(Consumption),
         Efficiency=sc(Efficiency),
         Feeding=`Feeding level`,
         `Available Energy` = sc(`C for growth`),
         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`)) %>% 
  tidyr::gather(Rate,value,Feeding,Energy,M,Efficiency) %>%
  mutate(Rate = relevel(as.factor(Rate),'Feeding'))

ggplot(sc_feed) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate),alpha=0.7) +
  theme_cowplot()+
  facet_wrap(~Scenario)+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_discrete('')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative rate')

```

Temperature affects size via evolved reaction norm on ecological time-scales:

```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=2}

gout_fs <- plot_data_growth_tO2(fs,n_int = 50)

#browser()
norm <- gout_fs$alloc %>% 
  group_by(Temperature) %>%
  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
            m=ls[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1])

cp <- ggplot() +
  geom_line(aes(x=t, y=ls,col=as.factor(Temperature)),data=gout_fs$alloc) +
  geom_point(aes(x=ts, y=m),data=norm) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  #theme_cowplot()+
  viridis::scale_colour_viridis(discrete = T,guide='none')+
  theme(
    panel.background = element_blank(),
    plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Length (cm)',
       x='Age  (years)')

scs <- list(ss,sl,fs,fl)
scn <- unique(scenarios$Scenario)
gouts <- lapply(scs,plot_data_growth_tO2,n_int = 50)

alloc <- bind_rows(lapply(1:length(gouts), function(x) {
  y <- gouts[[x]][['alloc']]
  y$Scenario <- scn[x]
  y}))

norm <- alloc %>% 
  group_by(Scenario,Temperature) %>%
  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
            ls=ls[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
            alloc=allocs[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1]) %>%
  mutate(ls = sc(ls))

np <-  ggplot() +
  geom_line(aes(x=Temperature, y=ls, linetype=Scenario),data=norm) +
  theme(
    panel.background = element_blank(),
    plot.background = element_blank())+
  #scale_color_discrete(guide='none')+
  #scale_shape_discrete(guide='none')+
  coord_cartesian()+
  labs(y = 'Relative length',
       x='Temperature')

cowplot::plot_grid(cp,np,rel_widths = c(0.4,0.6))

```

# {.col-2}

## Traits

Two strategists: minimising mortality $M$ or maximising energy gain $P$

$P$ strategy: 
* Maximise intake at the cost of higher standard metabolism to feeding maintain activity and larger gut.
* Live with higher $M$

$M$ strategy: 
* Minimise $M$ by minimising dangerous feeding activty, minimise resting metabolism

## Evolutionary impact

Size-at maturation reacts strongly to temperature changes in the model, however, changes are small on ecological time-scales ($\lt$1mm per year)

```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=3}

winfs <- bind_rows(lapply(1:length(gouts), function(x) {
  y <- gouts[[x]][['winfs']]
  y$Scenario <- scn[x]
  y}))

wtfs <- winfs %>% group_by(Scenario) %>%
  mutate(length=sc(lw(Temp)))

cpG <- ggplot(wtfs) +
  geom_line(aes(x=Temperature, y=length, linetype=Scenario),alpha=0.7) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  #theme_cowplot()+
  scale_linetype_discrete(guide='none')+
  theme(
    panel.background = element_blank(),
    plot.background = element_blank())+
  #scale_color_discrete(guide='none')+
  #scale_shape_discrete(guide='none')+
  #scale_y_log10()+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative adult length')

npG <- ggplot(wtfs) +
  geom_line(aes(x=Temperature, y=L/length, linetype=Scenario),alpha=0.7) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  #theme_cowplot()+
  theme(
    panel.background = element_blank(),
    plot.background = element_blank())+
  #scale_color_discrete(guide='none')+
  #scale_shape_discrete(guide='none')+
  coord_cartesian(ylim=quantile(wtfs$L/wtfs$length,c(0.05,0.95),na.rm=T)) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression(Percent~change~y^-1))

cowplot::plot_grid(cpG,npG,rel_widths = c(0.4,0.6))

```

# {.col-1}

## Acknowledgements

P. Neubauer acknowledges funding from the Royal Society of New Zealand Marsden Fast Start grant 14-DFG-001.

All code for this poster is accessble from github.

# {.col-1}
## References

### 2017-08-18 model.R

@@ -1,3 +1,13 @@
+inv_logit3 <- function(m,mstar,a,b,c) {
+  z = (m-mstar)*cos(atan(b))-a*sin(atan(b))
+  #zstar = mstar*cos(atan(b))-a*sin(atan(b))
+  #1/(1+ (z/mstar)^-c)
+  1/(1+exp(-(c*z)))
+}
+
+lw <- function(w) (w/0.01)^(1/3)
+
+
 O2_plotfun <- function(etas,Tops){
   grid <- expand.grid(eta = etas,
                       Topt = Tops)
@@ -31,47 +41,14 @@ O2_plotfun <- function(etas,Tops){
 
 plot_data_temp <- function(v){
   
-  out = eval_tau_eq(gamma=v$gamma,
-                    delta=v$delta,
-                    phi=v$phi,
-                    h=v$h,
-                    beta=v$beta,
-                    k=v$k,
-                    p=v$p,
-                    q=v$q,
-                    n=v$n,
-                    m=10^seq(-1,5,l=100),
-                    M=v$M,
-                    v=v$v)
+  lm = 10^seq(-2,5,l=v$lm)
   
-  pd <- data_frame(m=10^seq(-1,5,l=100))
-  pd$tau_uc <- out
-  
-  #browser()
-  O2 = O2_supply(O2=seq(1,10,l=length(v$temp)),Topt=v$Topt,O2crit=v$O2crit,Tmax=v$temp[length(v$temp)],T=v$Topt,delta=v$lO,omega=v$shape,P50=v$P50,n=v$n)
-  tau_o2 = sapply(eval_tau_max_o2(f=O2,omega = v$omega,
-                                  gamma=v$gamma,
-                                  delta=v$delta,
-                                  phi=v$phi,
-                                  h=v$h,
-                                  beta=v$beta,
-                                  k=v$k,
-                                  p=v$p,
-                                  q=v$q,
-                                  n=v$n,
-                                  m=v$m
-  ),min,out)
-  
-  tau_o2[tau_o2<0] <- 0
-  tau_o2[tau_o2>1] <- 1
-  
-  o2frame <- data_frame(O2=seq(1,10,l=100),tau_o2 = tau_o2)
-  
-  O2_tcor <- 8.310212
+  O2_tcor <- O2_fact(v$temp,5)
[…]

### 2017-09-11 draft.Rnw
arg
final psoter etc

@@
 We develop a general trait-based model of carbon and oxygen budgets to determine the relative influence of thermal sensitivity, oxygen limitation, and environmental conditions on ectotherm body size.
-Our model provides a physiological basis for changes in species size and observed ecological consequences of temperature, and ties together various strands of thought about the ecological consequences of increased temperatures.
+Our model provides a general physiological basis for changes in species size and observed ecological consequences of temperature, and ties together various strands of thought about the ecological consequences of increased temperatures.
 
@@
 However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems.
-Through this cascade of scales, incorrect or approxiamte model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\cite{brander_overconfidence_2013, lefevre_models_2017}).
+Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\cite{brander_overconfidence_2013, lefevre_models_2017}).
 In marine fish, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017}).
@@
 However, while increasing metabolic costs are real, energy acquisition is an abstract, phenomenological description that lumps ecological aspects of foraging activity and prey availability.
-At a more mechanistic level of energy acquisition, consistent responses of foraging and energy aquisition with temperature have remained elusive (\cite{englund_temperature_2011,rall_universal_2012}), with variable responses across habitats and taxa.
-This is perhaps not surprising given variable foraging ecologies, but it remains unclear how temperature dependant feeding ecology impacts growth and adult size.
+At a more mechanistic level of energy acquisition, consistent responses of foraging and energy acquisition with temperature have remained elusive (\cite{englund_temperature_2011,rall_universal_2012}), with variable responses across habitats and taxa.
+This is perhaps not surprising given variable foraging ecologies, but it remains unclear how temperature dependent feeding ecology impacts growth and adult size.
 
@@
 How exactly temperature influences physiological rates and limits, however, has been a matter of debate, not least because of the variable responses observed among different species.
-In most species, the standard metabolism (i.e., the metabolic cost of maintenance and routine activity such as ventilation) increases near exponentially with temperature.
-A prevalent view is that the maximum metabolic rate (i.e., the metabolic rate at maximum sustained exercise) has a  dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
-This leads to the view of a modal curve for metabolic scope (the available oxygen/energy for activity), and suggests that towards the upper end of this curve, organisms will run out of oxygen.
+In most species, the standard metabolism (SM; the metabolic cost of maintenance and routine activity such as ventilation) increases near exponentially with temperature.
+A prevalent view is that the maximum metabolic rate (MMR; the metabolic rate at maximum sustained exercise) has a  dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
+This leads to the view of a modal curve for metabolic scope (MMR-SM; the available oxygen/energy for additional activity), and suggests that towards the upper end of this curve, organisms will run out of oxygen.
 
-This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth.
-In some species, however, maximum metabolic rate may be steadily increasing (\cite{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor.
+This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM), and hence body size.
+In some species, however, maximum metabolic rate may be steadily increasing (\cite{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor at high temperatures.
 Consequently, the difference in observed physiological responses may at least partially determine temperature effects on body size for individual species.
-In addition to physiological differences, the assumed coefficients for temperature sensitivity of metabolism and size scaling exponents are different between species, and can disproportionately affect inferences about future organism size \cite{lefevre_models_2017, kozlowski_can_2004}.
+In addition to physiological differences, the assumed coefficients for temperature sensitivity of metabolism and size scaling exponents are different between species, and can disproportionately affect future organism size \cite{lefevre_models_2017, kozlowski_can_2004}.
 
@@
 
-\section{Setting up the model}
+\section{Methods}
 
@@
 Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets.
-In setting up the model we make a number of key assumptions, which are similar to those made in Holt \& Jorgensen.
 At a high level, we assume that animals will adapt activity levels to optimise available energy for growth and reproduction.
@@
 
-The oxygen budget $P_{0_2}$, determines physiological limits to aerobic acitivity.
+The oxygen budget $P_{0_2}$, determines physiological limits to aerobic activity.
 Demand ($D_{O_2}$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy and growth - $\beta f_C h c_T w^q$) and ``active metabolism", the sum of standard (or resting) metabolism and the metabolic costs of foraging ($[1+\tau \delta] c_T k w^n$), with $\omega$ determining amount of oxygen required per unit of metabolised carbon.
-Metabolic scope is the difference between $S_{O_2}/w^n=f_{O_2}$, the amount of oxygen supplied per unit weight, and oxygen demand due to standard metabolism ($c_T k w^n$).
+Metabolic scope is the difference between $S_{O_2}/w^n=f_{O_2}$, the amount of oxygen supplied per unit weight, and oxygen demand due to standard metabolism ($\omega c_T k w^n$).
 
@@
 
-We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness \footnote{I \emph{think} this amounts to maximizing R0 if no more growth occurs: life expectancy is 1/M and reporoductive output is proportional to energy}.
+We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness \footnote{I \emph{think} this amounts to maximizing R0 if no more growth occurs: life expectancy is 1/M and reproductive output is proportional to energy}.
 We further assume here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M_{\tau,w} = \tau^\eta \rho w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=1$, that is, at constant maximum activity and $M$ is the effective mortality at realised levels of activity at weight $w$.
@@
 
-Life history theory suggests that the maximum\/asymptotic weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity).
+Life history theory suggests that the adult weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity).
 Note that $W_{\infty}$ depends on temperature only through $\tau$ and changes in $P_C$ as temperature changes metabolic and enzymatic rates.
 We thus impose no direct constraint on $W_{\infty}$.
+
+\subsection{Trait based scenarios}
+
+We now explore the sensitivity of size on a number of ecological and physiological traits.
+We model variable oxygen limitation through a set of three scenarios that reflect responses found empirically (\cite{lefevre_are_2016}; Figure \ref{fig:O2_fig}), ranging from an increasing MMR with temperature over most of the range (scenario 1), via a slightly dome-shaped response (scenario 2) to a strongly dome-shaped MMR (scenario 3).
+
+Other physiological traits explored here are the FAS $\delta$, which determines the cost of active metabolism relative to standard metabolism.
+FAS ca vary strongly between species but is constant with weight (\cite{lefevre_models_2017, killen_ecological_2016}), and range from approximately 2 to 12, with most values found around 3-6.
+Here we explore values of 3-5.
+We explore the sensitivity to metabolic exponents by assuming that the exponent ranges between 0.85 and 0.9, with a base-case of 0.88 (\cite{lefevre_models_2017}).
 
@@
 Realised activity is the smaller of the limiting and optimal levels at each temperature, with activity limited by O2 supply as pictured by dashed lines in b).
-Optimal acitivity steadily increases to compensate for rising metabolic costs (dotted line in b) with temperature until limited by oxygen (overlapping supply (dashed) and demand (solid) curves in b).
-(c) Rising activity lelves keeps feeding levels constant (solid line in c).
+Optimal activity steadily increases to compensate for rising metabolic costs (dotted line in b) with temperature until limited by oxygen (overlapping supply (dashed) and demand (solid) curves in b).
+(c) Rising activity levels keeps feeding levels constant (solid line in c).
 Mortality levels (dashed) increase as activity increases with temperature, while available energy (carbon, dotted line) for growth and reproduction peaks and decreases.
 Note that energy is only limited by oxygen-limited activity levels at low temperatures in scenario 3.
-The rate of change of available energy relative to mortality drives the adult size, which delines near linearly in log-space without oxygen limitations, and lower and upper limits imposed as oxygen limits activity and energy aquisition.}
+The rate of change of available energy relative to mortality drives the adult size, which declines near linearly in log-space without oxygen limitations, and lower and upper limits imposed as oxygen limits activity and energy acquisition.}
 \label{fig:act_fig}
@@
 
-Higher temperature have cascading effects through their influence on both metabolic and ecological rates (Figure \ref{fig:act_fig}).
-To maintain optimal energy aquisition for growth and reproduction relative to mortality, activity levels generally increase, until they reach limitations imposed by oxygen supply (Figure \ref{fig:act_fig}a).
+Increasing temperatures have cascading effects through their influence on both metabolic and ecological rates (Figure \ref{fig:act_fig}).
+To maintain optimal energy acquisition for growth and reproduction relative to mortality, activity levels generally increase, until they reach limitations imposed by oxygen supply (Figure \ref{fig:act_fig}a).
 This limit occurs when active metabolic costs equal oxygen supply (Figure \ref{fig:act_fig}b), and are therefore more pronounced for species with strongly dome-shaped maximum-metabolic rates (scenario 3 in Figure \ref{fig:act_fig}).

### 2017-09-11 model_meeting.tex
final psoter etc

\documentclass[xcolor={table}]{beamer}
\usepackage{multirow} 
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\usetheme{Dragonfly}

\title{Sizing the effects of temparture on fishes}
\subtitle{Current state and future direction}

\projectcode{}
\author{Philipp Neubauer}
\date{\today}

\newcommand{\p}{\bigskip\par}

\begin{document}

%% --------------------------------

\titleslide

\begin{frame}{Aims}

  {\bf Draw a line in the sand - current state \& future
    direction under IEMRS}
  \p

  Current project (PAU2016-03) supports moving data logger project towards
    complete coverage using VMS or electronic reporting
  \p

  IEMRS will require electronic logging on all boats - will
    force complete coverage of electronic reporting on PCELR scale

\end{frame}

\end{document}

### 2017-09-11 poster/poster.Rmd
final psoter etc

@@
 ```{r setup, include=FALSE}
+
+require(ggplot2)
+require(cowplot)
+
 knitr::opts_chunk$set(echo = FALSE,warning = F,message = F,
-                      cache=T,autodep = T,dev = "svg")  # Hide code by default. Can override chunk-by-chunk
+                      cache=T,autodep = T,dev = "svg",dev.args= list(bg  = 'transparent'))  # Hide code by default. Can override chunk-by-chunk
 ```
-
-# {.col-1}
-
-## Introduction
-
-Size-at-maturation and maximum size are key traits, defining ecoloical niches and driving ecological interactions [@andersen_asymptotic_2006].
-Temperature has been identified in various contexts as a key driver of organism size (Bergman's rule, Temperature size rule...) [@atkinson_temperature_1994].
-Climate change may therefore have strong effects on organism size and follow on effects at population and ecosystem levels, but no clear framework to understand effects of temperature.
-
-**Aim: Develop a eco-physiological model to predict effects of changing temperatures on organism size over ecological and evolutionary time-scales**
-
-# {.col-2}
-
-## Model
-
-We set up a weight ($w$) based model consisting of mass and oxygen balance equations:
-
-Feeding - type 2 response with parameters for maximum consumption rate $\gamma$ and maximum intake $h$, modulated by feeding activity $\tau$:
-$$ f = \frac{{\color{uclagold}\tau} \gamma w^{p}\Theta}{{\color{uclagold}\tau}\gamma w^{p}\Theta  + {\color{bondiblue} T^c_{h} h w^{q}}} $$
-
-Mass balance: Intake is assimilated with loss from heat increment $\phi$ and absorbtion $\beta$. Metabolic loss due to standard and feeding activity ($\tau$) metabolic costs
-$$ P =(1-\beta-\phi)f {\color{bondiblue} T^c_{h} h w^{q}}-{\color{sinopia}k(1+{\color{uclagold}\tau\delta}) T^c_{M} w^n} $$
-
-Oxygen balance: Oxygen sets the limit for metabolism via the cost of metabolising one gram of feed $\omega$ relative to the potential oxygen supply $f_{O_2}w^n$:
-$$P_{0_2} = f_{O_2}w^n - \omega(\beta f_C {\color{bondiblue} T^c_{h} h w^{q}} +{\color{sinopia}k(1+{\color{uclagold}\tau\delta}) T^c_{M} w^n})$$
-
-Mortality: Weight based with base mortality $m_0$ and activity related mortality $m_\tau$.
-
-$$M = (m_0 + {\color{uclagold}\tau}m_{\color{uclagold}\tau})w^{1-p}$$
-${\bf \tau}$ **is optimised at any temperature via Gilliam's rule (argmax${\bf _\tau\{P/M\}}$)**
-
-## Ecological dynamics
-With increasing temperature, most organisms will increase activity $\tau$ to offset increased metabolic costs.
-
-Feeding level, available energy and mortality are impacted by response to temperature
-
-Oxygen sets metabolic limits at extreme temperatures
 
@@
 
+int_m <- 1000
+int_temp <- 40
+
 # Sluggish small
-ss <- list(beta=0.15,
+ss <- list(c=0.3,
+           beta=0.15,
            delta=4,
@@
            shape=3,
-           temp=seq(5,26,l=100),
+           temp=seq(5,26,l=int_temp),
            Topt=20, 
@@
            tmax=30,
-           tr=0.3,
+           tr=0.9,
            v=6,
-           lm=5000,
+           lm=int_m,
            nu=-0.2
@@
 
-# sluggish large
-sl <- ss
-sl$nu <- -0.3
-
-# fast large
-fl <- sl
-fl$lO <- 2
-fl$k <- 1.5
-fl$h <- 40
-fl$v <- 1
-fl$M <- 0.3
-
-# fast large
-fs <- fl
+# fast small
+fs <- ss
+fs$lO <- 2
+fs$k <- 1.5
+fs$h <- 40
+fs$v <- 6
+fs$M <- 0.3
+fs$tmax <- 20
 fs$nu <- -0.2
 
-scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('Sluggish small','Sluggish large','Active small','Active large'),each=100))),
+scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy'),each=int_temp))),
                        bind_rows(plot_data_temp(ss),
-                                 plot_data_temp(sl),
-                                 plot_data_temp(fs),
-                                 plot_data_temp(fl)))
+                                 plot_data_temp(fs)))
 
@@
 
-```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=2}
+# {.col-1}
 
-require(ggplot2)
-require(cowplot)
+## Introduction
+
+&nbsp;
+
+Size-at-maturation and maximum size are key traits, defining ecological niches and driving ecological interactions [@andersen_asymptotic_2006].
+Temperature has been identified in various contexts as a key driver of organism size (Bergman's rule, Temperature-size-rule...) [@atkinson_temperature_1994].
+Climate change may therefore have strong effects on organism size and follow on effects at population and ecosystem levels, but no clear framework to understand effects of temperature [@lefevre_models_2017].
+
+&nbsp;
+
+**Aim: Develop a eco-physiological model [@holt_climate_2014] to predict effects of changing temperatures on organism size over ecological and evolutionary time-scales**
+
+# {.col-2}
+
+## Model
+
+&nbsp;
+
+We set up a weight ($w$) based model consisting of mass and oxygen balance equations:
+
+Feeding - type 2 functional response with parameters for maximum consumption rate $\gamma$, modulated by feeding activity $\tau$, and maximum intake $h$, which responds to temperature via $T^c_{M}$:
+$$ f = \frac{{\color{uclagold}\tau} \gamma w^{p}\Theta}{{\color{uclagold}\tau}\gamma w^{p}\Theta  + {\color{bondiblue} T^c_{h} h w^{q}}} $$
+
+Mass balance: Intake is assimilated with loss from heat increment $\phi$ and absorption $\beta$.
+Metabolic loss due to standard and feeding activity ($\tau$) metabolic costs, modulated by temperature via $T^c_{M}$
+$$ P =(1-\beta-\phi)f {\color{bondiblue} T^c_{h} h w^{q}}-{\color{sinopia}k(1+{\color{uclagold}\tau\delta}) T^c_{M} w^n} $$
+
+Oxygen balance: Oxygen sets the limit for metabolism via the cost of metabolising one gram of feed $\omega$ relative to the potential oxygen supply $f_{O_2}w^n$:
+$$P_{0_2} = f_{O_2}w^n - \omega(\beta f_C {\color{bondiblue} T^c_{h} h w^{q}} +{\color{sinopia}k(1+{\color{uclagold}\tau\delta}) T^c_{M} w^n})$$
+
+Mortality: Weight based with base mortality $m_0$ and activity related mortality $m_\tau$.
+
+$$M = (m_0 + {\color{uclagold}\tau}m_{\color{uclagold}\tau})w^{1-p}$$
+${\bf \tau}$ **is optimised at any temperature via Gilliam's rule (argmax${\bf _\tau\{P/M\}}$)**
+
+&nbsp;
+
+Strategy trade-off: minimising mortality $M$ or maximising energy gain $P$
+
+&nbsp;
+
+$P$ strategy: Maximise intake at the cost of higher standard metabolism to maintain feeding activity and larger gut. Live with higher $M$.
+
+&nbsp;
+
+$M$ strategy: Minimise $M$ by minimising dangerous feeding activity, minimise resting metabolism.
+
+## Temperature impact on size
+
+&nbsp;
+
+```{r fig.width=7,fig.height=2.5,fig.cap='Figure 3: **On ecological time-scales**, temperature affects size via evolved maturation-reaction norms [@marty_impact_2011].
+Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
+Increasing temparture (left panel, purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (right panel).'}
+
+gout_fs <- plot_data_growth_tO2(fs)
+
+#browser()
+norm <- gout_fs$t_growth %>% 
+  group_by(Temperature) %>%
+  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1])
+
+cp <- ggplot() +
+  geom_line(aes(x=t, y=t_length,col=as.factor(Temperature)),data=gout_fs$t_growth) +
+  geom_point(aes(x=ts, y=m),data=norm) +
+  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
+  theme_cowplot()+
+  viridis::scale_colour_viridis(discrete = T,guide='none')+
+  theme(plot.margin = margin(2, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  coord_cartesian()+
+  labs(y = 'Length (cm)',
+       x='Age  (years)')
+
+scs <- list(ss,fs)
+scn <- unique(scenarios$Scenario)
+gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 4)
+
+alloc <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- gouts[[x]][['t_growth']]
+  y$Scenario <- scn[x]
+  y}))
+
+norm <- alloc %>% 
+  group_by(Scenario,Temperature) %>%
+  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
+            ls=t_length[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
+            alloc=allocs[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1]) %>%
+  mutate(ls = sc(ls))
+
+np <-  ggplot() +
+  geom_line(aes(x=Temperature, y=ls, linetype=Scenario),data=norm) +
+  theme_cowplot()+
+  theme(plot.margin = margin(2, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  #scale_color_discrete(guide='none')+
+  #scale_shape_discrete(guide='none')+
+  coord_cartesian()+
+  labs(y = 'Relative length',
+       x='Temperature')
+
+cowplot::plot_grid(cp,np,rel_widths = c(0.4,0.6))
+
+```
+
+&nbsp;
+
+```{r fig.width=7,fig.height=2.5,fig.cap='Figure 4: **On evolutionary time-scales**, selection moves the reaction norm.
+Size-at-maturation reacts strongly to temperature changes in the model (left panel).
+Selection (S) induced changes in size are slow for M strategists, fast for P strategists.'}
+
+winfs <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- gouts[[x]][['winfs']]
+  y$Scenario <- scn[x]
+  y}))
+
+wtfs <- winfs %>% group_by(Scenario) %>%
+  mutate(length=sc(lw(l)))
+
+cpG <- ggplot(wtfs) +
+  geom_line(aes(x=Temperature, y=length, linetype=Scenario),alpha=0.7) +
+  theme_cowplot()+
+  scale_linetype_discrete(guide='none')+
+  theme(plot.margin = margin(3, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y='Relative adult length')
+
+npG <- ggplot(wtfs) +
+  geom_line(aes(x=Temperature, y=L/length, linetype=Scenario),alpha=0.7) +
+  theme(plot.margin = margin(3, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  coord_cartesian(ylim=quantile(wtfs$L/wtfs$length,c(0.05,0.95),na.rm=T)) + 
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression(S~response~y^-1))
+
+cowplot::plot_grid(cpG,npG,rel_widths = c(0.4,0.6))
+
+```
+
+# {.col-2}
+
+## Ecological dynamics
+
+```{r fig.width=7,fig.height=2,fig.cap='Figure 1: With increasing temperature, most organisms will increase activity $\\tau$ to offset increased metabolic costs.
+Oxygen sets metabolic limits at extreme temperatures.'}
 
@@
   facet_wrap(~Scenario)+
-  theme(strip.background = element_blank(),
+  theme(plot.margin = margin(0, 6, 0, 6),
+        strip.background = element_blank(),
         panel.background = element_blank(),
@@
 ```
-\newline
-```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=2}
 
-sc <- function(x) x/max(x,na.rm=T)
+```{r fig.width=7,fig.height=2,fig.cap='Figure 2: Feeding level, available energy and mortality are impacted by increased activity and the metabolic response to temperature.'}
 
@@
 
-Temperature affects size via evolved reaction norm on ecological time-scales:
+## Take home messages
 
-```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=2}
+<span style="font-size: 300%;">
 
-gout_fs <- plot_data_growth_tO2(fs,n_int = 50)
+&nbsp;
 
-#browser()
-norm <- gout_fs$alloc %>% 
-  group_by(Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=ls[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1])
+&nbsp;
 
-cp <- ggplot() +
-  geom_line(aes(x=t, y=ls,col=as.factor(Temperature)),data=gout_fs$alloc) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  #theme_cowplot()+
-  viridis::scale_colour_viridis(discrete = T,guide='none')+
-  theme(
-    panel.background = element_blank(),
-    plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
+* **On ecological time-scales changes in adult size due to temperature alone will likely be small, and masked by changes in the environment.**
 
-scs <- list(ss,sl,fs,fl)
-scn <- unique(scenarios$Scenario)
-gouts <- lapply(scs,plot_data_growth_tO2,n_int = 50)
+&nbsp;
 
-alloc <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['alloc']]
-  y$Scenario <- scn[x]
-  y}))
+&nbsp;
 
-norm <- alloc %>% 
-  group_by(Scenario,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
-            ls=ls[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
-            alloc=allocs[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1]) %>%
-  mutate(ls = sc(ls))
+* **On evolutionary time-scales, size responds strongly. The relative selection response is strongest at temperature extremes.**
 
-np <-  ggplot() +
-  geom_line(aes(x=Temperature, y=ls, linetype=Scenario),data=norm) +
-  theme(
-    panel.background = element_blank(),
-    plot.background = element_blank())+
-  #scale_color_discrete(guide='none')+
-  #scale_shape_discrete(guide='none')+
-  coord_cartesian()+
-  labs(y = 'Relative length',
-       x='Temperature')
+&nbsp;
 
-cowplot::plot_grid(cp,np,rel_widths = c(0.4,0.6))
+&nbsp;
 
-```
+* **Size of $P$ strategy species with high activity reacts more strongly compared to sluggish $M$ strategy species.**
 
-# {.col-2}
-
-## Traits
-
-Two strategists: minimising mortality $M$ or maximising energy gain $P$
-
-$P$ strategy: 
-* Maximise intake at the cost of higher standard metabolism to feeding maintain activity and larger gut.
-* Live with higher $M$
-
-$M$ strategy: 
-* Minimise $M$ by minimising dangerous feeding activty, minimise resting metabolism
-
-## Evolutionary impact
-
-Size-at maturation reacts strongly to temperature changes in the model, however, changes are small on ecological time-scales ($\lt$1mm per year)
-
-```{r dev.args= list(bg = 'transparent'),fig.width=7,fig.height=3}
-
-winfs <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['winfs']]
-  y$Scenario <- scn[x]
-  y}))
-
-wtfs <- winfs %>% group_by(Scenario) %>%
-  mutate(length=sc(lw(Temp)))
-
-cpG <- ggplot(wtfs) +
-  geom_line(aes(x=Temperature, y=length, linetype=Scenario),alpha=0.7) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  #theme_cowplot()+
-  scale_linetype_discrete(guide='none')+
-  theme(
-    panel.background = element_blank(),
-    plot.background = element_blank())+
-  #scale_color_discrete(guide='none')+
-  #scale_shape_discrete(guide='none')+
-  #scale_y_log10()+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative adult length')
-
-npG <- ggplot(wtfs) +
-  geom_line(aes(x=Temperature, y=L/length, linetype=Scenario),alpha=0.7) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  #theme_cowplot()+
-  theme(
-    panel.background = element_blank(),
-    plot.background = element_blank())+
-  #scale_color_discrete(guide='none')+
-  #scale_shape_discrete(guide='none')+
-  coord_cartesian(ylim=quantile(wtfs$L/wtfs$length,c(0.05,0.95),na.rm=T)) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression(Percent~change~y^-1))
-
-cowplot::plot_grid(cpG,npG,rel_widths = c(0.4,0.6))
-
-```
+</span>
 
@@
 
-## Acknowledgements
+## Acknowledgements & References
 
-P. Neubauer acknowledges funding from the Royal Society of New Zealand Marsden Fast Start grant 14-DFG-001.
+P.
+Neubauer acknowledges funding from the Royal Society of New Zealand Marsden Fast Start grant 14-DFG-001.
+All code for the model and this poster is accessible from github at repository Adaptive-dynamics/Sizing-fx-of-temperature.
 
-All code for this poster is accessble from github.
-
-# {.col-1}
-## References
+&nbsp;

### 2017-09-11 model.R

@@ -4,7 +4,7 @@ inv_logit3 <- function(m,mstar,a,b,c) {
   #1/(1+ (z/mstar)^-c)
   1/(1+exp(-(c*z)))
 }
-
+sc <- function(x) x/max(x,na.rm=T)
 lw <- function(w) (w/0.01)^(1/3)
 
 
@@ -160,60 +160,46 @@ plot_data_growth <- function(v){
   )
 }
 
-plot_data_growth_tO2 <- function(v,lm = 10^seq(-2,6,l=1000),n_int=100){
+plot_data_growth_tO2 <- function(v){
+  
+  n_int <- length(v$temp)
+  lm = 10^seq(-2,6,l=v$lm)
+  O2_range <- seq(1,10,l=n_int)
+  
+  #### Step 1 get mstar=mo+slope*age for all Temp
+  #browser()
+  
+  mout <- model_out_growth(temp=v$temp,
+                           temp_ref=v$temp_ref,
+                           l=v$lm,
+                           Ea=v$Ea,
+                           gamma=v$gamma,
+                           delta=v$delta,
+                           phi=v$phi,
+                           h=v$h,
+                           beta=v$beta,
+                           k=v$k,
+                           p=v$p,
+                           q=v$q,
+                           n=v$n,
+                           mstar = mout_ref$winf,
+                           tmax = v$tmax,
+                           slope=v$slope,
+                           tr=v$tr,
+                           v=v,
+                           lm=lm)
+  
+  winfs <- mout$winfs
+  
+  ### Step 2 calc mat for selected response 
   
   #browser()
-  O2_range <- seq(1,10,l=n_int)
-  winfs <- data.frame(matrix(NA,n_int,3))
-  winfs[,1] <- O2_range
-  winfs[,2] <- seq(min(v$temp),max(v$temp),l=n_int)
   
-  taus_ref <- get_taus(v,1,10,v$temp_ref,m=lm)
-  
-  mout_ref <- model_out_par(tau_max = taus_ref$tau_max,
-                            M=v$M,
-                            v=v$v,
-                            nu=v$nu,
-                            temp=v$temp_ref,
-                            temp_ref=v$temp_ref,
-                            Ea=v$Ea,
[…]

### 2017-09-11 script.R

@@ -15,7 +15,7 @@ sc1 <- list(beta=0.15,
             k=1.2,
             lO=1, 
             m=100, 
-            M=2 ,
+            M=0.1 ,
             n=0.88, 
             O2crit=2, 
             omega=0.03, 
@@ -27,7 +27,7 @@ sc1 <- list(beta=0.15,
             temp=seq(8,26,l=100),
             Topt=20, 
             Tref=15 ,
-            v=1)
+            v=0.5)
 
 sc2 <- list(beta=0.15,
             delta=4,
@@ -37,7 +37,7 @@ sc2 <- list(beta=0.15,
             k=1.2,
             lO=1, 
             m=100, 
-            M=2 ,
+            M=0.1 ,
             n=0.88, 
             O2crit=2, 
             omega=0.03, 
@@ -49,7 +49,7 @@ sc2 <- list(beta=0.15,
             temp=seq(8,26,l=100),
             Topt=20, 
             Tref=15 ,
-            v=1)
+            v=0.5)
 
 sc3 <- list(beta=0.15,
             delta=4,
@@ -59,7 +59,7 @@ sc3 <- list(beta=0.15,
             k=1.2,
             lO=1, 
             m=100,  
-            M=2 ,
+            M=0.1 ,
             n=0.88, 
             O2crit=2, 
             omega=0.03, 
@@ -71,7 +71,7 @@ sc3 <- list(beta=0.15,
             temp=seq(8,26,l=100),
             Topt=20, 
             Tref=15 ,
-            v=1)
+            v=0.5)
 
 scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(1:3,each=100))),
                        bind_rows(plot_data_temp(sc1),
@@ -81,34 +81,34 @@ scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(1:3,each=100))),
 ggp <-lst()
 
 sc_act <- tidyr::gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"))
+  mutate(Activity = relevel(as.factor(Activity), "Realised")) %>%
+  filter(Scenario==3)
 
 ggp[['Activity']] <- ggplot(sc_act) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity, col=Scenario),alpha=0.7) +
[…]

### 2017-09-19 draft.Rnw
fixes

@@
 
-We now explore the sensitivity of size on a number of ecological and physiological traits.
-We model variable oxygen limitation through a set of three scenarios that reflect responses found empirically (\cite{lefevre_are_2016}; Figure \ref{fig:O2_fig}), ranging from an increasing MMR with temperature over most of the range (scenario 1), via a slightly dome-shaped response (scenario 2) to a strongly dome-shaped MMR (scenario 3).
-
-Other physiological traits explored here are the FAS $\delta$, which determines the cost of active metabolism relative to standard metabolism.
-FAS ca vary strongly between species but is constant with weight (\cite{lefevre_models_2017, killen_ecological_2016}), and range from approximately 2 to 12, with most values found around 3-6.
-Here we explore values of 3-5.
-We explore the sensitivity to metabolic exponents by assuming that the exponent ranges between 0.85 and 0.9, with a base-case of 0.88 (\cite{lefevre_models_2017}).
-
 \begin{table}
@@
 
-\begin{figure}[ht!]
-\includegraphics[width=\linewidth]{activity} 
-\caption[Activity, feeding and maximum length as a function of temperature]{Consequences of increasing temperature on activity levels, feeding and maximum weight for an individual weighing 100g.
-(a) Optimal (dashed line), limiting (dotted line) and realised (solid line) activity as a function of temperature.
-Realised activity is the smaller of the limiting and optimal levels at each temperature, with activity limited by O2 supply as pictured by dashed lines in b).
-Optimal activity steadily increases to compensate for rising metabolic costs (dotted line in b) with temperature until limited by oxygen (overlapping supply (dashed) and demand (solid) curves in b).
-(c) Rising activity levels keeps feeding levels constant (solid line in c).
-Mortality levels (dashed) increase as activity increases with temperature, while available energy (carbon, dotted line) for growth and reproduction peaks and decreases.
-Note that energy is only limited by oxygen-limited activity levels at low temperatures in scenario 3.
-The rate of change of available energy relative to mortality drives the adult size, which declines near linearly in log-space without oxygen limitations, and lower and upper limits imposed as oxygen limits activity and energy acquisition.}
-\label{fig:act_fig}
-\end{figure}
+<<Scenarios>>=
 
-Increasing temperatures have cascading effects through their influence on both metabolic and ecological rates (Figure \ref{fig:act_fig}).
-To maintain optimal energy acquisition for growth and reproduction relative to mortality, activity levels generally increase, until they reach limitations imposed by oxygen supply (Figure \ref{fig:act_fig}a).
-This limit occurs when active metabolic costs equal oxygen supply (Figure \ref{fig:act_fig}b), and are therefore more pronounced for species with strongly dome-shaped maximum-metabolic rates (scenario 3 in Figure \ref{fig:act_fig}).
+require(ggplot2)
+require(cowplot)
+require(dplyr)
+source('model.R')
 
-Although increasing energy levels maintain a constant feeding level, increased maximum consumption with temperature leads to a dome-shaped response in available energy (Figure \ref{fig:act_fig}c).
-Since the rate of change of available energy relative to mortality determines adult size,
+int_m <- 500
+int_t <- 500
+int_temp <- 50
 
-\begin{figure}[ht!]
-\includegraphics[width=\linewidth]{winf} 
-\caption[Influence of ecological and physiological variables on $W_\infty$]{Influence of scaling of mortality with activity (a), consumption rate (b), factorial aerobic scope (FAR; c), and exponent of metabolic rate on adult size $W\infty$.}
-\label{fig:winf_fig}
-\end{figure}
+# Sluggish small
+ss <- list(c=0.3,
+           beta=0.15,
+           delta=4,
+           Ea=0.52, 
+           gamma=40, 
+           h=20, 
+           k=1,
+           lO=1, 
+           m=10, 
+           M=0.1 ,
+           n=0.8, 
+           O2crit=2, 
+           omega=0.25, 
+           p=0.75,
+           P50=4.2, 
+           phi=0.25, 
+           q=0.75 ,
+           shape=3,
+           temp=seq(5,26,l=int_temp),
+           Topt=20, 
+           temp_ref=15,
+           slope=-0.5,
+           tmax=10,
+           tr=0.5,
+           v=6,
+           lm=int_m,
+           nu=-0.2,
+           dt=int_t,
+           min_m=-2,
+           max_m= 1.5
+)
+
+# fast small
+fs <- ss
+fs$lO <- 2
+fs$k <- 1.5
+fs$h <- 40
+#fs$v <- 2
+#fs$M <- 0.8
+fs$n <- 0.75
+fs$p <- 0.70
+fs$q <- 0.70
+
+fl <- fs
+fl$p <- 0.75
+fl$q <- 0.75
+#fl$nu <- -0.25
+fl$tr <- 0.05
+fl$tmax <- 40
+fl$max_m <- 5
+
+sl <- ss
+sl$p <- 0.8
+sl$q <- 0.8
+#sl$nu <- -0.25
+sl$tmax <- 40
+sl$max_m <- 5
+sl$tr <- 0.05
+
+scs <- list(ss,fs,sl,fl)
+
+scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
+                                  Size = as.factor(rep(c('Small','Large'),each=int_temp*2))),
+                       bind_rows(lapply(scs, plot_data_temp)))
+
+scn <- rep(unique(scenarios$Scenario),2)
+scz <- rep(unique(scenarios$Size),each=2)
+
+@
+
+<<activity,fig.cap='With increasing temperature, most organisms will increase activity $\\tau$ to offset increased metabolic costs. Oxygen sets metabolic limits at extreme temperatures.'>>=
+
+sc_act <- tidyr::gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
+  mutate(Activity = relevel(as.factor(Activity), "Realised"))
+
+ggplot(sc_act) + 
+  geom_line(aes(x=Temperature, y=value, linetype=Activity),alpha=0.7) +
+  theme_cowplot()+
+  facet_grid(Size~Scenario)+
+  theme(plot.margin = margin(0, 6, 0, 6),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank()) + 
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression('Activity ' (tau)))
+
+@
+
+<<feeding,fig.cap='Figure 2: Feeding level, available energy and mortality are impacted by increased activity and the metabolic response to temperature.'>>=
+
+sc_feed <- scenarios %>%
+  #filter(!grepl('large',Scenario)) %>% 
+  group_by(Scenario,Size) %>%
+  mutate(Consumption=sc(Consumption),
+         Efficiency=sc(Efficiency),
+         Feeding=`Feeding level`,
+         `Available Energy` = sc(`C for growth`),
+         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`)) %>% 
+  tidyr::gather(Rate,value,Feeding,Energy,M,Efficiency) %>%
+  mutate(Rate = relevel(as.factor(Rate),'Feeding'))
+
+ggplot(sc_feed) + 
+  geom_line(aes(x=Temperature, y=value, linetype=Rate),alpha=0.7) +
+  theme_cowplot()+
+  facet_grid(Size~Scenario)+
+  theme(plot.margin = margin(0, 6, 0, 6),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_discrete('')+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y='Relative rate')
+
+@
+
+<< norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms \cite{marty_impact_2011}.
+Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
+Increasing temparture (left panel, purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (right panel).'>>=
+
+gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 1)
+
+t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- gouts[[x]][['t_growth']]
+  y$Scenario <- scn[x]
+  y$Size <- scz[x]
+  y}))
+
+#browser()
+norm <- t_growth %>% 
+  group_by(Scenario,Size,Temperature) %>%
+  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1])
+
+cp <- ggplot() +
+  geom_line(aes(x=t, y=t_length,col=as.factor(Temperature)),data=t_growth) +
+  geom_point(aes(x=ts, y=m),data=norm) +
+  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
+  theme_cowplot()+
+  facet_wrap(Size~Scenario,scales='free')+
+  viridis::scale_colour_viridis(discrete = T,guide='none')+
+  theme(plot.margin = margin(2, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  coord_cartesian()+
+  labs(y = 'Length (cm)',
+       x='Age  (years)')
+
+alloc <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- gouts[[x]][['t_growth']]
+  y$Scenario <- scn[x]
+  y$Size <- scz[x]
+  y}))
+
+norm <- alloc %>% 
+  group_by(Scenario,Size,Temperature) %>%
+  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
+            ls=t_length[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
+            alloc=allocs[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1]) %>%
+  mutate(ls = sc(ls))
+
+np <-  ggplot() +
+  geom_line(aes(x=Temperature, y=ls, linetype=Scenario,col=Size),data=norm) +
+  theme_cowplot()+
+  theme(plot.margin = margin(2, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  #scale_color_discrete(guide='none')+
+  #scale_shape_discrete(guide='none')+
+  coord_cartesian()+
+  labs(y = 'Relative length',
+       x='Temperature')
+
+cowplot::plot_grid(cp,np,nrow=1)
+@
+
+<<evo, fig.cap='On evolutionary time-scales, selection moves the reaction norm.
+Size-at-maturation reacts strongly to temperature changes in the model (left panel).
+Selection (S) induced changes in size are slow for M strategists, fast for P strategists.'>>=
+
+winfs <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- gouts[[x]][['winfs']]
+  y$Scenario <- scn[x]
+  y$Size <- scz[x]
+  y}))
+
+wtfs <- winfs %>% group_by(Scenario,Size) %>%
+  mutate(length=sc(lw(l)))
+
+cpG <- ggplot(wtfs) +
+  geom_line(aes(x=Temperature, y=length, col=Size,linetype=Scenario),alpha=0.7) +
+  theme_cowplot()+
+  #scale_linetype_discrete(guide='none')+
+  theme(plot.margin = margin(3, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y='Relative adult length')
+
+npG <- ggplot(wtfs) +
+  geom_line(aes(x=Temperature, y=G/l, col=Size,linetype=Scenario),alpha=0.7) +
+  theme(plot.margin = margin(3, 6, 0, 6),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  #coord_cartesian(ylim=quantile(wtfs$L/wtfs$l,c(0.05,0.95),na.rm=T)) + 
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression(S~response~y^-1))
+
+cowplot::plot_grid(cpG,npG,rel_widths = c(0.5,0.5))
+
+@
 

### 2017-09-19 model.R

@@ -6,7 +6,7 @@ inv_logit3 <- function(m,mstar,a,b,c) {
 }
 sc <- function(x) x/max(x,na.rm=T)
 lw <- function(w) (w/0.01)^(1/3)
-
+wl <- function(l) 0.01*l^3
 
 O2_plotfun <- function(etas,Tops){
   grid <- expand.grid(eta = etas,
@@ -41,7 +41,7 @@ O2_plotfun <- function(etas,Tops){
 
 plot_data_temp <- function(v){
   
-  lm = 10^seq(-2,5,l=v$lm)
+  lm = seq(10^v$min_m,10^v$max_m,l=v$lm)
   
   O2_tcor <- O2_fact(v$temp,5)
   f=O2_supply(10*O2_tcor,Topt=v$Topt,O2crit=v$O2crit,Tmax=v$temp[length(v$temp)],T=v$temp,delta=v$lO,omega=v$shape,P50=v$P50,n=v$n)
@@ -120,50 +120,10 @@ plot_data_temp <- function(v){
   
 }
 
-plot_data_growth <- function(v){
-  
-  tau_uc = eval_tau_eq(gamma=v$gamma,
-                       delta=v$delta,
-                       phi=v$phi,
-                       h=v$h,
-                       beta=v$beta,
-                       k=v$k,
-                       p=v$p,
-                       q=v$q,
-                       n=v$n,
-                       m=10^seq(1,5,l=1000),
-                       M=v$M,
-                       v=v$v)
-  
-  tau_uc[tau_uc<0] <- 0
-  tau_uc[tau_uc>1] <- 1
-  
-  taus <- get_taus(v,tau_uc,10,v$temp_ref)
-  
-  model_out_par(tau_max = taus$tau_max,
-                tau = taus$tau,
-                tau_uc = tau_uc,
-                tau_o2 = taus$tau_o2,
-                M=v$M,
-                temp=v$temp_ref,
-                Ea=v$Ea,
-                gamma=v$gamma,
-                delta=v$delta,
-                phi=v$phi,
-                h=v$h,
-                beta=v$beta,
-                k=v$k,
-                p=v$p,
-                q=v$q,
-                n=v$n,
-                m = 10^seq(1,5,l=1000)
-  )
-}
-
 plot_data_growth_tO2 <- function(v){
   
   n_int <- length(v$temp)
-  lm = 10^seq(-2,6,l=v$lm)
+  lm = seq(10^v$min_m,10^v$max_m,l=v$lm)
[…]

### 2017-09-19 run.sh

@@ -7,4 +7,4 @@ set -ex
 #docker push docker.dragonfly.co.nz/adaptive_activity
 
 docker run --rm  -v $PWD:/work -w /work \
-  docker.dragonfly.co.nz/dragonverse-17.04 ./build.sh
+  docker.dragonfly.co.nz/dragonverse-17.04:2017-06-28 ./build.sh

### 2017-10-02 draft.Rnw
some progress

@@
 
-\title{Sizing the effects of temperature on fish - from physiology to ecology}
+\title{Drivers of fish size in a changing climate}
 \author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
@@
 We develop a general trait-based model of carbon and oxygen budgets to determine the relative influence of thermal sensitivity, oxygen limitation, and environmental conditions on ectotherm body size.
-Our model provides a general physiological basis for changes in species size and observed ecological consequences of temperature, and ties together various strands of thought about the ecological consequences of increased temperatures.
+We use this model to contrast the response of size-at-maturation and asymptotic size in small and large fish with traits favoring high production versus reduced mortality.
+The immediate plastic and epigenetic response of size is govered by evolved maturation reaction norms that are largely independent of traits.
+The evolutionary response, however, is more pronounced in active species, suggesting a potentially stronger reponse to climate drivers.
+We suggest that this model provides a mechanistic underpinning that ties together various strands of thought and observation about ecological consequences of increased temperatures.
 
@@
 
-We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness \footnote{I \emph{think} this amounts to maximizing R0 if no more growth occurs: life expectancy is 1/M and reproductive output is proportional to energy}.
-We further assume here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M_{\tau,w} = \tau^\eta \rho w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=1$, that is, at constant maximum activity and $M$ is the effective mortality at realised levels of activity at weight $w$.
-
-\begin{center}
-\input{m}
-\end{center}
+We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness.
+We further assume here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M_{\tau,w} = (\rho+\eta\tau) w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standrad metabolism.
+$M$ is then the effective mortality at realised levels of activity $\tau$ at weight $w$.
 
@@
 
-Life history theory suggests that the adult weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity).
-Note that $W_{\infty}$ depends on temperature only through $\tau$ and changes in $P_C$ as temperature changes metabolic and enzymatic rates.
-We thus impose no direct constraint on $W_{\infty}$.
+\subsection{Allocation to reproduction and ecological size response}
+
+On ecological time-scales, temperature affects size via its effets on the energy budget and the investment of available (surplus) energy into reproduction and growth.
+The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm.
+The maturation reaction norm describes the probability of maturing at a certain age under different growth conditions \cite[e.g., ][]{dieckmann_probabilistic_2007}, though we will use a slightly different definition here since our model is not probabilitic at the population level: we define the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
+The allocation is parametrised as $\phi(z,c) = 1/(1+exp(-(c*z)))$, where $z = (w-w^*)\times cos(atan(b))-a\times sin(atan(b))$ rotates the coordiante system about the slope $b$ of the reaction norm, $a$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allcoation shifts from somatic growth to reproduction.
+
+The slope of the reaction norm is evolutionarily determined by the strngth of the co-variation between growth and mortality for a given population in a given environment \cite{marty_impact_2011}, with strongly positive co-variation leading to the relatively flat reaction norms observed for most populations of fish.
+We do not explicitly model these interactions here (aside from the dependence of mortality on $\tau$) as we are interested in parsing out the effect of temperature, and we assume that reaction norms evolved over relatively stable temperature regimes in the past.
+In other words, we assume that temperature was not a key driver of covariations between growth and mortality.
+In that scenario, good growth conditions (e.g., from increased prey density) probably alter the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators), indepnedently of temparture influences.
+Consequently, we assume that the evolved slope of the reaction norm is a trait for a particular species or population.
+Since most reaction norms are relatively flat, we instead explore how deviations from a flat reaction norm influence maturation size and asymptotic size under varying temperatures.
+
+\subsection{Evolutionary size response}
+
+The maturation reaction norm is subjected to selective pressure when through a gradual change in temperature, mean environmental conditions change and previously evolved reaction norms become sub-optimal.
+To investigate how size will change over longer, evolutionary time-scales, we calculate the expected life-time reproduction, $R0$ as temperature changes from a reference temperature $T_ref$.
+We assumed that the covariation between mortality and growth remains similar as temperatures change (i.e., temperature remains independent of covariation between growth and mortality), and we optimised $R0$ with respect to $m*$ at each temperature.
+From this, we calculated the the expected rate of change (i.e., the selection response) of $m*$ with resepct to temperature as $S = \sigma_w^* h^2 R0'/R0$, where $R0' = dR0/dT$.
 
@@
 
+We explored impacts along two trait axes.
+The first axis aims to contrast species along a gradient of life-history that, at the one end, maximises production (energy aquisition) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production.
+This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \cite{charnov_evolutionary_2013}.
+In other words, this axis contrasts species of similar size with sluggish versus active life-histories.
+
+To implement this axis, we use the result that species with a more active, production oriented life-history (e.g., pelagic species) have a higher standard metabolism and lower weight scaling of metabolic costs \cite{killen_intraspecific_2010}.
+We assume that that higher standard metabolism is due to increased digestive capacity (i.e., is used for gut maintenance CITE).
+In practice, we assume that approxiamtely 50\% of the standard metabolic cost is due to gut maintenance, such that a doubeling of the maximum ingestion leads to a 50\% increase in standard metabolic cost.
+We further assume that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity.
+Exact parameter values are given in Table \ref{tab:parameters}.
+
+The second trait axis aims to be orthogonal to the first and contrast changes in size for species of large and small absolute size, but with similar investment in production or mortality avoidance (i.e., with the same value on the first trait axis).
+We assume that mortlity is largely fixed by the life history strategy on the first axis (via $\rho$ and $\eta$), and that size is largely determined by differences in weight scaling between metabolism and consumption, thereby leading to differential changes in production with size, which in turn determines absolute size \cite{charnov_evolutionary_2013, kozlowski_optimal_1996, thygesen_how_2005}.
+
+\newcommand\T{\rule{0pt}{2.6ex}}
+
 \begin{table}
 \caption{Parameters}
-\begin{tabular}{ll}
-Description & Value \\
+\label{tab:parameters}
+\begin{tabular}{llrrrr}
+Description & Symbol & \multicolumn{4}{c}{Value} \T\\
 \hline
-Specific dynamic action & $\beta = 0.15$ \\
-Egestion and excretion & $\phi = 0.25$ \\
-Consumption rate$^1$ & $\Theta \gamma \approx h w^{p-q}$ (g$_C$/time) \\
-Coef.~for maximum consumption rate & $h \approx 20 $g$_{WW}^{1-n}$/yr \\
-Activity coefficient & $\delta \approx 3$ \\
-Exponent for max.~consumption & $q=0.75$ \\
-Exponent for clearance rate & $p=0.8$ \\
-Exponent for std.~metabolism & $n=0.88$ \\
+\multicolumn{6}{c}{\textbf{Biomass Metabolism}} \T\\
+Activity coefficient & $\delta$ & \multicolumn{4}{c}{4} \\
+Specific dynamic action & $\beta$ & \multicolumn{4}{c}{0.15} \\
+Egestion and excretion & $\phi$ & \multicolumn{4}{c}{0.25} \\
+
+% Exponent for std.~metabolism & $n=0.88$ \\
+\multicolumn{6}{c}{\textbf{Feeding ecology}} \T\\
+Consumption rate$^1$ & $ \gamma\Theta $ & \multicolumn{4}{c}{$\frac{h w^{p-q}}{(1/f-1)\tau} (g\cdot y$^{-1}$)} \T \\
+% Exponent for max.~consumption & $q=0.75$ \\
+% Coef.~for maximum consumption rate & $h \approx 20 $g$_{WW}^{1-n}$/yr \\
+% Exponent for clearance rate & $p=0.75$ \\
+\multicolumn{6}{c}{\textbf{Oxygen budget}} \T \\
+
 \hline
-\multicolumn{2}{p{\textwidth}}{$^1$ This is under the assumption that the amount of encountered food $\Theta$ is roughly independent of body size.
+\multicolumn{6}{p{\textwidth}}{$^1$ This is under the assumption that the amount of encountered food $\Theta$ is roughly independent of body size.
 This gives and order-of-magnitude estimate of the product $\Theta \gamma $.}
@@
 
+<< setup,echo=FALSE,include=F>>=
+knitr::opts_chunk$set(echo = F, message = F,cache = T,autodep = T)
+
+require(dplyr)
+require(rlang)
+require(cowplot)
+@
+
 <<Scenarios>>=
 
-require(ggplot2)
-require(cowplot)
-require(dplyr)
 source('model.R')
@@
 
-<< norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms \cite{marty_impact_2011}.
+<< norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}).
 Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
@@
 
+Life history theory suggests that the adult weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity).
+Note that $W_{\infty}$ depends on temperature only through $\tau$ and changes in $P_C$ as temperature changes metabolic and enzymatic rates.
+We thus impose no direct constraint on $W_{\infty}$.
+
+\begin{itemize}
+
+\item Adaptation
+\item What does evolution act on?
+
+\end{itemize}
+
 \end{spacing}

### 2017-10-02 model.R

@@ -372,7 +372,7 @@ model_out_growth <- function(temp,
     
     sl <- abs((nPM-lPM)/(winfs$Temperature[t+1]-winfs$Temperature[t-1]))
     
-    G[t] <- 0.04*this.l*sl/tPM
+    G[t] <- 0.004*this.l*sl/tPM
   }       
   
   

### 2017-10-02 draft.Rnw
make error go away!
try to fix norm figure

@@
 \multicolumn{6}{c}{\textbf{Feeding ecology}} \T\\
-Consumption rate$^1$ & $ \gamma\Theta $ & \multicolumn{4}{c}{$\frac{h w^{p-q}}{(1/f-1)\tau} (g\cdot y$^{-1}$)} \T \\
+Consumption rate$^1$ & $ \gamma\Theta $ & \multicolumn{4}{c}{$\frac{h w^{p-q}}{(1/f-1)\tau} (g\cdot y^{-1}$)} \T \\
 % Exponent for max.~consumption & $q=0.75$ \\
@@
 
-int_m <- 500
+int_m <- 1000
 int_t <- 500
@@
 Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
-Increasing temparture (left panel, purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (right panel).'>>=
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (bottom panel).'>>=
 
-gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 1)
+gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 4)
 
@@
 
-cowplot::plot_grid(cp,np,nrow=1)
+cowplot::plot_grid(cp,np,nrow=2)
 @

### 2017-10-02 model.R
fix evo figure

@@ -361,7 +361,7 @@ model_out_growth <- function(temp,
               opt=unique(opt))
   
   G <- rep(NA,length(unique(winfs$Temperature)))
-  
+  #browser()
   for(t in 2:(length(winfs$Temperature)-1)) {
     tau = winfs$Temperature[t]
     this.l <- winfs$l[t]
@@ -372,12 +372,12 @@ model_out_growth <- function(temp,
     
     sl <- abs((nPM-lPM)/(winfs$Temperature[t+1]-winfs$Temperature[t-1]))
     
-    G[t] <- 0.004*this.l*sl/tPM
+    G[t] <- 0.04*this.l*sl/tPM
   }       
   
   
   sG <- sign(G)
-  winfs$G <- G/max(winfs$t,1)
+  winfs$G <- G/max(winfs$t,1,na.rm = T)
   winfs$L <- 10*(lw(winfs$l + winfs$G)-lw(winfs$l))
   
   

### 2017-10-05 draft.Rnw
fix evo figure
some changes

@@
 
-int_m <- 1000
-int_t <- 500
+int_m <- 1000/2
+int_t <- 1000/2
 int_temp <- 50
@@
            m=10, 
-           M=0.1 ,
-           n=0.8, 
+           n=0.85, 
            O2crit=2, 
@@
            temp_ref=15,
-           slope=-0.5,
-           tmax=10,
-           tr=0.5,
+           slope=-0.3,
+           tmax=15,
+           tr=1,
+           M=0.1,
            v=6,
            lm=int_m,
-           nu=-0.2,
+           nu=0.75-1,
            dt=int_t,
            min_m=-2,
-           max_m= 1.5
+           max_m= 2
 )
@@
 fs$h <- 40
-#fs$v <- 2
-#fs$M <- 0.8
-fs$n <- 0.75
-fs$p <- 0.70
-fs$q <- 0.70
+fs$v <- 1
+fs$M <- 1
 
 fl <- fs
-fl$p <- 0.75
-fl$q <- 0.75
-#fl$nu <- -0.25
-fl$tr <- 0.05
+fl$n <- 0.8
+fl$tr <- 0.2
 fl$tmax <- 40
-fl$max_m <- 5
+fl$max_m <- 4
 
 sl <- ss
-sl$p <- 0.8
-sl$q <- 0.8
-#sl$nu <- -0.25
+fl$n <- 0.8
 sl$tmax <- 40
-sl$max_m <- 5
-sl$tr <- 0.05
+sl$max_m <- 4
+sl$tr <- 0.2
 
@@
 
-gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 4)
+gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
 
@@
 
-cowplot::plot_grid(cp,np,nrow=2)
+cowplot::plot_grid(cp,np,nrow=2,rel_heights = c(0.65,0.35))
 @
@@
 Size-at-maturation reacts strongly to temperature changes in the model (left panel).
-Selection (S) induced changes in size are slow for M strategists, fast for P strategists.'>>=
+Selection (S) induced changes in size are slow for M strategists, fast for P strategists.',fig.height=4>>=
 

### 2017-10-13 draft.Rnw
semi-finalise table, scenarios, plots etc

@@
 \usepackage{setspace}
+\usepackage{booktabs}
 \usepackage{subfig}
@@
 \usepackage{pdflscape}
+\usepackage{multirow}
 \usepackage{longtable}
@@
 \usepackage[american]{babel}
-\usepackage[backend=biber,style=apa,language=american, labeldate=year,
-uniquename=false, maxcitenames=2,maxbibnames=200,uniquelist=false,mincitenames=1]{biblatex}
+\usepackage[backend=biber,
+mincitenames = 1,
+maxcitenames = 1,
+uniquename = false,
+uniquelist = false,
+citestyle = authoryear-comp]{biblatex}%
 \usepackage{lineno, blindtext}
-\DeclareLanguageMapping{american}{american-apa}
 \addbibresource{Sizing-fx-of-temperature.bib}
@@
 
-\title{Drivers of fish size in a changing climate}
+\title{Fish size response to climate warming}
 \author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
@@
 Increasing temperatures under climate change are thought to affect individual physiology of ectotherms through increases in metabolic demands, leading to decreases in body-size with concomitant effects on species ecology.
-Although intuitively appealing, the magnitude, as well as when and where such changes are expected in an ecosystem context remains unclear.
-We develop a general trait-based model of carbon and oxygen budgets to determine the relative influence of thermal sensitivity, oxygen limitation, and environmental conditions on ectotherm body size.
-We use this model to contrast the response of size-at-maturation and asymptotic size in small and large fish with traits favoring high production versus reduced mortality.
-The immediate plastic and epigenetic response of size is govered by evolved maturation reaction norms that are largely independent of traits.
+Although intuitively appealing, the magnitude, as well as when and where such changes are expected remains controversial.
+We developped a general trait-based model of carbon and oxygen budgets to determine the relative influence of thermal sensitivity, oxygen limitation, and environmental conditions on ectotherm body size.
+We use this model to contrast the response of size-at-maturation and asymptotic size in small and large fish with traits favoring fast growth versus reduced mortality.
+The immediate (plastic) response of size is govered by evolved maturation reaction norms that are largely independent of traits.
 The evolutionary response, however, is more pronounced in active species, suggesting a potentially stronger reponse to climate drivers.
-We suggest that this model provides a mechanistic underpinning that ties together various strands of thought and observation about ecological consequences of increased temperatures.
+We suggest that this model provides a mechanistic underpinning that ties together various strands of thought and observation about ecological consequences of increasing temperatures.
 
@@
 However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems.
-Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\cite{brander_overconfidence_2013, lefevre_models_2017}).
+Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes.
 In marine fish, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017}).
@@
 A prevalent view is that the maximum metabolic rate (MMR; the metabolic rate at maximum sustained exercise) has a  dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
-This leads to the view of a modal curve for metabolic scope (MMR-SM; the available oxygen/energy for additional activity), and suggests that towards the upper end of this curve, organisms will run out of oxygen.
+This leads to the view of a modal curve for metabolic scope (MMR minus SM; the available oxygen/energy for additional activity), and suggests that towards the upper end of this curve, organisms will , simply put, run out of oxygen.
 
@@
 P_C &= S_C - D_C \\
-  &=(1-\beta-\phi)f_C h c_T w^q  -(1+\tau \delta)c_T k w^n \\
+  &=(1-\beta-\phi)f_C h c_T w^q  - c_T k w^n - \tau \delta c_T k w  \\
 P_{0_2} &= S_{O_2} - D_{O_2} \\
-        &= f_{O_2}w^n - \omega \left( \beta f_C h c_T w^q +(1+\tau \delta) c_T k w^n \right)
+        &= f_{O_2}w^n - \omega \left( \beta f_C h c_T w^q + c_T k w^n + \tau \delta c_T k w \right)
 \end{align}
@@
 In the following, we will refer to $\tau$ as the activity fraction for sake of generality.
-Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke2002predator, sentis2013parsing}), is assumed to scale with temperature as $c_T = e^{E_a(T-T_0)/kTT_0}$.
+Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}), is assumed to scale with temperature as $c_T = e^{E_a(T-T_0)/kTT_0}$.
 Available carbon $P_C$ is determined by supply ($S_C$) from prey consumption ($f_C h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
-Metabolic costs ($D_C$) are those of standard metabolism ($k w^n$), as well as active metabolism (scaled in units of standard metabolism as $\delta k w^n$, with $\delta$ the factorial aerobic scope (FAS)), with the activity fraction $\tau$ determining the fraction of time that the active metabolism cost applies.
+Metabolic costs ($D_C$) are those of standard metabolism ($k w^n$), as well as active metabolism (scaled in units of standard metabolism as $\delta k w$, with $\delta$ the factorial aerobic scope (FAS)), with the activity fraction $\tau$ determining the fraction of time that the active metabolism cost applies.
+Note that active metabolism scales directly with $w$, owing to muscular demands scaling approxiuamtely isometrically (CITE Glazier, Brett).
 
@@
 On ecological time-scales, temperature affects size via its effets on the energy budget and the investment of available (surplus) energy into reproduction and growth.
-The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm.
-The maturation reaction norm describes the probability of maturing at a certain age under different growth conditions \cite[e.g., ][]{dieckmann_probabilistic_2007}, though we will use a slightly different definition here since our model is not probabilitic at the population level: we define the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
-The allocation is parametrised as $\phi(z,c) = 1/(1+exp(-(c*z)))$, where $z = (w-w^*)\times cos(atan(b))-a\times sin(atan(b))$ rotates the coordiante system about the slope $b$ of the reaction norm, $a$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allcoation shifts from somatic growth to reproduction.
+The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which describes the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}).
+We use a slightly different definition here since our model is not probabilitic at the population level: we define the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
+The allocation is parametrised as $\phi(z,c) = 1/(1+\exp(-(c*z)))$, where $z = (w-w^*)\times \text{cos}(\text{atan}(b))-a\times \text{sin}(\text{atan}(b))$ rotates the coordiante system about the slope $b$ of the reaction norm, $a$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allcoation shifts from somatic growth to reproduction.
 
-The slope of the reaction norm is evolutionarily determined by the strngth of the co-variation between growth and mortality for a given population in a given environment \cite{marty_impact_2011}, with strongly positive co-variation leading to the relatively flat reaction norms observed for most populations of fish.
+The slope of maturation reaction norms is evolutionarily determined by the strength of the co-variation between growth and mortality for a given population in a given environment (\cite{marty_impact_2011}), with strongly positive co-variation leading to the relatively flat reaction norms observed for most populations of fish.
 We do not explicitly model these interactions here (aside from the dependence of mortality on $\tau$) as we are interested in parsing out the effect of temperature, and we assume that reaction norms evolved over relatively stable temperature regimes in the past.
 In other words, we assume that temperature was not a key driver of covariations between growth and mortality.
-In that scenario, good growth conditions (e.g., from increased prey density) probably alter the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators), indepnedently of temparture influences.
+In that scenario, good growth conditions (e.g., from increased prey density) probably alter the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators), independently of temperature influences.
 Consequently, we assume that the evolved slope of the reaction norm is a trait for a particular species or population.
-Since most reaction norms are relatively flat, we instead explore how deviations from a flat reaction norm influence maturation size and asymptotic size under varying temperatures.
+Since most reaction norms are relatively flat, we simply assume a flat reaction norm.
 
@@
 The maturation reaction norm is subjected to selective pressure when through a gradual change in temperature, mean environmental conditions change and previously evolved reaction norms become sub-optimal.
-To investigate how size will change over longer, evolutionary time-scales, we calculate the expected life-time reproduction, $R0$ as temperature changes from a reference temperature $T_ref$.
-We assumed that the covariation between mortality and growth remains similar as temperatures change (i.e., temperature remains independent of covariation between growth and mortality), and we optimised $R0$ with respect to $m*$ at each temperature.
-From this, we calculated the the expected rate of change (i.e., the selection response) of $m*$ with resepct to temperature as $S = \sigma_w^* h^2 R0'/R0$, where $R0' = dR0/dT$.
+To investigate how size will change over evolutionary time-scales, we calculate the expected life-time reproduction, $R0$ as temperature changes from a reference temperature $T_ref$.
+We assumed that the covariation between mortality and growth remains similar as temperatures change (i.e., temperature remains independent of covariation between growth and mortality, and ), and we optimised $R0$ with respect to $w*$ at each temperature.
+From this, we calculated the the expected rate of change (i.e., the selection response) of $w*$ with resepct to temperature as $S = \sigma_w^* h^2 R0'/R0$, where $R0' = dR0/dT$, where we take $h$ to be about 0.2 and we assume a coefficient of variation about $w$ of 0.2.
 
@@
 
-We explored impacts along two trait axes.
+We explored ecological and evolutionary impacts along two ecological trait axes.
 The first axis aims to contrast species along a gradient of life-history that, at the one end, maximises production (energy aquisition) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production.
 This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \cite{charnov_evolutionary_2013}.
-In other words, this axis contrasts species of similar size with sluggish versus active life-histories.
+In other words, this axis contrasts species of similar size with defensive/sluggish versus active  life-histories.
 
@@
 We assume that that higher standard metabolism is due to increased digestive capacity (i.e., is used for gut maintenance CITE).
-In practice, we assume that approxiamtely 50\% of the standard metabolic cost is due to gut maintenance, such that a doubeling of the maximum ingestion leads to a 50\% increase in standard metabolic cost.
+In practice, we assume that approximately 50\% of the standard metabolic cost is due to gut maintenance, such that a doubeling of the maximum ingestion leads to a 50\% increase in standard metabolic cost.
 We further assume that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity.
@@
 The second trait axis aims to be orthogonal to the first and contrast changes in size for species of large and small absolute size, but with similar investment in production or mortality avoidance (i.e., with the same value on the first trait axis).
-We assume that mortlity is largely fixed by the life history strategy on the first axis (via $\rho$ and $\eta$), and that size is largely determined by differences in weight scaling between metabolism and consumption, thereby leading to differential changes in production with size, which in turn determines absolute size \cite{charnov_evolutionary_2013, kozlowski_optimal_1996, thygesen_how_2005}.
+Inter-specific meta-analyses often show that metabolism scales with mass to a power of roughly 3/4 (\cite[e.g., ][]{brown_toward_2004}).
+This contrasts with inter-specific weight scaling, which is often found to be higher than 3/4 (\cite{killen_little_2007,ohlberger_intraspecific_2012}).
+We thus assume a trait axis based on metabolic cost per unit weight, which naturally leads to differences in absolute size in our model.
 
@@
 \begin{tabular}{llrrrr}
-Description & Symbol & \multicolumn{4}{c}{Value} \T\\
-\hline
-\multicolumn{6}{c}{\textbf{Biomass Metabolism}} \T\\
-Activity coefficient & $\delta$ & \multicolumn{4}{c}{4} \\
-Specific dynamic action & $\beta$ & \multicolumn{4}{c}{0.15} \\
-Egestion and excretion & $\phi$ & \multicolumn{4}{c}{0.25} \\
-
-% Exponent for std.~metabolism & $n=0.88$ \\
-\multicolumn{6}{c}{\textbf{Feeding ecology}} \T\\
-Consumption rate$^1$ & $ \gamma\Theta $ & \multicolumn{4}{c}{$\frac{h w^{p-q}}{(1/f-1)\tau} (g\cdot y^{-1}$)} \T \\
-% Exponent for max.~consumption & $q=0.75$ \\
-% Coef.~for maximum consumption rate & $h \approx 20 $g$_{WW}^{1-n}$/yr \\
-% Exponent for clearance rate & $p=0.75$ \\
-\multicolumn{6}{c}{\textbf{Oxygen budget}} \T \\
+ \multirow{3}{*}{Description} &  \multirow{3}{*}{Symbol (unit)} & \multicolumn{4}{r}{Value} \\
+ \cmidrule{3-6}
+ & & \multicolumn{2}{r}{M-strategy}  & \multicolumn{2}{r}{P-strategy} \\
+ \cmidrule{3-4}\cmidrule{5-6}
+ & & Small & Large & Small & Large \\
 
 \hline
-\multicolumn{6}{p{\textwidth}}{$^1$ This is under the assumption that the amount of encountered food $\Theta$ is roughly independent of body size.
-This gives and order-of-magnitude estimate of the product $\Theta \gamma $.}
+\addlinespace
+\multicolumn{6}{c}{\textbf{Biomass Metabolism}} \\
+Activity coefficient & $\delta$ & 4 & 4  & 4  & 4  \\
+Specific dynamic action & $\beta$ & 0.15& 0.15& 0.15& 0.15\\
+Egestion and excretion & $\phi$ & 0.25 & 0.25 & 0.25 & 0.25 \\
+Coeff. for std.~metabolism  & $k$ ($g\cdot y^{-1}$)  & 1 & 0.7 & 1.5 & 1\\
+Exponent for std.~metabolism & $n$ & 0.8 &0.8 & 0.75 & 0.75 \\
+
+\addlinespace
+\multicolumn{6}{c}{\textbf{Feeding ecology}}\\
+Coeff. for Encountered food & $\gamma\Theta$ ($y^{-1}$)& 60 & 60 & 60 & 60\\
+Exponent for clearance rate $\gamma$ & $p=n$ & 0.8  & 0.8 & 0.75 & 0.75 \\
+Coeff. for Maximum consumption rate & $h$ ($y^{-1}$) & 30 & 30 & 60 & 60 \\
+Exponent for max.~consumption $\gamma$ & $q=n$ & 0.8 & 0.8 & 0.75 & 0.75 \\
+Coeff. for constant mortality & $M$ ($g\cdot y^{-1}$) & 0.1 & 0.1 & 1 & 1 \\
+Coeff. for activity related mortality & $\rho$ ($y^{-1}$) & 6  & 6 & 1 & 1\\
+Exponent for mortality & $\nu=h-1$ & -0.2 & -0.2 & -0.25 & -0.25 \\
+
+\addlinespace
+\multicolumn{6}{c}{\textbf{Temperature}}\\
+Reference temperature (°C) & $T_{ref}$ & 15 & 15 & 15 & 15 \\
+Activation energy & $E_a$ & 0.52 & 0.52 & 0.52 & 0.52 \\
+Temperature at maximum MMR & $T_{max}$ & 20 & 20& 20& 20\\
+Temperature range & $T^-_{lethal}$--$T^+_{lethal}$ & \multicolumn{4}{c}{5--26} \\
+
+\addlinespace
+\multicolumn{6}{c}{\textbf{Reaction norm}}\\
+
+Slope & $b$ & 0  & 0 & 0 & 0\\
+Reaction & $c$ & 0.5 & 0.1 & 0.5 & 0.1 \\
+
+\addlinespace
+\multicolumn{6}{c}{\textbf{Oxygen budget}} \\
+Critical $O_2$ & $P_{crit}$ ($mg\cdot L^{-1}$) & 2 & 2& 2& 2\\
+Disolved $O_2$ at $0.5\times f_{max}(O_2)$  & $P50$ ($mg\cdot L^{-1}$) & 4  & 4  & 4  & 4 \\
+Doming for $O_2$ supply & $\eta$ & 3 & 3 & 3 & 3\\
+Level of $O_2$ supply  & $\zeta$ ($g\cdot y^{-1}$) &  1 & 1 & 2 & 2\\
+
+\hline
 \end{tabular}
@@
 << setup,echo=FALSE,include=F>>=
-knitr::opts_chunk$set(echo = F, message = F,cache = T,autodep = T)
+knitr::opts_chunk$set(echo = F, message = F,cache=T,autodep = T)
 
@@
 
-int_m <- 1000/2
-int_t <- 1000/2
-int_temp <- 50
+int_m <- 1000
+int_t <- 1000
+int_temp <- 30
 
@@
            Ea=0.52, 
-           gamma=40, 
-           h=20, 
+           gamma=60, 
+           h=30, 
            k=1,
-           lO=1, 
+           lO=0.5, 
            m=10, 
-           n=0.85, 
+           n=0.8, 
            O2crit=2, 
            omega=0.25, 
-           p=0.75,
+           p=0.8,
            P50=4.2, 
            phi=0.25, 
-           q=0.75 ,
+           q=0.8,
            shape=3,
@@
            slope=-0.3,
-           tmax=15,
-           tr=1,
+           tmax=10,
+           tr=0.5,
            M=0.1,
@@
            lm=int_m,
-           nu=0.75-1,
+           nu=0.8-1,
            dt=int_t,
            min_m=-2,
-           max_m= 2
+           max_m= 3
 )
@@
 fs <- ss
-fs$lO <- 2
+fs$lO <- 1
 fs$k <- 1.5
-fs$h <- 40
+fs$h <- 60
 fs$v <- 1
 fs$M <- 1
+fs$nu<- 0.75-1
+fs$n <- 0.75
+fs$p <- 0.75
+fs$q <- 0.75
+fs$tmax <- 5
 
 fl <- fs
-fl$n <- 0.8
-fl$tr <- 0.2
-fl$tmax <- 40
+fl$n <- 0.75
+fl$k <- 1
+fl$tr <- 0.1
+fl$tmax <- 20
 fl$max_m <- 4
@@
 sl <- ss
-fl$n <- 0.8
-sl$tmax <- 40
+sl$n <- 0.8
+sl$k <- 0.7
+sl$tmax <- 50
 sl$max_m <- 4
-sl$tr <- 0.2
+sl$tr <- 0.1
 
@@
 
-<<activity,fig.cap='With increasing temperature, most organisms will increase activity $\\tau$ to offset increased metabolic costs. Oxygen sets metabolic limits at extreme temperatures.'>>=
+<<activity,fig.cap='With increasing temperature, most organisms will increase activity $\\tau$ to offset increased metabolic costs.
+Oxygen sets metabolic limits at extreme temperatures.
+Responses are shown for arbitrary M- and P-strategy (left and right columns, respectively), for small and large species (top and bottom rows, respectively).'>>=
 
@@
   facet_grid(Size~Scenario)+
-  theme(plot.margin = margin(0, 6, 0, 6),
-        strip.background = element_blank(),
+  theme(strip.text = element_blank(),
         panel.background = element_blank(),
@@
 
-<<feeding,fig.cap='Figure 2: Feeding level, available energy and mortality are impacted by increased activity and the metabolic response to temperature.'>>=
+<<feeding,fig.cap='Feeding level, available energy and mortality are impacted by increased activity and the metabolic response to temperature.
+Responses are shown for arbitrary M- and P-strategy (left and right columns, respectively), for small and large species (top and bottom rows, respectively).
+Energy is plotted relative to maximum over all temperatures.'>>=
 
@@
          `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,M,Efficiency) %>%
+  tidyr::gather(Rate,value,Feeding,Energy,M) %>%
   mutate(Rate = relevel(as.factor(Rate),'Feeding'))
@@
 
+<<calc-gouts>>=
+
+gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 4)
+
+@
+
 << norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}).
 Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (bottom panel).'>>=
-
-gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (bottom left panel), whereas asymptotic size is affected by changes in absolute energy available for growth.'>>=
 
@@
 cp <- ggplot() +
-  geom_line(aes(x=t, y=t_length,col=as.factor(Temperature)),data=t_growth) +
+  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
   geom_point(aes(x=ts, y=m),data=norm) +
@@
   facet_wrap(Size~Scenario,scales='free')+
-  viridis::scale_colour_viridis(discrete = T,guide='none')+
-  theme(plot.margin = margin(2, 6, 0, 6),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
+  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
+  theme(panel.background = element_blank(),
+        plot.background = element_blank(),
+        strip.text  = element_blank())+
   coord_cartesian()+
@@
             ls=t_length[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1],
+            l=max(t_length, na.rm=T),
             alloc=allocs[ifelse(any(abs(allocs-0.5)<0.05),which.min(abs(allocs-0.5)),NA)-1]) %>%
-  mutate(ls = sc(ls))
+  mutate(lm = sc(ls),
+         lt = sc(l)) %>%
+  tidyr::gather('type','length',lm,lt)
 
 np <-  ggplot() +
-  geom_line(aes(x=Temperature, y=ls, linetype=Scenario,col=Size),data=norm) +
+
+  geom_line(aes(x=Temperature, y=length, linetype=Scenario,col=Size),data=norm) +
+  facet_wrap(~type,scales='free_y') +
   theme_cowplot()+
-  theme(plot.margin = margin(2, 6, 0, 6),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
+  theme(panel.background = element_blank(),
+        plot.background = element_blank(),
+        strip.text = element_blank())+
   #scale_color_discrete(guide='none')+
@@
   labs(y = 'Relative length',
-       x='Temperature')
+       x=expression(Temperature~(degree*C)))
 
@@
 <<evo, fig.cap='On evolutionary time-scales, selection moves the reaction norm.
-Size-at-maturation reacts strongly to temperature changes in the model (left panel).
-Selection (S) induced changes in size are slow for M strategists, fast for P strategists.',fig.height=4>>=
+Size-at-maturation reacts strongly to temperature changes in the model (top left panel).
+Selection (S) induced changes in size are slow for M strategists, fast for P strategists.
+(top right panel).
+In absolute terms, these changes are slow for both small (bottom left panel) and large fish (bottom right panel)',fig.height=6>>=
 
@@
   theme_cowplot()+
-  #scale_linetype_discrete(guide='none')+
-  theme(plot.margin = margin(3, 6, 0, 6),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  labs(x = expression("Mean temperature " ( degree*C)),
+  scale_linetype_discrete(guide='none')+
+  scale_color_discrete(guide='none')+
+  theme(panel.background = element_blank(),
+        plot.background = element_blank(),)+
+  labs(x = '',
        y='Relative adult length')
@@
   geom_line(aes(x=Temperature, y=G/l, col=Size,linetype=Scenario),alpha=0.7) +
-  theme(plot.margin = margin(3, 6, 0, 6),
-        panel.background = element_blank(),
+  theme(panel.background = element_blank(),
         plot.background = element_blank())+
-  #coord_cartesian(ylim=quantile(wtfs$L/wtfs$l,c(0.05,0.95),na.rm=T)) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
+  labs(x = '',
        y=expression(S~response~y^-1))
 
-cowplot::plot_grid(cpG,npG,rel_widths = c(0.5,0.5))
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(npG)
+
+npTs <- ggplot(wtfs) +
+  geom_line(aes(x=Temperature, y=G, linetype=Scenario)) +
+  facet_wrap(~Size,scales='free_y') +
+  theme(panel.background = element_blank(),
+        plot.background = element_blank(),
+        strip.text = element_blank(),
+        legend.position="none")+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression(S~response~mm.y^-1))
+
+require(gridExtra)
+grid.arrange(arrangeGrob(
+  arrangeGrob(cpG,npG+ theme(legend.position="none"),ncol=2),
+  npTs,nrow=2),
+  mylegend, ncol=2,widths=c(10,2))
+# 
+# cp <- cowplot::plot_grid(cpG,npG,rel_widths = c(0.4,0.6),ncol = 2)
+# 
+# cowplot::plot_grid(cp,npTs,nrow=2)
 

### 2017-10-13 model.R

@@ -44,7 +44,7 @@ plot_data_temp <- function(v){
   lm = seq(10^v$min_m,10^v$max_m,l=v$lm)
   
   O2_tcor <- O2_fact(v$temp,5)
-  f=O2_supply(10*O2_tcor,Topt=v$Topt,O2crit=v$O2crit,Tmax=v$temp[length(v$temp)],T=v$temp,delta=v$lO,omega=v$shape,P50=v$P50,n=v$n)
+  f=O2_supply(10*O2_tcor,Topt=v$Topt,O2crit=v$O2crit,Tmax=v$temp[length(v$temp)],T=v$temp,delta=v$lO,omega=v$shape,P50=v$P50)
   #browser()
   max_tau <- eval_tau_max_temp(f=f,
                                temp=v$temp,
@@ -98,7 +98,7 @@ plot_data_temp <- function(v){
   
   
   #browser()
-  scope <- f*v$m^v$n-model_frame$Metabolism*v$omega
+  scope <- f*v$m-model_frame$Metabolism*v$omega
   scope[scope<0.0001] <- 0
   #browser()
   
@@ -112,7 +112,7 @@ plot_data_temp <- function(v){
               M = (tau_max*v$v+v$M)*v$m^v$nu,
               Optimum = sapply(sapply(tau,max,0),min,1),
               Scope=ifelse(scope<0.0001,0,scope),
-              `Max Metabolism` = f*v$m^v$n,
+              `Max Metabolism` = f*v$m,
               `Active Metabolism` = model_frame$Metabolism*v$omega,
               `Std Metabolism` = model_frame$Std*v$omega,
               Viable = as.numeric(tau_max>0.0001 & model_frame[['C for growth']]>0.0001))
@@ -182,29 +182,6 @@ plot_data_growth_tO2 <- function(v){
   
 }
 
-
-# Activity model
-
-eval_tau_eq <- function(gamma=50,
-                        delta=2,
-                        phi=10,
-                        h=30,
-                        beta=0.75,
-                        k=2,
-                        p=0.8,
-                        q=0.9,
-                        n=0.8,
-                        m=100,
-                        M=0.2,
-                        v=1){
-  
[…]

### 2017-10-16 draft.Rnw
draft; close #1

@@
 Although intuitively appealing, the magnitude, as well as when and where such changes are expected remains controversial.
-We developped a general trait-based model of carbon and oxygen budgets to determine the relative influence of thermal sensitivity, oxygen limitation, and environmental conditions on ectotherm body size.
+We developed a general trait-based model of carbon and oxygen budgets to determine the relative influence of thermal sensitivity, oxygen limitation, and environmental conditions on ectotherm body size.
 We use this model to contrast the response of size-at-maturation and asymptotic size in small and large fish with traits favoring fast growth versus reduced mortality.
-The immediate (plastic) response of size is govered by evolved maturation reaction norms that are largely independent of traits.
-The evolutionary response, however, is more pronounced in active species, suggesting a potentially stronger reponse to climate drivers.
+The immediate (plastic) response of size is governed by evolved maturation reaction norms that are largely independent of traits.
+The evolutionary response, however, is more pronounced in active species, suggesting a potentially stronger response to climate drivers.
 We suggest that this model provides a mechanistic underpinning that ties together various strands of thought and observation about ecological consequences of increasing temperatures.
@@
 
-In the constrained activity model, ectotherms adjust the relative amounts of time ($\tau$) spent foraging and resting/hiding to optimise the net energy/mass gain $P_C$ relative to natural mortality.
+In the constrained activity model, ectotherms adjust the relative amounts of time ($\tau$) spent foraging and resting/hiding to optimise the net energy/mass gain $P$ relative to natural mortality.
 Since both energy gain and loss are sensitive to temperature and oxygen limitations, both the activity level and the net energy gain will be subject to these environmental constraints.
@@
 
-The model is written in terms of carbon (or energy) and oxygen balance equations:
+The model is written in terms of weight $w$ and oxygen balance equations at temperature $T$:
 
 \begin{align}
-f_C &= \frac{\tau }{\tau  + \frac{h c_T w^{q-p}}{\gamma\Theta} } \label{eq:f} \\
-P_C &= S_C - D_C \\
+f(w,T) &= \frac{\tau }{\tau  + \frac{h c_T w^{q-p}}{\gamma\Theta} } \label{eq:f} \\
+P(w,T) &= S(w,T) - D(w,T) \\
   &=(1-\beta-\phi)f_C h c_T w^q  - c_T k w^n - \tau \delta c_T k w  \\
-P_{0_2} &= S_{O_2} - D_{O_2} \\
-        &= f_{O_2}w^n - \omega \left( \beta f_C h c_T w^q + c_T k w^n + \tau \delta c_T k w \right)
+P(w,T)_{0_2} &= S(w,T)_{O_2} - D(w,T)_{O_2} \\
+        &= f_{O_2}(t)w^n - \omega \left( \beta f(w,T) h c_T w^q + c_T k w^n + \tau \delta c_T k w \right)
 \end{align}
 
-where $f$ is the feeding level ([0,1]) at weight $w$, determined by the fraction of time spent foraging (or proportion of maximum attack rate) $\tau$, consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h w^q$.
+where $f(w,T)$ is the feeding level ([0,1]) at weight $w$ and temperature $T$, determined by the fraction of time spent foraging (or proportion of maximum attack rate) $\tau$, consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h w^q$.
 In the following, we will refer to $\tau$ as the activity fraction for sake of generality.
 Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}), is assumed to scale with temperature as $c_T = e^{E_a(T-T_0)/kTT_0}$.
-Available carbon $P_C$ is determined by supply ($S_C$) from prey consumption ($f_C h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
-Metabolic costs ($D_C$) are those of standard metabolism ($k w^n$), as well as active metabolism (scaled in units of standard metabolism as $\delta k w$, with $\delta$ the factorial aerobic scope (FAS)), with the activity fraction $\tau$ determining the fraction of time that the active metabolism cost applies.
-Note that active metabolism scales directly with $w$, owing to muscular demands scaling approxiuamtely isometrically (CITE Glazier, Brett).
+Available carbon $P(w,T)$ is determined by supply ($S(w,T)$) from prey consumption ($f_C h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
+Metabolic demands ($D(w,T)$) are those of standard metabolism ($k w^n$), as well as active metabolism, scaled in units of standard metabolism as $\delta k w$, with $\delta$ the factorial aerobic scope (FAS)).
+The activity fraction $\tau$ determines the fraction of time that the active metabolism cost applies.
+Note that active metabolism scales directly with $w$, owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}).
+In the following we drop dependencies on weight and temperature in the notation for sake of readability.
 
 The oxygen budget $P_{0_2}$, determines physiological limits to aerobic activity.
-Demand ($D_{O_2}$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy and growth - $\beta f_C h c_T w^q$) and ``active metabolism", the sum of standard (or resting) metabolism and the metabolic costs of foraging ($[1+\tau \delta] c_T k w^n$), with $\omega$ determining amount of oxygen required per unit of metabolised carbon.
-Metabolic scope is the difference between $S_{O_2}/w^n=f_{O_2}$, the amount of oxygen supplied per unit weight, and oxygen demand due to standard metabolism ($\omega c_T k w^n$).
+Demand ($D_{O_2}$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy and growth - $\beta f h c_T w^q$) and ``active metabolism", the sum of standard (or resting) metabolism ($c_T k w^n$) and the metabolic costs of foraging ($\tau \delta c_T k w$), with $\omega$ determining amount of oxygen required per unit of metabolised carbon.
+Metabolic scope is the difference between $S_{O_2}/w^n=f_{O_2}(T)$, the maximum amount of oxygen supplied per unit weight at temperature $T$, and oxygen demand due to standard metabolism ($\omega c_T k w^n$).
 
 The maximum oxygen consumption---usually assumed to occur at the maximum metabolic rate (MMR)---is the oxygen consumption during maximal activity level that can be sustained over some time.
-This level is determined by oxygen delivery to organs and muscles.
 At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function \cite[e.g.,][]{lefrancois_influence_2003}.
-We specify $P_{50}$ as the point where the MMR (or oxygen supply) has dropped by 50\% relative to the saturation level $l$ \footnote{Could also use the same functional form as the consumption of food for simplicity: $f_{O_2} = \Gamma \Theta_{O_2}/\Gamma \Theta_{O_2} + h_{O_2} = \Theta_{O_2}/(\Theta_{O_2} + P_{50}).$}.
+We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $l$ \footnote{Could also use the same functional form as the consumption of food for simplicity: $f_{O_2} = \Gamma \Theta_{O_2}/\Gamma \Theta_{O_2} + h_{O_2} = \Theta_{O_2}/(\Theta_{O_2} + P_{50}).$}.
 Oxygen supply, and hence the MMR, are usually found to be temperature dependent \cite{lefevre_are_2016}.
-We follow \cite{gnauck2013freshwater, lefrancois_influence_2003} and use a dome shaped function that peaks at the optimal temperature (optimal in the sense of maximising the MMR).
-Thus:
+We follow \cite{gnauck2013freshwater, lefrancois_influence_2003} and use a flexible dome shaped function:
 
 \begin{align}
-f_{O_2}&=\lambda(1-e^{O_2\log(0.5)/P50}),\\
-\lambda&=\zeta(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}})^\eta \times \exp(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}),
+f_{O_2}(T)&=\lambda(T)(1-e^{O_2\log(0.5)/P50}),\\
+\lambda(T)&=\zeta(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}})^\eta \times \exp(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}),
 \end{align}
 
-with $f_{O_2}$ the oxygen supply (MMR), $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which the MMR is optimised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (Figure \ref{fig:O2_fig}).
-Note that we can emulate a MMR that increases up to the lethal temperature by setting the optimal temperature for MMR close to the maximum temperature.
+with $f_{O_2}$ the oxygen supply.
+Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term describes the saturation dependence on ambient $O_2$.
+To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (Figure \ref{fig:O2_fig}).
+Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (Figure \ref{fig:O2_fig}).
 
@@
 
-We now assume that organisms will adjust their activity level to maximise available energy relative to mortality $M$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P_C/M)$, with $F$ a measure of fitness.
-We further assume here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M_{\tau,w} = (\rho+\eta\tau) w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standrad metabolism.
+We now assume that fish will adjust their activity level to maximise fitness $F$: $\tau_{\text{opt}}$ = $\max_\tau(F)$ = $\max_\tau(P/M)$, which amounts to maximizing available energy relative to mortality $M$ \cite{gilliam_habitat_1987,sainmont_effective_2015}).
+We further assume here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M(w) = (\rho+\eta\tau) w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism.
 $M$ is then the effective mortality at realised levels of activity $\tau$ at weight $w$.
@@
 
-\subsection{Allocation to reproduction and ecological size response}
-
-On ecological time-scales, temperature affects size via its effets on the energy budget and the investment of available (surplus) energy into reproduction and growth.
-The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which describes the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}).
-We use a slightly different definition here since our model is not probabilitic at the population level: we define the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
-The allocation is parametrised as $\phi(z,c) = 1/(1+\exp(-(c*z)))$, where $z = (w-w^*)\times \text{cos}(\text{atan}(b))-a\times \text{sin}(\text{atan}(b))$ rotates the coordiante system about the slope $b$ of the reaction norm, $a$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allcoation shifts from somatic growth to reproduction.
-
-The slope of maturation reaction norms is evolutionarily determined by the strength of the co-variation between growth and mortality for a given population in a given environment (\cite{marty_impact_2011}), with strongly positive co-variation leading to the relatively flat reaction norms observed for most populations of fish.
-We do not explicitly model these interactions here (aside from the dependence of mortality on $\tau$) as we are interested in parsing out the effect of temperature, and we assume that reaction norms evolved over relatively stable temperature regimes in the past.
-In other words, we assume that temperature was not a key driver of covariations between growth and mortality.
-In that scenario, good growth conditions (e.g., from increased prey density) probably alter the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators), independently of temperature influences.
-Consequently, we assume that the evolved slope of the reaction norm is a trait for a particular species or population.
-Since most reaction norms are relatively flat, we simply assume a flat reaction norm.
-
-\subsection{Evolutionary size response}
-
-The maturation reaction norm is subjected to selective pressure when through a gradual change in temperature, mean environmental conditions change and previously evolved reaction norms become sub-optimal.
-To investigate how size will change over evolutionary time-scales, we calculate the expected life-time reproduction, $R0$ as temperature changes from a reference temperature $T_ref$.
-We assumed that the covariation between mortality and growth remains similar as temperatures change (i.e., temperature remains independent of covariation between growth and mortality, and ), and we optimised $R0$ with respect to $w*$ at each temperature.
-From this, we calculated the the expected rate of change (i.e., the selection response) of $w*$ with resepct to temperature as $S = \sigma_w^* h^2 R0'/R0$, where $R0' = dR0/dT$, where we take $h$ to be about 0.2 and we assume a coefficient of variation about $w$ of 0.2.
-
 \subsection{Trait based scenarios}
@@
 We explored ecological and evolutionary impacts along two ecological trait axes.
-The first axis aims to contrast species along a gradient of life-history that, at the one end, maximises production (energy aquisition) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production.
+The first axis aims to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production.
 This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \cite{charnov_evolutionary_2013}.
@@
 We assume that that higher standard metabolism is due to increased digestive capacity (i.e., is used for gut maintenance CITE).
-In practice, we assume that approximately 50\% of the standard metabolic cost is due to gut maintenance, such that a doubeling of the maximum ingestion leads to a 50\% increase in standard metabolic cost.
+In practice, we assume that approximately 50\% of the standard metabolic cost is due to gut maintenance, such that a doubling of the maximum ingestion leads to a 50\% increase in standard metabolic cost.
 We further assume that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity.
@@
 
-The second trait axis aims to be orthogonal to the first and contrast changes in size for species of large and small absolute size, but with similar investment in production or mortality avoidance (i.e., with the same value on the first trait axis).
-Inter-specific meta-analyses often show that metabolism scales with mass to a power of roughly 3/4 (\cite[e.g., ][]{brown_toward_2004}).
+The second trait axis aims to be orthogonal to the first and contrast changes in size with temperature for species of large and small absolute size, but with similar investment in production or mortality avoidance (i.e., with the same value on the first trait axis).
+Inter-specific meta-analyses often show that resting metabolism scales with mass to a power of roughly 3/4 (\cite[e.g., ][]{brown_toward_2004}).
 This contrasts with inter-specific weight scaling, which is often found to be higher than 3/4 (\cite{killen_little_2007,ohlberger_intraspecific_2012}).
@@
 
-Slope & $b$ & 0  & 0 & 0 & 0\\
+Slope & $b$ & 0 (-0.5,0.5)  & 0 (-0.5,0.5) & 0 (-0.5,0.5) & 0 (-0.5,0.5)\\
 Reaction & $c$ & 0.5 & 0.1 & 0.5 & 0.1 \\
@@
 Critical $O_2$ & $P_{crit}$ ($mg\cdot L^{-1}$) & 2 & 2& 2& 2\\
-Disolved $O_2$ at $0.5\times f_{max}(O_2)$  & $P50$ ($mg\cdot L^{-1}$) & 4  & 4  & 4  & 4 \\
+Dissolved $O_2$ at $0.5\times f_{max}(O_2)$  & $P50$ ($mg\cdot L^{-1}$) & 4  & 4  & 4  & 4 \\
 Doming for $O_2$ supply & $\eta$ & 3 & 3 & 3 & 3\\
@@
 \end{table}
+
+\subsection{Allocation to reproduction and ecological size response}
+
+On ecological time-scales, temperature affects size via its effects on the energy budget and the investment of available (surplus) energy into reproduction and growth.
+The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}).
+We use a slightly different definition here since our model is not probabilistic at the population level: we define the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
+The allocation is parametrised as
+$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
+$$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$ 
+rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
+
+The slope of maturation reaction norms is evolutionarily determined by the strength of the co-variation between growth and mortality for a given population in a given environment (\cite{marty_impact_2011}).
+Strongly positive co-variation leads to the relatively flat reaction norms observed for most populations of fish.
+We do not explicitly model these interactions here (aside from the dependence of mortality on $\tau$) as we are interested in parsing out the effect of temperature, and we assume that reaction norms evolved over relatively stable temperature regimes in the past.
+In other words, we assume that temperature was not a key driver of covariation between growth and mortality.
+In that scenario, good growth conditions (e.g., from increased prey density) probably alter the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators).
+Consequently, we assume that the evolved slope of the reaction norm is a trait for a particular species or population.
+
+\subsection{Evolutionary size response}
+
+The maturation reaction norm is subject to selective pressure when through a gradual change in temperature, mean environmental conditions change and previously evolved reaction norms become sub-optimal.
+To investigate how size will change over evolutionary time-scales, we calculated the expected life-time reproduction $R0$ with respect to $w^*$ as temperature $T$ changes from a reference temperature $T_ref$:
+
+$$R0 = \int_0^\infty \phi(z(t,w_t,w^*))P(w_t,T)S_{0 \rightarrow t} dt, \text{, where}$$
+$$S_{0 \rightarrow t} = \int_0^t \exp(-M(w_t))dt$$
+
+is survival from birth to age $t$.
+We assumed that the covariation between mortality and growth remains similar as temperatures change (i.e., temperature remains independent of covariation between growth and mortality, and the reaction norm slope does not change substantially), and we optimised $R0$ with respect to $w^*$ at each temperature.
+From this, we calculated the the expected rate of change (i.e., the selection response) of $w^*$ with respect to temperature as $S = \sigma_w^* h^2 R0'/R0$, where $R0' = dR0/dT$, where we take the heritability term $h^2$ to be about 0.2 and we assumed a coefficient of variation about $w$ of 0.2 for $\sigma_w$.
 
@@
 int_t <- 1000
-int_temp <- 30
+int_temp <- 50
 
@@
            temp_ref=15,
-           slope=-0.3,
-           tmax=10,
+           slope=-.3,
+           tmax=15,
            tr=0.5,
@@
 fl <- fs
-fl$n <- 0.75
 fl$k <- 1
@@
 sl$n <- 0.8
-sl$k <- 0.7
+sl$k <- 0.8
 sl$tmax <- 50
@@
 Oxygen sets metabolic limits at extreme temperatures.
-Responses are shown for arbitrary M- and P-strategy (left and right columns, respectively), for small and large species (top and bottom rows, respectively).'>>=
+Responses are shown for arbitrary M- and P-strategy (left and right columns, respectively), for small and large species (top and bottom rows, respectively).',fig.align='center'>>=
 
@@
 Responses are shown for arbitrary M- and P-strategy (left and right columns, respectively), for small and large species (top and bottom rows, respectively).
-Energy is plotted relative to maximum over all temperatures.'>>=
+Energy is plotted relative to maximum over all temperatures.',fig.align='center'>>=
 
@@
 Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (bottom left panel), whereas asymptotic size is affected by changes in absolute energy available for growth.'>>=
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (bottom left panel), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=
 
@@
 Size-at-maturation reacts strongly to temperature changes in the model (top left panel).
-Selection (S) induced changes in size are slow for M strategists, fast for P strategists.
-(top right panel).
-In absolute terms, these changes are slow for both small (bottom left panel) and large fish (bottom right panel)',fig.height=6>>=
+Selection (S) induced changes in size are slow for M strategists, fast for P strategists (top right panel; note that selection response is normalised by size here for comparison, i.e., cahnges are shown proportional to size at each temperature).
+In absolute terms, these changes are slow for both small (bottom left panel) and large fish (bottom right panel)',fig.height=6,fig.align='center'>>=
 
@@
 
+<<goutss>>=
+
+fs_n <- fs
+fs_n$slope <- -0.5
+fs_p <- fs
+fs_p$slope <- 0.5
+
+scss <- list(fs,fs_n,fs_p)
+scns <- c(0,-0.5,0.5)
+goutss <- parallel::mclapply(scss,plot_data_growth_tO2,mc.cores = 4)
+@
+
+<<plot_gouts, fig.cap='Selection response for changes in size with temperature (in mm per year) for populations with positive, flat and negative reaction norm slopes.
+The slope of the reaction norm does not influence the evolutionary response (assuming the slope stays fixed).',fig.height=3,fig.width=4,fig.align='center'>>=
+
+winfs <- bind_rows(lapply(1:length(goutss), function(x) {
+  y <- goutss[[x]][['winfs']]
+  y$Scenario <- as.factor(scns[x])
+  y}))
+
+wtfss <- winfs %>% group_by(Scenario) %>%
+  mutate(length=sc(lw(l)))
+
+ggplot(wtfss) +
+  geom_line(aes(x=Temperature, y=G, linetype=Scenario)) +
+  theme(panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_discrete('Slope')+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression(S~response~mm.y^-1))
+
+@
+
 \section{Discussion}
 
-Life history theory suggests that the adult weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P_C/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity).
-Note that $W_{\infty}$ depends on temperature only through $\tau$ and changes in $P_C$ as temperature changes metabolic and enzymatic rates.
+Life history theory suggests that the adult weight $W_{\infty}$ is found at the size at which all energy is allocated to reproduction, which optimally occurs at $\frac{\partial P/M}{\partial w}=1$ in the case of size-dependent mortality (provided concavity with respect to mass of this quantity).
+Note that $W_{\infty}$ depends on temperature only through $\tau$ and changes in $P$ as temperature changes metabolic and enzymatic rates.
 We thus impose no direct constraint on $W_{\infty}$.

### 2017-10-16 model.R

@@ -343,23 +343,22 @@ model_out_growth <- function(temp,
   allocs <- array(0, c(temps,l,dt))
   
   R0 <- array(0, c(temps,l,dt))
-  surv <- array(0, c(temps,l,dt))
-  
-  s[,,1] <- min(wl(lm))
-  
+  mu <- array(0, c(temps,l,dt))
   
   dts <- (tmax/(dt-1))
+  s[,,1] <- min(wl(lm))
+  
   
   for(t in 2:dt) {
     tm1 <- get_taus(v,1,10,temp,s[,,t-1])
     Es <- (1-phi-beta)*(tm1*gamma*s[,,t-1]^p/(tm1*gamma*s[,,t-1]^p+tc*h*s[,,t-1]^q))*tc*h*s[,,t-1]^q -k*tc*s[,,t-1]^n-tm1*delta*k*tc*s[,,t-1]
     allocs[,,t] <- pmax(allocs[,,t-1],t(apply(lw(s[,,t-1]),1,inv_logit3,lm,ts[t],slope,tr)))
     
-    mt <- (tm1*v$v+v$M)*s[,,t-1]^v$nu
-    surv[,,t] <- surv[,,t-1] + dts*mt
-    R0[,,t] <- R0[,,t-1] + dts*allocs[,,t]*Es*exp(-surv[,,t])
     
     s[,,t] <- s[,,t-1]+dts*(1-allocs[,,t])*Es
+    mu[,,t] <- mu[,,t-1] + dts*(tm1*v$v+v$M)*s[,,t]^v$nu
+    R0[,,t] <- R0[,,t-1] + dts*allocs[,,t]*Es*exp(-mu[,,t])
+    
   }
   ls <- lw(s)
   opt <- apply(R0[,,dt],1,function(x) ifelse(any(!is.nan(x)),which.max(x),NA))
@@ -372,20 +371,20 @@ model_out_growth <- function(temp,
   
   lss <- reshape2::melt(s)
   colnames(lss) <- c('Temperature','t','size')
+  lss$opt <- opt[lss$Temperature]
   lss$Temperature <- temp[lss$Temperature]
   lss$t <- ts[lss$t]
-  lss$opt <- opt[lss$Temperature]
   
   alloc <- reshape2::melt(allocs)
   colnames(alloc) <- c('Temperature','t','allocs')
-  alloc$Temperature <- temp[alloc$Temperature]
   alloc$t <- ts[alloc$t]
[…]

### 2018-02-05 draft.Rnw
landscape table
draft paper!!

@@
 
-\newcommand\T{\rule{0pt}{2.6ex}}
+\begin{landscape}
 
@@
 \end{table}
+
+\end{landscape}
 
@@
        y='Relative rate')
+
+sco <- tidyr::gather(scenarios,Rate,value,`Max Metabolism`, `Active Metabolism`, `Std Metabolism`)
+
+ggplot(sco) + 
+  geom_line(aes(x=Temperature, y=value, linetype=Rate),alpha=0.7) +
+  theme_cowplot()+
+  facet_grid(Size~Scenario)+
+  theme(strip.text = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_discrete('')+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression(Oxygen~(mg.yr^-1)))
 

### 2018-02-05 draft_model_only.Rnw
draft paper!!

\documentclass[a4paper, toc=index,abstract=true]{scrartcl}
\usepackage{gensymb}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{pdflscape}
\usepackage{multirow}
\usepackage{longtable}
\usepackage[toc,page]{appendix}
\usepackage{array,booktabs}
\usepackage[american]{babel}
\usepackage[backend=biber,
mincitenames = 1,
maxcitenames = 1,
uniquename = false,
uniquelist = false,
citestyle = authoryear-comp]{biblatex}%
\usepackage{lineno, blindtext}
\addbibresource{Sizing-fx-of-temperature.bib}
\captionsetup[table]{singlelinecheck=false}

\title{Beyond conceptual eco-physiological hypotheses: insights from a general size and trait-based model of ectotherm thermal performance}
\author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
        Ken H. Andersen\\Centre for Ocean Life
        Danish Technical University, Lyngby, Denmark}

\begin{document}

\maketitle

\begin{spacing}{1.9}

\pagenumbering{gobble}
\begin{abstract}

Increasing temperatures under climate change are thought to affect individual physiology of ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology. Although intuitively appealing, the driving mechanisms behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance. Whether or not oxygen limitations via the metabolic scope, or a lack thereof, have major ecological consequences remains a highly contested question. Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of thermal sensitivity of metabolic rates, oxygen limitation, and environmental conditions on thermal performance. We show that oxygen limitation is not necessary to explain performance curves that are correlated with metabolic scope. Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology. Furthermore, our model reveals that fitness trends with temperature likely oppose trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum. We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.

\end{abstract}
{\large Keywords:} thermal performance curves, OCLTT, metabolic rates, climate change

\newpage

\section{Introduction}

Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\cite{deutsch_climate_2015,pinsky_marine_2013,brown_toward_2004}). As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\cite{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}). However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems. Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\cite{brander_overconfidence_2013, lefevre_models_2017}). In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017}).

There are few general concepts and models that can explain thermal performance and ecological responses to temperature. To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed changes of attack rates with temperature (\cite{englund_temperature_2011,rall_universal_2012}), from fundamental physiological processes. Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependant, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{vucic-pestic_warming_2011, guiet_effects_2016}).

Although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups. A phenomenological description that assumes a general ecological temperature response thus leads to difficulties with extrapolation when observed ecological responses are heterogeneous across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}). In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011}). Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.

Physiologically, a long held view has been that temperature is a controlling factor while oxygen supply sets the physiological limits (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016}). How exactly temperature influences ectotherm physiological rates and limits, however, has been a matter of debate, not least because of the variable responses observed among different species. In most species, the standard metabolism (SM; the metabolic cost of maintenance and routine activity such as ventilation) increases near exponentially with temperature. A prevalent view is that the maximum metabolic rate (MMR; the metabolic rate at maximum sustained exercise) has a dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}). This leads to the view of a uni-modal curve for metabolic scope (MMR minus SM; the available oxygen/energy for additional activity), and suggests that towards the upper end of this curve, organisms will, simply put, run out of oxygen.

This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM). In some species, however, maximum metabolic rate increases steadily (\cite{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor at high temperatures. Indeed, it has been argued that oxygen is unlikely to determine performance for most species over most of their temperature range as oxygen limits are rarely reached during normal activity (\cite{jutfelt_oxygen-and_2018, holt_climate_2015}).

Here, we propose a general quantitative size- and trait-based eco-physiological model to derive general predictions about temperature impacts on ectotherm physiology, performance and ecology. We describe simple size-dependent physiological processes within an ecological context, and, using a simple optimisation argument, show that observed ecological responses of different life-history strategies can be predicted on the basis of optimised bio-energetics under different temperatures.

\section{Methods}

\subsection{Key assumptions}

Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets (\cite{holt_climate_2015,holt_climate_2014}). At a high level, we assume that animals will adapt activity levels to optimise available energy for growth and reproduction relative to mortality risk. Available energy is limited either by food capture, food processing capacity, or by available oxygen. We further assume that temperature acts directly on rates that are determined by enzymatic activity: digestive activity (via maximum consumption) and metabolic costs. Consequently, temperature only acts on ecological rates (e.g., actual feeding rates) via optimisation of activity levels.

\subsection{Model description}

The quantitative size- and trait-based thermal impact model lets ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy $P$ gain relative to natural mortality. Since both energy gain and loss are sensitive to temperature and oxygen limitations, both the activity level and the net energy gain will be subject to these environmental constraints. Their interplay thus determines available energy for growth and reproduction.

The model is written in terms of weight $w$ and oxygen balance equations at temperature $T$:

\begin{align}
f(w,T) &= \frac{\tau }{\tau  + \frac{h c_T w^{q-p}}{\gamma\Theta} } \label{eq:f} \\
P(w,T) &= S(w,T) - D(w,T) \\
  &=(1-\beta-\phi)f(w,T) h c_T w^q  - c_T k w^n - \tau \delta c_T k w  \\
P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
        &= f_{O_2}(T)w^n - \omega \left( \beta f(w,T) h c_T w^q + c_T k w^n + \tau \delta c_T k w \right)
\end{align}

where $f(w,T)$ is the feeding level ([0,1]) at weight $w$ and temperature $T$, determined by the fraction of time spent foraging (or proportion of maximum attack rate) $\tau$, consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h w^q$. In the following, we will refer to $\tau$ as the activity fraction for sake of generality. Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}), is assumed to scale with temperature as $c_T = e^{E_a(T-T_0)/kTT_0}$. Available energy $P(w,T)$ is determined by supply ($S(w,T)$) from prey consumption ($f(w,T) h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested. Metabolic demands ($D(w,T)$) are those of standard metabolism ($k w^n$), as well as active metabolism, scaled in units of standard metabolism as $\delta k w$, with $\delta$ the factorial aerobic scope (FAS). The activity fraction $\tau$ determines the fraction of time that the active metabolism cost applies. Note that active metabolism scales directly with $w$, owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}).

The oxygen budget $P_{0_2}(w,T)$, determines physiological limits to aerobic activity. Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy, growth and reproduction - $\beta f h c_T w^q$) and ``active metabolism", the sum of standard (or resting) metabolism ($c_T k w^n$) and the metabolic costs of foraging ($\tau \delta c_T k w$), with $\omega$ determining amount of oxygen required per unit of metabolised feed. Metabolic scope is the difference between $S_{O_2}(w,T)=f_{O_2}(T)w^n$, the maximum amount of oxygen supplied at temperature $T$, and oxygen demand due to standard metabolism ($\omega c_T k w^n$). We assume that the maximum oxygen supply (MOS), follows a flexible dome-shaped function that can emulate both a dome-shaped MOS as well as MOS that increas continously up to a lethal temeprature (Figure \ref{fig:O2_fig}, Appendix A).

We assumed that fish will adjust their activity level to maximise $F$: maximize available energy relative to mortality: $\tau_{\text{opt}}$ = $\text{argmax}_{\tau_{w,T}}F(\tau_{w,T})$ = $\text{argmax}_{\tau_{w,T}}P(\tau_{w,T})/M(\tau_{w,T})$. This optimisation is also known as Gilliam's rule (\cite{gilliam_habitat_1987}) and represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for simulating opmisation in changing environments (\cite{sainmont_effective_2015}). We further assumed here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M(w) = (\rho+\eta\tau) w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism. $M$ is then the effective mortality at realised levels of activity $\tau$ at weight $w$.

We assumed that the metabolic scope dictates the upper limit of this activity, such that at $\tau_{\text{max}}$, oxygen demand $D_{0_2}$ equals total supply $S_{0_2}$. Both temperature and oxygen will influence $\tau$, such that at a given temperature and oxygen concentration, $\tau_{w,T,O_2} = \text{min}\left( \tau_{\text{opt}},\tau_{\text{max}} \right)$, meaning we assumed that animals will adapt their effort to optimise fitness $F$ given temperature and oxygen constraints.

\subsection{Growth response}

Temperature affects growth via its effects on the energy budget and the investment of available (surplus) energy into reproduction and growth. The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}). We used a slightly different definition here since our model is not probabilistic at the population level: we defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size. The allocation was parametrised as 
$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
$$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$ 
rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.

The slope of maturation reaction norms is evolutionarily determined by the strength of the co-variation between growth and mortality for a given population in a given environment. Strongly positive co-variation leads to the relatively flat reaction norms observed for most fish populations (\cite{marty_impact_2011}). This covariation is probably the consequence of good growth conditions (e.g., from increased prey density) altering the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators). We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past. Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm \ref{fig:MRN}). The intercept of this reaction norm was found numerically by maximising fitness ($R0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was asumed fixed as temperatures change.

\subsection{Fitness consequences}

Fitness consequences for particular life-history strategies (trait combinations, see below) at different temperatures can be investigated if one considers the time-scales in the model to be short relative to evolutionary time-scales (i.e., if the model represents ecological time-scales). On these time-scales, we asume that adaptative responses are negligeable. We investigate over-all fitness with respect to temperature by calculating R0 for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here. R0 was calculated as

$$R0 = \int_0^\infty \phi(z(t,w_t,w^*))P(w_t,T)S_{0 \rightarrow t} dt, \text{, where}$$
$$S_{0 \rightarrow t} = \int_0^t \exp(-M(w_t))dt$$

\subsection{Trait based scenarios}

To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context. Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the P-strategy) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth M-strategy). This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}). In other words, this axis contrasts species of similar size (here $W_{\infty}\sim 30$cm) with defensive/sluggish versus active life-histories.

To implement this axis, we used the result that species with a more
active, production oriented life-history (e.g., predatory pelagic
fish) have a higher standard metabolism and lower weight scaling of
metabolic costs
(\cite{priede_metabolic_1985,killen_intraspecific_2010}). We assumed
that higher standard metabolism is due to increased digestive capacity
(i.e., is used for gut maintenance), though high muscle mass and a
larger heart will also contribute to higher standard metabolism in
active species (\cite{priede_metabolic_1985}). In practice, we assumed
that approximately 50\% of the standard metabolic cost is due to gut
maintenance, such that a doubling of the maximum ingestion leads to a
50\% increase in standard metabolic cost (i.e., $\Delta_k/\Delta_h=0.5$). We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M^{M-strat}(w) = (0.1+6\tau) w^{q-1}$ and $M^{M-strat}(w) = (1+\tau) w^{q-1}$). Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.

We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temeprature, where death may be induced by sudden failure to deliver oxgyen to vital organs). In practice, this was achieved as described above by setting the maximum oxygen deliver close to the lethal temperature (\ref{fig:O2_fig}).

\begin{table}
\caption{Parameters of the constrained activity model for two scenarios: M-strategy and P-strategy species. For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.}
\label{tab:parameters}
\begin{tabular}{llcc}
 \multirow{2}{*}{Description} &  \multirow{2}{*}{Symbol (unit)} & \multicolumn{2}{r}{Value} \\
 \cmidrule{3-4}
 & & M-strategy  & P-strategy \\

\hline
\addlinespace
\multicolumn{4}{c}{\textbf{Biomass Metabolism}} \\
Activity coefficient & $\delta$ & \multicolumn{2}{c}{4}    \\
Specific dynamic action & $\beta$ & \multicolumn{2}{c}{0.15} \\
Egestion and excretion & $\phi$ & \multicolumn{2}{c}{0.25}  \\
Coeff. for std.~metabolism  & $k$ ($g\cdot y^{-1}$)  & 1 &  1.5 \\
Exponent for std.~metabolism & $n$ & 0.88 & 0.75  \\

\addlinespace
\multicolumn{4}{c}{\textbf{Feeding ecology}}\\
Coeff. for Encountered food & $\gamma\Theta$ ($y^{-1}$)& \multicolumn{2}{c}{60} \\
Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
Coeff. for Maximum consumption rate & $h$ ($y^{-1}$) & 30 & 60  \\
Exponent for max.~consumption $\gamma$ & $q$ & \multicolumn{2}{c}{0.8} \\
Coeff. for constant mortality & $M$ ($g\cdot y^{-1}$) & 0.1  & 1  \\
Coeff. for activity related mortality & $\rho$ ($y^{-1}$) & 6 & 1\\
Exponent for mortality & $\nu$ & \multicolumn{2}{c}{0.2} \\

\addlinespace
\multicolumn{4}{c}{\textbf{Temperature}}\\
Reference temperature (°C) & $T_{ref}$ & \multicolumn{2}{c}{15} \\
Activation energy & $E_a$ & \multicolumn{2}{c}{0.52} \\
Temperature at maximum MOS & $T_{max}$ & \multicolumn{2}{c}{20/25}\\
Temperature range & $T^-_{lethal}$--$T^+_{lethal}$ & \multicolumn{2}{c}{5--26} \\

\addlinespace
\multicolumn{4}{c}{\textbf{Reaction norm}}\\

Slope & $b$ & \multicolumn{2}{c}{0}\\
Reaction & $c$ & \multicolumn{2}{c}{0.5} \\

\addlinespace
\multicolumn{4}{c}{\textbf{Oxygen budget}} \\
Critical $O_2$ & $P_{crit}$ ($mg\cdot L^{-1}$) & \multicolumn{2}{c}{2}\\
Dissolved $O_2$ at $0.5\times f_{max}(O_2)$  & $P50$ ($mg\cdot L^{-1}$) & \multicolumn{2}{c}{4} \\
Doming for $O_2$ supply & $\eta$ & \multicolumn{2}{c}{3/0.1}\\
Level of $O_2$ supply  & $\zeta$ ($g\cdot y^{-1}$) &  0.5 & 1\\

\hline
\end{tabular}
\end{table}

<< setup,echo=FALSE,include=F>>=
knitr::opts_chunk$set(echo = F, message = F,cache=T,autodep = T)

require(dplyr)
require(tidyr)
require(rlang)
require(cowplot)

source('model.R')

@

<<Scenarios>>=

int_m <- 500
int_t <- 500
int_temp <- 50

# Sluggish small
ss <- list(c=0.3,
           beta=0.15,
           delta=4,
           Ea=0.52, 
           gamma=60, 
           h=30, 
           k=1,
           lO=0.5, 
           m=10, 
           n=0.88, 
           O2crit=2, 
           omega=0.25, 
           p=0.8,
           P50=4.2, 
           phi=0.25, 
           q=0.8,
           shape=3,
           temp=seq(5,26,l=int_temp),
           Topt=20, 
           temp_ref=15,
           slope=0,
           tmax=20,
           tr=0.5,
           M=0.1,
           v=6,
           lm=int_m,
           nu=0.8-1,
           dt=int_t,
           min_m=-2,
           max_m= 3
)

# fast small0.8-1
fs <- ss
fs$lO <- 1
fs$k <- 1.5
fs$h <- 60
fs$v <- 1
fs$M <- 1
fs$nu<- 0.8-1
fs$n <- 0.75
fs$p <- 0.8
fs$q <- 0.8
fs$tmax <- 10

fl <- fs
fl$shape <- 0.1
fl$Topt <- 25

sl <- ss
sl$shape <- 0.1
sl$Topt <- 25

scs <- list(ss,fs,sl,fl)
scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
                       bind_rows(lapply(scs, plot_data_temp)))

scn <- rep(unique(scenarios$Scenario),2)
scz <- rep(unique(scenarios$O2lim),each=2)

@

\section{Results}

Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (Figure \ref{fig:activity}). This adjustment is especially pronounced in M-strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (Figure \ref{fig:size-act}). A similar increase in activity is observed for small P-strategy individuals (e.g., post-larval) for which even initial activity levels are very high (Figure \ref{fig:size-act}). For these individuals, the increasing activity and metabolic demands leads to an active metabolic rate that is close to their MMR. For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (Figure \ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature. However, larger P-strategy individuals are predicted to show a dome-shaped adjustment in activity levels at intermediate sizes, and a decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.

\begin{figure}
\centering
<<activity, fig.height=7,fig.width=6>>=

sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
  mutate(Activity = relevel(as.factor(Activity), "Realised"),
         Dispatch = paste(Scenario,O2lim))

cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')

lab1 <- as_labeller(c(`M strategy Rising` ='c',
                   `M strategy Domed`  ='a',
                   `P strategy Rising` ='g',
                   `P strategy Domed` = 'e'))

lab2 <- as_labeller(c(`M strategy Rising` ='d',
                   `M strategy Domed`  ='b',
                   `P strategy Rising` ='h',
                   `P strategy Domed` = 'f'))

ggsc <- ggplot(sc_act) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
  mutate(Dispatch = paste(Scenario,O2lim))

ggso <- sco %>%
  ggplot() + 
   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression(Oxygen~(mg.yr^-1)))

cowplot::plot_grid(ggsc,ggso,ncol=2)

@
\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c,e]) at increasing temperatures for a 10g fish, with corresponding oxygen demand (right column [b,d,f]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; a--d) and P-strategy (fast life-history; e--h). For each strategy, the first row (i.e., a--b; e--f) depicts a life-history with a dome-shaped MOS for increasing temperature, and the second row (i.e., c--d; g--h) corresponds to a species with continuously increasing MOS with temperature.}
\label{fig:activity}
\end{figure}

<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=

ssm <- ss
ssm$m <- 1.25

ssl <- ss
ssl$m <- 80

fsm <- fs
fsm$m <- 1.25

fsl <- fs
fsl$m <- 80

scss <- list(ssm,ss,ssl,fsm,fs,fsl)

scenarios_s <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('M strategy','P strategy'),each=3),each=int_temp)),
                                  Size = as.factor(rep(rep(c('Small','Medium','Large'),2),each=int_temp))),
                       bind_rows(lapply(scss, plot_data_temp)))

sc_acts <- gather(scenarios_s,Activity,value,Optimum, Limit,Realised) %>%
  mutate(Activity = relevel(as.factor(Activity), "Realised"),
         Dispatch = paste(Scenario,Size))

laba <- as_labeller(c(`M strategy Small` ='a',
                   `P strategy Small`  ='b',
                   `M strategy Medium` ='c',
                   `P strategy Medium` = 'd',
                   `M strategy Large` = 'e',
                   `P strategy Large` = 'f'
))

sc_acts$Dispatch <- factor(sc_acts$Dispatch,levels=unique(sc_acts$Dispatch)[order(unlist(laba(unique(sc_acts$Dispatch))))])

ggplot(sc_acts) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

@

Adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (Figure \ref{fig:feeding}). For M-strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy lead to an over-all decline in the ratio of $P$ to $M$. Available energy shows a dome-shaped response to temperature in M-strategists, and is maximised at relatively high temperatures. However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS. Growth efficiency ($P/f$) follows a near identical trend due to the relatively flat response in $f$.

For P-strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (Figure \ref{fig:feeding}). Again, growth efficiency peaks at relatively high temperatures, but in this scenario available energy $P$ peaks at much lower temperatures. Given the relatively flat mortality levels, the ratio of $P/M$ largely follows the trend in $P$.

<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g). Responses are shown for M- and P-strategy (top and bottom rows, respectively), for species with and without oxygen limitation (left and right columns, respectively). Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center'>>=

lab <- as_labeller(c(`M strategy Rising` ='b',
                   `M strategy Domed`  ='a',
                   `P strategy Rising` ='d',
                   `P strategy Domed` = 'c'))

sc_feed <- scenarios %>%
  #filter(!grepl('large',Scenario)) %>% 
  group_by(Scenario,O2lim) %>%
  mutate(Consumption=sc(Consumption),
         Efficiency=sc(Efficiency),
         Feeding=`Feeding level`,
         `Available Energy` = sc(`C for growth`),
         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
         Fitness = sc(Energy/M)) %>% 
  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
         Dispatch = paste(Scenario,O2lim))

ggplot(sc_feed) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
  theme_cowplot()+
  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4,1),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative rate')

@

Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (Figure \ref{fig:norms}). For all trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures. This can be explained by ontogenetic shifts in temperature optima for growth (Figure \ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals for either trait-scenario grow. For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.

<<calc-gouts>>=

gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)

@

<<norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}). Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size. Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=

t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
  y <- gouts[[x]][['t_growth']] 
  y$Scenario <- scn[x]
  y$O2lim <- scz[x]
  y$Dispatch <- paste(scn[x],scz[x])
  y}))

#browser()
norm <- t_growth %>% 
  mutate(Dispatch = paste(Scenario,O2lim)) %>%
  group_by(Dispatch,Temperature) %>%
  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])

ggplot() +
  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
  geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Length (cm)',
       x='Age  (years)')

@

<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=

sc_feed <- scenarios_s %>%
  #filter(!grepl('large',Scenario)) %>% 
  group_by(Scenario,Size) %>%
  mutate(Consumption=sc(Consumption),
         Efficiency=sc(Efficiency),
         Feeding=`Feeding level`,
         `Available Energy` = sc(`C for growth`),
         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
         Fitness = sc(Energy/M)) %>% 
  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
         Dispatch = paste(Scenario,Size))

sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])

ggplot(sc_feed) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
  theme_cowplot()+
  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4,1),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative rate')

@

Over-all fitness consequences mirror trends in the ratio of $P/M$ (Figure \ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\cite{sainmont_effective_2015}). With increasing temperatures, fitness declines at our basic parameter settings, in opposition to growth and aerobic scope. At low temperatures, fitness is limited by aerobic scope, with the magnitude determined by the extend of doming in aerobic scope. Note that this limitation through the aerobic scope appears at higher temperatures than apparent from Figure \ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (Figure \ref{fig:size-rates}). Fitness trends with temperature are strongly dependant on metabolic costs of activity (Figure \ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for M-strategy species, and moves the fitness optimum to higher temperatures for P-strategy species.

<<>>=
ssm <- ss
ssm$delta <- 2

ssl <- ss
ssl$delta <- 1

fsm <- fs
fsm$delta <- 2

fsl <- fs
fsl$delta <- 1

scsa <- list(ss,ssm,ssl,fs,fsm,fsl)
scna <- rep(unique(scenarios$Scenario),each=3)
scza <- rep(c('High','Medium','Low'),3)

gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)

@

<<fit, fig.cap='Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b; blue: $\\delta=4$; orange: $\\delta=2$ and green: $\\delta=1$).',fig.align='center',fig.height=6>>=

R0s <- bind_rows(lapply(1:length(gouts), function(x) {
  y <- data.frame(gouts[[x]]['R0'])
  y$Temperature <-gouts[[x]][['winfs']]$Temperature
  y$Scenario <- scn[x]
  y$O2lim <- scz[x]
  y$Dispatch <- paste(scn[x],scz[x])
  y}))

R0s <- R0s %>% group_by(Scenario) %>%
  mutate(R0 = R0/max(R0, na.rm=T))

f1 <- ggplot(R0s) + 
  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=O2lim,group=Dispatch)) +
  theme_cowplot()+
  theme(
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = '',
       y=expression('R0/R0'[max])) +
    theme(axis.title.x=element_blank(),
          axis.text.x = element_text(colour = NA))

R0s <- bind_rows(lapply(1:length(gouta), function(x) {
  y <- data.frame(gouta[[x]]['R0'])
  y$Temperature <-gouta[[x]][['winfs']]$Temperature
  y$Scenario <- scna[x]
  y$ActivityCost <- scza[x]
  y$Dispatch <- paste(scna[x],scza[x])
  y}))

R0s <- R0s %>% group_by(Dispatch) %>%
  mutate(R0 = R0/max(R0, na.rm=T))

f2 <- ggplot(R0s) + 
  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=ActivityCost,group=Dispatch)) +
  theme_cowplot()+
  theme(
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('R0/R0'[max]))

cowplot::plot_grid(f1,f2,ncol=1,labels = 'auto')

@

\section{Discussion}

In this study, we attempt to provide a general mechanistic basis for exploring thermal sensitivities of ectotherm organisms. Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\cite{pauly_sound_2017,lefevre_modelling_2017}). We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organismal response to temperature. The general model and its parameter values are also easily adjusted to reflect particular organisms or theories.

It has been argued that the OCLTT as a concept provides a basis to explain observed responses to climate change on the basis of oxygen limitation via the aerobic scope (\cite{portner_physiology_2008,portner_oxygen-and_2010}), and simple oxygen budgets have been used to predict metabolic constraints on organismal activity due to warming ocean temperatures (\cite{deutsch_climate_2015}). As a conceptual framework, however, the OCLTT is subject not only to semantic dispute but also criticism of its core concept of oxygen limitation (\cite{jutfelt_oxygen-and_2018,lefevre_are_2016}).

Our quantitative thermal impact model generalises existing eco-physiological models for particular species and stocks (\cite{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}), and allows to develop a more nuanced understanding of interactions between temperature, oxygen limitation and ecology for species with varying traits. In line with the conceptual framework of Fry's aerobic scope and the OCLTT, our model suggests that oxygen limitation can be a potentially important ecological driver, especially at extreme temperatures for species with declining MOSs in such temperature regimes. At the onset of this limitation, ecological parameters change drastically, and growth, mortality are strongly impacted. This limitation closely mimics limitations seen in wild fish (\cite{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite{armstrong_diel_2013,claireaux_physiology_1995}). Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages. For instance, oxygen limitation is a more severe constraint for small individuals (Figure \ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.

Variation in performance metrics away from temperature extremes, even if potentially correlated with aerobic scope (e.g., growth efficiency), are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour. Predictions from our model, in line with metabolic experiments and other physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\cite{lucas_utilization_1992,priede_metabolic_1985}). Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\cite{priede_natural_1977,priede_metabolic_1985}). Furthermore, as a limit for long-term performance, the MOS does not usually impose a limitation on short term energy demands, as fish can incur oxygen debt during swimming bursts during which the MOS is exceeded (\cite{brett_metabolic_1972,priede_metabolic_1985}). A logical conclusion is that the metabolic scope is only limiting to performance at extreme temperatures where MOS is low due to impaired oxygen delivery.

Importantly, fitness is predicted to decline with increasing temeprature in nearly all scenarios. This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures. In many species, both the aerobic scope and growth efficiency peak at relatively high temperatures within the potential thermal range, yet species are generally found at temperatures lower than these optima (\cite{magnuson_thermal_1997, claireaux_influence_2000}). This apparent paradox can be explained by an opposing trend in fitness: fitness is predicted to decline with increasing temeprature in nearly all scenarios, and leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures. The decline in fitness is caused by a decline in available energy with temperature, and a constant or increasing mortality rate. Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\cite{claireaux_influence_2000, magnuson_thermal_1997}). However, in relatively homogeneous habitats such as marine ecosystems, for example, the simple negative relationship between growth and fitness across the temperature range provides a parsimonious explanation for this apparent paradox.

Our model prediction of declining fitness with temperature is
particularly sensitive to activity costs, with low activity costs
leading to increased fitness at warmer temperatures. Our
base-parametrisation is based on the assumption that the fractional
aerobic scope reflects the cost of maximal activity (i.e., cost of
$\tau=1$) relative to standard metabolism. The fractional scope varies
widely around an average of $\delta \approx 4$ (\cite[e.g.,
][]{killen_ecological_2016}), however, this approximation may not
reflect actual activity cost as swimming at MMR in fast predatory fish
is far more efficient than swimming of sluggish fish, such as flatfish
(\cite{priede_metabolic_1985}). Such an efficiency gain may occur as a result of more efficient form or physiology, or simply by reduced drag at large size (e.g., whale-sharks), and may be a key requirement to the viability of active pelagic predatory fish in tropical waters.

Our prediction of constantly decreasing fitness with temperature, especially for relatively inactive species (M-strategists), contrasts with a previous species-specific eco-physiological model for cod that includes similar constraints to our model (\cite{holt_climate_2014,holt_climate_2015}), and which predicted relatively high fitness at high temperatures. Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, however the product of $\delta*\tau$ is on the same order of magnitude in both models. Differences may also be due to key assumptions about time-scales in the model --- we assume an evolutionarily fixed maturation reaction norm that drives relative growth and reproductive output across temperatures. In other words, we explicitly model species responses on ecological time-scales. Models of Holt \& Joergensen have assumed that adaption of reproductive investment is instantaneous with changing temperatures --- species display an evolutionarily optimal maturation-reaction at any temperature (\cite{holt_climate_2014,holt_climate_2015}). This, however, would require foresight about future environmental conditions and related reproductive output. In practice this optimisation occurs through selection, and we suggest that our "short-sighted" optimisation of activity coupled with a evolutionarily stable maturation-reaction norm provides a more explicit separation of evolutionary and ecological time-scales.

That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\cite{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}). Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\cite{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (M-strategy) life-history. Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$). This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\cite{priede_metabolic_1985}).

Optimal activity is predicted to increase with temperature in all but one of our simulations. This prediction is confirmed by many observations in experimental and field conditions for both larval and adult fish (\cite{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}). This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses. Only large individuals of the simulated P-strategy species will optimally decrease activity as a result of increased temperature. In this case, additional activity will lead to comparatively small gains from feeding relative to the cost of activity and SDA, owing to the non-linearity of the functional response.

Taken together, the physiological processes and optimisation described in our model provides a mechanistic underpinning for observations about changes of ecological rates, such as
increasing or dome-shaped consumption or attack-rates with temperature
(\cite{biro_mechanisms_2007,englund_temperature_2011,rall_universal_2012}). Depending on the
strength of oxygen limitation and the development of the optimal
activity level over the range of temperatures considered, attack rates
and feeding rates may appear to be steadily increasing via increased
optimal activity, or dome-shaped from oxygen limitation or dome-shaped
optimal activity. Thus, rather than assuming \emph{ad hoc} changes in ecological rates in response to temperature that may not be transferable between species and traits, the change in these rates may be mechanistically described in terms of optimal ecological adjustments to physiological constraints.

The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\cite{cheung_shrinking_2013, pauly_sound_2017}). We suggest that the general trait-based approach presented here provides a parsimonious compromise between overly-simplistic approximations that may provide misleading predictions about future ecosystems (\cite{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\cite{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}). In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT. Predictions from the OCLTT are both contributing to patterns in fitness and ecological rates shown here, but are also only part of the picture, and we suggest that future improvements of predictive frameworks should center on model critisism and improvements, and leave behind semantic discussions about conceptual constructs that are difficult to explicitly link to data.

\end{spacing}

\printbibliography

\appendix

\section{Specification of temperature dependent oxygen availibility}

The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR). Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^max_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\cite{priede_metabolic_1985}). We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR. We assume that oxygen supply is temperature dependent and we follows a flexible dome-shaped function (\cite{gnauck2013freshwater, lefrancois_influence_2003}):

\begin{align}
f_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{crit})\log(0.5)/(P50-P_{crit}})\right(,\\
\lambda(T)&=\zeta(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}})^\eta \times \exp(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}),
\end{align}

Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term describes the saturation dependence on ambient $O_2$ at temeprature $T$ ($O_2(T)$). At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}). We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{crit}$ is the ambient concentaration at which oxgygen supply ceases. Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentaration at 5\degree C. To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (Figure \ref{fig:O2_fig}). Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature.

\input{O2_fig}

\section{Maturation-reaction norm}

<<MRN, fig.cap='Proportion of energy allocated to reproduction, as a function of age (a) and size (b). With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.',fig.align='center',fig.height=6>>=

lam <- gouts[[1]]$t_growth

mr1 <- ggplot(lam) + 
  geom_line(aes(x=t, y=allocs,col=Temperature,group=as.factor(Temperature))) +
  #geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Proportion',
       x='Age  (years)')

mr2 <- ggplot(lam) + 
  geom_line(aes(x=t_length, y=allocs,col=Temperature,group=as.factor(Temperature))) +
  #geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Proportion',
       x='Size (cm)')

cowplot::plot_grid(mr1,mr2,ncol=1,labels = 'auto')

@

\end{document}

### 2018-02-05 draft_model_only.tex
draft paper!!

--- 2018-02-05 draft_model_only.Rnw
@@
-\documentclass[a4paper, toc=index,abstract=true]{scrartcl}
+\documentclass[a4paper, toc=index,abstract=true]{scrartcl}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage{gensymb}
@@
         Danish Technical University, Lyngby, Denmark}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-<< setup,echo=FALSE,include=F>>=
-knitr::opts_chunk$set(echo = F, message = F,cache=T,autodep = T)
-
-require(dplyr)
-require(tidyr)
-require(rlang)
-require(cowplot)
-
-source('model.R')
-
-@
-
-<<Scenarios>>=
-
-int_m <- 500
-int_t <- 500
-int_temp <- 50
-
-# Sluggish small
-ss <- list(c=0.3,
-           beta=0.15,
-           delta=4,
-           Ea=0.52, 
-           gamma=60, 
-           h=30, 
-           k=1,
-           lO=0.5, 
-           m=10, 
-           n=0.88, 
-           O2crit=2, 
-           omega=0.25, 
-           p=0.8,
-           P50=4.2, 
-           phi=0.25, 
-           q=0.8,
-           shape=3,
-           temp=seq(5,26,l=int_temp),
-           Topt=20, 
-           temp_ref=15,
-           slope=0,
-           tmax=20,
-           tr=0.5,
-           M=0.1,
-           v=6,
-           lm=int_m,
-           nu=0.8-1,
-           dt=int_t,
-           min_m=-2,
-           max_m= 3
-)
-
-# fast small0.8-1
-fs <- ss
-fs$lO <- 1
-fs$k <- 1.5
-fs$h <- 60
-fs$v <- 1
-fs$M <- 1
-fs$nu<- 0.8-1
-fs$n <- 0.75
-fs$p <- 0.8
-fs$q <- 0.8
-fs$tmax <- 10
-
-fl <- fs
-fl$shape <- 0.1
-fl$Topt <- 25
-
-sl <- ss
-sl$shape <- 0.1
-sl$Topt <- 25
-
-scs <- list(ss,fs,sl,fl)
-scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
-                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
-                       bind_rows(lapply(scs, plot_data_temp)))
-
-scn <- rep(unique(scenarios$Scenario),2)
-scz <- rep(unique(scenarios$O2lim),each=2)
-
-@
-
 \section{Results}
@@
 \centering
-<<activity, fig.height=7,fig.width=6>>=
 
-sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,O2lim))
+\includegraphics[width=\maxwidth]{images/activity-1}
 
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
-
-lab1 <- as_labeller(c(`M strategy Rising` ='c',
-                   `M strategy Domed`  ='a',
-                   `P strategy Rising` ='g',
-                   `P strategy Domed` = 'e'))
-
-lab2 <- as_labeller(c(`M strategy Rising` ='d',
-                   `M strategy Domed`  ='b',
-                   `P strategy Rising` ='h',
-                   `P strategy Domed` = 'f'))
-
-ggsc <- ggplot(sc_act) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols, guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
-  mutate(Dispatch = paste(Scenario,O2lim))
-
-ggso <- sco %>%
-  ggplot() + 
-   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols, guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression(Oxygen~(mg.yr^-1)))
-
-cowplot::plot_grid(ggsc,ggso,ncol=2)
-
-@
 \caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c,e]) at increasing temperatures for a 10g fish, with corresponding oxygen demand (right column [b,d,f]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; a--d) and P-strategy (fast life-history; e--h).
@@
 
-<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+\begin{figure}
 
-ssm <- ss
-ssm$m <- 1.25
+{\centering \includegraphics[width=\maxwidth]{images/size-act-1}
 
-ssl <- ss
-ssl$m <- 80
+}
 
-fsm <- fs
-fsm$m <- 1.25
-
-fsl <- fs
-fsl$m <- 80
-
-scss <- list(ssm,ss,ssl,fsm,fs,fsl)
-
-scenarios_s <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('M strategy','P strategy'),each=3),each=int_temp)),
-                                  Size = as.factor(rep(rep(c('Small','Medium','Large'),2),each=int_temp))),
-                       bind_rows(lapply(scss, plot_data_temp)))
-
-sc_acts <- gather(scenarios_s,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,Size))
-
-laba <- as_labeller(c(`M strategy Small` ='a',
-                   `P strategy Small`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy Large` = 'e',
-                   `P strategy Large` = 'f'
-))
-
-sc_acts$Dispatch <- factor(sc_acts$Dispatch,levels=unique(sc_acts$Dispatch)[order(unlist(laba(unique(sc_acts$Dispatch))))])
-
-ggplot(sc_acts) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols, guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-@
+\caption[Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g]{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.}\label{fig:size-act}
+\end{figure}
 
@@
 
-<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g).
+\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{images/feeding-1}
+
+}
+
+\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g)]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g).
 Responses are shown for M- and P-strategy (top and bottom rows, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center'>>=
-
-lab <- as_labeller(c(`M strategy Rising` ='b',
-                   `M strategy Domed`  ='a',
-                   `P strategy Rising` ='d',
-                   `P strategy Domed` = 'c'))
-
-sc_feed <- scenarios %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,O2lim) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,O2lim))
-
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
-
-@
+Energy and fitness are plotted relative to maximum over all temperatures.}\label{fig:feeding}
+\end{figure}
 
@@
 
-<<calc-gouts>>=
+\begin{figure}
 
-gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
+{\centering \includegraphics[width=\maxwidth]{images/norms-1}
 
-@
+}
 
-<<norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}).
+\caption[On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\cite{marty_impact_2011})]{On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\cite{marty_impact_2011}).
 Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.}\label{fig:norms}
+\end{figure}
 
-t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
-  y}))
+\begin{figure}
 
-#browser()
-norm <- t_growth %>% 
-  mutate(Dispatch = paste(Scenario,O2lim)) %>%
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
+{\centering \includegraphics[width=\maxwidth]{images/size-rates-1}
 
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
+}
 
-@
-
-<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
-
-sc_feed <- scenarios_s %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,Size) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,Size))
-
-sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])
-
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
-
-@
+\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.}\label{fig:size-rates}
+\end{figure}
 
@@
 
-<<>>=
-ssm <- ss
-ssm$delta <- 2
+\begin{figure}
 
-ssl <- ss
-ssl$delta <- 1
+{\centering \includegraphics[width=\maxwidth]{images/fit-1}
 
-fsm <- fs
-fsm$delta <- 2
+}
 
-fsl <- fs
-fsl$delta <- 1
-
-scsa <- list(ss,ssm,ssl,fs,fsm,fsl)
-scna <- rep(unique(scenarios$Scenario),each=3)
-scza <- rep(c('High','Medium','Low'),3)
-
-gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
-
-@
-
-<<fit, fig.cap='Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b; blue: $\\delta=4$; orange: $\\delta=2$ and green: $\\delta=1$).',fig.align='center',fig.height=6>>=
-
-R0s <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- data.frame(gouts[[x]]['R0'])
-  y$Temperature <-gouts[[x]][['winfs']]$Temperature
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
-  y}))
-
-R0s <- R0s %>% group_by(Scenario) %>%
-  mutate(R0 = R0/max(R0, na.rm=T))
-
-f1 <- ggplot(R0s) + 
-  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=O2lim,group=Dispatch)) +
-  theme_cowplot()+
-  theme(
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = '',
-       y=expression('R0/R0'[max])) +
-    theme(axis.title.x=element_blank(),
-          axis.text.x = element_text(colour = NA))
-
-R0s <- bind_rows(lapply(1:length(gouta), function(x) {
-  y <- data.frame(gouta[[x]]['R0'])
-  y$Temperature <-gouta[[x]][['winfs']]$Temperature
-  y$Scenario <- scna[x]
-  y$ActivityCost <- scza[x]
-  y$Dispatch <- paste(scna[x],scza[x])
-  y}))
-
-R0s <- R0s %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T))
-
-f2 <- ggplot(R0s) + 
-  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=ActivityCost,group=Dispatch)) +
-  theme_cowplot()+
-  theme(
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('R0/R0'[max]))
-
-cowplot::plot_grid(f1,f2,ncol=1,labels = 'auto')
-
-@
+\caption[Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b]{Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b; blue: $\delta=4$; orange: $\delta=2$ and green: $\delta=1$).}\label{fig:fit}
+\end{figure}
 
@@
 
-<<MRN, fig.cap='Proportion of energy allocated to reproduction, as a function of age (a) and size (b).
-With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.',fig.align='center',fig.height=6>>=
+\begin{figure}
 
-lam <- gouts[[1]]$t_growth
+{\centering \includegraphics[width=\maxwidth]{images/MRN-1}
 
-mr1 <- ggplot(lam) + 
-  geom_line(aes(x=t, y=allocs,col=Temperature,group=as.factor(Temperature))) +
-  #geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Proportion',
-       x='Age  (years)')
+}
 
-mr2 <- ggplot(lam) + 
-  geom_line(aes(x=t_length, y=allocs,col=Temperature,group=as.factor(Temperature))) +
-  #geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Proportion',
-       x='Size (cm)')
-
-cowplot::plot_grid(mr1,mr2,ncol=1,labels = 'auto')
-
-@
+\caption[Proportion of energy allocated to reproduction, as a function of age (a) and size (b)]{Proportion of energy allocated to reproduction, as a function of age (a) and size (b).
+With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.}\label{fig:MRN}
+\end{figure}
 

### 2018-02-05 build.sh

@@ -5,4 +5,4 @@ set -ex
 #Rscript -e 'install.packages("purrr",repo="http://cloud.r-project.org/")'
 make
 
-cp draft.pdf /output/
+cp *.pdf /output/

### 2018-02-05 model.R

@@ -98,12 +98,12 @@ plot_data_temp <- function(v){
   
   
   #browser()
-  scope <- f*v$m-model_frame$Metabolism*v$omega
+  scope <- f*v$m-model_frame$std*v$omega
   scope[scope<0.0001] <- 0
   #browser()
   
   
-  
+  #browser()
   bind_cols(model_frame,
             data_frame(
               Temperature=v$temp,
@@ -112,9 +112,9 @@ plot_data_temp <- function(v){
               M = (tau_max*v$v+v$M)*v$m^v$nu,
               Optimum = sapply(sapply(tau,max,0),min,1),
               Scope=ifelse(scope<0.0001,0,scope),
-              `Max Metabolism` = f*v$m,
-              `Active Metabolism` = model_frame$Metabolism*v$omega,
-              `Std Metabolism` = model_frame$Std*v$omega,
+              `Max` = f*v$m,
+              `Active` = model_frame$Met*v$omega,
+              `Std` = model_frame$std*v$omega,
               Viable = as.numeric(tau_max>0.0001 & model_frame[['C for growth']]>0.0001))
   )
   
@@ -177,6 +177,7 @@ plot_data_growth_tO2 <- function(v){
   
   list(winfs=winfs,
        growth=mout$growth,
+       R0=mout$R0s,
        g_growth=mouts$g_growth,
        t_growth=mouts$t_growth)
   
@@ -307,8 +308,8 @@ model_out <- function(tau_max,
              `C for growth` = e, 
              Efficiency = efficiency, 
              `Predation rate`=predation_rate, 
-             Metabolism = met,
-             Std = k*tc*m^n)
+             Met = met,
+             std = k*tc*m^n)
 }
 
 model_out_growth <- function(temp,
@@ -419,7 +420,7 @@ model_out_growth <- function(temp,
   
   
   
-  list(winfs=winfs, growth=growth)
+  list(winfs=winfs, growth=growth, R0s  = R0[,which.min(abs(winfs$Temperature-v$temp_ref)),dt])
   
 }
 

### 2018-02-05 run.sh

@@ -7,4 +7,4 @@ set -ex
 #docker push docker.dragonfly.co.nz/adaptive_activity
 
 docker run --rm  -v $PWD:/work -w /work \
-  docker.dragonfly.co.nz/dragonverse-17.04:2017-06-28 ./build.sh
+  docker.dragonfly.co.nz/dragonverse-17.04 ./build.sh

### 2018-02-05 build.sh
remove pesky .tex

@@ -3,6 +3,6 @@
 set -ex
 
 #Rscript -e 'install.packages("purrr",repo="http://cloud.r-project.org/")'
-make
+make -B
 
 cp *.pdf /output/

### 2018-03-20 draft_model_only.Rnw
Feb 5th draft

@@
 
-ggsc <- ggplot(sc_act) + 
+ggsc <- ggplot(sc_act %>% filter(Dispatch=='M strategy Domed')) + 
   geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
   theme_cowplot()+
-  scale_color_manual(values = cols, guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
+  scale_color_manual(values = cols)+
+  scale_linetype()+
+  #facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-ggso <- sco %>%
+ggso <- sco  %>% filter(Dispatch=='M strategy Domed') %>%
   ggplot() + 
@@
   theme_cowplot()+
-  scale_color_manual(values = cols, guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
+  scale_color_manual(values = cols)+
+  scale_linetype()+
+  #facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-ggplot(sc_acts) + 
+ggplot(sc_acts %>% filter(Dispatch=='P strategy Large')) + 
   geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
   theme_cowplot()+
-  scale_color_manual(values = cols, guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
+  scale_color_manual(values = cols)+
+  scale_linetype()+
+  #facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-ggplot(sc_feed) + 
+ggplot(sc_feed%>% filter(Dispatch=='M strategy Domed')) + 
   geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
   theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
+  #facet_wrap(~Dispatch,labeller = lab,ncol=2)+
   theme(strip.text = element_text(hjust = 0),
@@
         plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
+  scale_linetype_manual(values=c(1:4,1))+
+  scale_color_manual(values = cols)+
   labs(x = expression("Mean temperature " ( degree*C)),
@@
 
-gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
+gouts <- parallel::mclapply(scs[2],plot_data_growth_tO2,mc.cores = 2)
 
@@
   geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
+  #geom_point(aes(x=ts, y=m),data=norm) +
   # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
@@
   theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
+  #facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
   viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
@@
   scale_color_manual(values = cols,guide='none')+
-  labs(x = '',
-       y=expression('R0/R0'[max])) +
-    theme(axis.title.x=element_blank(),
-          axis.text.x = element_text(colour = NA))
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression('R0/R0'[max]))
 

### 2018-03-20 draft_model_only.Rnw
add theory discussion in intro

@@
 We show that oxygen limitation is not necessary to explain performance curves that are correlated with metabolic scope.
-Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology.
+Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology (i.e., food aquisition and mortality).
 Furthermore, our model reveals that fitness trends with temperature likely oppose trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
@@
 
-There are few general concepts and models that can explain thermal performance and ecological responses to temperature.
+There is currently no accepted universal concept or general mechanistic model that explains thermal performance and ecological responses to temperature (\cite{lefevre_are_2016, jutfelt_oxygen-and_2018}).
+Two main theories are debated as potential general therories describing temeprature influences on ectotherms.
+The theory of Oxygen and Capacity Limitation of Temperature (OCLTT; \cite{portner_oxygen-and_2010}),  based on the general idea of oxygen limitation for major ecological processes (growth, fitness, etc; see below), provides a conceptual framework rather than a mechanistic theoretical framework, and its major assumptions have been called into question on numerous occasions (\cite[e.g., ][]{lefevre_are_2016, jutfelt_oxygen-and_2018}).
+The gill-oxygen limitation theory (GOLT) aims to provide a physiological justification for the use of a temperature and oxygen scaled version of the von Bertalanffi growth model as a mechanistic model of thermal performance.
+The validity of gill limitation of oxygen supply, as well as the ultimate limitation of growth by oxygen in all conditions, is strongly debated (\cite{brander_overconfidence_2013,pauly_sound_2017,lefevre_modelling_2017,lefevre_models_2017}).
+In addition, the von Bertalanffi growth model only encapsulates a highly abstract view of organism bio-energetics and ecology, with no reference to ecological rates such as food aquisition, mortality and reproduction.
+As such, it can only represent a very limited set of aspects of species ecology, and cannot on its own account for changes in ecological rates that are often observed with temperature (\cite{englund_temperature_2011,rall_universal_2012}).
+
 To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed changes of attack rates with temperature (\cite{englund_temperature_2011,rall_universal_2012}), from fundamental physiological processes.
 Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependant, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{vucic-pestic_warming_2011, guiet_effects_2016}).
-
-Although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups.
-A phenomenological description that assumes a general ecological temperature response thus leads to difficulties with extrapolation when observed ecological responses are heterogeneous across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
-In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011}).
-Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.
+However, although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups.
+Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology, and explicitly link physiological constraints and ecology.
 
@@
 
-This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
+This view was encapsulated in the OCLTT (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
 In some species, however, maximum metabolic rate increases steadily (\cite{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor at high temperatures.

### 2018-03-21 draft_model_only.Rnw
lots of changes in response to Ken's comments

@@
 
-Here, we propose a general quantitative size- and trait-based eco-physiological model to derive general predictions about temperature impacts on ectotherm physiology, performance and ecology.
-We describe simple size-dependent physiological processes within an ecological context, and, using a simple optimisation argument, show that observed ecological responses of different life-history strategies can be predicted on the basis of optimised bio-energetics under different temperatures.
+Here, we propose a mechanistic, quantitative size- and trait-based eco-physiological model to derive general predictions about temperature impacts on ectotherm physiology, performance and ecology.
+Our aim was to produce a model that is general --- a model that incorporates simple descriptions of general processes, but ignoring particularities that may apply to specific species and contexts.
+In other words, it is the model framework that is general, rather than the particular parameters and the responses they induce.
+We show that this simple framework can lead to rather different temperature responses that depend on traits, organism size and ecological factors such as food availibility and mortality.
 
@@
 
-where $f(w,T)$ is the feeding level ([0,1]) at weight $w$ and temperature $T$, determined by the fraction of time spent foraging (or proportion of maximum attack rate) $\tau$, consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h w^q$.
+where $f(w,T)$ is the feeding level ([0,1]) at weight $w$ and temperature $T$, determined by consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$), maximum consumption $h w^q$, and $\tau$, which can be interpreted as the proportion of time spent foraging (or proportion of maximum attack rate) or a multiplyer on a basal foraging speed, such that at $\tau=1$, foraging occurs at maximum speed.
 In the following, we will refer to $\tau$ as the activity fraction for sake of generality.
-Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}), is assumed to scale with temperature as $c_T = e^{E_a(T-T_0)/kTT_0}$.
+Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}), is assumed to scale with temperature according to the Arrhenius scaling $c_T = e^{E_a(T-T_0)/k \times T \times T_0}$.
 Available energy $P(w,T)$ is determined by supply ($S(w,T)$) from prey consumption ($f(w,T) h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
 Metabolic demands ($D(w,T)$) are those of standard metabolism ($k w^n$), as well as active metabolism, scaled in units of standard metabolism as $\delta k w$, with $\delta$ the factorial aerobic scope (FAS).
-The activity fraction $\tau$ determines the fraction of time that the active metabolism cost applies.
-Note that active metabolism scales directly with $w$, owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}).
+The activity fraction $\tau$ determines the proportion of total metabolic costs that are due to active metabolism.
+Note that we assume that active metabolism scales directly with $w$, owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}).
+In practice, the scaling may not be strictly isometric owing to reduced drag at larger size (\cite[e.g., ][]{ware_bioenergetics_1978}), as well as non-strictly isometric growth of muscle mass with weight.
+However, the precise exponents of standard and foraging metabolism only alter predictions quantitatively, but do not change the over-all results.
 
@@
 The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}).
-We used a slightly different definition here since our model is not probabilistic at the population level: we defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
+We defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
 The allocation was parametrised as
-$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
+$$\phi(z) = 1/(1+\exp(-(c*(w_t-w^*)))),$$$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
 $$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$  
@@
 We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past.
-Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm \ref{fig:MRN}).
+Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a slightly negative slope in the reaction norm \ref{fig:MRN}).
 The intercept of this reaction norm was found numerically by maximising fitness ($R0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was asumed fixed as temperatures change.
+
+As growth is also fundamentally driven by resource availibility, we contrast the growth reponse to temperature at the baseline level (Table \ref{tab:parameters}), with a 30\% reduction and increase in available resources.
 
@@
 This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
-In other words, this axis contrasts species of similar size (here $W_{\infty}\sim 30$cm) with defensive/sluggish versus active life-histories.
+In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm) with defensive/sluggish versus active life-histories.
 
@@
 maintenance, such that a doubling of the maximum ingestion leads to a
-50\% increase in standard metabolic cost (i.e., $\Delta_k/\Delta_h=0.5$).
+50\% increase in standard metabolic cost.
 We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M^{M-strat}(w) = (0.1+6\tau) w^{q-1}$ and $M^{M-strat}(w) = (1+\tau) w^{q-1}$).
 Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
+Together, these assumed trait differences lead to very different recological and bio-energetic responses of M- and P-strategists (Figure \ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for M-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to feeding level) at high activity levels.
+A slower increase in available energy and M with $tau$ for P-strategists leads to a higher $\tau_{\text{opt}}$.
 
 We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temeprature, where death may be induced by sudden failure to deliver oxgyen to vital organs).
-In practice, this was achieved as described above by setting the maximum oxygen deliver close to the lethal temperature (\ref{fig:O2_fig}).
+In practice, this was achieved as described above by setting the maximum oxygen deliver close to the lethal temperature (Figure \ref{fig:O2_fig}).
 
@@
 \caption{Parameters of the constrained activity model for two scenarios: M-strategy and P-strategy species.
-For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.}
+For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
+Values in brackets for $\\gamma$ are alternative resource availibility scenarios.}
 \label{tab:parameters}
@@
 \multicolumn{4}{c}{\textbf{Feeding ecology}}\\
-Coeff. for Encountered food & $\gamma\Theta$ ($y^{-1}$)& \multicolumn{2}{c}{60} \\
+Coeff. for Encountered food & $\gamma\Theta$ ($y^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
 Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
@@
 
-Slope & $b$ & \multicolumn{2}{c}{0}\\
+Slope &  & \multicolumn{2}{c}{0}\\
 Reaction & $c$ & \multicolumn{2}{c}{0.5} \\
@@
 source('model.R')
+cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
 
@@
 
-int_m <- 500
-int_t <- 500
-int_temp <- 50
+int_m <- 100
+int_t <- 100
+int_temp <- 30
 
@@
            n=0.88, 
+           o=1,
            O2crit=2, 
@@
            temp_ref=15,
-           slope=0,
+           slope=-0.5,
            tmax=20,
@@
 fs$n <- 0.75
+fs$o <- 1
 fs$p <- 0.8
@@
 scs <- list(ss,fs,sl,fl)
+
+baseline <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
+                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
+                       bind_rows(lapply(scs, get_model_out,seq(0.05,1,l=int_temp))))
+
 scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
@@
 A similar increase in activity is observed for small P-strategy individuals (e.g., post-larval) for which even initial activity levels are very high (Figure \ref{fig:size-act}).
-For these individuals, the increasing activity and metabolic demands leads to an active metabolic rate that is close to their MMR.
+For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
 For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (Figure \ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
+For species with a rising MOS with temperature, oxygen is not limiting (Figure \ref{fig:activitys}).
 However, larger P-strategy individuals are predicted to show a dome-shaped adjustment in activity levels at intermediate sizes, and a decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
+
+<<scenarios,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted as a function of changing activity at constant temperature ($T=15$\\degree C) for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
+Responses are shown for M- and P-strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
+Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center',fig.height=3,fig.width=6>>=
+
+lab <- as_labeller(c(`M strategy Domed`  ='a',
+                   `P strategy Domed` = 'b'))
+
+sc_bl <- baseline %>% filter(O2lim=='Domed') %>%
+  #filter(!grepl('large',Scenario)) %>% 
+  group_by(Scenario,O2lim) %>%
+  mutate(Consumption=sc(Consumption),
+         Efficiency=sc(Efficiency),
+         Feeding=`Feeding level`,
+         `Available Energy` = sc(`C for growth`),
+         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
+         Fitness = sc(Energy/M)) %>% 
+  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
+  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
+         Dispatch = paste(Scenario,O2lim))
+
+ggplot(sc_bl) + 
+  geom_line(aes(x=tau, y=value, linetype=Rate,col=Rate,group=Rate)) +
+  theme_cowplot()+
+  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
+  theme(strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_manual(values=c(1:4,1),guide='none')+
+  scale_color_manual(values = cols,guide='none')+
+   labs(x = expression('Activity ' (tau)),
+       y='Relative rate')
+
+@
 
@@
 \centering
-<<activity, fig.height=7,fig.width=6>>=
+<<activity, fig.height=4,fig.width=6>>=
 
@@
 
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
+lab1 <- as_labeller(c(`M strategy Domed`  ='a',
+                   `P strategy Domed` = 'c'))
 
-lab1 <- as_labeller(c(`M strategy Rising` ='c',
-                   `M strategy Domed`  ='a',
-                   `P strategy Rising` ='g',
-                   `P strategy Domed` = 'e'))
+lab2 <- as_labeller(c(`M strategy Domed`  ='b',
+                   `P strategy Domed` = 'd'))
 
-lab2 <- as_labeller(c(`M strategy Rising` ='d',
-                   `M strategy Domed`  ='b',
-                   `P strategy Rising` ='h',
-                   `P strategy Domed` = 'f'))
-
-ggsc <- ggplot(sc_act %>% filter(Dispatch=='M strategy Domed')) + 
+ggsc <- ggplot(sc_act %>% filter(O2lim=='Domed')) + 
   geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
   theme_cowplot()+
-  scale_color_manual(values = cols)+
-  scale_linetype()+
-  #facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
+  scale_color_manual(values = cols,guide='none')+
+  scale_linetype(guide='none')+
+  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-ggso <- sco  %>% filter(Dispatch=='M strategy Domed') %>%
+ggso <- sco %>% filter(O2lim=='Domed') %>%
   ggplot() + 
    geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols)+
-  scale_linetype()+
-  #facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
+  theme_cowplot() +
+  scale_color_manual(values = cols,guide='none')+
+  scale_linetype(guide='none')+
+  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
   theme(strip.text = element_text(hjust = 0),
@@
 @
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c,e]) at increasing temperatures for a 10g fish, with corresponding oxygen demand (right column [b,d,f]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; a--d) and P-strategy (fast life-history; e--h).
-For each strategy, the first row (i.e., a--b; e--f) depicts a life-history with a dome-shaped MOS for increasing temperature, and the second row (i.e., c--d; g--h) corresponds to a species with continuously increasing MOS with temperature.}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; candd).}
 \label{fig:activity}
@@
 
-<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
 
@@
 
-ggplot(sc_acts %>% filter(Dispatch=='P strategy Large')) + 
+ggplot(sc_acts) + 
   geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
   theme_cowplot()+
-  scale_color_manual(values = cols)+
-  scale_linetype()+
-  #facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
+  scale_color_manual(values = cols,guide='none')+
+  scale_linetype(guide='none')+
+  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-Adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (Figure \ref{fig:feeding}).
-For M-strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy lead to an over-all decline in the ratio of $P$ to $M$.
+Temeprature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (Figure \ref{fig:feeding}).
+For M-strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
 Available energy shows a dome-shaped response to temperature in M-strategists, and is maximised at relatively high temperatures.
@@
 
-<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g).
-Responses are shown for M- and P-strategy (top and bottom rows, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center'>>=
+<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
+Responses are shown for M- and P-strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
+Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center',fig.height=3,fig.width=6>>=
 
-lab <- as_labeller(c(`M strategy Rising` ='b',
-                   `M strategy Domed`  ='a',
-                   `P strategy Rising` ='d',
-                   `P strategy Domed` = 'c'))
+lab <- as_labeller(c(`M strategy Domed`  ='a',
+                   `P strategy Domed` = 'b'))
 
-sc_feed <- scenarios %>%
+sc_feed <- scenarios %>% filter(O2lim=='Domed') %>%
   #filter(!grepl('large',Scenario)) %>% 
@@
 
-ggplot(sc_feed%>% filter(Dispatch=='M strategy Domed')) + 
+ggplot(sc_feed) + 
   geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
   theme_cowplot()+
-  #facet_wrap(~Dispatch,labeller = lab,ncol=2)+
+  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
   theme(strip.text = element_text(hjust = 0),
@@
         plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1))+
-  scale_color_manual(values = cols)+
+  scale_linetype_manual(values=c(1:4,1),guide='none')+
+  scale_color_manual(values = cols,guide='none')+
   labs(x = expression("Mean temperature " ( degree*C)),
@@
 Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (Figure \ref{fig:norms}).
-For all trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures.
+For both trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures.
 This can be explained by ontogenetic shifts in temperature optima for growth (Figure \ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals for either trait-scenario grow.
 For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
+Resource availibility storngly modulates this growth response to temeprature: low resource availibility leads to strong differences in asymptotic size, whereas high food availibility leads to an almost inverted response
 
@@
 
-gouts <- parallel::mclapply(scs[2],plot_data_growth_tO2,mc.cores = 2)
+ssgl <- ss
+ssgl$gamma <- 40
+
+ssgh <- ss
+ssgh$gamma <- 80
+
+fsgl <- fs
+fsgl$gamma <- 40
+
+fsgh <- fs
+fsgh$gamma <- 80
+
+scsg <- list(ssgl,ss,ssgh,fsgl,fs,fsgh)
+
+mstar_ss <- plot_data_growth_tO2(ss)$mstar
+mstar_fs <- plot_data_growth_tO2(fs)$mstar
+
+goutss <- parallel::mclapply(list(ssgl,ss,ssgh),
+                             plot_data_growth_tO2,
+                             mstar=mstar_ss,
+                             mc.cores = 3)
+
+goutsf <- parallel::mclapply(list(fsgl,fs,fsgh),
+                             plot_data_growth_tO2,
+                             mstar=mstar_fs,
+                             mc.cores = 3)
+
+gouts <- c(goutss,goutsf)
 
@@
 <<norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}).
-Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Growth curves are shown for M- (left column [a,c,e]) and P-strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).',fig.align='center',fig.width=6>>=
+
+labla <- as_labeller(c(`M strategy Low` ='a',
+                   `P strategy Low`  ='b',
+                   `M strategy Medium` ='c',
+                   `P strategy Medium` = 'd',
+                   `M strategy High` = 'e',
+                   `P strategy High` = 'f'
+))
 
@@
   y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
+  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
+  y$Food<- rep(c('Low','Medium','High'),2)[x]
+  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
   y}))
+
+t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
 
@@
 norm <- t_growth %>% 
-  mutate(Dispatch = paste(Scenario,O2lim)) %>%
   group_by(Dispatch,Temperature) %>%
@@
   geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  #geom_point(aes(x=ts, y=m),data=norm) +
+  geom_point(aes(x=ts, y=m),data=norm) +
   # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
@@
   theme_cowplot()+
-  #facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
+  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
   viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
@@
        x='Age  (years)')
-
-@
-
-<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
-
-sc_feed <- scenarios_s %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,Size) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,Size))
-
-sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])
-
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
 
@@
 gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
-
+goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
 @
@@
 
-R0s <- bind_rows(lapply(1:length(gouts), function(x) {
+R0s <- bind_rows(lapply(1:length(goutr), function(x) {
   y <- data.frame(gouts[[x]]['R0'])
@@
 
-R0s <- R0s %>% group_by(Scenario) %>%
+R0s <- R0s %>% group_by(Dispatch) %>%
   mutate(R0 = R0/max(R0, na.rm=T))
@@
 
-cowplot::plot_grid(f1,f2,ncol=1,labels = 'auto')
+R0s <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- data.frame(gouts[[x]]['R0'])
+   y$Temperature <-gouts[[x]][['winfs']]$Temperature
+  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
+  y$Food<- rep(c('Low','Medium','High'),2)[x]
+  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
+  y}))
+
+R0s <- R0s %>% group_by(Dispatch) %>%
+  mutate(R0 = R0/max(R0, na.rm=T))
+
+f3 <- ggplot(R0s) + 
+  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=Food,group=Dispatch)) +
+  theme_cowplot()+
+  theme(
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_manual(values=c(1:4),guide='none')+
+  scale_color_manual(values = cols,guide='none')+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression('R0/R0'[max]))
+
+cowplot::plot_grid(f1,f2,f3,ncol=1,labels = 'auto')
 
@@
 
-lam <- gouts[[1]]$t_growth
+lam <- gouts[[2]]$t_growth
 
@@
 
+\section{Supplementary results}
+
+\begin{figure}
+\centering
+<<activitys, fig.height=4,fig.width=6>>=
+
+sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
+  mutate(Activity = relevel(as.factor(Activity), "Realised"),
+         Dispatch = paste(Scenario,O2lim))
+
+cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
+
+lab1 <- as_labeller(c(`M strategy Rising`  ='a',
+                   `P strategy Rising` = 'c'))
+
+lab2 <- as_labeller(c(`M strategy Rising`  ='b',
+                   `P strategy Rising` = 'd'))
+
+ggsc <- ggplot(sc_act %>% filter(O2lim=='Rising')) + 
+  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
+  theme_cowplot()+
+  scale_color_manual(values = cols,guide='none')+
+  scale_linetype(guide='none')+
+  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
+  theme(strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank()) + 
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression('Activity ' (tau)))
+
+sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
+  mutate(Dispatch = paste(Scenario,O2lim))
+
+ggso <- sco %>% filter(O2lim=='Rising') %>%
+  ggplot() + 
+   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
+  theme_cowplot() +
+  scale_color_manual(values = cols,guide='none')+
+  scale_linetype(guide='none')+
+  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
+  theme(strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank()) + 
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression(Oxygen~(mg.yr^-1)))
+
+cowplot::plot_grid(ggsc,ggso,ncol=2)
+
+@
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; candd).}
+\label{fig:activity-rising}
+\end{figure}
+
+<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+
+sc_feed <- scenarios_s %>%
+  #filter(!grepl('large',Scenario)) %>% 
+  group_by(Scenario,Size) %>%
+  mutate(Consumption=sc(Consumption),
+         Efficiency=sc(Efficiency),
+         Feeding=`Feeding level`,
+         `Available Energy` = sc(`C for growth`),
+         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
+         Fitness = sc(Energy/M)) %>% 
+  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
+  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
+         Dispatch = paste(Scenario,Size))
+
+sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])
+
+ggplot(sc_feed) + 
+  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
+  theme_cowplot()+
+  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
+  theme(strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_manual(values=c(1:4,1),guide='none')+
+  scale_color_manual(values = cols,guide='none')+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y='Relative rate')
+
+@
 \end{document}

### 2018-03-21 build.sh

@@ -3,6 +3,6 @@
 set -ex
 
 #Rscript -e 'install.packages("purrr",repo="http://cloud.r-project.org/")'
-make -B
+make
 
 cp *.pdf /output/

### 2018-03-21 model.R

@@ -60,6 +60,7 @@ plot_data_temp <- function(v){
                                p=v$p,
                                q=v$q,
                                n=v$n,
+                               o=v$o,
                                m=v$m)
   tau <- eval_tau_eq_temp(temp=v$temp,
                           temp_ref=v$temp_ref,
@@ -73,6 +74,7 @@ plot_data_temp <- function(v){
                           p=v$p,
                           q=v$q,
                           n=v$n,
+                          o=v$o,
                           m=v$m,
                           M=v$M,
                           v=v$v)
@@ -94,6 +96,7 @@ plot_data_temp <- function(v){
                            p=v$p,
                            q=v$q,
                            n=v$n,
+                           o=v$o,
                            m=v$m)
   
   
@@ -120,7 +123,7 @@ plot_data_temp <- function(v){
   
 }
 
-plot_data_growth_tO2 <- function(v){
+plot_data_growth_tO2 <- function(v,mstar=NULL){
   
   n_int <- length(v$temp)
   lm = seq(10^v$min_m,10^v$max_m,l=v$lm)
@@ -142,6 +145,7 @@ plot_data_growth_tO2 <- function(v){
                            p=v$p,
                            q=v$q,
                            n=v$n,
+                           o=v$o,
                            tmax = v$tmax,
                            slope=v$slope,
                            tr=v$tr,
@@ -155,6 +159,8 @@ plot_data_growth_tO2 <- function(v){
   
   #browser()
   
+  mstar = ifelse(!is.null(mstar),mstar, lw(lm[winfs$opt[which.min(abs(winfs$Temperature-v$temp_ref))]]))
+  
   mouts <- model_out_growth_check(temp=winfs$Temperature,
                                   temp_ref=v$temp_ref,
                                   Ea=v$Ea,
[…]

### 2018-03-21 draft_model_only.Rnw
add resource paragraph in discussion

@@
 Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology (i.e., food aquisition and mortality).
-Furthermore, our model reveals that fitness trends with temperature likely oppose trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
+We find that resource availibility strongly modulates growth and fitness repsonses to temperature, with individuals in low-resource environments showing increased growth sensitivity and stronger fitness gradients with temperature.
+Furthermore, our model reveals that fitness is often minimised a low temperatures.
+This trend opposes trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
 We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.
@@
 Our aim was to produce a model that is general --- a model that incorporates simple descriptions of general processes, but ignoring particularities that may apply to specific species and contexts.
+We focus here on fish for the parametrisation of our model, however, the framework is not limited to fish and may, with slight modifications, be suitable for most ectotherms.
 In other words, it is the model framework that is general, rather than the particular parameters and the responses they induce.
@@
 Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (Figure \ref{fig:norms}).
-For both trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures.
+For both trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures \ref{fig:norms02}).
 This can be explained by ontogenetic shifts in temperature optima for growth (Figure \ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals for either trait-scenario grow.
 For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
-Resource availibility storngly modulates this growth response to temeprature: low resource availibility leads to strong differences in asymptotic size, whereas high food availibility leads to an almost inverted response
+Resource availibility storngly modulates this growth response to temeprature: low resource availibility leads to strong differences in asymptotic size, whereas high food availibility leads to high growth and larger asymptitic length at high temperatures.
 
@@
 Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for M- (left column [a,c,e]) and P-strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).',fig.align='center',fig.width=6>>=
+Growth curves are shown for M- (left column [a,c,e]) and P-strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
 
@@
 Fitness trends with temperature are strongly dependant on metabolic costs of activity (Figure \ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for M-strategy species, and moves the fitness optimum to higher temperatures for P-strategy species.
+Similarly, changes in the growth reponse to temperature lead to changes in fitness optima, with higher optimum temperatures, especially for P-strategists, and a slower decline of fitness with temperature.
 
@@
 
+Resource availibility imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
+Changes in prey availibility thus influece the temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal acitivity level.
+In low-food environments, changing energetic demands with temeprature are not easily adjusted for, and any adjustment demands higher energic costs and mortality risk.
+This environment-driven change in costs of temperature adjustments leads to the strong modulation of the growth repsonse, as well as changing gradients in fitness with temperature in these environments.
+In particular, in low-food environments, asymptitic size is strongly reduced at high temperatures, whereas this is not necessarily the case in high-food environments.
+Increased growth and mortality changes at low temperatures lead to a more strongly domed fitness curve.
+
 Our model prediction of declining fitness with temperature is
@@
 Our prediction of constantly decreasing fitness with temperature, especially for relatively inactive species (M-strategists), contrasts with a previous species-specific eco-physiological model for cod that includes similar constraints to our model (\cite{holt_climate_2014,holt_climate_2015}), and which predicted relatively high fitness at high temperatures.
-Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, however the product of $\delta*\tau$ is on the same order of magnitude in both models.
+Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, the product of $\delta*\tau$ is on the same order of magnitude in both models.
 Differences may also be due to key assumptions about time-scales in the model --- we assume an evolutionarily fixed maturation reaction norm that drives relative growth and reproductive output across temperatures.
@@
 @
+
+<<norms02, fig.cap='Contrasting growth reponses at baseline resource availibility for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
+Growth curves are shown for M- (left column [a,c]) and P-strategists (right column [b,d]).
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=
+
+lab <- as_labeller(c(`M strategy Domed`  ='a',
+                   `P strategy Domed` = 'b',
+                   `M strategy Rising`  ='c',
+                   `P strategy Rising` = 'd'))
+
+t_growth <- bind_rows(lapply(1:length(goutr), function(x) {
+  y <- gouts[[x]][['t_growth']] 
+  y$Scenario <- scn[x]
+  y$O2lim <- scz[x]
+  y$Dispatch <- paste(scn[x],scz[x])
+  y}))
+
+#browser()
+norm <- t_growth %>% 
+  mutate(Dispatch = paste(Scenario,O2lim)) %>%
+  group_by(Dispatch,Temperature) %>%
+  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
+            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
+            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
+            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
+
+ggplot() +
+  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
+  geom_point(aes(x=ts, y=m),data=norm) +
+  #geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
+  #geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
+  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
+  theme_cowplot()+
+  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
+  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
+  theme(legend.text = element_text(size=8),
+        legend.title = element_text(size=9),
+        strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  coord_cartesian()+
+  labs(y = 'Length (cm)',
+       x='Age  (years)')
+
+@
+
 \end{document}

### 2018-03-22 draft.Rnw
draft march 22nd

@@
 cpG <- ggplot(wtfs) +
-  geom_line(aes(x=Temperature, y=length, col=Size,linetype=Scenario),alpha=0.7) +
+  geom_line(aes(x=Temperature, y=length, linetype=Scenario),alpha=0.7) +
   theme_cowplot()+
@@
         plot.background = element_blank(),)+
-  labs(x = '',
+  labs(x = expression("Mean temperature " ( degree*C)),
        y='Relative adult length')
@@
         plot.background = element_blank())+
-  labs(x = '',
+  labs(x = expression("Mean temperature " ( degree*C)),
        y=expression(S~response~y^-1))

### 2018-03-22 draft_model_only.Rnw
draft march 22nd

@@
 
-There is currently no accepted universal concept or general mechanistic model that explains thermal performance and ecological responses to temperature (\cite{lefevre_are_2016, jutfelt_oxygen-and_2018}).
-Two main theories are debated as potential general therories describing temeprature influences on ectotherms.
+There is currently no accepted universal concept or general mechanistic model that explains ectotherm thermal performance and ecological responses to temperature (\cite{lefevre_are_2016, jutfelt_oxygen-and_2018}).
+In fish, two main theories are debated as potential general therories describing temeprature influences on ectotherms.
 The theory of Oxygen and Capacity Limitation of Temperature (OCLTT; \cite{portner_oxygen-and_2010}),  based on the general idea of oxygen limitation for major ecological processes (growth, fitness, etc; see below), provides a conceptual framework rather than a mechanistic theoretical framework, and its major assumptions have been called into question on numerous occasions (\cite[e.g., ][]{lefevre_are_2016, jutfelt_oxygen-and_2018}).
@@
 Available energy $P(w,T)$ is determined by supply ($S(w,T)$) from prey consumption ($f(w,T) h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
-Metabolic demands ($D(w,T)$) are those of standard metabolism ($k w^n$), as well as active metabolism, scaled in units of standard metabolism as $\delta k w$, with $\delta$ the factorial aerobic scope (FAS).
+Metabolic demands ($D(w,T)$) are those of standard metabolism ($k w^n$), as well as active metabolism, scaled in units of standard metabolism as $\delta k w$, with $\delta$ determining the maginitude of activity cost relative to standard metabolic costs.
 The activity fraction $\tau$ determines the proportion of total metabolic costs that are due to active metabolism.
 Note that we assume that active metabolism scales directly with $w$, owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}).
-In practice, the scaling may not be strictly isometric owing to reduced drag at larger size (\cite[e.g., ][]{ware_bioenergetics_1978}), as well as non-strictly isometric growth of muscle mass with weight.
+In practice, the scaling may not be strictly isometric owing to reduced drag at larger size (\cite[e.g., ][]{ware_bioenergetics_1978}), as well as non-strictly isometric growth of muscle mass and other relevant factors with weight (\cite{killen_little_2007}).
 However, the precise exponents of standard and foraging metabolism only alter predictions quantitatively, but do not change the over-all results.
@@
 \multicolumn{4}{c}{\textbf{Biomass Metabolism}} \\
-Activity coefficient & $\delta$ & \multicolumn{2}{c}{4}    \\
+Activity coefficient & $\delta$ ($g^{n}$) & \multicolumn{2}{c}{4}    \\
 Specific dynamic action & $\beta$ & \multicolumn{2}{c}{0.15} \\
 Egestion and excretion & $\phi$ & \multicolumn{2}{c}{0.25}  \\
-Coeff. for std.~metabolism  & $k$ ($g\cdot y^{-1}$)  & 1 &  1.5 \\
+Coeff. for std.~metabolism  & $k$ ($g^{1-n}\cdot y^{-1}$)  & 1 &  1.5 \\
 Exponent for std.~metabolism & $n$ & 0.88 & 0.75  \\
@@
 \multicolumn{4}{c}{\textbf{Feeding ecology}}\\
-Coeff. for Encountered food & $\gamma\Theta$ ($y^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
+Coeff. for Encountered food & $\gamma\Theta$ ($g^{1-p} \cdot y^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
 Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
-Coeff. for Maximum consumption rate & $h$ ($y^{-1}$) & 30 & 60  \\
-Exponent for max.~consumption $\gamma$ & $q$ & \multicolumn{2}{c}{0.8} \\
+Coeff. for Maximum consumption rate & $h$ ($g^{1-q}\cdot y^{-1}$) & 30 & 60  \\
+Exponent for max.~consumption $h$ & $q$ & \multicolumn{2}{c}{0.8} \\
 Coeff. for constant mortality & $M$ ($g\cdot y^{-1}$) & 0.1  & 1  \\
@@
 
-mstar_ss <- plot_data_growth_tO2(ss)$mstar
-mstar_fs <- plot_data_growth_tO2(fs)$mstar
+#mstar_ss <- plot_data_growth_tO2(ss)$mstar
+#mstar_fs <- plot_data_growth_tO2(fs)$mstar
+
+mstar_ss <- 50
+mstar_fs <- 50
 
@@
 
-gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
-goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
+gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mstar=50,mc.cores = 3)
+goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mstar=50,mc.cores = 2)
 @
@@
 For instance, oxygen limitation is a more severe constraint for small individuals (Figure \ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
+Also, changes in environmental oxygen supply, if beyond an oganisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
 
@@
 Resource availibility imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
-Changes in prey availibility thus influece the temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal acitivity level.
-In low-food environments, changing energetic demands with temeprature are not easily adjusted for, and any adjustment demands higher energic costs and mortality risk.
+Changes in prey availibility thus influence individual temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal acitivity level.
+In low-food environments, changing energetic demands with temperature are not easily adjusted for, and any adjustment demands higher energic costs and mortality risk.
 This environment-driven change in costs of temperature adjustments leads to the strong modulation of the growth repsonse, as well as changing gradients in fitness with temperature in these environments.
-In particular, in low-food environments, asymptitic size is strongly reduced at high temperatures, whereas this is not necessarily the case in high-food environments.
-Increased growth and mortality changes at low temperatures lead to a more strongly domed fitness curve.
+In particular, in low-food environments, asymptotic size is strongly reduced at high temperatures, whereas this is not necessarily the case in high-food environments.
+Increased growth and mortality changes in such environments then combine to produce a more strongly domed fitness curve than in environemts where food supply is not limiting.
 
@@
 The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
-Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^max_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\cite{priede_metabolic_1985}).
+Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\cite{priede_metabolic_1985}).
 We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR.
-We assume that oxygen supply is temperature dependent and we follows a flexible dome-shaped function (\cite{gnauck2013freshwater, lefrancois_influence_2003}):
+We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\cite{gnauck2013freshwater, lefrancois_influence_2003}):
 
 \begin{align}
-f_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{crit})\log(0.5)/(P50-P_{crit}})\right(,\\
-\lambda(T)&=\zeta(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}})^\eta \times \exp(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}),
+f_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{crit})\log(0.5)/(P50-P_{crit})}\right),\\
+\lambda(T)&=\zeta\left(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right)^\eta \times \exp\left(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right),
 \end{align}

### 2018-04-19 draft_model_only.Rnw
updated

@@
 
-Increasing temperatures under climate change are thought to affect individual physiology of ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology.
-Although intuitively appealing, the driving mechanisms behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance.
+Increasing temperature under climate change is thought to affect physiology of ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology.
+Although intuitively appealing, the driving mechanism behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance.
 Whether or not oxygen limitations via the metabolic scope, or a lack thereof, have major ecological consequences remains a highly contested question.
@@
 This trend opposes trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
-We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.
+We suggest that this model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.
 
@@
 The allocation was parametrised as
-$$\phi(z) = 1/(1+\exp(-(c*(w_t-w^*)))),$$$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
+$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
 $$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$  
@@
 For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (Figure \ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
-For species with a rising MOS with temperature, oxygen is not limiting (Figure \ref{fig:activitys}).
+For species with a rising MOS with temperature, oxygen is not limiting (Figure \ref{fig:activity-rising}).
 However, larger P-strategy individuals are predicted to show a dome-shaped adjustment in activity levels at intermediate sizes, and a decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
@@
 
-#mstar_ss <- plot_data_growth_tO2(ss)$mstar
-#mstar_fs <- plot_data_growth_tO2(fs)$mstar
-
-mstar_ss <- 50
-mstar_fs <- 50
+mstar_ss <- plot_data_growth_tO2(ss)$mstar
+mstar_fs <- plot_data_growth_tO2(fs)$mstar
+
+#mstar_ss <- 50
+#mstar_fs <- 50
 
@@
 
-gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mstar=50,mc.cores = 3)
-goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mstar=50,mc.cores = 2)
+gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
+goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
 @
@@
 @
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; candd).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; c, d).}
 \label{fig:activity-rising}
@@
 
-<<norms02, fig.cap='Contrasting growth reponses at baseline resource availibility for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
-Growth curves are shown for M- (left column [a,c]) and P-strategists (right column [b,d]).
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=
+\begin{figure}
+\centering
+<<norms02, fig.align='center',fig.height=6>>=
 
@@
 @
+\caption{Contrasting growth reponses at baseline resource availibility for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
+Growth curves are shown for M- (left column [a,c]) and P-strategists (right column [b,d]).
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.}
+\label{fig:activity-rising}
+\end{figure}
 

### 2018-04-20 draft_model_only.Rnw
Updated first part of the methods section

--- 2018-03-21 draft_model_only.Rnw
@@
 We show that oxygen limitation is not necessary to explain performance curves that are correlated with metabolic scope.
-Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology (i.e., food aquisition and mortality).
-We find that resource availibility strongly modulates growth and fitness repsonses to temperature, with individuals in low-resource environments showing increased growth sensitivity and stronger fitness gradients with temperature.
-Furthermore, our model reveals that fitness is often minimised a low temperatures.
-This trend opposes trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
+Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology.
+Furthermore, our model reveals that fitness trends with temperature likely oppose trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
 We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.
@@
 
-There is currently no accepted universal concept or general mechanistic model that explains thermal performance and ecological responses to temperature (\cite{lefevre_are_2016, jutfelt_oxygen-and_2018}).
-Two main theories are debated as potential general therories describing temeprature influences on ectotherms.
-The theory of Oxygen and Capacity Limitation of Temperature (OCLTT; \cite{portner_oxygen-and_2010}),  based on the general idea of oxygen limitation for major ecological processes (growth, fitness, etc; see below), provides a conceptual framework rather than a mechanistic theoretical framework, and its major assumptions have been called into question on numerous occasions (\cite[e.g., ][]{lefevre_are_2016, jutfelt_oxygen-and_2018}).
-The gill-oxygen limitation theory (GOLT) aims to provide a physiological justification for the use of a temperature and oxygen scaled version of the von Bertalanffi growth model as a mechanistic model of thermal performance.
-The validity of gill limitation of oxygen supply, as well as the ultimate limitation of growth by oxygen in all conditions, is strongly debated (\cite{brander_overconfidence_2013,pauly_sound_2017,lefevre_modelling_2017,lefevre_models_2017}).
-In addition, the von Bertalanffi growth model only encapsulates a highly abstract view of organism bio-energetics and ecology, with no reference to ecological rates such as food aquisition, mortality and reproduction.
-As such, it can only represent a very limited set of aspects of species ecology, and cannot on its own account for changes in ecological rates that are often observed with temperature (\cite{englund_temperature_2011,rall_universal_2012}).
-
+There are few general concepts and models that can explain thermal performance and ecological responses to temperature.
 To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed changes of attack rates with temperature (\cite{englund_temperature_2011,rall_universal_2012}), from fundamental physiological processes.
 Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependant, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{vucic-pestic_warming_2011, guiet_effects_2016}).
-However, although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups.
-Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology, and explicitly link physiological constraints and ecology.
+
+Although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups.
+A phenomenological description that assumes a general ecological temperature response thus leads to difficulties with extrapolation when observed ecological responses are heterogeneous across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
+In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011}).
+Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.
 
@@
 
-This view was encapsulated in the OCLTT (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
+This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
 In some species, however, maximum metabolic rate increases steadily (\cite{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor at high temperatures.
@@
 
-Here, we propose a mechanistic, quantitative size- and trait-based eco-physiological model to derive general predictions about temperature impacts on ectotherm physiology, performance and ecology.
-Our aim was to produce a model that is general --- a model that incorporates simple descriptions of general processes, but ignoring particularities that may apply to specific species and contexts.
-We focus here on fish for the parametrisation of our model, however, the framework is not limited to fish and may, with slight modifications, be suitable for most ectotherms.
-In other words, it is the model framework that is general, rather than the particular parameters and the responses they induce.
-We show that this simple framework can lead to rather different temperature responses that depend on traits, organism size and ecological factors such as food availibility and mortality.
+Here, we propose a general quantitative size- and trait-based eco-physiological model to derive general predictions about temperature impacts on ectotherm physiology, performance and ecology.
+We describe simple size-dependent physiological processes within an ecological context, and, using a simple optimisation argument, show that observed ecological responses of different life-history strategies can be predicted on the basis of optimised bio-energetics under different temperatures.
 
@@
 Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets (\cite{holt_climate_2015,holt_climate_2014}).
-At a high level, we assume that animals will adapt activity levels to optimise available energy for growth and reproduction relative to mortality risk.
-Available energy is limited either by food capture, food processing capacity, or by available oxygen.
+We assume that animals will adapt activity levels to optimise available energy for growth and reproduction relative to mortality risk.
+Available energy is determined either by food capture, food processing capacity, or by available oxygen.
 We further assume that temperature acts directly on rates that are determined by enzymatic activity: digestive activity (via maximum consumption) and metabolic costs.
@@
 \subsection{Model description}
-
-The quantitative size- and trait-based thermal impact model lets ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy $P$ gain relative to natural mortality.
-Since both energy gain and loss are sensitive to temperature and oxygen limitations, both the activity level and the net energy gain will be subject to these environmental constraints.
+Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality.
+In the following, we refer to $\tau$ as the activity fraction for sake of generality.
+Since both energy gain and metabolic losses are sensitive to temperature and oxygen limitations, both the activity level and the net energy gain will be subject to these environmental constraints.
 Their interplay thus determines available energy for growth and reproduction.
 
-The model is written in terms of weight $w$ and oxygen balance equations at temperature $T$:
+Net energy gain $P$ (mass per time) is the difference between supply $S$ and metabolic demands $D$, each being functions of body weight $w$ and temperature $T$:
+\begin{align}
+P(w,T) &= S(w,T) - D(w,T) \\
+          &=(1-\beta-\phi)f(w,T) h c(T) w^q  - c(T) k w^n - \tau \delta c(T) k w  \\
+  \label{eq:P}
+\end{align}
+where the feeding level ($[0:1]$)is given by a Holling type II function response:
+\begin{align}
+  f(w,T) &= \frac{\tau \gamma\Theta w^{p} }{\tau \gamma\Theta w^{p} + h c(T) w^q} }, \label{eq:f} \\
+\end{align}
+where $h c(T) w^q$ is the maximum consumption rate.
+The corresponding function for oxygen is given in Appendix A.
+The feeding level ([0,1]) is determined by the fraction of time spent foraging $\tau$, foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
+The supply is discounted by the loss due to specific dynamic action  $\beta$ (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
 
+Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}, and the activity fraction \emph{(Important note: you cannot interpret $\delta$ as the factorial aerobic scope (FAS) when the two metabolisms scale with different exponents!.
+I therefore propose to rename the constant to $k_a$)}.
+
+Temperature scaling of all metabolic rates (standard and active metabolism and maximum consumption rate) is determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}) as $c(T) = e^{E_a(T-T_0)/(kTT_0)}$.
+
+The oxygen budget $P_{0_2}(w,T)$ (oxygen per time) follows a similar form to the mass budget:
 \begin{align}
-f(w,T) &= \frac{\tau }{\tau  + \frac{h c_T w^{q-p}}{\gamma\Theta} } \label{eq:f} \\
-P(w,T) &= S(w,T) - D(w,T) \\
-  &=(1-\beta-\phi)f(w,T) h c_T w^q  - c_T k w^n - \tau \delta c_T k w  \\
   P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
-        &= f_{O_2}(T)w^n - \omega \left( \beta f(w,T) h c_T w^q + c_T k w^n + \tau \delta c_T k w \right)
+        &= s_(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
 \end{align}
+Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.
+The oxygen supply scales with body weight as $w^n$ multiplied by a flexible dome-shaped function ($s(t)$) \emph{I've changed this away from $f$, because $f$ was used above for a function that is in the range 0:1, while this one has a unit} that can emulate both a dome-shaped MOS as well as MOS that increas continously up to a lethal temeprature (Figure \ref{fig:O2_fig}, Appendix A).
 
-where $f(w,T)$ is the feeding level ([0,1]) at weight $w$ and temperature $T$, determined by consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$), maximum consumption $h w^q$, and $\tau$, which can be interpreted as the proportion of time spent foraging (or proportion of maximum attack rate) or a multiplyer on a basal foraging speed, such that at $\tau=1$, foraging occurs at maximum speed.
-In the following, we will refer to $\tau$ as the activity fraction for sake of generality.
-Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}), is assumed to scale with temperature according to the Arrhenius scaling $c_T = e^{E_a(T-T_0)/k \times T \times T_0}$.
-Available energy $P(w,T)$ is determined by supply ($S(w,T)$) from prey consumption ($f(w,T) h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
-Metabolic demands ($D(w,T)$) are those of standard metabolism ($k w^n$), as well as active metabolism, scaled in units of standard metabolism as $\delta k w$, with $\delta$ the factorial aerobic scope (FAS).
-The activity fraction $\tau$ determines the proportion of total metabolic costs that are due to active metabolism.
-Note that we assume that active metabolism scales directly with $w$, owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}).
-In practice, the scaling may not be strictly isometric owing to reduced drag at larger size (\cite[e.g., ][]{ware_bioenergetics_1978}), as well as non-strictly isometric growth of muscle mass with weight.
-However, the precise exponents of standard and foraging metabolism only alter predictions quantitatively, but do not change the over-all results.
+Fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \cite{gilliam_habitat_1987}:
+\begin{equation}
+  \tau^* = \argmax_{\tau} \{ \frac{P(w,T)}{M(w)} \}.
+\end{equation}
+This optimisation represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for optimisation in stable environments (\cite{sainmont_effective_2015}).
+Mortality scales with activity fraction and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}):
+\begin{equation}
+  \label{eq:M}
+  M(w) = (\rho+\eta\tau) w^{q-1},
+\end{equation}
+$\rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism.
+Activity is limited by available oxygen, such that $P_{O_2}$ is not allowed to be negative \emph{Is that a correct interpretation?}.
 
-The oxygen budget $P_{0_2}(w,T)$, determines physiological limits to aerobic activity.
-Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy, growth and reproduction - $\beta f h c_T w^q$) and ``active metabolism", the sum of standard (or resting) metabolism ($c_T k w^n$) and the metabolic costs of foraging ($\tau \delta c_T k w$), with $\omega$ determining amount of oxygen required per unit of metabolised feed.
-Metabolic scope is the difference between $S_{O_2}(w,T)=f_{O_2}(T)w^n$, the maximum amount of oxygen supplied at temperature $T$, and oxygen demand due to standard metabolism ($\omega c_T k w^n$).
-We assume that the maximum oxygen supply (MOS), follows a flexible dome-shaped function that can emulate both a dome-shaped MOS as well as MOS that increas continously up to a lethal temeprature (Figure \ref{fig:O2_fig}, Appendix A).
-
-We assumed that fish will adjust their activity level to maximise $F$: maximize available energy relative to mortality: $\tau_{\text{opt}}$ = $\text{argmax}_{\tau_{w,T}}F(\tau_{w,T})$ = $\text{argmax}_{\tau_{w,T}}P(\tau_{w,T})/M(\tau_{w,T})$.
-This optimisation is also known as Gilliam's rule (\cite{gilliam_habitat_1987}) and represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for simulating opmisation in changing environments (\cite{sainmont_effective_2015}).
-We further assumed here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M(w) = (\rho+\eta\tau) w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism.
-$M$ is then the effective mortality at realised levels of activity $\tau$ at weight $w$.
-
-We assumed that the metabolic scope dictates the upper limit of this activity, such that at $\tau_{\text{max}}$, oxygen demand $D_{0_2}$ equals total supply $S_{0_2}$.
+%We assumed that the metabolic scope dictates the upper limit of this activity, such that at $\tau_{\text{max}}$, oxygen demand $D_{0_2}$ equals total supply $S_{0_2}$.
 Both temperature and oxygen will influence $\tau$, such that at a given temperature and oxygen concentration, $\tau_{w,T,O_2} = \text{min}\left( \tau_{\text{opt}},\tau_{\text{max}} \right)$, meaning we assumed that animals will adapt their effort to optimise fitness $F$ given temperature and oxygen constraints.
@@
 The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}).
-We defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
+We used a slightly different definition here since our model is not probabilistic at the population level: we defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
 The allocation was parametrised as
-$$\phi(z) = 1/(1+\exp(-(c*(w_t-w^*)))),$$$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
+$$\phi(z) = 1/(1+\exp(-(c z))) \text{, where }$$
 $$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$ 
@@
 We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past.
-Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a slightly negative slope in the reaction norm \ref{fig:MRN}).
+Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm \ref{fig:MRN}).
 The intercept of this reaction norm was found numerically by maximising fitness ($R0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was asumed fixed as temperatures change.
-
-As growth is also fundamentally driven by resource availibility, we contrast the growth reponse to temperature at the baseline level (Table \ref{tab:parameters}), with a 30\% reduction and increase in available resources.
 
@@
 This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
-In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm) with defensive/sluggish versus active life-histories.
+In other words, this axis contrasts species of similar size (here $W_{\infty}\sim 30$cm) with defensive/sluggish versus active life-histories.
 
@@
 maintenance, such that a doubling of the maximum ingestion leads to a
-50\% increase in standard metabolic cost.
+50\% increase in standard metabolic cost (i.e., $\Delta_k/\Delta_h=0.5$).
 We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M^{M-strat}(w) = (0.1+6\tau) w^{q-1}$ and $M^{M-strat}(w) = (1+\tau) w^{q-1}$).
 Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
-Together, these assumed trait differences lead to very different recological and bio-energetic responses of M- and P-strategists (Figure \ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for M-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to feeding level) at high activity levels.
-A slower increase in available energy and M with $tau$ for P-strategists leads to a higher $\tau_{\text{opt}}$.
 
 We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temeprature, where death may be induced by sudden failure to deliver oxgyen to vital organs).
-In practice, this was achieved as described above by setting the maximum oxygen deliver close to the lethal temperature (Figure \ref{fig:O2_fig}).
+In practice, this was achieved as described above by setting the maximum oxygen deliver close to the lethal temperature (\ref{fig:O2_fig}).
 
@@
 \caption{Parameters of the constrained activity model for two scenarios: M-strategy and P-strategy species.
-For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
-Values in brackets for $\\gamma$ are alternative resource availibility scenarios.}
+For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.}
 \label{tab:parameters}
@@
 \multicolumn{4}{c}{\textbf{Feeding ecology}}\\
-Coeff. for Encountered food & $\gamma\Theta$ ($y^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
+Coeff. for Encountered food & $\gamma\Theta$ ($y^{-1}$)& \multicolumn{2}{c}{60} \\
 Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
@@
 \multicolumn{4}{c}{\textbf{Temperature}}\\
-Reference temperature (°C) & $T_{ref}$ & \multicolumn{2}{c}{15} \\
+Reference temperature (??C) & $T_{ref}$ & \multicolumn{2}{c}{15} \\
 Activation energy & $E_a$ & \multicolumn{2}{c}{0.52} \\
@@
 
-Slope &  & \multicolumn{2}{c}{0}\\
+Slope & $b$ & \multicolumn{2}{c}{0}\\
 Reaction & $c$ & \multicolumn{2}{c}{0.5} \\
@@
 source('model.R')
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
 
@@
 
-int_m <- 100
-int_t <- 100
-int_temp <- 30
+int_m <- 500
+int_t <- 500
+int_temp <- 50
 
@@
            n=0.88, 
-           o=1,
            O2crit=2, 
@@
            temp_ref=15,
-           slope=-0.5,
+           slope=0,
            tmax=20,
@@
 fs$n <- 0.75
-fs$o <- 1
 fs$p <- 0.8
@@
 scs <- list(ss,fs,sl,fl)
-
-baseline <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
-                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
-                       bind_rows(lapply(scs, get_model_out,seq(0.05,1,l=int_temp))))
-
 scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
@@
 A similar increase in activity is observed for small P-strategy individuals (e.g., post-larval) for which even initial activity levels are very high (Figure \ref{fig:size-act}).
-For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
+For these individuals, the increasing activity and metabolic demands leads to an active metabolic rate that is close to their MMR.
 For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (Figure \ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
-For species with a rising MOS with temperature, oxygen is not limiting (Figure \ref{fig:activitys}).
 However, larger P-strategy individuals are predicted to show a dome-shaped adjustment in activity levels at intermediate sizes, and a decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
-
-<<scenarios,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted as a function of changing activity at constant temperature ($T=15$\\degree C) for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for M- and P-strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center',fig.height=3,fig.width=6>>=
-
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b'))
-
-sc_bl <- baseline %>% filter(O2lim=='Domed') %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,O2lim) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,O2lim))
-
-ggplot(sc_bl) + 
-  geom_line(aes(x=tau, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-   labs(x = expression('Activity ' (tau)),
-       y='Relative rate')
-
-@
 
@@
 \centering
-<<activity, fig.height=4,fig.width=6>>=
+<<activity, fig.height=7,fig.width=6>>=
 
@@
 
-lab1 <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'c'))
+cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
 
-lab2 <- as_labeller(c(`M strategy Domed`  ='b',
-                   `P strategy Domed` = 'd'))
+lab1 <- as_labeller(c(`M strategy Rising` ='c',
+                   `M strategy Domed`  ='a',
+                   `P strategy Rising` ='g',
+                   `P strategy Domed` = 'e'))
 
-ggsc <- ggplot(sc_act %>% filter(O2lim=='Domed')) + 
+lab2 <- as_labeller(c(`M strategy Rising` ='d',
+                   `M strategy Domed`  ='b',
+                   `P strategy Rising` ='h',
+                   `P strategy Domed` = 'f'))
+
+ggsc <- ggplot(sc_act) + 
   geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
   theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
+  scale_color_manual(values = cols, guide='none')+
   scale_linetype(guide='none')+
@@
 
-ggso <- sco %>% filter(O2lim=='Domed') %>%
+ggso <- sco %>%
   ggplot() + 
    geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot() +
-  scale_color_manual(values = cols,guide='none')+
+  theme_cowplot()+
+  scale_color_manual(values = cols, guide='none')+
   scale_linetype(guide='none')+
@@
 @
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; candd).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c,e]) at increasing temperatures for a 10g fish, with corresponding oxygen demand (right column [b,d,f]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; a--d) and P-strategy (fast life-history; e--h).
+For each strategy, the first row (i.e., a--b; e--f) depicts a life-history with a dome-shaped MOS for increasing temperature, and the second row (i.e., c--d; g--h) corresponds to a species with continuously increasing MOS with temperature.}
 \label{fig:activity}
@@
 
-<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
 
@@
   theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
+  scale_color_manual(values = cols, guide='none')+
   scale_linetype(guide='none')+
@@
 
-Temeprature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (Figure \ref{fig:feeding}).
-For M-strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
+Adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (Figure \ref{fig:feeding}).
+For M-strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy lead to an over-all decline in the ratio of $P$ to $M$.
 Available energy shows a dome-shaped response to temperature in M-strategists, and is maximised at relatively high temperatures.
@@
 
-<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for M- and P-strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center',fig.height=3,fig.width=6>>=
+<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g).
+Responses are shown for M- and P-strategy (top and bottom rows, respectively), for species with and without oxygen limitation (left and right columns, respectively).
+Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center'>>=
 
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b'))
+lab <- as_labeller(c(`M strategy Rising` ='b',
+                   `M strategy Domed`  ='a',
+                   `P strategy Rising` ='d',
+                   `P strategy Domed` = 'c'))
 
-sc_feed <- scenarios %>% filter(O2lim=='Domed') %>%
+sc_feed <- scenarios %>%
   #filter(!grepl('large',Scenario)) %>% 
@@
 Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (Figure \ref{fig:norms}).
-For both trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures \ref{fig:norms02}).
+For all trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures.
 This can be explained by ontogenetic shifts in temperature optima for growth (Figure \ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals for either trait-scenario grow.
 For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
-Resource availibility storngly modulates this growth response to temeprature: low resource availibility leads to strong differences in asymptotic size, whereas high food availibility leads to high growth and larger asymptitic length at high temperatures.
 
@@
 
-ssgl <- ss
-ssgl$gamma <- 40
-
-ssgh <- ss
-ssgh$gamma <- 80
-
-fsgl <- fs
-fsgl$gamma <- 40
-
-fsgh <- fs
-fsgh$gamma <- 80
-
-scsg <- list(ssgl,ss,ssgh,fsgl,fs,fsgh)
-
-mstar_ss <- plot_data_growth_tO2(ss)$mstar
-mstar_fs <- plot_data_growth_tO2(fs)$mstar
-
-goutss <- parallel::mclapply(list(ssgl,ss,ssgh),
-                             plot_data_growth_tO2,
-                             mstar=mstar_ss,
-                             mc.cores = 3)
-
-goutsf <- parallel::mclapply(list(fsgl,fs,fsgh),
-                             plot_data_growth_tO2,
-                             mstar=mstar_fs,
-                             mc.cores = 3)
-
-gouts <- c(goutss,goutsf)
+gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
 
@@
 <<norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}).
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for M- (left column [a,c,e]) and P-strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
-
-labla <- as_labeller(c(`M strategy Low` ='a',
-                   `P strategy Low`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy High` = 'e',
-                   `P strategy High` = 'f'
-))
+Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size.
+Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=
 
@@
   y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
+  y$Scenario <- scn[x]
+  y$O2lim <- scz[x]
+  y$Dispatch <- paste(scn[x],scz[x])
   y}))
-
-t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
 
@@
 norm <- t_growth %>% 
+  mutate(Dispatch = paste(Scenario,O2lim)) %>%
   group_by(Dispatch,Temperature) %>%
@@
   theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
+  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
   viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
@@
 
+<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+
+sc_feed <- scenarios_s %>%
+  #filter(!grepl('large',Scenario)) %>% 
+  group_by(Scenario,Size) %>%
+  mutate(Consumption=sc(Consumption),
+         Efficiency=sc(Efficiency),
+         Feeding=`Feeding level`,
+         `Available Energy` = sc(`C for growth`),
+         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
+         Fitness = sc(Energy/M)) %>% 
+  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
+  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
+         Dispatch = paste(Scenario,Size))
+
+sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])
+
+ggplot(sc_feed) + 
+  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
+  theme_cowplot()+
+  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
+  theme(strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_manual(values=c(1:4,1),guide='none')+
+  scale_color_manual(values = cols,guide='none')+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y='Relative rate')
+
+@
+
 Over-all fitness consequences mirror trends in the ratio of $P/M$ (Figure \ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\cite{sainmont_effective_2015}).
@@
 Fitness trends with temperature are strongly dependant on metabolic costs of activity (Figure \ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for M-strategy species, and moves the fitness optimum to higher temperatures for P-strategy species.
-Similarly, changes in the growth reponse to temperature lead to changes in fitness optima, with higher optimum temperatures, especially for P-strategists, and a slower decline of fitness with temperature.
 
@@
 gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
-goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
+
 @
@@
 
-R0s <- bind_rows(lapply(1:length(goutr), function(x) {
+R0s <- bind_rows(lapply(1:length(gouts), function(x) {
   y <- data.frame(gouts[[x]]['R0'])
@@
 
-R0s <- R0s %>% group_by(Dispatch) %>%
+R0s <- R0s %>% group_by(Scenario) %>%
   mutate(R0 = R0/max(R0, na.rm=T))
@@
   scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('R0/R0'[max]))
+  labs(x = '',
+       y=expression('R0/R0'[max])) +
+    theme(axis.title.x=element_blank(),
+          axis.text.x = element_text(colour = NA))
 
@@
 
-R0s <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- data.frame(gouts[[x]]['R0'])
-   y$Temperature <-gouts[[x]][['winfs']]$Temperature
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-R0s <- R0s %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T))
-
-f3 <- ggplot(R0s) + 
-  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=Food,group=Dispatch)) +
-  theme_cowplot()+
-  theme(
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('R0/R0'[max]))
-
-cowplot::plot_grid(f1,f2,f3,ncol=1,labels = 'auto')
+cowplot::plot_grid(f1,f2,ncol=1,labels = 'auto')
 
@@
 
-Resource availibility imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
-Changes in prey availibility thus influece the temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal acitivity level.
-In low-food environments, changing energetic demands with temeprature are not easily adjusted for, and any adjustment demands higher energic costs and mortality risk.
-This environment-driven change in costs of temperature adjustments leads to the strong modulation of the growth repsonse, as well as changing gradients in fitness with temperature in these environments.
-In particular, in low-food environments, asymptitic size is strongly reduced at high temperatures, whereas this is not necessarily the case in high-food environments.
-Increased growth and mortality changes at low temperatures lead to a more strongly domed fitness curve.
-
 Our model prediction of declining fitness with temperature is
@@
 Our prediction of constantly decreasing fitness with temperature, especially for relatively inactive species (M-strategists), contrasts with a previous species-specific eco-physiological model for cod that includes similar constraints to our model (\cite{holt_climate_2014,holt_climate_2015}), and which predicted relatively high fitness at high temperatures.
-Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, the product of $\delta*\tau$ is on the same order of magnitude in both models.
+Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, however the product of $\delta*\tau$ is on the same order of magnitude in both models.
 Differences may also be due to key assumptions about time-scales in the model --- we assume an evolutionarily fixed maturation reaction norm that drives relative growth and reproductive output across temperatures.
@@
 
-lam <- gouts[[2]]$t_growth
+lam <- gouts[[1]]$t_growth
 
@@
 
-\section{Supplementary results}
-
-\begin{figure}
-\centering
-<<activitys, fig.height=4,fig.width=6>>=
-
-sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,O2lim))
-
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
-
-lab1 <- as_labeller(c(`M strategy Rising`  ='a',
-                   `P strategy Rising` = 'c'))
-
-lab2 <- as_labeller(c(`M strategy Rising`  ='b',
-                   `P strategy Rising` = 'd'))
-
-ggsc <- ggplot(sc_act %>% filter(O2lim=='Rising')) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
-  mutate(Dispatch = paste(Scenario,O2lim))
-
-ggso <- sco %>% filter(O2lim=='Rising') %>%
-  ggplot() + 
-   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot() +
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression(Oxygen~(mg.yr^-1)))
-
-cowplot::plot_grid(ggsc,ggso,ncol=2)
-
-@
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; candd).}
-\label{fig:activity-rising}
-\end{figure}
-
-<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
-
-sc_feed <- scenarios_s %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,Size) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,Size))
-
-sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])
-
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
-
-@
-
-<<norms02, fig.cap='Contrasting growth reponses at baseline resource availibility for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
-Growth curves are shown for M- (left column [a,c]) and P-strategists (right column [b,d]).
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=
-
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b',
-                   `M strategy Rising`  ='c',
-                   `P strategy Rising` = 'd'))
-
-t_growth <- bind_rows(lapply(1:length(goutr), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
-  y}))
-
-#browser()
-norm <- t_growth %>% 
-  mutate(Dispatch = paste(Scenario,O2lim)) %>%
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  #geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  #geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
-
 \end{document}

### 2018-07-02 draft_model_only.Rnw

--- 2018-04-19 draft_model_only.Rnw
@@
 
-\title{Beyond conceptual eco-physiological hypotheses: insights from a general size and trait-based model of ectotherm thermal performance}
+\title{Explaining thermal performance in fish: interplay of ecology and physiology drive growth and fitness response}
 \author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
@@
 
-Increasing temperature under climate change is thought to affect physiology of ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology.
-Although intuitively appealing, the driving mechanism behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance.
+Increasing temperatures under climate change are thought to affect individual physiology of ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology.
+Although intuitively appealing, the driving mechanisms behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance.
 Whether or not oxygen limitations via the metabolic scope, or a lack thereof, have major ecological consequences remains a highly contested question.
@@
 We show that oxygen limitation is not necessary to explain performance curves that are correlated with metabolic scope.
-Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology (i.e., food aquisition and mortality).
-We find that resource availibility strongly modulates growth and fitness repsonses to temperature, with individuals in low-resource environments showing increased growth sensitivity and stronger fitness gradients with temperature.
-Furthermore, our model reveals that fitness is often minimised a low temperatures.
-This trend opposes trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
-We suggest that this model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.
+Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology.
+Furthermore, our model reveals that fitness trends with temperature likely oppose trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
+We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.
 
@@
 
-There is currently no accepted universal concept or general mechanistic model that explains ectotherm thermal performance and ecological responses to temperature (\cite{lefevre_are_2016, jutfelt_oxygen-and_2018}).
-In fish, two main theories are debated as potential general therories describing temeprature influences on ectotherms.
-The theory of Oxygen and Capacity Limitation of Temperature (OCLTT; \cite{portner_oxygen-and_2010}),  based on the general idea of oxygen limitation for major ecological processes (growth, fitness, etc; see below), provides a conceptual framework rather than a mechanistic theoretical framework, and its major assumptions have been called into question on numerous occasions (\cite[e.g., ][]{lefevre_are_2016, jutfelt_oxygen-and_2018}).
-The gill-oxygen limitation theory (GOLT) aims to provide a physiological justification for the use of a temperature and oxygen scaled version of the von Bertalanffi growth model as a mechanistic model of thermal performance.
-The validity of gill limitation of oxygen supply, as well as the ultimate limitation of growth by oxygen in all conditions, is strongly debated (\cite{brander_overconfidence_2013,pauly_sound_2017,lefevre_modelling_2017,lefevre_models_2017}).
-In addition, the von Bertalanffi growth model only encapsulates a highly abstract view of organism bio-energetics and ecology, with no reference to ecological rates such as food aquisition, mortality and reproduction.
-As such, it can only represent a very limited set of aspects of species ecology, and cannot on its own account for changes in ecological rates that are often observed with temperature (\cite{englund_temperature_2011,rall_universal_2012}).
-
+There are few general concepts and models that can explain thermal performance and ecological responses to temperature.
 To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed changes of attack rates with temperature (\cite{englund_temperature_2011,rall_universal_2012}), from fundamental physiological processes.
 Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependant, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{vucic-pestic_warming_2011, guiet_effects_2016}).
-However, although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups.
-Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology, and explicitly link physiological constraints and ecology.
+
+Although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups.
+A phenomenological description that assumes a general ecological temperature response thus leads to difficulties with extrapolation when observed ecological responses are heterogeneous across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
+In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011}).
+Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.
 
@@
 \subsection{Model description}
-
-The quantitative size- and trait-based thermal impact model lets ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy $P$ gain relative to natural mortality.
-Since both energy gain and loss are sensitive to temperature and oxygen limitations, both the activity level and the net energy gain will be subject to these environmental constraints.
+Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality.
+In the following, we refer to $\tau$ as the activity fraction for sake of generality.
+Since both energy gain and metabolic losses are sensitive to temperature and oxygen limitations, both the activity level and the net energy gain will be subject to these environmental constraints.
 Their interplay thus determines available energy for growth and reproduction.
 
-The model is written in terms of weight $w$ and oxygen balance equations at temperature $T$:
-
+Net energy gain $P$ (mass per time) is the difference between supply $S$ and metabolic demands $D$, each being functions of body weight $w$ and temperature $T$:
 \begin{align}
-f(w,T) &= \frac{\tau }{\tau  + \frac{h c_T w^{q-p}}{\gamma\Theta} } \label{eq:f} \\
 P(w,T) &= S(w,T) - D(w,T) \\
-  &=(1-\beta-\phi)f(w,T) h c_T w^q  - c_T k w^n - \tau \delta c_T k w  \\
+          &=(1-\beta-\phi)f(w,T) h c(T) w^q  - c(T) k w^n - \tau \delta c(T) k w  \\
+  \label{eq:P}
+\end{align}
+where the feeding level ($[0:1]$)is given by a Holling type II function response:
+\begin{align}
+  f(w,T) &= \frac{\tau \gamma\Theta w^{p} }{\tau \gamma\Theta w^{p} + h c(T) w^q} }, \label{eq:f} \\
+\end{align}
+where $h c(T) w^q$ is the maximum consumption rate.
+The corresponding function for oxygen is given in Appendix A.
+The feeding level ([0,1]) is determined by the fraction of time spent foraging $\tau$, foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
+The supply is discounted by the loss due to specific dynamic action  $\beta$ (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
+
+Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}, and the activity fraction \emph{(Important note: you cannot interpret $\delta$ as the factorial aerobic scope (FAS) when the two metabolisms scale with different exponents!.
+I therefore propose to rename the constant to $k_a$)}.
+
+Temperature scaling of all metabolic rates (standard and active metabolism and maximum consumption rate) is determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}) as $c(T) = e^{E_a(T-T_0)/(kTT_0)}$.
+
+The oxygen budget $P_{0_2}(w,T)$ (oxygen per time) follows a similar form to the mass budget:
+\begin{align}
   P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
-        &= f_{O_2}(T)w^n - \omega \left( \beta f(w,T) h c_T w^q + c_T k w^n + \tau \delta c_T k w \right)
+        &= s_(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
 \end{align}
-
-where $f(w,T)$ is the feeding level ([0,1]) at weight $w$ and temperature $T$, determined by consumption rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$), maximum consumption $h w^q$, and $\tau$, which can be interpreted as the proportion of time spent foraging (or proportion of maximum attack rate) or a multiplyer on a basal foraging speed, such that at $\tau=1$, foraging occurs at maximum speed.
-In the following, we will refer to $\tau$ as the activity fraction for sake of generality.
-Maximum consumption, determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}), is assumed to scale with temperature according to the Arrhenius scaling $c_T = e^{E_a(T-T_0)/k \times T \times T_0}$.
-Available energy $P(w,T)$ is determined by supply ($S(w,T)$) from prey consumption ($f(w,T) h c_T w^q$), with $\beta$ a loss due to specific dynamic action (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
-Metabolic demands ($D(w,T)$) are those of standard metabolism ($k w^n$), as well as active metabolism, scaled in units of standard metabolism as $\delta k w$, with $\delta$ determining the maginitude of activity cost relative to standard metabolic costs.
-The activity fraction $\tau$ determines the proportion of total metabolic costs that are due to active metabolism.
-Note that we assume that active metabolism scales directly with $w$, owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}).
-In practice, the scaling may not be strictly isometric owing to reduced drag at larger size (\cite[e.g., ][]{ware_bioenergetics_1978}), as well as non-strictly isometric growth of muscle mass and other relevant factors with weight (\cite{killen_little_2007}).
-However, the precise exponents of standard and foraging metabolism only alter predictions quantitatively, but do not change the over-all results.
-
-The oxygen budget $P_{0_2}(w,T)$, determines physiological limits to aerobic activity.
-Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for SDA (i.e., the conversion of food into energy, growth and reproduction - $\beta f h c_T w^q$) and ``active metabolism", the sum of standard (or resting) metabolism ($c_T k w^n$) and the metabolic costs of foraging ($\tau \delta c_T k w$), with $\omega$ determining amount of oxygen required per unit of metabolised feed.
-Metabolic scope is the difference between $S_{O_2}(w,T)=f_{O_2}(T)w^n$, the maximum amount of oxygen supplied at temperature $T$, and oxygen demand due to standard metabolism ($\omega c_T k w^n$).
-We assume that the maximum oxygen supply (MOS), follows a flexible dome-shaped function that can emulate both a dome-shaped MOS as well as MOS that increas continously up to a lethal temeprature (Figure \ref{fig:O2_fig}, Appendix A).
-
-We assumed that fish will adjust their activity level to maximise $F$: maximize available energy relative to mortality: $\tau_{\text{opt}}$ = $\text{argmax}_{\tau_{w,T}}F(\tau_{w,T})$ = $\text{argmax}_{\tau_{w,T}}P(\tau_{w,T})/M(\tau_{w,T})$.
-This optimisation is also known as Gilliam's rule (\cite{gilliam_habitat_1987}) and represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for simulating opmisation in changing environments (\cite{sainmont_effective_2015}).
-We further assumed here that mortality scales with activity level and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}), such that $M(w) = (\rho+\eta\tau) w^{q-1}$, where $ \rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism.
-$M$ is then the effective mortality at realised levels of activity $\tau$ at weight $w$.
-
-We assumed that the metabolic scope dictates the upper limit of this activity, such that at $\tau_{\text{max}}$, oxygen demand $D_{0_2}$ equals total supply $S_{0_2}$.
+Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.
+The oxygen supply scales with body weight as $w^n$ multiplied by a flexible dome-shaped function ($s(t)$) \emph{I've changed this away from $f$, because $f$ was used above for a function that is in the range 0:1, while this one has a unit} that can emulate both a dome-shaped MOS as well as MOS that increas continously up to a lethal temeprature (Figure \ref{fig:O2_fig}, Appendix A).
+
+Fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \cite{gilliam_habitat_1987}:
+\begin{equation}
+  \tau^* = \argmax_{\tau} \{ \frac{P(w,T)}{M(w)} \}.
+\end{equation}
+This optimisation represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for optimisation in stable environments (\cite{sainmont_effective_2015}).
+Mortality scales with activity fraction and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}):
+\begin{equation}
+  \label{eq:M}
+  M(w) = (\rho+\eta\tau) w^{q-1},
+\end{equation}
+$\rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism.
+Activity is limited by available oxygen, such that $P_{O_2}$ is not allowed to be negative \emph{Is that a correct interpretation?}.
+
+%We assumed that the metabolic scope dictates the upper limit of this activity, such that at $\tau_{\text{max}}$, oxygen demand $D_{0_2}$ equals total supply $S_{0_2}$.
 Both temperature and oxygen will influence $\tau$, such that at a given temperature and oxygen concentration, $\tau_{w,T,O_2} = \text{min}\left( \tau_{\text{opt}},\tau_{\text{max}} \right)$, meaning we assumed that animals will adapt their effort to optimise fitness $F$ given temperature and oxygen constraints.
@@
 The allocation was parametrised as
-$$\phi(z) = 1/(1+\exp(-(c*z))) \text{, where }$$
+$$\phi(z) = 1/(1+\exp(-(c z))) \text{, where }$$
 $$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$  

### 2018-07-03 draft_model_only.Rnw
forward

@@
 Increasing temperatures under climate change are thought to affect individual physiology of ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology.
-Although intuitively appealing, the driving mechanisms behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance.
+Although intuitively appealing, the driving mechanism behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance.
 Whether or not oxygen limitations via the metabolic scope, or a lack thereof, have major ecological consequences remains a highly contested question.
-Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of thermal sensitivity of metabolic rates, oxygen limitation, and environmental conditions on thermal performance.
+Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of thermal sensitivity of metabolic rates, oxygen limitation, and environmental conditions on fish thermal performance.
 We show that oxygen limitation is not necessary to explain performance curves that are correlated with metabolic scope.
-Oxygen can drastically limit performance and fitness at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology.
-Furthermore, our model reveals that fitness trends with temperature likely oppose trends in growth and efficiency, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
-We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on ectotherm performance and effects of climate change on species with different metabolic and ecological traits.
+Oxygen can drastically limit performance and fitness, especially at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology.
+Furthermore, our model reveals that fitness trends with temperature can oppose trends in growth, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
+We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on the performance of fish and other ectotherms, and act as a null model for temperature impacts on species with different metabolic and ecological traits.
 
@@
 \subsection{Model description}
-Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality.
+Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality (\cite{gilliam_habitat_1987}).
 In the following, we refer to $\tau$ as the activity fraction for sake of generality.
@@
 \begin{align}
-  f(w,T) &= \frac{\tau \gamma\Theta w^{p} }{\tau \gamma\Theta w^{p} + h c(T) w^q} }, \label{eq:f} \\
+  f(w,T) &= \frac{\tau \gamma\Theta w^{p} }{\tau \gamma\Theta w^{p} + h c(T) w^q}, \label{eq:f} \\
 \end{align}
@@
 \begin{equation}
-  \tau^* = \argmax_{\tau} \{ \frac{P(w,T)}{M(w)} \}.
+  \tau^* = \text{argmax}_{\tau} \{ \frac{P(w,T)}{M(w)} \}.
 \end{equation}

### 2018-07-03 run.sh

@@ -7,4 +7,4 @@ set -ex
 #docker push docker.dragonfly.co.nz/adaptive_activity
 
 docker run --rm  -v $PWD:/work -w /work \
-  docker.dragonfly.co.nz/dragonverse-17.04 ./build.sh
+  docker.dragonfly.co.nz/dragonverse-18.04 ./build.sh

### 2018-07-04 draft_model_only.Rnw
MS

@@
 
-\title{Explaining thermal performance in fish: interplay of ecology and physiology drive growth and fitness response}
+\title{Explaining thermal performance of fish: interplay of behaviour, ecology and physiology drive growth and fitness responses}
 \author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
@@
 
-Increasing temperatures under climate change are thought to affect individual physiology of ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology.
+Increasing temperatures under climate change are thought to affect individual physiology of fish and other ectotherms through increases in metabolic demands, leading to changes in species performance with concomitant effects on species ecology.
 Although intuitively appealing, the driving mechanism behind thermal performance is contested: thermal performance (e.g., growth) appears correlated with metabolic scope (i.e., oxygen availability for activity) for a number of species, but a substantial number of datasets do not support oxygen limitation of long-term performance.
 Whether or not oxygen limitations via the metabolic scope, or a lack thereof, have major ecological consequences remains a highly contested question.
-Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of thermal sensitivity of metabolic rates, oxygen limitation, and environmental conditions on fish thermal performance.
+Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of metabolic rates, oxygen limitation, and environmental conditions on ecotherm performance.
 We show that oxygen limitation is not necessary to explain performance curves that are correlated with metabolic scope.
@@
 Furthermore, our model reveals that fitness trends with temperature can oppose trends in growth, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
-We suggest that this general model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on the performance of fish and other ectotherms, and act as a null model for temperature impacts on species with different metabolic and ecological traits.
+We suggest that this model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on the performance of fish and other ectotherms, and act as a null model for contrasting temperature impacts on species with different metabolic and ecological traits.
 
@@
 There are few general concepts and models that can explain thermal performance and ecological responses to temperature.
-To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed changes of attack rates with temperature (\cite{englund_temperature_2011,rall_universal_2012}), from fundamental physiological processes.
-Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependant, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{vucic-pestic_warming_2011, guiet_effects_2016}).
-
-Although ecological rates seem to follow some general patterns in the response to temprature (\cite{englund_temperature_2011,rall_universal_2012}), there is also significant heterogeneity between species and trait groups.
-A phenomenological description that assumes a general ecological temperature response thus leads to difficulties with extrapolation when observed ecological responses are heterogeneous across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
-In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011}).
+To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angilletta_temperature_2004,atkinson_temperature_1994}), or attack rates (\cite{englund_temperature_2011,rall_universal_2012}) with temperature, from fundamental physiological processes.
+Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{angilletta_temperature_2004,vucic-pestic_warming_2011, guiet_effects_2016}).
+
+Although ecological rates seem to follow some general patterns in the response to temperature , there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}).
+A phenomenological description that assumes a general ecological temperature response thus often fails to explain heterogeneity in ecological responses (\cite{angilletta_temperature_2004}), and leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
+In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011,lefevre_models_2017}).
 Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.
@@
 
-Here, we propose a general quantitative size- and trait-based eco-physiological model to derive general predictions about temperature impacts on ectotherm physiology, performance and ecology.
+Here, we propose a general quantitative size- and trait-based eco-physiological model to derive general predictions about temperature impacts on fish  physiology, performance and ecology.
 We describe simple size-dependent physiological processes within an ecological context, and, using a simple optimisation argument, show that observed ecological responses of different life-history strategies can be predicted on the basis of optimised bio-energetics under different temperatures.
@@
 P(w,T) &= S(w,T) - D(w,T) \\
-          &=(1-\beta-\phi)f(w,T) h c(T) w^q  - c(T) k w^n - \tau \delta c(T) k w  \\
+          &=(1-\beta-\phi)f(w,T) h c(T) w^q  - c(T) k w^n - \tau c(T) k_a w
   \label{eq:P}
@@
 \begin{align}
-  f(w,T) &= \frac{\tau \gamma\Theta w^{p} }{\tau \gamma\Theta w^{p} + h c(T) w^q}, \label{eq:f} \\
+  f(w,T) &= \frac{\tau \gamma\Theta w^{p} }{\tau \gamma\Theta w^{p} + h c(T) w^q}, \label{eq:f} 
 \end{align}
 where $h c(T) w^q$ is the maximum consumption rate.
-The corresponding function for oxygen is given in Appendix A.
 The feeding level ([0,1]) is determined by the fraction of time spent foraging $\tau$, foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
@@
 
-Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}, and the activity fraction \emph{(Important note: you cannot interpret $\delta$ as the factorial aerobic scope (FAS) when the two metabolisms scale with different exponents!.
-I therefore propose to rename the constant to $k_a$)}.
-
-Temperature scaling of all metabolic rates (standard and active metabolism and maximum consumption rate) is determined by digestive (enzymatic) processes (\cite{jeschke_predator_2002, sentis_parsing_2013}) as $c(T) = e^{E_a(T-T_0)/(kTT_0)}$.
-
-The oxygen budget $P_{0_2}(w,T)$ (oxygen per time) follows a similar form to the mass budget:
+Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}, and the activity fraction.
+Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \cite{jeschke_predator_2002, sentis_parsing_2013}) as $c(T) = e^{E_a(T-T_0)/(kTT_0)}$.
+
+The oxygen budget $P_{0_2}(w,T)$ (or aerobic scope) follows a similar form to the mass budget:
 \begin{align}
@@
 Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.
-The oxygen supply scales with body weight as $w^n$ multiplied by a flexible dome-shaped function ($s(t)$) \emph{I've changed this away from $f$, because $f$ was used above for a function that is in the range 0:1, while this one has a unit} that can emulate both a dome-shaped MOS as well as MOS that increas continously up to a lethal temeprature (Figure \ref{fig:O2_fig}, Appendix A).
+The oxygen supply scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as MOS that increase continuously up to a lethal temperature (fig.
+\ref{fig:O2_fig}, Appendix A).
 
@@
 $\rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism.
-Activity is limited by available oxygen, such that $P_{O_2}$ is not allowed to be negative \emph{Is that a correct interpretation?}.
-
-%We assumed that the metabolic scope dictates the upper limit of this activity, such that at $\tau_{\text{max}}$, oxygen demand $D_{0_2}$ equals total supply $S_{0_2}$.
-Both temperature and oxygen will influence $\tau$, such that at a given temperature and oxygen concentration, $\tau_{w,T,O_2} = \text{min}\left( \tau_{\text{opt}},\tau_{\text{max}} \right)$, meaning we assumed that animals will adapt their effort to optimise fitness $F$ given temperature and oxygen constraints.
+Activity is limited by available oxygen, such that the aerobic scope $P_{O_2}$ is not allowed to be negative over the time scales considered.
+In other words, we consider time scales that are long enough to ignore the ability of many ectotherms to go into oxygen debt, or to switch to anaerobic metabolism for limited periods of time.
+This means we assume that animals will adapt their effort to optimise fitness given temperature and oxygen constraints.
+
+\subsection{Defining performance metrics}
+
+Performance itself is a vague concept that is often used without definition in the relevant literature, but it is only defined in the context of a particular physiological or demographic parameter, with potentially different thermal response curves (\cite{jutfelt_oxygen-and_2018}).
+For instance, even though growth in ectotherms is often impacted by temperature (\cite{angilletta_temperature_2004}), measured performance may depend strongly on what aspect of growth is measured --- whether it is the growth increment at a particular size, growth efficiency per unit intake, the attained asymptotic size, or parameters of a fitted growth curve.
+We use and compare four performance measures with broad ecological and practical implications:
+
+\begin{itemize}
+
+\item Growth curves predicted through ontogeny, which allow us to compare growth performance early and late in life (i.e., juvenile growth vs asymptotic size).
+\item Growth efficiency, here defined as available energy relative to the feeding level (i.e., $\frac{P(w,T)}{f(w,T)}$.
+\item The ratio of $P/M$ (Gilliam's rule) used above as a short-sighted fitness aproximation.
+\item Fitness integrated over an individual's lifetime, defined as $R0$ (see below).
+
+\end{itemize}
 
@@
 We defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
-The allocation was parametrised as
-$$\phi(z) = 1/(1+\exp(-(c z))) \text{, where }$$
-$$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$  
-rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
 
@@
 We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past.
-Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a slightly negative slope in the reaction norm \ref{fig:MRN}).
-The intercept of this reaction norm was found numerically by maximising fitness ($R0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was asumed fixed as temperatures change.
-
-As growth is also fundamentally driven by resource availibility, we contrast the growth reponse to temperature at the baseline level (Table \ref{tab:parameters}), with a 30\% reduction and increase in available resources.
+Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm (i.e., allocation to reproduction is a function of size only; fig.
+\ref{fig:MRN}), although sloping reaction norms can be formulated and used in our framework (see appendix \ref{sec:MRN}).
+The intercept of this reaction norm was found numerically by maximising fitness ($R0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was assumed fixed as temperatures change.
+
+The allocation was parametrised as 
+$$\phi(w^*) = 1/(1+\exp(-cw^*))$$,
+where $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
+
+As growth is also fundamentally driven by resource availability, we contrast the growth response to temperature at the baseline level (Table \ref{tab:parameters}), with a 1/3 reduction and increase in available resources.
 
@@
 Fitness consequences for particular life-history strategies (trait combinations, see below) at different temperatures can be investigated if one considers the time-scales in the model to be short relative to evolutionary time-scales (i.e., if the model represents ecological time-scales).
-On these time-scales, we asume that adaptative responses are negligeable.
+On these time-scales, we assume that adaptive responses are negligible.
 We investigate over-all fitness with respect to temperature by calculating R0 for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
@@
 $$R0 = \int_0^\infty \phi(z(t,w_t,w^*))P(w_t,T)S_{0 \rightarrow t} dt, \text{, where}$$
-$$S_{0 \rightarrow t} = \int_0^t \exp(-M(w_t))dt$$
+$$S_{0 \rightarrow t} = \int_0^t \exp(-M(w_t))\text{dt}$$
 
@@
 To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
-Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the P-strategy) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth M-strategy).
+Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the production strategy, indicated by a supercript $p$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth safe strategy, indicated by a supercript $s$).
 This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
@@
 50\% increase in standard metabolic cost.
-We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M^{M-strat}(w) = (0.1+6\tau) w^{q-1}$ and $M^{M-strat}(w) = (1+\tau) w^{q-1}$).
+We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M^{s}(w) = (0.1+6\tau) w^{q-1}$ and $M^{p}(w) = (1+\tau) w^{q-1}$).
 Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
-Together, these assumed trait differences lead to very different recological and bio-energetic responses of M- and P-strategists (Figure \ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for M-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to feeding level) at high activity levels.
-A slower increase in available energy and M with $tau$ for P-strategists leads to a higher $\tau_{\text{opt}}$.
-
-We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temeprature, where death may be induced by sudden failure to deliver oxgyen to vital organs).
-In practice, this was achieved as described above by setting the maximum oxygen deliver close to the lethal temperature (Figure \ref{fig:O2_fig}).
+Together, these assumed trait differences lead to very different ecological and bio-energetic responses of safe- and production strategists (fig.
+\ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for safe-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to feeding level) at high activity levels.
+A slower increase in available energy and M with $\tau$ for production strategists leads to a higher $\tau_{\text{opt}}$.
+
+We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \cite{salin_inadequate_2016,iftikar_mitochondria_2013}).
+In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig.
+\ref{fig:O2_fig}).
+Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\cite{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
+However the over-all mechanism would be the same to the one assumed here, with different untis (e.g., ATP instead of $O_2$).
 
 \begin{table}
-\caption{Parameters of the constrained activity model for two scenarios: M-strategy and P-strategy species.
+\caption{Parameters of the constrained activity model for two scenarios: safe strategy and production strategy species.
 For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
-Values in brackets for $\\gamma$ are alternative resource availibility scenarios.}
+Values in brackets for $\gamma$ are alternative resource availability scenarios.}
 \label{tab:parameters}
@@
  \cmidrule{3-4}
- & & M-strategy  & P-strategy \\
+ & & safe strategy  & production strategy \\
 
@@
 \multicolumn{4}{c}{\textbf{Biomass Metabolism}} \\
-Activity coefficient & $\delta$ ($g^{n}$) & \multicolumn{2}{c}{4}    \\
 Specific dynamic action & $\beta$ & \multicolumn{2}{c}{0.15} \\
 Egestion and excretion & $\phi$ & \multicolumn{2}{c}{0.25}  \\
-Coeff. for std.~metabolism  & $k$ ($g^{1-n}\cdot y^{-1}$)  & 1 &  1.5 \\
+Coeff. for std.~metabolism  & $k$ (g$^{1-n}\cdot$y$^{-1}$)  & 1 &  1.5 \\
+Coeff. for act.~metabolism  & $k$ (g$ \cdot$y$^{-1}$)  & 4 &  2 \\
 Exponent for std.~metabolism & $n$ & 0.88 & 0.75  \\
@@
 \multicolumn{4}{c}{\textbf{Feeding ecology}}\\
-Coeff. for Encountered food & $\gamma\Theta$ ($g^{1-p} \cdot y^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
+Coeff. for Encountered food & $\gamma\Theta$ (g$^{1-p} \cdot$y$^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
 Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
-Coeff. for Maximum consumption rate & $h$ ($g^{1-q}\cdot y^{-1}$) & 30 & 60  \\
+Coeff. for Maximum consumption rate & $h$ (g$^{1-q}\cdot$y$^{-1}$) & 30 & 60  \\
 Exponent for max.~consumption $h$ & $q$ & \multicolumn{2}{c}{0.8} \\
-Coeff. for constant mortality & $M$ ($g\cdot y^{-1}$) & 0.1  & 1  \\
-Coeff. for activity related mortality & $\rho$ ($y^{-1}$) & 6 & 1\\
+Coeff. for constant mortality & $M$ (g$\cdot$y$^{-1}$) & 0.1  & 1  \\
+Coeff. for activity related mortality & $\rho$(y$^{-1}$) & 6 & 1\\
 Exponent for mortality & $\nu$ & \multicolumn{2}{c}{0.2} \\
@@
 \multicolumn{4}{c}{\textbf{Temperature}}\\
-Reference temperature (°C) & $T_{ref}$ & \multicolumn{2}{c}{15} \\
+Reference temperature  & $T_{\text{ref}}$ (°C)& \multicolumn{2}{c}{15} \\
 Activation energy & $E_a$ & \multicolumn{2}{c}{0.52} \\
-Temperature at maximum MOS & $T_{max}$ & \multicolumn{2}{c}{20/25}\\
-Temperature range & $T^-_{lethal}$--$T^+_{lethal}$ & \multicolumn{2}{c}{5--26} \\
+Temperature at maximum MOS & $T_{\text{max}}$ & \multicolumn{2}{c}{20/25}\\
+Temperature range & $T^-_{\text{lethal}}$--$T^+_{\text{lethal}}$ & \multicolumn{2}{c}{5--26} \\
 
@@
 \multicolumn{4}{c}{\textbf{Oxygen budget}} \\
-Critical $O_2$ & $P_{crit}$ ($mg\cdot L^{-1}$) & \multicolumn{2}{c}{2}\\
-Dissolved $O_2$ at $0.5\times f_{max}(O_2)$  & $P50$ ($mg\cdot L^{-1}$) & \multicolumn{2}{c}{4} \\
+Critical $O_2$ & $P_{\text{crit}}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{2}\\
+Dissolved $O_2$ at $0.5\times f_{\text{max}}(O_2)$  & $P50$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{4} \\
 Doming for $O_2$ supply & $\eta$ & \multicolumn{2}{c}{3/0.1}\\
-Level of $O_2$ supply  & $\zeta$ ($g\cdot y^{-1}$) &  0.5 & 1\\
+Level of $O_2$ supply  & $\zeta$ (g$\cdot$y$^{-1}$) &  0.5 & 1\\
 
@@
 
-int_m <- 100
-int_t <- 100
+int_m <- 500
+int_t <- 500
 int_temp <- 30
@@
 ss <- list(c=0.3,
-           beta=0.15,
+           beta=0.1,
            delta=4,
@@
 fs$n <- 0.75
+fs$delta <- 4
 fs$o <- 1
@@
 
+ffl <- fs
+ffl$gamma <- 20
+
+fsl <- ss
+fsl$gamma <- 20
+
+ffh <- fs
+ffl$gamma <- 80
+
+fsh <- ss
+fsl$gamma <- 80
+
 scs <- list(ss,fs,sl,fl)
+fscs <- list(fsh,ffh,fsl,ffl)
 
 baseline <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
-                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
-                       bind_rows(lapply(scs, get_model_out,seq(0.05,1,l=int_temp))))
+                                  Food = as.factor(rep(c('High','Low'),each=int_temp*2))),
+                       bind_rows(lapply(fscs, get_model_out,seq(0.05,1,l=int_temp))))
 
@@
 
-Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (Figure \ref{fig:activity}).
-This adjustment is especially pronounced in M-strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (Figure \ref{fig:size-act}).
-A similar increase in activity is observed for small P-strategy individuals (e.g., post-larval) for which even initial activity levels are very high (Figure \ref{fig:size-act}).
+Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig.
+\ref{fig:activity}).
+This adjustment is especially pronounced in safe strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig.
+\ref{fig:size-act}).
+A similar increase in activity is observed for small production strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.
+\ref{fig:size-act}).
 For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
-For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (Figure \ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
-For species with a rising MOS with temperature, oxygen is not limiting (Figure \ref{fig:activity-rising}).
-However, larger P-strategy individuals are predicted to show a dome-shaped adjustment in activity levels at intermediate sizes, and a decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
-
-<<scenarios,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted as a function of changing activity at constant temperature ($T=15$\\degree C) for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for M- and P-strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center',fig.height=3,fig.width=6>>=
-
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b'))
-
-sc_bl <- baseline %>% filter(O2lim=='Domed') %>%
+For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig.
+\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
+For species with a rising MOS with temperature, oxygen is not limiting (fig.
+\ref{fig:activity-rising}).
+However, larger production strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
+This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig.
+\ref{fig:size-act_low}).
+
+<<scenarios,fig.cap='Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\\degree C) for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
+Responses are shown for safe- (a and b, respectively) and production strategy (c and d), for species in high (left column) and low (right column) food environments.
+All rates are plotted relative to their maximum for each trait scenario (i.e., by row), the optimal activity level $\\tau^*$ is indicated by the dotted vertical line.',fig.align='center',fig.height=5,fig.width=6>>=
+
+lab <- as_labeller(c(`M strategy High`  ='a',
+                   `P strategy High` = 'c',
+                   `M strategy Low`  ='b',
+                   `P strategy Low` = 'd'))
+
+sc_bl <- baseline  %>%
   #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,O2lim) %>%
+  group_by(Scenario) %>%
   mutate(Consumption=sc(Consumption),
          Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,O2lim))
-
-ggplot(sc_bl) + 
-  geom_line(aes(x=tau, y=value, linetype=Rate,col=Rate,group=Rate)) +
+         Feeding=sc(`Feeding level`),
+         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
+         `Relative M` = sc(M),
+         `Energy` = sc(`Available Energy`),
+         Fitness = sc(`Available Energy`/M)) %>% 
+  tidyr::gather(Rate,value,Energy,Efficiency,`Relative M`,Fitness) %>%
+  mutate(Rate = factor(Rate,levels = c('Energy','Efficiency','Fitness')),
+         Dispatch = paste(Scenario,Food))
+
+tstar <- baseline  %>%
+  group_by(Scenario, Food) %>%
+  mutate(`Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
+         Fitness = sc(`Available Energy`/M)) %>% 
+  summarise(tstar = tau[which.max(Fitness)]) %>%
+  mutate(Dispatch = paste(Scenario,Food))
+
+ggplot() + 
+  geom_line(aes(x=tau, y=value, linetype=Rate,col=Rate,group=Rate),data=sc_bl) +
+  geom_vline(aes(xintercept=tstar),linetype=3,data=tstar) +
   theme_cowplot()+
   facet_wrap(~Dispatch,labeller = lab,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
+  theme(strip.text = element_text(hjust = 0.05),
         strip.background = element_blank(),
@@
 @
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; candd).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for safe strategy (slow life history; a \& b) and production strategy (fast life-history; c \& d).}
 \label{fig:activity}
@@
 
-<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for safe strategy (slow life history; left column [a,c,e]) and production strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
 
@@
 
-Temeprature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (Figure \ref{fig:feeding}).
-For M-strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
-Available energy shows a dome-shaped response to temperature in M-strategists, and is maximised at relatively high temperatures.
+Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.
+\ref{fig:feeding}).
+For safe strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
+Available energy shows a dome-shaped response to temperature in safe strategists, and is maximised at relatively high temperatures.
 However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS.
-Growth efficiency ($P/f$) follows a near identical trend due to the relatively flat response in $f$.
-
-For P-strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (Figure \ref{fig:feeding}).
+Growth efficiency  follows a near identical trend due to the relatively flat response in the feeding level $f$.
+
+For production strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig.
+\ref{fig:feeding}).
 Again, growth efficiency peaks at relatively high temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
@@
 <<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for M- and P-strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center',fig.height=3,fig.width=6>>=
+Responses are shown for safe  and production strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
+Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center',fig.height=5,fig.width=6>>=
 
@@
          Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
+         M=sc(M),
+         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
+         `Relative M` = sc(M),
+         `Energy` = sc(`Available Energy`),
+         Fitness = sc(`Available Energy`/M)) %>% 
   tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
@@
   theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
+  facet_wrap(~Dispatch,labeller = lab,ncol=1)+
+  theme(strip.text = element_text(hjust = 0.05),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_linetype_manual(values=c(1:4,1))+
+  scale_color_manual(values = cols)+
   labs(x = expression("Mean temperature " ( degree*C)),
@@
 
-Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (Figure \ref{fig:norms}).
-For both trait scenarios, fastest growth occurred at temperatures close to the lethal temperature, with declining growth for oxygen limited species at high temperatures \ref{fig:norms02}).
-This can be explained by ontogenetic shifts in temperature optima for growth (Figure \ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals for either trait-scenario grow.
+Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig.
+\ref{fig:norms}).
+For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig.
+\ref{fig:norms_O2}).
+This can be explained by ontogenetic shifts in temperature optima for growth (fig.
+\ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals in either trait-scenario grow.
 For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
-Resource availibility storngly modulates this growth response to temeprature: low resource availibility leads to strong differences in asymptotic size, whereas high food availibility leads to high growth and larger asymptitic length at high temperatures.
+
+Resource availability strongly modulates this growth response to temperature: low resource availability leads to strong differences in asymptotic size, whereas high food availability leads to fast growth and larger asymptotic length at high temperatures (fig.
+\ref{fig:norms}).
+In addition, in very resource poor conditions, individuals may not grow to reproductive size in our scenario of a flat MRN.
+Over-all growth responses to temperature are not strongly affected by the assumed slope of the MRN (figs.
+\ref{fig:norms_neg},\ref{fig:norms_pos}), although a negatively sloped MRN does ensure maturation in low resource environments.
 
@@
 
-#mstar_ss <- 50
-#mstar_fs <- 50
+#mstar_ss <- 18
+#mstar_fs <- 18
 
@@
 
-<<norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}).
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for M- (left column [a,c,e]) and P-strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+<<norms, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
 Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
@@
 
-Over-all fitness consequences mirror trends in the ratio of $P/M$ (Figure \ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\cite{sainmont_effective_2015}).
+Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig.
+\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\cite{sainmont_effective_2015}).
 With increasing temperatures, fitness declines at our basic parameter settings, in opposition to growth and aerobic scope.
 At low temperatures, fitness is limited by aerobic scope, with the magnitude determined by the extend of doming in aerobic scope.
-Note that this limitation through the aerobic scope appears at higher temperatures than apparent from Figure \ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (Figure \ref{fig:size-rates}).
-Fitness trends with temperature are strongly dependant on metabolic costs of activity (Figure \ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for M-strategy species, and moves the fitness optimum to higher temperatures for P-strategy species.
-Similarly, changes in the growth reponse to temperature lead to changes in fitness optima, with higher optimum temperatures, especially for P-strategists, and a slower decline of fitness with temperature.
+Note that this limitation through the aerobic scope appears at higher temperatures than apparent from fig.
+\ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (fig.
+\ref{fig:size-rates}).
+Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig.
+\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for safe strategy species, and moves the fitness optimum to higher temperatures for production strategy species.
+Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for production strategists, and a slower decline of fitness with temperature.
 
@@
 gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
-goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)
-@
-
-<<fit, fig.cap='Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b; blue: $\\delta=4$; orange: $\\delta=2$ and green: $\\delta=1$).',fig.align='center',fig.height=6>>=
+goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 3)
+@
+
+<<fit, fig.cap='Fitness (R0), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for safe- (a) and production strategy (b) species at the assumed maturation-raction norm and base parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)',fig.align='center',fig.height=8>>=
 
 R0s <- bind_rows(lapply(1:length(goutr), function(x) {
-  y <- data.frame(gouts[[x]]['R0'])
-  y$Temperature <-gouts[[x]][['winfs']]$Temperature
+  y <- data.frame(goutr[[x]]['R0'])
+  y$Temperature <-goutr[[x]][['winfs']]$Temperature
   y$Scenario <- scn[x]
@@
 
- f1 <- ggplot(R0s) + 
-  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=O2lim,group=Dispatch)) +
-  theme_cowplot()+
-  theme(
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('R0/R0'[max]))
-
-R0s <- bind_rows(lapply(1:length(gouta), function(x) {
+sizes = c(0.5,1,1.5)
+
+f1.1 <- ggplot(R0s%>% filter(Scenario=='M strategy')) + 
+  geom_line(aes(x=Temperature, y=R0, col=O2lim)) +
+  theme_cowplot()+
+  theme(axis.text.x = element_text(colour = 'white'),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+    scale_colour_manual(values=cols,guide='none')+
+  labs(x = ' ',
+       y='Relative fitness')
+
+ f1.2 <- ggplot(R0s%>% filter(Scenario=='P strategy')) + 
+  geom_line(aes(x=Temperature, y=R0, col=O2lim)) +
+  theme_cowplot()+
+  theme(axis.text = element_text(colour = 'white'),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_colour_manual(values=cols,guide='none')+
+  labs(x = ' ',
+       y=' ')
+
+R0ss <- bind_rows(lapply(1:length(gouta), function(x) {
   y <- data.frame(gouta[[x]]['R0'])
@@
 
-R0s <- R0s %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T))
-
-f2 <- ggplot(R0s) + 
-  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=ActivityCost,group=Dispatch)) +
-  theme_cowplot()+
-  theme(
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('R0/R0'[max]))
-
-R0s <- bind_rows(lapply(1:length(gouts), function(x) {
+R0ss <- R0ss %>% group_by(Dispatch) %>%
+  mutate(R0 = R0/max(R0, na.rm=T),
+         ActivityCost = factor(ActivityCost,levels=c('Low','Medium','High')))
+
+f2.1 <- ggplot(R0ss%>% filter(Scenario=='M strategy')) + 
+  geom_line(aes(x=Temperature, y=R0,group=ActivityCost,size=as.numeric(ActivityCost)/3)) +
+  theme_cowplot()+
+  theme(axis.text.x = element_text(colour = 'white'),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_size(guide='none',range = c(0.8,1.2))+
+  labs(x = ' ',
+       y='Relative fitness')
+
+f2.2 <- ggplot(R0ss%>% filter(Scenario=='P strategy')) + 
+  geom_line(aes(x=Temperature, y=R0,group=ActivityCost,size=as.numeric(ActivityCost)/3)) +
+  theme_cowplot()+
+  theme(axis.text = element_text(colour = 'white'),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_size(guide='none',range = c(0.8,1.2))+
+  labs(x =' ',
+       y=' ')
+
+R0sss <- bind_rows(lapply(1:length(gouts), function(x) {
   y <- data.frame(gouts[[x]]['R0'])
@@
 
-R0s <- R0s %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T))
-
-f3 <- ggplot(R0s) + 
-  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=Food,group=Dispatch)) +
+R0sss <- R0sss %>% group_by(Dispatch) %>%
+  mutate(R0 = R0/max(R0, na.rm=T),
+         Food = factor(Food,levels=c('High','Medium','Low')))
+
+f3.1 <- ggplot(R0sss %>% filter(Scenario=='M strategy')) + 
+  geom_line(aes(x=Temperature, y=R0,group=Food,size=as.numeric(Food)/3)) +
   theme_cowplot()+
@@
         plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
+  scale_size(guide='none',range = c(0.8,1.2))+
   labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('R0/R0'[max]))
-
-cowplot::plot_grid(f1,f2,f3,ncol=1,labels = 'auto')
+       y='Relative fitness')
+
+f3.2 <- ggplot(R0sss %>% filter(Scenario=='P strategy')) + 
+  geom_line(aes(x=Temperature, y=R0,group=Food,size=as.numeric(Food)/3)) +
+  theme_cowplot()+
+  theme(axis.text.y = element_text(colour = 'white'),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  scale_size(guide='none',range = c(0.8,1.2))+
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=' ')
+
+cowplot::plot_grid(f1.1,f1.2,f2.1,f2.2,f3.1,f3.2,ncol=2,labels = 'auto')
 
@@
 Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\cite{pauly_sound_2017,lefevre_modelling_2017}).
-We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organismal response to temperature.
+We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organism response to temperature.
 The general model and its parameter values are also easily adjusted to reflect particular organisms or theories.
@@
 At the onset of this limitation, ecological parameters change drastically, and growth, mortality are strongly impacted.
-This limitation closely mimics limitations seen in wild fish (\cite{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite{armstrong_diel_2013,claireaux_physiology_1995}).
+This limitation closely mimics limitations seen in wild fish (\cite{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}).
 Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages.
-For instance, oxygen limitation is a more severe constraint for small individuals (Figure \ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
-Also, changes in environmental oxygen supply, if beyond an oganisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
+For instance, oxygen limitation is a more severe constraint for small individuals (fig.
+\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
+Furthermore, changes in environmental oxygen supply, if beyond an organisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
 
 Variation in performance metrics away from temperature extremes, even if potentially correlated with aerobic scope (e.g., growth efficiency), are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
-Predictions from our model, in line with metabolic experiments and other physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\cite{lucas_utilization_1992,priede_metabolic_1985}).
+Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\cite{lucas_utilization_1992,priede_metabolic_1985}).
 Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\cite{priede_natural_1977,priede_metabolic_1985}).
@@
 
-Importantly, fitness is predicted to decline with increasing temeprature in nearly all scenarios.
+Importantly, fitness is predicted to decline with increasing temperature in nearly all our simulation scenarios.
 This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
 In many species, both the aerobic scope and growth efficiency peak at relatively high temperatures within the potential thermal range, yet species are generally found at temperatures lower than these optima (\cite{magnuson_thermal_1997, claireaux_influence_2000}).
-This apparent paradox can be explained by an opposing trend in fitness: fitness is predicted to decline with increasing temeprature in nearly all scenarios, and leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
+This apparent paradox can be explained by an opposing trend in fitness: fitness is predicted to decline with increasing temperature in nearly all scenarios, and leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
 The decline in fitness is caused by a decline in available energy with temperature, and a constant or increasing mortality rate.
@@
 
-Resource availibility imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
-Changes in prey availibility thus influence individual temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal acitivity level.
-In low-food environments, changing energetic demands with temperature are not easily adjusted for, and any adjustment demands higher energic costs and mortality risk.
-This environment-driven change in costs of temperature adjustments leads to the strong modulation of the growth repsonse, as well as changing gradients in fitness with temperature in these environments.
+Resource availability imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
+Changes in prey availability thus influence individual temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal activity level.
+In low-food environments, changing energetic demands with temperature are not easily adjusted for, and any adjustment demands higher energetic costs and mortality risk.
+This environment-driven change in costs of temperature adjustments leads to the strong modulation of the growth response, as well as changing gradients in fitness with temperature in these environments.
 In particular, in low-food environments, asymptotic size is strongly reduced at high temperatures, whereas this is not necessarily the case in high-food environments.
-Increased growth and mortality changes in such environments then combine to produce a more strongly domed fitness curve than in environemts where food supply is not limiting.
+Increased growth and mortality changes in such environments then combine to produce a more strongly domed fitness curve than in environments where food supply is not limiting.
 
@@
 
-Our prediction of constantly decreasing fitness with temperature, especially for relatively inactive species (M-strategists), contrasts with a previous species-specific eco-physiological model for cod that includes similar constraints to our model (\cite{holt_climate_2014,holt_climate_2015}), and which predicted relatively high fitness at high temperatures.
+Our prediction of constantly decreasing fitness with temperature, especially for relatively inactive species (safe strategists), contrasts with a previous species-specific eco-physiological model for cod that includes similar constraints to our model (\cite{holt_climate_2014,holt_climate_2015}), and which predicted relatively high fitness at high temperatures.
 Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, the product of $\delta*\tau$ is on the same order of magnitude in both models.
@@
 That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\cite{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
-Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\cite{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (M-strategy) life-history.
+Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\cite{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (safe strategy) life-history.
 Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
@@
 
-Optimal activity is predicted to increase with temperature in all but one of our simulations.
-This prediction is confirmed by many observations in experimental and field conditions for both larval and adult fish (\cite{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
+Optimal activity is predicted to increase with temperature in nearly all cases, but it is sensitive to the cost of activity - at higher cost relative to the potential pay-off, activity may even decline at high temeprature.
+Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\cite{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
 This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses.
-Only large individuals of the simulated P-strategy species will optimally decrease activity as a result of increased temperature.
+Only large individuals of the simulated production strategy species will optimally decrease activity as a result of increased temperature.
 In this case, additional activity will lead to comparatively small gains from feeding relative to the cost of activity and SDA, owing to the non-linearity of the functional response.
 
-Taken together, the physiological processes and optimisation described in our model provides a mechanistic underpinning for observations about changes of ecological rates, such as
+Taken together, the physiological processes and optimisation described in our model provide a mechanistic underpinning for observations about changes of ecological rates, such as
 increasing or dome-shaped consumption or attack-rates with temperature
@@
 
+Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\cite{atkinson_temperature_1994}), without needing to evoke direct changes in ecological rates with temperature.
+This leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (fig.s \ref{fig:norms}, \ref{fig:norms_O2}).
+Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\cite{angilletta_temperature_2004}).
+
 The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\cite{cheung_shrinking_2013, pauly_sound_2017}).
-We suggest that the general trait-based approach presented here provides a parsimonious compromise between overly-simplistic approximations that may provide misleading predictions about future ecosystems (\cite{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\cite{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
+We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\cite{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\cite{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
 In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT.
@@
 
-\section{Specification of temperature dependent oxygen availibility}
+\section{Specification of temperature dependent oxygen availability}
 
@@
 
-Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term describes the saturation dependence on ambient $O_2$ at temeprature $T$ ($O_2(T)$).
+Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term describes the saturation dependence on ambient $O_2$ at temperature $T$ ($O_2(T)$).
 At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}).
-We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{crit}$ is the ambient concentaration at which oxgygen supply ceases.
-Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentaration at 5\degree C.
-To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (Figure \ref{fig:O2_fig}).
+We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{crit}$ is the ambient concentration at which oxygen supply ceases.
+Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentration at 5\degree C.
+To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (fig.
+\ref{fig:O2_fig}).
 Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature.
@@
 \section{Maturation-reaction norm}
+\label{sec:MRN}
+
+A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig. \ref{fig:MRN}).
 
@@
 
-lam <- gouts[[2]]$t_growth
+lam <- goutr[[3]]$t_growth
 
@@
 @
+
+To express a MRN that varies as a function of age, we can reparametrise the MRN as:
+$$\phi(z) = 1/(1+\exp(-(c z))) \text{, where }$$
+$$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$  
+rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
 
@@
 @
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; aandb) and P-strategy (fast life-history; c, d).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for safe strategy (slow life history; aandb) and production strategy (fast life-history; c, d).}
 \label{fig:activity-rising}
@@
 
-<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+<<size-act_low,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm; e--f), for a production strategy (fast life-history) species with a dome-shaped maximum metabolic rate with respect to temperature.
+',fig.align='center'>>=
+
+scsa[[4]]$m <- 80
+scsa[[5]]$m <- 80
+scsa[[6]]$m <- 80
+
+scenarios_d <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('P strategy'),each=3),each=int_temp)),
+                                   AC= as.factor(rep(rep(c('High','Medium','Low'),1),each=int_temp))),
+                       bind_rows(lapply(scsa[4:6], plot_data_temp)))
+
+sc_actd <- gather(scenarios_d,Activity,value,Optimum, Limit,Realised) %>%
+  mutate(Activity = relevel(as.factor(Activity), "Realised"),
+         Dispatch = paste(Scenario,AC))
+
+laba <- as_labeller(c(`P strategy Low` ='a',
+                   `P strategy Medium`  ='b',
+                   `P strategy High` ='c'))
+
+sc_actd$Dispatch <- factor(sc_actd$Dispatch,levels=unique(sc_actd$Dispatch)[order(unlist(laba(unique(sc_actd$Dispatch))))])
+
+ggplot(sc_actd) + 
+  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
+  theme_cowplot()+
+  scale_color_manual(values = cols,guide='none')+
+  scale_linetype(guide='none')+
+  facet_wrap(~Dispatch,ncol = 1,labeller = laba)+
+  theme(strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank()) + 
+  labs(x = expression("Mean temperature " ( degree*C)),
+       y=expression('Activity ' (tau)))
+
+@
+
+<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for safe strategy (slow life history; left column [a,c,e]) and production strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.
+Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center'>>=
 
@@
          Feeding=`Feeding level`,
-         `Available Energy` = sc(`C for growth`),
-         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
-         Fitness = sc(Energy/M)) %>% 
+         M = sc(M),
+         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
+         `Relative M` = sc(M),
+         `Energy` = sc(`Available Energy`),
+         Fitness = sc(`Available Energy`/M)) %>%  
   tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
@@
 \centering
-<<norms02, fig.align='center',fig.height=6>>=
+<<norms_O2, fig.align='center',fig.height=6>>=
 
@@
 t_growth <- bind_rows(lapply(1:length(goutr), function(x) {
-  y <- gouts[[x]][['t_growth']] 
+  y <- goutr[[x]][['t_growth']] 
   y$Scenario <- scn[x]
@@
 @
-\caption{Contrasting growth reponses at baseline resource availibility for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
-Growth curves are shown for M- (left column [a,c]) and P-strategists (right column [b,d]).
-Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.}
-\label{fig:activity-rising}
+\caption{Contrasting growth responses at baseline resource availability for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
+Growth curves are shown for safe- (left column [a,c]) and production strategists (right column [b,d]).
+Increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.}
+\label{fig:norms_O2}
 \end{figure}
 
+<<>>=
+
+scsg <- lapply(scsg,function(x) {x$slope=-1;x})
+
+goutss <- parallel::mclapply(scsg[1:3],
+                             plot_data_growth_tO2,
+                             mstar=mstar_ss,
+                             mc.cores = 3)
+
+goutsf <- parallel::mclapply(scsg[4:6],
+                             plot_data_growth_tO2,
+                             mstar=mstar_fs,
+                             mc.cores = 3)
+
+gouts <- c(goutss,goutsf)
+
+@
+
+<<norms_neg, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
+
+labla <- as_labeller(c(`M strategy Low` ='a',
+                   `P strategy Low`  ='b',
+                   `M strategy Medium` ='c',
+                   `P strategy Medium` = 'd',
+                   `M strategy High` = 'e',
+                   `P strategy High` = 'f'
+))
+
+t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- gouts[[x]][['t_growth']] 
+  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
+  y$Food<- rep(c('Low','Medium','High'),2)[x]
+  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
+  y}))
+
+t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
+
+#browser()
+norm <- t_growth %>% 
+  group_by(Dispatch,Temperature) %>%
+  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
+            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
+            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
+            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
+
+ggplot() +
+  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
+  geom_point(aes(x=ts, y=m),data=norm) +
+  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
+  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
+  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
+  theme_cowplot()+
+  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
+  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
+  theme(legend.text = element_text(size=8),
+        legend.title = element_text(size=9),
+        strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  coord_cartesian()+
+  labs(y = 'Length (cm)',
+       x='Age  (years)')
+
+@
+
+<<>>=
+
+scsg <- lapply(scsg,function(x) {x$slope=1;x})
+
+goutss <- parallel::mclapply(scsg[1:3],
+                             plot_data_growth_tO2,
+                             mstar=mstar_ss,
+                             mc.cores = 3)
+
+goutsf <- parallel::mclapply(scsg[4:6],
+                             plot_data_growth_tO2,
+                             mstar=mstar_fs,
+                             mc.cores = 3)
+
+gouts <- c(goutss,goutsf)
+
+@
+
+<<norms_pos, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
+
+labla <- as_labeller(c(`M strategy Low` ='a',
+                   `P strategy Low`  ='b',
+                   `M strategy Medium` ='c',
+                   `P strategy Medium` = 'd',
+                   `M strategy High` = 'e',
+                   `P strategy High` = 'f'
+))
+
+t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
+  y <- gouts[[x]][['t_growth']] 
+  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
+  y$Food<- rep(c('Low','Medium','High'),2)[x]
+  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
+  y}))
+
+t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
+
+#browser()
+norm <- t_growth %>% 
+  group_by(Dispatch,Temperature) %>%
+  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
+            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
+            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
+            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
+            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
+
+ggplot() +
+  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
+  geom_point(aes(x=ts, y=m),data=norm) +
+  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
+  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
+  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
+  theme_cowplot()+
+  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
+  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
+  theme(legend.text = element_text(size=8),
+        legend.title = element_text(size=9),
+        strip.text = element_text(hjust = 0),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  coord_cartesian()+
+  labs(y = 'Length (cm)',
+       x='Age  (years)')
+
+@
+
 \end{document}

### 2018-07-04 model.R

@@ -307,7 +307,7 @@ model_out <- function(tau_max,
   inp <- (1-phi-beta)*f*tc*h*m^q
   out <- k*tc*m^n + tau_max*delta*k*tc*m^o
   e <-  inp -out
-  efficiency <- e/f
+  efficiency <- e/(f)
   efficiency[efficiency<0] <- 0
   predation_rate <- f/phi
   

### 2018-07-06 MS_AMNat.Rnw
AmNat submission

--- 2018-07-04 draft_model_only.Rnw
@@
-\documentclass[a4paper, toc=index,abstract=true]{scrartcl}
+\documentclass[11pt]{article}
+\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
+\usepackage{fullpage}
 \usepackage{gensymb}
-\usepackage{geometry}
-\usepackage{enumitem}
-\usepackage{setspace}
+\usepackage{multirow}
 \usepackage{booktabs}
-\usepackage{subfig}
-\usepackage{placeins}
 \usepackage{amsmath}
-\usepackage{pdflscape}
-\usepackage{multirow}
-\usepackage{longtable}
-\usepackage[toc,page]{appendix}
-\usepackage{array,booktabs}
-\usepackage[american]{babel}
-\usepackage[backend=biber,
-mincitenames = 1,
-maxcitenames = 1,
-uniquename = false,
-uniquelist = false,
-citestyle = authoryear-comp]{biblatex}%
-\usepackage{lineno, blindtext}
-\addbibresource{Sizing-fx-of-temperature.bib}
-\captionsetup[table]{singlelinecheck=false}
-
-\title{Explaining thermal performance of fish: interplay of behaviour, ecology and physiology drive growth and fitness responses}
-\author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
-        Ken H. Andersen\\Centre for Ocean Life
-        Danish Technical University, Lyngby, Denmark}
+\usepackage[authoryear,sectionbib,sort]{natbib}
+\linespread{1.7}
+\usepackage[utf8]{inputenc}
+\usepackage{lineno}
+\usepackage{titlesec}
+\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
+\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
+\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
+\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}
+
+\title{Thermal performance of fish is explained by an interplay between physiology, behaviour, and ecology}
+
+% \author{Philipp Neubauer^{1,\ast}$ \\ 
+%         Ken H. Andersen$^{2,\dag}$}
+
+\date{}
 
@@
 
-\begin{spacing}{1.9}
-
-\pagenumbering{gobble}
-\begin{abstract}
+% \noindent{} 1. Dragonfly Data Science, PO Box 27535, Wellington 6141, New Zealand;
+% 
+% \noindent{} 2. Centre for Ocean Life, National Institute of Aquatic Resources, Technical University of Denmark, 7 Kemitorvet B-202, 2800 Kongens Lyngby, Denmark;
+
+\bigskip
+
+\textit{Manuscript elements}: Figure~1, figure~2, table~1, online appendices~A and B (including figure~A1 and figure~A2). Figure~2 is to print in color.
+
+\bigskip
+
+\textit{Keywords}: thermal performance, OCLTT, metabolic rate, climate change
+
+\bigskip
+
+\textit{Manuscript type}: Article.
+
+\bigskip
+
+\noindent{\footnotesize Prepared using the suggested \LaTeX{} template for \textit{Am.\ Nat.}}
+
+\linenumbers{}
+\modulolinenumbers[3]
+
+\newpage{}
+
+\section*{Abstract}
 
@@
 Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of metabolic rates, oxygen limitation, and environmental conditions on ecotherm performance.
-We show that oxygen limitation is not necessary to explain performance curves that are correlated with metabolic scope.
-Oxygen can drastically limit performance and fitness, especially at temperature extremes, but changes in thermal performance are primarily driven by the interplay of changing metabolic rates and species ecology.
+We show that oxygen limitation is not necessary to explain performance variation with temperature.
+Oxygen can drastically limit performance and fitness, especially at temperature extremes, but changes in thermal performance are primarily driven by the interplay between changing metabolic rates and species ecology.
 Furthermore, our model reveals that fitness trends with temperature can oppose trends in growth, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
-We suggest that this model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on the performance of fish and other ectotherms, and act as a null model for contrasting temperature impacts on species with different metabolic and ecological traits.
-
-\end{abstract}
-{\large Keywords:} thermal performance curves, OCLTT, metabolic rates, climate change
+Our model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on the performance of fish and other ectotherms, and act as a null model for contrasting temperature impacts on species with different metabolic and ecological traits.
 
@@
 
-\section{Introduction}
-
-Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\cite{deutsch_climate_2015,pinsky_marine_2013,brown_toward_2004}).
-As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\cite{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).
+\section*{Introduction}
+
+Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\citealt{deutsch_climate_2015,pinsky_marine_2013}).
+As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\citealt{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).
 However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems.
-Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\cite{brander_overconfidence_2013, lefevre_models_2017}).
-In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017}).
-
-There are few general concepts and models that can explain thermal performance and ecological responses to temperature.
-To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angilletta_temperature_2004,atkinson_temperature_1994}), or attack rates (\cite{englund_temperature_2011,rall_universal_2012}) with temperature, from fundamental physiological processes.
-Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{angilletta_temperature_2004,vucic-pestic_warming_2011, guiet_effects_2016}).
-
-Although ecological rates seem to follow some general patterns in the response to temperature , there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}).
-A phenomenological description that assumes a general ecological temperature response thus often fails to explain heterogeneity in ecological responses (\cite{angilletta_temperature_2004}), and leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
+Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\citealt{brander_overconfidence_2013, lefevre_models_2017}).
+In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\citealt{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\citealt{brander_overconfidence_2013, lefevre_models_2017,jutfelt_oxygen-and_2018}).
+
+Although there are conceptual and model frameworks to explain aspects of thermal performance and ecological responses to temperature (\citealt{fry_effects_1947,brown_toward_2004,pauly_sound_2017,portner_oxygen-and_2010}), many of these remain controversial as they appear limited in their generality or predictive capacity (\citealt{lefevre_models_2017,jutfelt_oxygen-and_2018}).
+To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in  ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angilletta_temperature_2004,atkinson_temperature_1994}), or attack rates (\citealt{englund_temperature_2011,rall_universal_2012}) with temperature, from fundamental physiological processes.
+Instead, and as advocated by the metabolic theory of ecology (\citealt{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{angilletta_temperature_2004,vucic-pestic_warming_2011, guiet_effects_2016}).
+
+A phenomenological description that assumes a general ecological temperature response often fails to explain heterogeneity in ecological responses (\citealt{angilletta_temperature_2004,rall_universal_2012}).
+Although ecological rates seem to follow some general patterns in the response to temperature, there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}).
+This leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
 In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011,lefevre_models_2017}).
@@
 
-Physiologically, a long held view has been that temperature is a controlling factor while oxygen supply sets the physiological limits (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016}).
+Physiologically, a long held view has been that temperature is a controlling factor while oxygen supply sets the physiological limits (\citealt{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016}).
 How exactly temperature influences ectotherm physiological rates and limits, however, has been a matter of debate, not least because of the variable responses observed among different species.
 In most species, the standard metabolism (SM; the metabolic cost of maintenance and routine activity such as ventilation) increases near exponentially with temperature.
-A prevalent view is that the maximum metabolic rate (MMR; the metabolic rate at maximum sustained exercise) has a dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\cite{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
+A prevalent view is that the maximum metabolic rate (MMR; the metabolic rate at maximum sustained exercise) has a dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\citealt{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
 This leads to the view of a uni-modal curve for metabolic scope (MMR minus SM; the available oxygen/energy for additional activity), and suggests that towards the upper end of this curve, organisms will, simply put, run out of oxygen.
 
-This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\cite{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
-In some species, however, maximum metabolic rate increases steadily (\cite{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor at high temperatures.
-Indeed, it has been argued that oxygen is unlikely to determine performance for most species over most of their temperature range as oxygen limits are rarely reached during normal activity (\cite{jutfelt_oxygen-and_2018, holt_climate_2015}).
+This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\citealt{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
+In some species, however, maximum metabolic rate increases steadily (\citealt{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor at high temperatures.
+Indeed, it has been argued that oxygen is unlikely to determine performance for most species over most of their temperature range as oxygen limits are rarely reached during normal activity (\citealt{jutfelt_oxygen-and_2018, holt_climate_2015}).
 
@@
 
-\section{Methods}
-
-\subsection{Key assumptions}
-
-Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets (\cite{holt_climate_2015,holt_climate_2014}).
+\section*{Methods}
+
+\subsection*{Key assumptions}
+
+Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets (\citealt{holt_climate_2015,holt_climate_2014}).
 We assume that animals will adapt activity levels to optimise available energy for growth and reproduction relative to mortality risk.
@@
 
-\subsection{Model description}
-Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality (\cite{gilliam_habitat_1987}).
+\subsection*{Model description}
+Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality (\citealt{gilliam_habitat_1987}).
 In the following, we refer to $\tau$ as the activity fraction for sake of generality.
@@
 \end{align}
-where the feeding level ($[0:1]$)is given by a Holling type II function response:
+where the feeding level $[0:1]$ is given by a Holling type II function response:
 \begin{align}
@@
 where $h c(T) w^q$ is the maximum consumption rate.
-The feeding level ([0,1]) is determined by the fraction of time spent foraging $\tau$, foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
+The feeding level is determined by the fraction of time spent foraging $\tau$ (henceforth the activity fraction), foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
 The supply is discounted by the loss due to specific dynamic action  $\beta$ (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
 
-Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}, and the activity fraction.
-Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \cite{jeschke_predator_2002, sentis_parsing_2013}) as $c(T) = e^{E_a(T-T_0)/(kTT_0)}$.
+Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazier_activity_2009,brett1965relation}, and the activity fraction.
+Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approimated by an Arrhenious scaling $c(T) = e^{E_a(T-T_0)/(bTT_0)}$, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (here 15 degrees Celsius), and $b$ is the Bolzman constant.
+Note that we only scale rates related to enzymatic activity with temperature, we do assume that ecological rates such as foraging rates or activity are a direct function of temperature.
+Rather, they are modulated by an individual's behavioural response to temperature driven physiological changes.
 
@@
   P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
-        &= s_(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
+        &= S_{O_2}c_{O_2}(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
 \end{align}
 Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.
-The oxygen supply scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as MOS that increase continuously up to a lethal temperature (fig.
-\ref{fig:O2_fig}, Appendix A).
-
-Fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \cite{gilliam_habitat_1987}:
+The oxygen supply ($S_{O_2}c_{O_2}(T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig./~\ref{fig:O2_fig_used}).
+The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
+Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\citealt{priede_metabolic_1985}).
+We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR.
+We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck2013freshwater, lefrancois_influence_2003}):
+
+\begin{align}
+s_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{\text{crit}})\log(0.5)/(P\text{50}-P_{\text{crit}})}\right),\\
+\lambda(T)&=\zeta\left(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right)^\eta \times \exp\left(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right),
+\end{align}
+
+Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the $s_{O_2}(T)$ term describes the saturation dependence on ambient $O_2$ at temperature $T$ ($O_2(T)$).
+At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}).
+We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{\text{crit}}$ is the ambient concentration at which oxygen supply ceases.
+Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentration at 5\degree C.
+To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height.
+Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig./~\ref{fig:O2_fig}).
+
+\input{O2_fig}
+
+In pour model, fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \citealt{gilliam_habitat_1987}:
 \begin{equation}
@@
 \end{equation}
-This optimisation represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for optimisation in stable environments (\cite{sainmont_effective_2015}).
-Mortality scales with activity fraction and weight as $w^{q-1}$ (\cite{andersen_how_2009, hartvig_food_2011}):
+This optimisation represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for optimisation in stable environments (\citealt{sainmont_effective_2015}).
+Mortality scales with activity fraction and weight as $w^{q-1}$ (\citealt{andersen_how_2009, hartvig_food_2011}):
 \begin{equation}
@@
 In other words, we consider time scales that are long enough to ignore the ability of many ectotherms to go into oxygen debt, or to switch to anaerobic metabolism for limited periods of time.
-This means we assume that animals will adapt their effort to optimise fitness given temperature and oxygen constraints.
-
-\subsection{Defining performance metrics}
-
-Performance itself is a vague concept that is often used without definition in the relevant literature, but it is only defined in the context of a particular physiological or demographic parameter, with potentially different thermal response curves (\cite{jutfelt_oxygen-and_2018}).
-For instance, even though growth in ectotherms is often impacted by temperature (\cite{angilletta_temperature_2004}), measured performance may depend strongly on what aspect of growth is measured --- whether it is the growth increment at a particular size, growth efficiency per unit intake, the attained asymptotic size, or parameters of a fitted growth curve.
+This means we assume that animals will adjust their foraging effort to optimise fitness given temperature and oxygen constraints.
+Note, that this optimal foraging assumption drives ecological responses as a consequence of physiological constraints, rather than as a direct response to temperature itself.
+
+\subsection*{Defining performance metrics}
+
+Performance itself is a vague concept that is often used without definition in the relevant literature, but it is only defined in the context of a particular physiological or demographic parameter, with potentially different thermal response curves (\citealt{jutfelt_oxygen-and_2018}).
+For instance, even though growth in ectotherms is often impacted by temperature (\citealt{angilletta_temperature_2004}), measured performance may depend strongly on what aspect of growth is measured --- whether it is the growth increment at a particular size, growth efficiency per unit intake, the attained asymptotic size, or parameters of a fitted growth curve.
 We use and compare four performance measures with broad ecological and practical implications:
@@
 \item Growth curves predicted through ontogeny, which allow us to compare growth performance early and late in life (i.e., juvenile growth vs asymptotic size).
-\item Growth efficiency, here defined as available energy relative to the feeding level (i.e., $\frac{P(w,T)}{f(w,T)}$.
-\item The ratio of $P/M$ (Gilliam's rule) used above as a short-sighted fitness aproximation.
-\item Fitness integrated over an individual's lifetime, defined as $R0$ (see below).
+\item Production efficiency, here defined as available energy for both growth and reproduction, relative to the food consumption (i.e., $\frac{P(w,T)}{f(w,T)h c(T) w^q)}$.
+\item The dimensionless ratio of $\frac{P}{Mw}$, which is analogous to the short-sighted fitness aproximation (Gilliam's rule) used above.
+\item Fitness integrated over an individual's lifetime, defined as $R_0$ (see below).
 
@@
 
-\subsection{Growth response}
+\subsection*{Growth response}
 
@@
 The slope of maturation reaction norms is evolutionarily determined by the strength of the co-variation between growth and mortality for a given population in a given environment.
-Strongly positive co-variation leads to the relatively flat reaction norms observed for most fish populations (\cite{marty_impact_2011}).
+Strongly positive co-variation leads to the relatively flat reaction norms observed for most fish populations (\citealt{marty_impact_2011}).
 This covariation is probably the consequence of good growth conditions (e.g., from increased prey density) altering the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators).
 We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past.
-Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm (i.e., allocation to reproduction is a function of size only; fig.
-\ref{fig:MRN}), although sloping reaction norms can be formulated and used in our framework (see appendix \ref{sec:MRN}).
-The intercept of this reaction norm was found numerically by maximising fitness ($R0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was assumed fixed as temperatures change.
+Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm (i.e., allocation to reproduction is a function of size only; fig./~\ref{fig:MRN}), although sloping reaction norms can be formulated and used in our framework (see appendix \ref{sec:MRN}).
+The intercept of this reaction norm was found numerically by maximising fitness ($R_0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was assumed fixed as temperatures change.
 
 The allocation was parametrised as 
-$$\phi(w^*) = 1/(1+\exp(-cw^*))$$,
+\[ \phi(w^*) = 1/(1+\exp(-cw^*))\],
 where $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
@@
 
-\subsection{Fitness consequences}
+\subsection*{Fitness consequences}
 
@@
 On these time-scales, we assume that adaptive responses are negligible.
-We investigate over-all fitness with respect to temperature by calculating R0 for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
-R0 was calculated as
-
-$$R0 = \int_0^\infty \phi(z(t,w_t,w^*))P(w_t,T)S_{0 \rightarrow t} dt, \text{, where}$$
-$$S_{0 \rightarrow t} = \int_0^t \exp(-M(w_t))\text{dt}$$
-
-\subsection{Trait based scenarios}
-
-To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
-Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the production strategy, indicated by a supercript $p$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth safe strategy, indicated by a supercript $s$).
-This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
-In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm) with defensive/sluggish versus active life-histories.
-
-To implement this axis, we used the result that species with a more
-active, production oriented life-history (e.g., predatory pelagic
-fish) have a higher standard metabolism and lower weight scaling of
-metabolic costs
-(\cite{priede_metabolic_1985,killen_intraspecific_2010}). We assumed
-that higher standard metabolism is due to increased digestive capacity
-(i.e., is used for gut maintenance), though high muscle mass and a
-larger heart will also contribute to higher standard metabolism in
-active species (\cite{priede_metabolic_1985}). In practice, we assumed
-that approximately 50\% of the standard metabolic cost is due to gut
-maintenance, such that a doubling of the maximum ingestion leads to a
-50\% increase in standard metabolic cost.
-We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M^{s}(w) = (0.1+6\tau) w^{q-1}$ and $M^{p}(w) = (1+\tau) w^{q-1}$).
-Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
-Together, these assumed trait differences lead to very different ecological and bio-energetic responses of safe- and production strategists (fig.
-\ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for safe-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to feeding level) at high activity levels.
-A slower increase in available energy and M with $\tau$ for production strategists leads to a higher $\tau_{\text{opt}}$.
-
-We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \cite{salin_inadequate_2016,iftikar_mitochondria_2013}).
-In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig.
-\ref{fig:O2_fig}).
-Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\cite{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
-However the over-all mechanism would be the same to the one assumed here, with different untis (e.g., ATP instead of $O_2$).
-
-\begin{table}
-\caption{Parameters of the constrained activity model for two scenarios: safe strategy and production strategy species.
-For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
-Values in brackets for $\gamma$ are alternative resource availability scenarios.}
-\label{tab:parameters}
-\begin{tabular}{llcc}
- \multirow{2}{*}{Description} &  \multirow{2}{*}{Symbol (unit)} & \multicolumn{2}{r}{Value} \\
- \cmidrule{3-4}
- & & safe strategy  & production strategy \\
-
-\hline
-\addlinespace
-\multicolumn{4}{c}{\textbf{Biomass Metabolism}} \\
-Specific dynamic action & $\beta$ & \multicolumn{2}{c}{0.15} \\
-Egestion and excretion & $\phi$ & \multicolumn{2}{c}{0.25}  \\
-Coeff. for std.~metabolism  & $k$ (g$^{1-n}\cdot$y$^{-1}$)  & 1 &  1.5 \\
-Coeff. for act.~metabolism  & $k$ (g$ \cdot$y$^{-1}$)  & 4 &  2 \\
-Exponent for std.~metabolism & $n$ & 0.88 & 0.75  \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Feeding ecology}}\\
-Coeff. for Encountered food & $\gamma\Theta$ (g$^{1-p} \cdot$y$^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
-Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
-Coeff. for Maximum consumption rate & $h$ (g$^{1-q}\cdot$y$^{-1}$) & 30 & 60  \\
-Exponent for max.~consumption $h$ & $q$ & \multicolumn{2}{c}{0.8} \\
-Coeff. for constant mortality & $M$ (g$\cdot$y$^{-1}$) & 0.1  & 1  \\
-Coeff. for activity related mortality & $\rho$(y$^{-1}$) & 6 & 1\\
-Exponent for mortality & $\nu$ & \multicolumn{2}{c}{0.2} \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Temperature}}\\
-Reference temperature  & $T_{\text{ref}}$ (°C)& \multicolumn{2}{c}{15} \\
-Activation energy & $E_a$ & \multicolumn{2}{c}{0.52} \\
-Temperature at maximum MOS & $T_{\text{max}}$ & \multicolumn{2}{c}{20/25}\\
-Temperature range & $T^-_{\text{lethal}}$--$T^+_{\text{lethal}}$ & \multicolumn{2}{c}{5--26} \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Reaction norm}}\\
-
-Slope &  & \multicolumn{2}{c}{0}\\
-Reaction & $c$ & \multicolumn{2}{c}{0.5} \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Oxygen budget}} \\
-Critical $O_2$ & $P_{\text{crit}}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{2}\\
-Dissolved $O_2$ at $0.5\times f_{\text{max}}(O_2)$  & $P50$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{4} \\
-Doming for $O_2$ supply & $\eta$ & \multicolumn{2}{c}{3/0.1}\\
-Level of $O_2$ supply  & $\zeta$ (g$\cdot$y$^{-1}$) &  0.5 & 1\\
-
-\hline
-\end{tabular}
-\end{table}
+We investigate over-all fitness with respect to temperature by calculating $R_0$ for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
+$R_0$ was calculated as
+
+\[R_0(T) = \int_0^\infty \phi(w(t),w^*)P(w(t),T)S_{0 \rightarrow t}(T) \text{d}t, \text{, where} \\
+S_{0 \rightarrow t}(T) = \int_0^t \exp(-M(w(t),T))\text{d}t \]
 
@@
 
-\section{Results}
-
-Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig.
-\ref{fig:activity}).
-This adjustment is especially pronounced in safe strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig.
-\ref{fig:size-act}).
-A similar increase in activity is observed for small production strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.
-\ref{fig:size-act}).
-For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
-For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig.
-\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
-For species with a rising MOS with temperature, oxygen is not limiting (fig.
-\ref{fig:activity-rising}).
-However, larger production strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
-This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig.
-\ref{fig:size-act_low}).
-
 <<scenarios,fig.cap='Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\\degree C) for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for safe- (a and b, respectively) and production strategy (c and d), for species in high (left column) and low (right column) food environments.
-All rates are plotted relative to their maximum for each trait scenario (i.e., by row), the optimal activity level $\\tau^*$ is indicated by the dotted vertical line.',fig.align='center',fig.height=5,fig.width=6>>=
-
-lab <- as_labeller(c(`M strategy High`  ='a',
-                   `P strategy High` = 'c',
-                   `M strategy Low`  ='b',
-                   `P strategy Low` = 'd'))
+Responses are shown for slow- (a) and fast strategy (b).
+All rates are plotted relative to their maximum for each trait scenario, the optimal activity level $\\tau^*$ is indicated by the dotted vertical line.',fig.align='center',fig.height=3,fig.width=6>>=
+
+lab <- as_labeller(c(
+                   `M strategy Low`  ='a',
+                   `P strategy Low` = 'b'))
 
 sc_bl <- baseline  %>%
-  #filter(!grepl('large',Scenario)) %>% 
+  filter(Food == 'Low') %>% 
   group_by(Scenario) %>%
@@
 tstar <- baseline  %>%
+  filter(Food == 'Low') %>%
   group_by(Scenario, Food) %>%
@@
 @
+
+\subsection*{Trait based scenarios}
+
+To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
+Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the fast strategy, indicated by a subscript $f$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth slow strategy, indicated by a subcript $s$).
+This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
+In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm or $w_{\infty}\sim 270$g) with defensive/sluggish versus active life-histories.
+
+To implement this axis, we used the result that species with a more
+active, production oriented life-history (e.g., predatory pelagic
+fish) have a higher standard metabolism and lower weight scaling of
+metabolic costs
+(\citealt{priede_metabolic_1985,killen_intraspecific_2010}). We assumed
+that higher standard metabolism is due to increased digestive capacity
+(i.e., is used for gut maintenance), though high muscle mass and a
+larger heart will also contribute to higher standard metabolism in
+active species (\citealt{priede_metabolic_1985}). In practice, we assumed
+that approximately 50\% of the standard metabolic cost is due to gut
+maintenance, such that a doubling of the maximum ingestion leads to a
+50\% increase in standard metabolic cost.
+We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M_{s}(w) = (0.1+6\tau) w^{q-1}$ and $M_{f}(w) = (1+\tau) w^{q-1}$).
+Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
+Together, these assumed trait differences lead to very different ecological and bio-energetic responses of slow- and fast strategists (fig./~\ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for slow-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to food intake) at high activity levels.
+A slower increase in available energy and M with $\tau$ for fast strategists leads to a higher $\tau_{\text{opt}}$.
+
+We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \citealt{salin_inadequate_2016,iftikar_mitochondria_2013}).
+In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig./~\ref{fig:O2_fig}).
+Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\citealt{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
+However the over-all mechanism would be the same to the one assumed here, with different untis (e.g., ATP instead of $O_2$).
+
+\begin{table}
+\caption{Parameters of the constrained activity model for two scenarios: slow strategy and fast strategy species.
+For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
+Values in brackets for $\gamma$ are alternative resource availability scenarios.}
+\label{tab:parameters}
+\begin{tabular}{llcc}
+ \multirow{2}{*}{Description} &  \multirow{2}{*}{Symbol (unit)} & \multicolumn{2}{r}{Value} \\
+ \cmidrule{3-4}
+ & & slow strategy  & fast strategy \\
+
+\hline
+\addlinespace
+\multicolumn{4}{c}{\textbf{Biomass Metabolism}} \\
+Specific dynamic action & $\beta$ & \multicolumn{2}{c}{0.15} \\
+Egestion and excretion & $\phi$ & \multicolumn{2}{c}{0.25}  \\
+Coeff. for std.~metabolism  & $k$ (g$^{1-n}\cdot$y$^{-1}$)  & 1 &  1.5 \\
+Coeff. for act.~metabolism  & $k$ (g$ \cdot$y$^{-1}$)  & 4 &  2 \\
+Exponent for std.~metabolism & $n$ & 0.88 & 0.75  \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Feeding ecology}}\\
+Coeff. for Encountered food & $\gamma\Theta$ (g$^{1-p} \cdot$y$^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
+Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
+Coeff. for Maximum consumption rate & $h$ (g$^{1-q}\cdot$y$^{-1}$) & 30 & 60  \\
+Exponent for max.~consumption $h$ & $q$ & \multicolumn{2}{c}{0.8} \\
+Coeff. for constant mortality & $M$ (g$\cdot$y$^{-1}$) & 0.1  & 1  \\
+Coeff. for activity related mortality & $\rho$(y$^{-1}$) & 6 & 1\\
+Exponent for mortality & $\nu$ & \multicolumn{2}{c}{0.2} \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Temperature}}\\
+Reference temperature  & $T_{\text{ref}}$ (°C)& \multicolumn{2}{c}{15} \\
+Activation energy & $E_a$ & \multicolumn{2}{c}{0.52} \\
+Temperature at maximum MOS & $T_{\text{max}}$ & \multicolumn{2}{c}{20/25}\\
+Temperature range & $T^-_{\text{lethal}}$--$T^+_{\text{lethal}}$ & \multicolumn{2}{c}{5--26} \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Reaction norm}}\\
+
+Slope &  & \multicolumn{2}{c}{0}\\
+Reaction & $c$ & \multicolumn{2}{c}{0.5} \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Oxygen budget}} \\
+Critical $O_2$ & $P_{\text{crit}}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{2}\\
+Dissolved $O_2$ at $0.5\times f_{\text{max}}(O_2)$  & $P_{50}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{4} \\
+Doming for $O_2$ supply & $\eta$ & \multicolumn{2}{c}{3/0.1}\\
+Level of $O_2$ supply  & $\zeta$ (g$\cdot$y$^{-1}$) &  0.5 & 1\\
+
+\hline
+\end{tabular}
+\end{table}
+
+\section*{Results}
+
+Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig./~\ref{fig:activity}).
+This adjustment is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig./~\ref{fig:size-act}).
+A similar increase in activity is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig./~\ref{fig:size-act}).
+For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
+For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig./~\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
+For species with a rising MOS with temperature, oxygen is not limiting (fig./~\ref{fig:activity-rising}).
+However, larger fast strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
+This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig./~\ref{fig:size-act_low}).
 
@@
 @
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for safe strategy (slow life history; a \& b) and production strategy (fast life-history; c \& d).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; a \& b) and fast strategy (fast life-history; c \& d).}
 \label{fig:activity}
@@
 
-<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for safe strategy (slow life history; left column [a,c,e]) and production strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
 
@@
 
-Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.
-\ref{fig:feeding}).
-For safe strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
-Available energy shows a dome-shaped response to temperature in safe strategists, and is maximised at relatively high temperatures.
+Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig./~\ref{fig:feeding}).
+For slow strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
+Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures.
 However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS.
-Growth efficiency  follows a near identical trend due to the relatively flat response in the feeding level $f$.
-
-For production strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig.
-\ref{fig:feeding}).
-Again, growth efficiency peaks at relatively high temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
+Production efficiency follows a near opposite trend due to the relatively flat response in the feeding level $f$, but temperature driven increases in maximum consumption.
+
+For fast strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig./~\ref{fig:feeding}).
+Again, production efficiency peaks at relatively low temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
 Given the relatively flat mortality levels, the ratio of $P/M$ largely follows the trend in $P$.
@@
 <<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for safe  and production strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
+Responses are shown for slow  and fast strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
 Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center',fig.height=5,fig.width=6>>=
@@
 
-Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig.
-\ref{fig:norms}).
-For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig.
-\ref{fig:norms_O2}).
-This can be explained by ontogenetic shifts in temperature optima for growth (fig.
-\ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals in either trait-scenario grow.
+Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig./~\ref{fig:norms}).
+For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig./~\ref{fig:norms_O2}).
+This can be explained by ontogenetic shifts in temperature optima for growth (fig./~\ref{fig:size-rates}): for small individuals, available energy and growth consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals in either trait-scenario grow.
 For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
 
-Resource availability strongly modulates this growth response to temperature: low resource availability leads to strong differences in asymptotic size, whereas high food availability leads to fast growth and larger asymptotic length at high temperatures (fig.
-\ref{fig:norms}).
+Resource availability strongly modulates this growth response to temperature: low resource availability leads to strong differences in asymptotic size, whereas high food availability leads to fast growth and larger asymptotic length at high temperatures (figs./~\ref{fig:norms},\ref{fig:infs}).
 In addition, in very resource poor conditions, individuals may not grow to reproductive size in our scenario of a flat MRN.
@@
 <<norms, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
 Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
@@
 
-Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig.
-\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\cite{sainmont_effective_2015}).
+<<infs, fig.cap='Interactive effects of food availibility and temperature of the asymptotic size ($L_{\\infty}$), with increasing linewidth showing increasing prey availibility for a) slow and b) fast life-history species.',fig.align='center',fig.width=6,fig.height=3>>=
+
+infs <- t_growth %>% 
+  mutate(Food = factor(Food, levels=c('Low','Medium','High'))) %>%
+  group_by(Scenario, Food,Temperature) %>%
+  summarise(lmax = max(t_length)) %>%
+  mutate(wmax = wl(lmax))
+
+size <- tidyr::gather(infs,size,value,-Scenario, -Food,-Temperature)
+
+labls <- as_labeller(c(`M strategy` ='a',
+                   `P strategy`  ='b'))
+
+ggplot() +
+  geom_line(aes(x=Temperature, y=value,size=as.numeric(Food),group=Food),data=size%>% filter(size=='lmax')) +
+  theme_cowplot()+
+  scale_linetype_discrete(guide='none') +
+  facet_wrap(~Scenario,labeller = labls) + 
+  scale_size(guide='none',range = c(0.6,1.4))+
+  theme(legend.text = element_text(size=8),
+        legend.title = element_text(size=9),
+        strip.text = element_text(hjust = 0.05),
+        strip.background = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_blank())+
+  coord_cartesian()+
+  labs(y = expression(L[infinity]~(cm)),
+       x=expression("Mean temperature " ( degree*C)))
+
+@
+
+Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig./~\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\citealt{sainmont_effective_2015}).
 With increasing temperatures, fitness declines at our basic parameter settings, in opposition to growth and aerobic scope.
 At low temperatures, fitness is limited by aerobic scope, with the magnitude determined by the extend of doming in aerobic scope.
-Note that this limitation through the aerobic scope appears at higher temperatures than apparent from fig.
-\ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (fig.
-\ref{fig:size-rates}).
-Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig.
-\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for safe strategy species, and moves the fitness optimum to higher temperatures for production strategy species.
-Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for production strategists, and a slower decline of fitness with temperature.
+Note that this limitation through the aerobic scope appears at higher temperatures than apparent from fig./~\ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (fig./~\ref{fig:size-rates}).
+Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig./~\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for slow strategy species, and moves the fitness optimum to higher temperatures for fast strategy species.
+Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for fast strategists, and a slower decline of fitness with temperature.
 
@@
 
-<<fit, fig.cap='Fitness (R0), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for safe- (a) and production strategy (b) species at the assumed maturation-raction norm and base parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)',fig.align='center',fig.height=8>>=
+<<fit, fig.cap='Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and base parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)',fig.align='center',fig.height=8>>=
 
@@
         plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.8,1.2))+
+  scale_size(guide='none',range = c(0.6,1.4))+
   labs(x = ' ',
@@
         plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.8,1.2))+
+  scale_size(guide='none',range = c(0.6,1.4))+
   labs(x =' ',
@@
         plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.8,1.2))+
+  scale_size(guide='none',range = c(0.6,1.4))+
   labs(x = expression("Mean temperature " ( degree*C)),
@@
 
-\section{Discussion}
+\section*{Discussion}
 
 In this study, we attempt to provide a general mechanistic basis for exploring thermal sensitivities of ectotherm organisms.
-Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\cite{pauly_sound_2017,lefevre_modelling_2017}).
+Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\citealt{pauly_sound_2017,lefevre_modelling_2017}).
 We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organism response to temperature.
@@
 
-It has been argued that the OCLTT as a concept provides a basis to explain observed responses to climate change on the basis of oxygen limitation via the aerobic scope (\cite{portner_physiology_2008,portner_oxygen-and_2010}), and simple oxygen budgets have been used to predict metabolic constraints on organismal activity due to warming ocean temperatures (\cite{deutsch_climate_2015}).
-As a conceptual framework, however, the OCLTT is subject not only to semantic dispute but also criticism of its core concept of oxygen limitation (\cite{jutfelt_oxygen-and_2018,lefevre_are_2016}).
-
-Our quantitative thermal impact model generalises existing eco-physiological models for particular species and stocks (\cite{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}), and allows to develop a more nuanced understanding of interactions between temperature, oxygen limitation and ecology for species with varying traits.
+It has been argued that the OCLTT as a concept provides a basis to explain observed responses to climate change on the basis of oxygen limitation via the aerobic scope (\citealt{portner_physiology_2008,portner_oxygen-and_2010}), and simple oxygen budgets have been used to predict metabolic constraints on organismal activity due to warming ocean temperatures (\citealt{deutsch_climate_2015}).
+As a conceptual framework, however, the OCLTT is subject not only to semantic dispute but also criticism of its core concept of oxygen limitation (\citealt{jutfelt_oxygen-and_2018,lefevre_are_2016}).
+
+Our quantitative thermal impact model generalises existing eco-physiological models for particular species and stocks (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}), and allows to develop a more nuanced understanding of interactions between temperature, oxygen limitation and ecology for species with varying traits.
 In line with the conceptual framework of Fry's aerobic scope and the OCLTT, our model suggests that oxygen limitation can be a potentially important ecological driver, especially at extreme temperatures for species with declining MOSs in such temperature regimes.
 At the onset of this limitation, ecological parameters change drastically, and growth, mortality are strongly impacted.
-This limitation closely mimics limitations seen in wild fish (\cite{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}).
+This limitation closely mimics limitations seen in wild fish (\citealt{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}).
 Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages.
-For instance, oxygen limitation is a more severe constraint for small individuals (fig.
-\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
+For instance, oxygen limitation is a more severe constraint for small individuals (fig./~\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
 Furthermore, changes in environmental oxygen supply, if beyond an organisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
 
-Variation in performance metrics away from temperature extremes, even if potentially correlated with aerobic scope (e.g., growth efficiency), are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
-Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\cite{lucas_utilization_1992,priede_metabolic_1985}).
-Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\cite{priede_natural_1977,priede_metabolic_1985}).
-Furthermore, as a limit for long-term performance, the MOS does not usually impose a limitation on short term energy demands, as fish can incur oxygen debt during swimming bursts during which the MOS is exceeded (\cite{brett_metabolic_1972,priede_metabolic_1985}).
+Variation in performance metrics away from temperature extremes are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
+Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\citealt{lucas_utilization_1992,priede_metabolic_1985}).
+Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\citealt{priede_natural_1977,priede_metabolic_1985}).
+Furthermore, as a limit for long-term performance, the MOS does not usually impose a limitation on short term energy demands, as fish can incur oxygen debt during swimming bursts during which the MOS is exceeded (\citealt{brett_metabolic_1972,priede_metabolic_1985}).
 A logical conclusion is that the metabolic scope is only limiting to performance at extreme temperatures where MOS is low due to impaired oxygen delivery.
 
-Importantly, fitness is predicted to decline with increasing temperature in nearly all our simulation scenarios.
-This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
-In many species, both the aerobic scope and growth efficiency peak at relatively high temperatures within the potential thermal range, yet species are generally found at temperatures lower than these optima (\cite{magnuson_thermal_1997, claireaux_influence_2000}).
-This apparent paradox can be explained by an opposing trend in fitness: fitness is predicted to decline with increasing temperature in nearly all scenarios, and leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
-The decline in fitness is caused by a decline in available energy with temperature, and a constant or increasing mortality rate.
-Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\cite{claireaux_influence_2000, magnuson_thermal_1997}).
-However, in relatively homogeneous habitats such as marine ecosystems, for example, the simple negative relationship between growth and fitness across the temperature range provides a parsimonious explanation for this apparent paradox.
+In many species, both the aerobic scope and growth peak at relatively high temperatures within the potential thermal range, yet species are often found at temperatures lower than these optima (\citealt{magnuson_thermal_1997, claireaux_influence_2000}).
+Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\citealt{claireaux_influence_2000, magnuson_thermal_1997}).
+In nearly all our simulation scenarios, fitness is predicted to decline with increasing temperature.
+This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.s
 
@@
 leading to increased fitness at warmer temperatures. Our
-base-parametrisation is based on the assumption that the fractional
-aerobic scope reflects the cost of maximal activity (i.e., cost of
-$\tau=1$) relative to standard metabolism. The fractional scope varies
-widely around an average of $\delta \approx 4$ (\cite[e.g.,
-][]{killen_ecological_2016}), however, this approximation may not
+base-parametrisation is based on the assumption that activity cost $k_a$ reflects the cost of maximal activity (i.e., cost of
+$\tau=1$), and has the same pay-off for all life-histories. This approximation may not
 reflect actual activity cost as swimming at MMR in fast predatory fish
 is far more efficient than swimming of sluggish fish, such as flatfish
-(\cite{priede_metabolic_1985}).
+(\citealt{priede_metabolic_1985}).
 Such an efficiency gain may occur as a result of more efficient form or physiology, or simply by reduced drag at large size (e.g., whale-sharks), and may be a key requirement to the viability of active pelagic predatory fish in tropical waters.
 
-Our prediction of constantly decreasing fitness with temperature, especially for relatively inactive species (safe strategists), contrasts with a previous species-specific eco-physiological model for cod that includes similar constraints to our model (\cite{holt_climate_2014,holt_climate_2015}), and which predicted relatively high fitness at high temperatures.
-Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, the product of $\delta*\tau$ is on the same order of magnitude in both models.
-Differences may also be due to key assumptions about time-scales in the model --- we assume an evolutionarily fixed maturation reaction norm that drives relative growth and reproductive output across temperatures.
-In other words, we explicitly model species responses on ecological time-scales.
-Models of Holt \& Joergensen have assumed that adaption of reproductive investment is instantaneous with changing temperatures --- species display an evolutionarily optimal maturation-reaction at any temperature (\cite{holt_climate_2014,holt_climate_2015}).
-This, however, would require foresight about future environmental conditions and related reproductive output.
-In practice this optimisation occurs through selection, and we suggest that our "short-sighted" optimisation of activity coupled with a evolutionarily stable maturation-reaction norm provides a more explicit separation of evolutionary and ecological time-scales.
-
-That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\cite{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
-Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\cite{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (safe strategy) life-history.
+That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\citealt{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
+Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\citealt{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (slow strategy) life-history.
 Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
-This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\cite{priede_metabolic_1985}).
+This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\citealt{priede_metabolic_1985}).
 
 Optimal activity is predicted to increase with temperature in nearly all cases, but it is sensitive to the cost of activity - at higher cost relative to the potential pay-off, activity may even decline at high temeprature.
-Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\cite{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
+Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\citealt{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
 This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses.
-Only large individuals of the simulated production strategy species will optimally decrease activity as a result of increased temperature.
+Only large individuals of the simulated fast strategy species will optimally decrease activity as a result of increased temperature.
 In this case, additional activity will lead to comparatively small gains from feeding relative to the cost of activity and SDA, owing to the non-linearity of the functional response.
@@
 increasing or dome-shaped consumption or attack-rates with temperature
-(\cite{biro_mechanisms_2007,englund_temperature_2011,rall_universal_2012}). Depending on the
+(\citealt{biro_mechanisms_2007,englund_temperature_2011,rall_universal_2012}). Depending on the
 strength of oxygen limitation and the development of the optimal
@@
 
-Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\cite{atkinson_temperature_1994}), without needing to evoke direct changes in ecological rates with temperature.
-This leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (fig.s \ref{fig:norms}, \ref{fig:norms_O2}).
-Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\cite{angilletta_temperature_2004}).
-
-The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\cite{cheung_shrinking_2013, pauly_sound_2017}).
-We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\cite{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\cite{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
+Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\citealt{atkinson_temperature_1994}), without needing to evoke direct changes in ecological rates with temperature.
+The physiological basis leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (figs \ref{fig:norms}, \ref{fig:norms_O2}).
+Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\citealt{angilletta_temperature_2004}).
+
+In order to provide a general framework, our model setup is deliberatly minimalist, and probably under-parametrised to reflect ecological and life-history aspects of particular species, such as migrations, social behaviour or seasonal energy requirements.
+As such, this framework provides a null model to assess the diversity of possible responses in fish, and other ectotherms, to temperature in a highly simplified system.
+Nevertheless, it provides a starting point from which to explore the importance of costs and benefits of particular life-histories and thermal adaptations.
+For instance, a recent species-specific eco-physiological model for cod (\emph{Gadus morhua}) that includes similar physiological constraints to our model predicted relatively high fitness at high temperatures (\citealt{holt_climate_2014,holt_climate_2015}).
+Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \citet{holt_climate_2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive patterns could offset potential fitness declines with increasing temperatures.
+
+\section*{Conclusions}
+
+The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheung_shrinking_2013, pauly_sound_2017}).
+We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
 In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT.
@@
 
-\end{spacing}
-
-\printbibliography
-
-\appendix
-
-\section{Specification of temperature dependent oxygen availability}
-
-The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
-Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\cite{priede_metabolic_1985}).
-We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR.
-We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\cite{gnauck2013freshwater, lefrancois_influence_2003}):
-
-\begin{align}
-f_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{crit})\log(0.5)/(P50-P_{crit})}\right),\\
-\lambda(T)&=\zeta\left(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right)^\eta \times \exp\left(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right),
-\end{align}
-
-Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term describes the saturation dependence on ambient $O_2$ at temperature $T$ ($O_2(T)$).
-At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}).
-We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{crit}$ is the ambient concentration at which oxygen supply ceases.
-Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentration at 5\degree C.
-To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (fig.
-\ref{fig:O2_fig}).
-Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature.
-
-\input{O2_fig}
-
-\section{Maturation-reaction norm}
+% \section*{Acknowledgments}
+% 
+% The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
+PN was supported by a Marsden fast-start grant by the Royal Society Te Apārangi of New Zealand.
+KHA was supported by the Centre for Ocean Life, a VKR Centre of Excellence funded by the Villum Foundation.
+
+\newpage{}
+
+\titleformat{\section}{\normalfont\bfseries\sffamily}{APPENDIX \thesection:}{1em}{}
+\renewcommand{\theequation}{\thesection-\arabic{equation}}
+\renewcommand{\thetable}{\thesection-\arabic{table}}
+\renewcommand{\thefigure}{\thesection-\arabic{figure}}
+\setcounter{figure}{0}  % reset counter 
+\setcounter{table}{0}  % reset counter 
+\setcounter{equation}{0}  % reset counter
+
+\section*{Maturation-reaction norm}
 \label{sec:MRN}
 
-A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig. \ref{fig:MRN}).
+A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig./~\ref{fig:MRN}).
+
+To express a MRN that varies as a function of age, we can reparametrise the MRN as:
+\[\phi(z) = 1/(1+\exp(-(c z))) \text{, where }\\
+z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))\]
+rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
+
+\section*{Supplementary figures}
+
+\bibliographystyle{amnatnat}
+\begin{thebibliography}{55}
+\providecommand{\natexlab}[1]{#1}
+
+\bibitem[{Andersen et~al.(2009-10-01)Andersen, Farnsworth, Pedersen, Gislason,
+  and Beyer}]{andersenhow2009}
+Andersen, K.~H., K.~D. Farnsworth, M.~Pedersen, H.~Gislason, and J.~E. Beyer.
+  2009-10-01.
+\newblock How community ecology links natural mortality, growth, and production
+  of fish populations.
+\newblock {ICES} Journal of Marine Science: Journal du Conseil 66:1978--1984.
+
+\bibitem[{Angilletta et~al.(2004)Angilletta, Steury, and
+  Sears}]{angillettatemperature2004}
+Angilletta, M.~J., T.~D. Steury, and M.~W. Sears. 2004.
+\newblock Temperature, growth rate, and body size in ectotherms: Fitting pieces
+  of a life-history puzzle.
+\newblock Integrative and Comparative Biology 44:498--509.
+
+\bibitem[{Armstrong et~al.(2013)Armstrong, Schindler, Ruff, Brooks, Bentley,
+  and Torgersen}]{armstrongdiel2013}
+Armstrong, J.~B., D.~E. Schindler, C.~P. Ruff, G.~T. Brooks, K.~E. Bentley, and
+  C.~E. Torgersen. 2013.
+\newblock Diel horizontal migration in streams: juvenile fish exploit spatial
+  heterogeneity in thermal and trophic resources.
+\newblock Ecology 94:2066--2075.
+
+\bibitem[{Atkinson(1994)}]{atkinsontemperature1994}
+Atkinson, D. 1994.
+\newblock Temperature and organism size: a biological law for ectotherms?
+\newblock Advances in ecological research 25:1--1.
+
+\bibitem[{Biro et~al.(2007)Biro, Post, and Booth}]{biromechanisms2007}
+Biro, P.~A., J.~R. Post, and D.~J. Booth. 2007.
+\newblock Mechanisms for climate-induced mortality of fish populations in
+  whole-lake experiments.
+\newblock Proceedings of the National Academy of Sciences 104:9715--9719.
+
+\bibitem[{Brander et~al.(2013-08-21)Brander, Neuheimer, Andersen, and
+  Hartvig}]{branderoverconfidence2013}
+Brander, K., A.~Neuheimer, K.~H. Andersen, and M.~Hartvig. 2013-08-21.
+\newblock Overconfidence in model projections.
+\newblock {ICES} Journal of Marine Science 70:1065--1068.
+
+\bibitem[{Brett(1965)}]{brett1965relation}
+Brett, J. 1965.
+\newblock The relation of size to rate of oxygen consumption and sustained
+  swimming speed of sockeye salmon (oncorhynchus nerka).
+\newblock Journal of the Fisheries Board of Canada 22:1491--1501.
+
+\bibitem[{Brett(1972)}]{brettmetabolic1972}
+Brett, J.~R. 1972.
+\newblock The metabolic demand for oxygen in fish, particularly salmonids, and
+  a comparison with other vertebrates.
+\newblock Respiration physiology 14:151--170.
+
+\bibitem[{Brown et~al.(1989)Brown, Pepin, Methven, and
+  Somerton}]{brownfeeding1989}
+Brown, J.~A., P.~Pepin, D.~A. Methven, and D.~C. Somerton. 1989.
+\newblock The feeding, growth and behaviour of juvenile cod, gadus morhua l.,
+  in cold environments.
+\newblock Journal of Fish Biology 35:373--380.
+
+\bibitem[{Brown et~al.(2004)Brown, Gillooly, Allen, Savage, and
+  West}]{browntoward2004}
+Brown, J.~H., J.~F. Gillooly, A.~P. Allen, V.~M. Savage, and G.~B. West. 2004.
+\newblock Toward a metabolic theory of ecology.
+\newblock Ecology 85:1771--1789.
+
+\bibitem[{Charnov et~al.(2013)Charnov, Gislason, and
+  Pope}]{charnovevolutionary2013}
+Charnov, E.~L., H.~Gislason, and J.~G. Pope. 2013.
+\newblock Evolutionary assembly rules for fish life histories.
+\newblock Fish and Fisheries 14:213--224.
+
+\bibitem[{Cheung et~al.(2013)Cheung, Sarmiento, Dunne, Frölicher, Lam,
+  Palomares, Watson, and Pauly}]{cheungshrinking2013}
+Cheung, W.~W., J.~L. Sarmiento, J.~Dunne, T.~L. Frölicher, V.~W. Lam, M.~D.
+  Palomares, R.~Watson, and D.~Pauly. 2013.
+\newblock Shrinking of fishes exacerbates impacts of global ocean changes on
+  marine ecosystems.
+\newblock Nature Climate Change 3:254--258.
+
+\bibitem[{Claireaux and Lefrançois(2007)}]{claireauxlinking2007}
+Claireaux, G., and C.~Lefrançois. 2007.
+\newblock Linking environmental variability and fish performance: integration
+  through the concept of scope for activity.
+\newblock Philosophical Transactions of the Royal Society B: Biological
+  Sciences 362:2031--2041.
+
+\bibitem[{Claireaux et~al.(1995)Claireaux, Webber, Kerr, and
+  Boutilier}]{claireauxphysiology1995}
+Claireaux, G., D.~Webber, S.~Kerr, and R.~Boutilier. 1995.
+\newblock Physiology and behaviour of free-swimming atlantic cod (gadus morhua)
+  facing fluctuating temperature conditions.
+\newblock Journal of Experimental Biology 198:49--60.
+
+\bibitem[{Claireaux et~al.(2016-08-08)Claireaux, Webber, Lagardère, and
+  Kerr}]{claireauxinfluence2000}
+Claireaux, G., D.~M. Webber, J.-P. Lagardère, and S.~R. Kerr. 2016-08-08.
+\newblock Influence of water temperature and oxygenation on the aerobic
+  metabolic scope of atlantic cod (gadus morhua).
+\newblock Journal of Sea Research 44:257--265.
+
+\bibitem[{Deutsch et~al.(2015)Deutsch, Ferrel, Seibel, Pörtner, and
+  Huey}]{deutschclimate2015}
+Deutsch, C., A.~Ferrel, B.~Seibel, H.-O. Pörtner, and R.~B. Huey. 2015.
+\newblock Climate change tightens a metabolic constraint on marine habitats.
+\newblock Science 348:1132--1135.
+
+\bibitem[{Dieckmann and Heino(2007)}]{dieckmannprobabilistic2007}
+Dieckmann, U., and M.~Heino. 2007.
+\newblock Probabilistic maturation reaction norms: their history, strengths,
+  and limitations.
+\newblock Marine Ecology Progress Series 335:253--269.
+
+\bibitem[{Englund et~al.(2011)Englund, Öhlund, Hein, and
+  Diehl}]{englundtemperature2011}
+Englund, G., G.~Öhlund, C.~L. Hein, and S.~Diehl. 2011.
+\newblock Temperature dependence of the functional response.
+\newblock Ecology Letters 14:914--921.
+
+\bibitem[{Fry(1947)}]{fryeffects1947}
+Fry. 1947.
+\newblock Effects of the environment on animal activity .
+
+\bibitem[{Gilliam and Fraser(1987)}]{gilliamhabitat1987}
+Gilliam, J.~F., and D.~F. Fraser. 1987.
+\newblock Habitat selection under predation hazard: test of a model with
+  foraging minnows.
+\newblock Ecology 68:1856--1862.
+
+\bibitem[{Glazier(2009)}]{glazieractivity2009}
+Glazier, D.~S. 2009.
+\newblock Activity affects intraspecific body-size scaling of metabolic rate in
+  ectothermic animals.
+\newblock Journal of Comparative Physiology B 179:821--828.
+
+\bibitem[{Gnauck and Stra{\v{s}}kraba(2013)}]{gnauck2013freshwater}
+Gnauck, A., and M.~Stra{\v{s}}kraba. 2013.
+\newblock Freshwater ecosystems: modelling and simulation, vol.~8.
+\newblock Elsevier.
+
+\bibitem[{Guiet et~al.(2016)Guiet, Aumont, Poggiale, and
+  Maury}]{guieteffects2016}
+Guiet, J., O.~Aumont, J.-C. Poggiale, and O.~Maury. 2016.
+\newblock Effects of lower trophic level biomass and water temperature on fish
+  communities: A modelling study.
+\newblock Progress in Oceanography 146:22--37.
+
+\bibitem[{Hartvig et~al.(2011)Hartvig, Andersen, and Beyer}]{hartvigfood2011}
+Hartvig, M., K.~H. Andersen, and J.~E. Beyer. 2011.
+\newblock Food web framework for size-structured populations.
+\newblock Journal of Theoretical Biology 272:113--122.
+
+\bibitem[{Holt and Jorgensen(2014-11-04)}]{holtclimate2014}
+Holt, R.~E., and C.~Jorgensen. 2014-11-04.
+\newblock Climate warming causes life-history evolution in a model for atlantic
+  cod (gadus morhua).
+\newblock Conservation Physiology 2.
+
+\bibitem[{Holt and Jorgensen(2015)}]{holtclimate2015}
+---{}---{}---. 2015.
+\newblock Climate change in fish: effects of respiratory constraints on optimal
+  life history and behaviour.
+\newblock Biology Letters 11:20141032--20141032.
+
+\bibitem[{Hufnagl and Peck(2011)}]{hufnaglphysiological2011}
+Hufnagl, M., and M.~A. Peck. 2011.
+\newblock Physiological individual-based modelling of larval atlantic herring
+  (clupea harengus) foraging and growth: insights on climate-driven
+  life-history scheduling.
+\newblock {ICES} Journal of Marine Science 68:1170--1188.
+
+\bibitem[{Iftikar and Hickey(2013)}]{iftikarmitochondria2013}
+Iftikar, F.~I., and A.~J.~R. Hickey. 2013.
+\newblock Do mitochondria limit hot fish hearts? understanding the role of
+  mitochondrial function with heat stress in notolabrus celidotus.
+\newblock {PLOS} {ONE} 8:e64120.
+
+\bibitem[{Jeschke et~al.(2002)Jeschke, Kopp, and
+  Tollrian}]{jeschkepredator2002}
+Jeschke, J.~M., M.~Kopp, and R.~Tollrian. 2002.
+\newblock Predator functional responses: discriminating between handling and
+  digesting prey.
+\newblock Ecological Monographs 72:95--112.
+
+\bibitem[{Jutfelt et~al.(2018)Jutfelt, Norin, Ern, Overgaard, Wang, {McKenzie},
+  Lefevre, Nilsson, Metcalfe, and Hickey}]{jutfeltoxygen-and2018}
+Jutfelt, F., T.~Norin, R.~Ern, J.~Overgaard, T.~Wang, D.~J. {McKenzie},
+  S.~Lefevre, G.~E. Nilsson, N.~B. Metcalfe, and A.~J. Hickey. 2018.
+\newblock Oxygen-and capacity-limited thermal tolerance: blurring ecology and
+  physiology.
+\newblock Journal of Experimental Biology 221:jeb169615.
+
+\bibitem[{Killen et~al.(2010)Killen, Atkinson, and
+  Glazier}]{killenintraspecific2010}
+Killen, S.~S., D.~Atkinson, and D.~S. Glazier. 2010.
+\newblock The intraspecific scaling of metabolic rate with body mass in fishes
+  depends on lifestyle and temperature.
+\newblock Ecology Letters 13:184--193.
+
+\bibitem[{Lefevre(2016)}]{lefevreare2016}
+Lefevre, S. 2016.
+\newblock Are global warming and ocean acidification conspiring against marine
+  ectotherms? a meta-analysis of the respiratory effects of elevated
+  temperature, high {CO}2 and their interaction.
+\newblock Conservation Physiology 4.
+
+\bibitem[{Lefevre et~al.(2017)Lefevre, {McKenzie}, and
+  Nilsson}]{lefevremodels2017}
+Lefevre, S., D.~J. {McKenzie}, and G.~E. Nilsson. 2017.
+\newblock Models projecting the fate of fish populations under climate change
+  need to be based on valid physiological mechanisms.
+\newblock Global Change Biology .
+
+\bibitem[{Lefevre et~al.(2018)Lefevre, McKenzie, and
+  Nilsson}]{lefevremodelling2017}
+Lefevre, S., D.~J. McKenzie, and G.~E. Nilsson. 2018.
+\newblock In modelling effects of global warming, invalid assumptions lead to
+  unrealistic projections.
+\newblock Global change biology 24:553--556.
+
+\bibitem[{Lefrancois and Claireaux(2003)}]{lefrancoisinfluence2003}
+Lefrancois, C., and G.~Claireaux. 2003.
+\newblock Influence of ambient oxygenation and temperature on metabolic scope
+  and scope for heart rate in the common sole solea solea.
+\newblock Marine Ecology Progress Series 259:273--284.
+
+\bibitem[{Lucas and Priede(1992)}]{lucasutilization1992}
+Lucas, M.~C., and I.~G. Priede. 1992.
+\newblock Utilization of metabolic scope in relation to feeding and activity by
+  individual and grouped zebrafish, brachydanio rerio (hamilton-buchanan).
+\newblock Journal of Fish Biology 41:175--190.
+
+\bibitem[{Magnuson and {DeStasio}(1997)}]{magnusonthermal1997}
+Magnuson, J.~J., and B.~T. {DeStasio}. 1997.
+\newblock Thermal niche of fishes and global warming.
+\newblock Pages 377--408 \emph{in} C.~Wood and D.~{McDonald}, eds. Global
+  warming: implications for freshwater and marine fish, vol.~61. Cambridge
+  University Press.
+
+\bibitem[{Marty et~al.(2011)Marty, Dieckmann, Rochet, and
+  Ernande}]{martyimpact2011}
+Marty, L., U.~Dieckmann, M.-J. Rochet, and B.~Ernande. 2011.
+\newblock Impact of environmental covariation in growth and mortality on
+  evolving maturation reaction norms.
+\newblock The American Naturalist 177:E98--E118.
+
+\bibitem[{Myrick and Cech(2000)}]{myricktemperature2000}
+Myrick, C.~A., and J.~J. Cech. 2000.
+\newblock Temperature influences on california rainbow trout physiological
+  performance.
+\newblock Fish Physiology and Biochemistry 22:245--254.
+
+\bibitem[{Parmesan and Yohe(2003)}]{parmesanglobally2003}
+Parmesan, C., and G.~Yohe. 2003.
+\newblock A globally coherent fingerprint of climate change impacts across
+  natural systems.
+\newblock Nature 421:37--42.
+
+\bibitem[{Pauly and Cheung(2017)}]{paulysound2017}
+Pauly, D., and W.~W.~L. Cheung. 2017.
+\newblock Sound physiological knowledge and principles in modeling shrinking of
+  fishes under climate change.
+\newblock Global Change Biology 24:e15--e26.
+
+\bibitem[{Pinsky et~al.(2013)Pinsky, Worm, Fogarty, Sarmiento, and
+  Levin}]{pinskymarine2013}
+Pinsky, M.~L., B.~Worm, M.~J. Fogarty, J.~L. Sarmiento, and S.~A. Levin. 2013.
+\newblock Marine taxa track local climate velocities.
+\newblock Science 341:1239--1242.
+
+\bibitem[{Priede(1977)}]{priedenatural1977}
+Priede, I.~G. 1977.
+\newblock Natural selection for energetic efficiency and the relationship
+  between activity level and mortality.
+\newblock Nature 267:610--611.
+
+\bibitem[{Priede(1985)}]{priedemetabolic1985}
+---{}---{}---. 1985.
+\newblock Metabolic scope in fishes.
+\newblock Pages 33--64 \emph{in} Fish Energetics. Springer.
+
+\bibitem[{Pörtner(2010)}]{portneroxygen-and2010}
+Pörtner, H.-O. 2010.
+\newblock Oxygen-and capacity-limitation of thermal tolerance: a matrix for
+  integrating climate-related stressor effects in marine ecosystems.
+\newblock The Journal of experimental biology 213:881--893.
+
+\bibitem[{Pörtner and Farrell(2008)}]{portnerphysiology2008}
+Pörtner, H.~O., and A.~P. Farrell. 2008.
+\newblock Physiology and climate change.
+\newblock Science 322:690--692.
+
+\bibitem[{Rall et~al.(2012)Rall, Brose, Hartvig, Kalinkat, Schwarzmüller,
+  Vucic-Pestic, and Petchey}]{ralluniversal2012}
+Rall, B.~C., U.~Brose, M.~Hartvig, G.~Kalinkat, F.~Schwarzmüller,
+  O.~Vucic-Pestic, and O.~L. Petchey. 2012.
+\newblock Universal temperature and body-mass scaling of feeding rates.
+\newblock Phil. Trans. R. Soc. B 367:2923--2934.
+
+\bibitem[{Sainmont et~al.(2015-09)Sainmont, Andersen, Thygesen, Fiksen, and
+  Visser}]{sainmonteffective2015}
+Sainmont, J., K.~H. Andersen, U.~H. Thygesen, ?.~Fiksen, and A.~W. Visser.
+  2015-09.
+\newblock An effective algorithm for approximating adaptive behavior in
+  seasonal environments.
+\newblock Ecological Modelling 311:20--30.
+
+\bibitem[{Salin et~al.(2016)Salin, Auer, Anderson, Selman, and
+  Metcalfe}]{salininadequate2016}
+Salin, K., S.~K. Auer, G.~J. Anderson, C.~Selman, and N.~B. Metcalfe. 2016.
+\newblock Inadequate food intake at high temperatures is related to depressed
+  mitochondrial respiratory capacity.
+\newblock Journal of Experimental Biology 219:1356--1362.
+
+\bibitem[{Sentis et~al.(2013)Sentis, Hemptinne, and
+  Brodeur}]{sentisparsing2013}
+Sentis, A., J.-L. Hemptinne, and J.~Brodeur. 2013.
+\newblock Parsing handling time into its components: implications for responses
+  to a temperature gradient.
+\newblock Ecology 94:1675--1680.
+
+\bibitem[{Sswat et~al.(2018-01-25)Sswat, Stiasny, Jutfelt, Riebesell, and
+  Clemmesen}]{sswatgrowth2018}
+Sswat, M., M.~H. Stiasny, F.~Jutfelt, U.~Riebesell, and C.~Clemmesen.
+  2018-01-25.
+\newblock Growth performance and survival of larval atlantic herring, under the
+  combined effects of elevated temperatures and {CO}2.
+\newblock {PLOS} {ONE} 13:e0191947.
+
+\bibitem[{Stuart-Smith et~al.(2015)Stuart-Smith, Edgar, Barrett, Kininmonth,
+  and Bates}]{stuart-smiththermal2015}
+Stuart-Smith, R.~D., G.~J. Edgar, N.~S. Barrett, S.~J. Kininmonth, and A.~E.
+  Bates. 2015.
+\newblock Thermal biases and vulnerability to warming in the world’s marine
+  fauna.
+\newblock Nature 528:88--92.
+
+\bibitem[{Verberk et~al.(2016)Verberk, Overgaard, Ern, Bayley, Wang, Boardman,
+  and Terblanche}]{verberkdoes2016}
+Verberk, W. C. E.~P., J.~Overgaard, R.~Ern, M.~Bayley, T.~Wang, L.~Boardman,
+  and J.~S. Terblanche. 2016.
+\newblock Does oxygen limit thermal tolerance in arthropods? a critical review
+  of current evidence.
+\newblock Comparative Biochemistry and Physiology Part A: Molecular \&
+  Integrative Physiology 192:64--78.
+
+\bibitem[{Vucic-Pestic et~al.(2011-03-01)Vucic-Pestic, Ehnes, Rall, and
+  Brose}]{vucic-pesticwarming2011}
+Vucic-Pestic, O., R.~B. Ehnes, B.~C. Rall, and U.~Brose. 2011-03-01.
+\newblock Warming up the system: higher predator feeding rates but lower
+  energetic efficiencies.
+\newblock Global Change Biology 17:1301--1310.
+
+\bibitem[{Walther et~al.(2002)Walther, Post, Convey, Menzel, Parmesan, Beebee,
+  Fromentin, Hoegh-Guldberg, and Bairlein}]{waltherecological2002}
+Walther, G.-R., E.~Post, P.~Convey, A.~Menzel, C.~Parmesan, T.~J.~C. Beebee,
+  J.-M. Fromentin, O.~Hoegh-Guldberg, and F.~Bairlein. 2002.
+\newblock Ecological responses to recent climate change.
+\newblock Nature 416:389--395.
+
+\end{thebibliography}
+
+\subsection*{Online figure legends}
+
+\renewcommand{\thefigure}{A\arabic{figure}}
+\setcounter{figure}{0}
 
@@
 
-To express a MRN that varies as a function of age, we can reparametrise the MRN as:
-$$\phi(z) = 1/(1+\exp(-(c z))) \text{, where }$$
-$$z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))$$  
-rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
-
-\section{Supplementary results}
+\renewcommand{\thefigure}{B\arabic{figure}}
+\setcounter{figure}{0}
 
@@
 @
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for safe strategy (slow life history; aandb) and production strategy (fast life-history; c, d).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; aandb) and fast strategy (fast life-history; c, d).}
 \label{fig:activity-rising}
@@
 
-<<size-act_low,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm; e--f), for a production strategy (fast life-history) species with a dome-shaped maximum metabolic rate with respect to temperature.
+<<size-act_low,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm; e--f), for a fast strategy (fast life-history) species with a dome-shaped maximum metabolic rate with respect to temperature.
 ',fig.align='center'>>=
@@
 
-laba <- as_labeller(c(`P strategy Low` ='a',
+labal <- as_labeller(c(`P strategy Low` ='a',
                    `P strategy Medium`  ='b',
@@
 
-sc_actd$Dispatch <- factor(sc_actd$Dispatch,levels=unique(sc_actd$Dispatch)[order(unlist(laba(unique(sc_actd$Dispatch))))])
+sc_actd$Dispatch <- factor(sc_actd$Dispatch,levels=unique(sc_actd$Dispatch)[order(unlist(labal(unique(sc_actd$Dispatch))))])
 
@@
   scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = laba)+
+  facet_wrap(~Dispatch,ncol = 1,labeller = labal)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for safe strategy (slow life history; left column [a,c,e]) and production strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.
+<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.
 Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center'>>=
@@
 \caption{Contrasting growth responses at baseline resource availability for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
-Growth curves are shown for safe- (left column [a,c]) and production strategists (right column [b,d]).
+Growth curves are shown for slow- (left column [a,c]) and fast strategists (right column [b,d]).
 Increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.}
@@
 <<norms_neg, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
 Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
@@
 <<norms_pos, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
 Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=

### 2018-07-06 MS_AMNat.tex
AmNat submission

--- 2018-07-04 draft_model_only.Rnw
@@
-\documentclass[a4paper, toc=index,abstract=true]{scrartcl}
+\documentclass[11pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
+\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
+\usepackage{fullpage}
 \usepackage{gensymb}
-\usepackage{geometry}
-\usepackage{enumitem}
-\usepackage{setspace}
+\usepackage{multirow}
 \usepackage{booktabs}
-\usepackage{subfig}
-\usepackage{placeins}
 \usepackage{amsmath}
-\usepackage{pdflscape}
-\usepackage{multirow}
-\usepackage{longtable}
-\usepackage[toc,page]{appendix}
-\usepackage{array,booktabs}
-\usepackage[american]{babel}
-\usepackage[backend=biber,
-mincitenames = 1,
-maxcitenames = 1,
-uniquename = false,
-uniquelist = false,
-citestyle = authoryear-comp]{biblatex}%
-\usepackage{lineno, blindtext}
-\addbibresource{Sizing-fx-of-temperature.bib}
-\captionsetup[table]{singlelinecheck=false}
+\usepackage[authoryear,sectionbib,sort]{natbib}
+\linespread{1.7}
+\usepackage[utf8]{inputenc}
+\usepackage{lineno}
+\usepackage{titlesec}
+\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
+\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
+\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
+\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}
 
-\title{Explaining thermal performance of fish: interplay of behaviour, ecology and physiology drive growth and fitness responses}
-\author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
-        Ken H. Andersen\\Centre for Ocean Life
-        Danish Technical University, Lyngby, Denmark}
+\title{Thermal performance of fish is explained by an interplay between physiology, behaviour, and ecology}
 
+% \author{Philipp Neubauer^{1,\ast}$ \\ 
+%         Ken H. Andersen$^{2,\dag}$}
+
+\date{}
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-\begin{spacing}{1.9}
+% \noindent{} 1. Dragonfly Data Science, PO Box 27535, Wellington 6141, New Zealand;
+% 
+% \noindent{} 2. Centre for Ocean Life, National Institute of Aquatic Resources, Technical University of Denmark, 7 Kemitorvet B-202, 2800 Kongens Lyngby, Denmark;
 
-\pagenumbering{gobble}
-\begin{abstract}
+\bigskip
+
+\textit{Manuscript elements}: Figure~1, figure~2, table~1, online appendices~A and B (including figure~A1 and figure~A2). Figure~2 is to print in color.
+
+\bigskip
+
+\textit{Keywords}: thermal performance, OCLTT, metabolic rate, climate change
+
+\bigskip
+
+\textit{Manuscript type}: Article.
+
+\bigskip
+
+\noindent{\footnotesize Prepared using the suggested \LaTeX{} template for \textit{Am.\ Nat.}}
+
+\linenumbers{}
+\modulolinenumbers[3]
+
+\newpage{}
+
+\section*{Abstract}
 
@@
 
-\section{Introduction}
+\section*{Introduction}
 
-Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\cite{deutsch_climate_2015,pinsky_marine_2013,brown_toward_2004}).
+Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\cite{deutsch_climate_2015,pinsky_marine_2013}).
 As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\cite{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).
@@
 Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\cite{brander_overconfidence_2013, lefevre_models_2017}).
-In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017}).
+In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\cite{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\cite{brander_overconfidence_2013, lefevre_models_2017,jutfelt_oxygen-and_2018}).
 
-There are few general concepts and models that can explain thermal performance and ecological responses to temperature.
-To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in fundamental ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angilletta_temperature_2004,atkinson_temperature_1994}), or attack rates (\cite{englund_temperature_2011,rall_universal_2012}) with temperature, from fundamental physiological processes.
+Although there are conceptual and model frameworks to explain aspects of thermal performance and ecological responses to temperature (\cite{fry_effects_1947,brown_toward_2004,pauly_sound_2017,portner_oxygen-and_2010}), many of these remain controversial as they appear limited in their generality or predictive capacity (\cite{lefevre_models_2017,jutfelt_oxygen-and_2018}).
+To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in  ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angilletta_temperature_2004,atkinson_temperature_1994}), or attack rates (\cite{englund_temperature_2011,rall_universal_2012}) with temperature, from fundamental physiological processes.
 Instead, and as advocated by the metabolic theory of ecology (\cite{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{angilletta_temperature_2004,vucic-pestic_warming_2011, guiet_effects_2016}).
 
-Although ecological rates seem to follow some general patterns in the response to temperature , there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}).
-A phenomenological description that assumes a general ecological temperature response thus often fails to explain heterogeneity in ecological responses (\cite{angilletta_temperature_2004}), and leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
+A phenomenological description that assumes a general ecological temperature response often fails to explain heterogeneity in ecological responses (\cite{angilletta_temperature_2004,rall_universal_2012}).
+Although ecological rates seem to follow some general patterns in the response to temperature, there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}).
+This leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
 In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011,lefevre_models_2017}).
@@
 
-\section{Methods}
+\section*{Methods}
 
-\subsection{Key assumptions}
+\subsection*{Key assumptions}
 
@@
 
-\subsection{Model description}
+\subsection*{Model description}
 Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality (\cite{gilliam_habitat_1987}).
@@
 where $h c(T) w^q$ is the maximum consumption rate.
-The feeding level ([0,1]) is determined by the fraction of time spent foraging $\tau$, foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
+The feeding level is determined by the fraction of time spent foraging $\tau$ (henceforth the activity fraction), foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
 The supply is discounted by the loss due to specific dynamic action  $\beta$ (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
@@
 Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\cite{glazier_activity_2009,brett1965relation}, and the activity fraction.
-Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \cite{jeschke_predator_2002, sentis_parsing_2013}) as $c(T) = e^{E_a(T-T_0)/(kTT_0)}$.
+Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \cite{jeschke_predator_2002, sentis_parsing_2013}) and approimated by an Arrhenious scaling $c(T) = e^{E_a(T-T_0)/(bTT_0)}$, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (here 15 degrees Celsius), and $b$ is the Bolzman constant.
+Note that we only scale rates related to enzymatic activity with temperature, we do assume that ecological rates such as foraging rates or activity are a direct function of temperature.
+Rather, they are modulated by an individual's behavioural response to temperature driven physiological changes.
 
@@
   P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
-        &= s_(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
+        &= S_{O_2}c_{O_2}(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
 \end{align}
 Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.
-The oxygen supply scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as MOS that increase continuously up to a lethal temperature (fig.
-\ref{fig:O2_fig}, Appendix A).
+The oxygen supply ($S_{O_2}c_{O_2}(T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig./~\ref{fig:O2_fig_used}).
+The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
+Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\cite{priede_metabolic_1985}).
+We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR.
+We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\cite{gnauck2013freshwater, lefrancois_influence_2003}):
 
-Fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \cite{gilliam_habitat_1987}:
+\begin{align}
+s_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{\text{crit}})\log(0.5)/(P\text{50}-P_{\text{crit}})}\right),\\
+\lambda(T)&=\zeta\left(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right)^\eta \times \exp\left(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right),
+\end{align}
+
+Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the $s_{O_2}(T)$ term describes the saturation dependence on ambient $O_2$ at temperature $T$ ($O_2(T)$).
+At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}).
+We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{\text{crit}}$ is the ambient concentration at which oxygen supply ceases.
+Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentration at 5\degree C.
+To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height.
+Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig./~\ref{fig:O2_fig}).
+
+\input{O2_fig}
+
+In pour model, fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \cite{gilliam_habitat_1987}:
 \begin{equation}
@@
 In other words, we consider time scales that are long enough to ignore the ability of many ectotherms to go into oxygen debt, or to switch to anaerobic metabolism for limited periods of time.
-This means we assume that animals will adapt their effort to optimise fitness given temperature and oxygen constraints.
+This means we assume that animals will adjust their foraging effort to optimise fitness given temperature and oxygen constraints.
+Note, that this optimal foraging assumption drives ecological responses as a consequence of physiological constraints, rather than as a direct response to temperature itself.
 
-\subsection{Defining performance metrics}
+\subsection*{Defining performance metrics}
 
@@
 We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past.
-Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm (i.e., allocation to reproduction is a function of size only; fig.
-\ref{fig:MRN}), although sloping reaction norms can be formulated and used in our framework (see appendix \ref{sec:MRN}).
-The intercept of this reaction norm was found numerically by maximising fitness ($R0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was assumed fixed as temperatures change.
+Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm (i.e., allocation to reproduction is a function of size only; fig./~\ref{fig:MRN}), although sloping reaction norms can be formulated and used in our framework (see appendix \ref{sec:MRN}).
+The intercept of this reaction norm was found numerically by maximising fitness ($R_0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was assumed fixed as temperatures change.
 
@@
 On these time-scales, we assume that adaptive responses are negligible.
-We investigate over-all fitness with respect to temperature by calculating R0 for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
-R0 was calculated as
+We investigate over-all fitness with respect to temperature by calculating $R_0$ for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
+$R_0$ was calculated as
 
-$$R0 = \int_0^\infty \phi(z(t,w_t,w^*))P(w_t,T)S_{0 \rightarrow t} dt, \text{, where}$$
-$$S_{0 \rightarrow t} = \int_0^t \exp(-M(w_t))\text{dt}$$
+$$R_0(T) = \int_0^\infty \phi(w(t),w^*)P(w(t),T)S_{0 \rightarrow t}(T) \text{d}t, \text{, where}$$
+$$S_{0 \rightarrow t}(T) = \int_0^t \exp(-M(w(t),T))\text{d}t$$
 
-\subsection{Trait based scenarios}
+\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{images/scenarios-1}
+
+}
+
+\caption[Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\degree C) for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g)]{Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\degree C) for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g).
+Responses are shown for slow- (a) and fast strategy (b).
+All rates are plotted relative to their maximum for each trait scenario, the optimal activity level $\tau^*$ is indicated by the dotted vertical line.}\label{fig:scenarios}
+\end{figure}
+
+\subsection*{Trait based scenarios}
 
 To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
-Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the production strategy, indicated by a supercript $p$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth safe strategy, indicated by a supercript $s$).
+Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the fast strategy, indicated by a subscript $f$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth slow strategy, indicated by a subcript $s$).
 This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
-In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm) with defensive/sluggish versus active life-histories.
+In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm or $w_{\infty}\sim 270$g) with defensive/sluggish versus active life-histories.
 
@@
 50\% increase in standard metabolic cost.
-We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M^{s}(w) = (0.1+6\tau) w^{q-1}$ and $M^{p}(w) = (1+\tau) w^{q-1}$).
+We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M_{s}(w) = (0.1+6\tau) w^{q-1}$ and $M_{f}(w) = (1+\tau) w^{q-1}$).
 Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
-Together, these assumed trait differences lead to very different ecological and bio-energetic responses of safe- and production strategists (fig.
-\ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for safe-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to feeding level) at high activity levels.
-A slower increase in available energy and M with $\tau$ for production strategists leads to a higher $\tau_{\text{opt}}$.
+Together, these assumed trait differences lead to very different ecological and bio-energetic responses of slow- and fast strategists (fig./~\ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for slow-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to food intake) at high activity levels.
+A slower increase in available energy and M with $\tau$ for fast strategists leads to a higher $\tau_{\text{opt}}$.
 
 We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \cite{salin_inadequate_2016,iftikar_mitochondria_2013}).
-In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig.
-\ref{fig:O2_fig}).
+In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig./~\ref{fig:O2_fig}).
 Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\cite{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
@@
 \begin{table}
-\caption{Parameters of the constrained activity model for two scenarios: safe strategy and production strategy species.
+\caption{Parameters of the constrained activity model for two scenarios: slow strategy and fast strategy species.
 For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
@@
  \cmidrule{3-4}
- & & safe strategy  & production strategy \\
+ & & slow strategy  & fast strategy \\
 
@@
 Critical $O_2$ & $P_{\text{crit}}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{2}\\
-Dissolved $O_2$ at $0.5\times f_{\text{max}}(O_2)$  & $P50$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{4} \\
+Dissolved $O_2$ at $0.5\times f_{\text{max}}(O_2)$  & $P_{50}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{4} \\
 Doming for $O_2$ supply & $\eta$ & \multicolumn{2}{c}{3/0.1}\\
@@
 
-<< setup,echo=FALSE,include=F>>=
-knitr::opts_chunk$set(echo = F, message = F,cache=T,autodep = T)
+\section*{Results}
 
-require(dplyr)
-require(tidyr)
-require(rlang)
-require(cowplot)
-
-source('model.R')
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
-
-@
-
-<<Scenarios>>=
-
-int_m <- 500
-int_t <- 500
-int_temp <- 30
-
-# Sluggish small
-ss <- list(c=0.3,
-           beta=0.1,
-           delta=4,
-           Ea=0.52, 
-           gamma=60, 
-           h=30, 
-           k=1,
-           lO=0.5, 
-           m=10, 
-           n=0.88, 
-           o=1,
-           O2crit=2, 
-           omega=0.25, 
-           p=0.8,
-           P50=4.2, 
-           phi=0.25, 
-           q=0.8,
-           shape=3,
-           temp=seq(5,26,l=int_temp),
-           Topt=20, 
-           temp_ref=15,
-           slope=0,
-           tmax=20,
-           tr=0.5,
-           M=0.1,
-           v=6,
-           lm=int_m,
-           nu=0.8-1,
-           dt=int_t,
-           min_m=-2,
-           max_m= 3
-)
-
-# fast small0.8-1
-fs <- ss
-fs$lO <- 1
-fs$k <- 1.5
-fs$h <- 60
-fs$v <- 1
-fs$M <- 1
-fs$nu<- 0.8-1
-fs$n <- 0.75
-fs$delta <- 4
-fs$o <- 1
-fs$p <- 0.8
-fs$q <- 0.8
-fs$tmax <- 10
-
-fl <- fs
-fl$shape <- 0.1
-fl$Topt <- 25
-
-sl <- ss
-sl$shape <- 0.1
-sl$Topt <- 25
-
-ffl <- fs
-ffl$gamma <- 20
-
-fsl <- ss
-fsl$gamma <- 20
-
-ffh <- fs
-ffl$gamma <- 80
-
-fsh <- ss
-fsl$gamma <- 80
-
-scs <- list(ss,fs,sl,fl)
-fscs <- list(fsh,ffh,fsl,ffl)
-
-baseline <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
-                                  Food = as.factor(rep(c('High','Low'),each=int_temp*2))),
-                       bind_rows(lapply(fscs, get_model_out,seq(0.05,1,l=int_temp))))
-
-scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
-                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
-                       bind_rows(lapply(scs, plot_data_temp)))
-
-scn <- rep(unique(scenarios$Scenario),2)
-scz <- rep(unique(scenarios$O2lim),each=2)
-
-@
-
-\section{Results}
-
-Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig.
-\ref{fig:activity}).
-This adjustment is especially pronounced in safe strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig.
-\ref{fig:size-act}).
-A similar increase in activity is observed for small production strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.
-\ref{fig:size-act}).
+Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig./~\ref{fig:activity}).
+This adjustment is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig./~\ref{fig:size-act}).
+A similar increase in activity is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig./~\ref{fig:size-act}).
 For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
-For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig.
-\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
-For species with a rising MOS with temperature, oxygen is not limiting (fig.
-\ref{fig:activity-rising}).
-However, larger production strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
-This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig.
-\ref{fig:size-act_low}).
-
-<<scenarios,fig.cap='Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\\degree C) for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for safe- (a and b, respectively) and production strategy (c and d), for species in high (left column) and low (right column) food environments.
-All rates are plotted relative to their maximum for each trait scenario (i.e., by row), the optimal activity level $\\tau^*$ is indicated by the dotted vertical line.',fig.align='center',fig.height=5,fig.width=6>>=
-
-lab <- as_labeller(c(`M strategy High`  ='a',
-                   `P strategy High` = 'c',
-                   `M strategy Low`  ='b',
-                   `P strategy Low` = 'd'))
-
-sc_bl <- baseline  %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=sc(`Feeding level`),
-         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         `Relative M` = sc(M),
-         `Energy` = sc(`Available Energy`),
-         Fitness = sc(`Available Energy`/M)) %>% 
-  tidyr::gather(Rate,value,Energy,Efficiency,`Relative M`,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Energy','Efficiency','Fitness')),
-         Dispatch = paste(Scenario,Food))
-
-tstar <- baseline  %>%
-  group_by(Scenario, Food) %>%
-  mutate(`Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         Fitness = sc(`Available Energy`/M)) %>% 
-  summarise(tstar = tau[which.max(Fitness)]) %>%
-  mutate(Dispatch = paste(Scenario,Food))
-
-ggplot() + 
-  geom_line(aes(x=tau, y=value, linetype=Rate,col=Rate,group=Rate),data=sc_bl) +
-  geom_vline(aes(xintercept=tstar),linetype=3,data=tstar) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
-  theme(strip.text = element_text(hjust = 0.05),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-   labs(x = expression('Activity ' (tau)),
-       y='Relative rate')
-
-@
+For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig./~\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
+For species with a rising MOS with temperature, oxygen is not limiting (fig./~\ref{fig:activity-rising}).
+However, larger fast strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
+This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig./~\ref{fig:size-act_low}).
 
@@
 \centering
-<<activity, fig.height=4,fig.width=6>>=
 
-sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,O2lim))
+\includegraphics[width=\maxwidth]{images/activity-1}
 
-lab1 <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'c'))
-
-lab2 <- as_labeller(c(`M strategy Domed`  ='b',
-                   `P strategy Domed` = 'd'))
-
-ggsc <- ggplot(sc_act %>% filter(O2lim=='Domed')) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
-  mutate(Dispatch = paste(Scenario,O2lim))
-
-ggso <- sco %>% filter(O2lim=='Domed') %>%
-  ggplot() + 
-   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot() +
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression(Oxygen~(mg.yr^-1)))
-
-cowplot::plot_grid(ggsc,ggso,ncol=2)
-
-@
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for safe strategy (slow life history; a \& b) and production strategy (fast life-history; c \& d).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; a \& b) and fast strategy (fast life-history; c \& d).}
 \label{fig:activity}
@@
 
-<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for safe strategy (slow life history; left column [a,c,e]) and production strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
+\begin{figure}
 
-ssm <- ss
-ssm$m <- 1.25
+{\centering \includegraphics[width=\maxwidth]{images/size-act-1}
 
-ssl <- ss
-ssl$m <- 80
+}
 
-fsm <- fs
-fsm$m <- 1.25
+\caption[Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\infty}\sim 30$cm at 1.25g (5cm]{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\infty}\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.}\label{fig:size-act}
+\end{figure}
 
-fsl <- fs
-fsl$m <- 80
+Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig./~\ref{fig:feeding}).
+For slow strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
+Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures.
+However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS.
+Production efficiency follows a near opposite trend due to the relatively flat response in the feeding level $f$, but temperature driven increases in maximum consumption.
 
-scss <- list(ssm,ss,ssl,fsm,fs,fsl)
-
-scenarios_s <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('M strategy','P strategy'),each=3),each=int_temp)),
-                                  Size = as.factor(rep(rep(c('Small','Medium','Large'),2),each=int_temp))),
-                       bind_rows(lapply(scss, plot_data_temp)))
-
-sc_acts <- gather(scenarios_s,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,Size))
-
-laba <- as_labeller(c(`M strategy Small` ='a',
-                   `P strategy Small`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy Large` = 'e',
-                   `P strategy Large` = 'f'
-))
-
-sc_acts$Dispatch <- factor(sc_acts$Dispatch,levels=unique(sc_acts$Dispatch)[order(unlist(laba(unique(sc_acts$Dispatch))))])
-
-ggplot(sc_acts) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-@
-
-Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.
-\ref{fig:feeding}).
-For safe strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
-Available energy shows a dome-shaped response to temperature in safe strategists, and is maximised at relatively high temperatures.
-However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS.
-Growth efficiency  follows a near identical trend due to the relatively flat response in the feeding level $f$.
-
-For production strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig.
-\ref{fig:feeding}).
-Again, growth efficiency peaks at relatively high temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
+For fast strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig./~\ref{fig:feeding}).
+Again, production efficiency peaks at relatively low temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
 Given the relatively flat mortality levels, the ratio of $P/M$ largely follows the trend in $P$.
 
-<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
-Responses are shown for safe  and production strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center',fig.height=5,fig.width=6>>=
+\begin{figure}
 
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b'))
+{\centering \includegraphics[width=\maxwidth]{images/feeding-1}
 
-sc_feed <- scenarios %>% filter(O2lim=='Domed') %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,O2lim) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         M=sc(M),
-         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         `Relative M` = sc(M),
-         `Energy` = sc(`Available Energy`),
-         Fitness = sc(`Available Energy`/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,O2lim))
+}
 
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=1)+
-  theme(strip.text = element_text(hjust = 0.05),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1))+
-  scale_color_manual(values = cols)+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
+\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g)]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g).
+Responses are shown for slow  and fast strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
+Energy, mortality and fitness are plotted relative to their maximum over all temperatures.}\label{fig:feeding}
+\end{figure}
 
-@
-
-Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig.
-\ref{fig:norms}).
-For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig.
-\ref{fig:norms_O2}).
-This can be explained by ontogenetic shifts in temperature optima for growth (fig.
-\ref{fig:size-rates}): for small individuals, available energy and growth efficiency consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals in either trait-scenario grow.
+Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig./~\ref{fig:norms}).
+For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig./~\ref{fig:norms_O2}).
+This can be explained by ontogenetic shifts in temperature optima for growth (fig./~\ref{fig:size-rates}): for small individuals, available energy and growth consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals in either trait-scenario grow.
 For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
 
-Resource availability strongly modulates this growth response to temperature: low resource availability leads to strong differences in asymptotic size, whereas high food availability leads to fast growth and larger asymptotic length at high temperatures (fig.
-\ref{fig:norms}).
+Resource availability strongly modulates this growth response to temperature: low resource availability leads to strong differences in asymptotic size, whereas high food availability leads to fast growth and larger asymptotic length at high temperatures (figs./~\ref{fig:norms},\ref{fig:infs}).
 In addition, in very resource poor conditions, individuals may not grow to reproductive size in our scenario of a flat MRN.
@@
 
-<<calc-gouts>>=
+\begin{figure}
 
-ssgl <- ss
-ssgl$gamma <- 40
+{\centering \includegraphics[width=\maxwidth]{images/norms-1}
 
-ssgh <- ss
-ssgh$gamma <- 80
+}
 
-fsgl <- fs
-fsgl$gamma <- 40
+\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms}
+\end{figure}
 
-fsgh <- fs
-fsgh$gamma <- 80
+\begin{figure}
 
-scsg <- list(ssgl,ss,ssgh,fsgl,fs,fsgh)
+{\centering \includegraphics[width=\maxwidth]{images/infs-1}
 
-mstar_ss <- plot_data_growth_tO2(ss)$mstar
-mstar_fs <- plot_data_growth_tO2(fs)$mstar
+}
 
-#mstar_ss <- 18
-#mstar_fs <- 18
+\caption[Interactive effects of food availibility and temperature of the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing prey availibility for a) slow and b) fast life-history species]{Interactive effects of food availibility and temperature of the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing prey availibility for a) slow and b) fast life-history species.}\label{fig:infs}
+\end{figure}
 
-goutss <- parallel::mclapply(list(ssgl,ss,ssgh),
-                             plot_data_growth_tO2,
-                             mstar=mstar_ss,
-                             mc.cores = 3)
-
-goutsf <- parallel::mclapply(list(fsgl,fs,fsgh),
-                             plot_data_growth_tO2,
-                             mstar=mstar_fs,
-                             mc.cores = 3)
-
-gouts <- c(goutss,goutsf)
-
-@
-
-<<norms, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
-
-labla <- as_labeller(c(`M strategy Low` ='a',
-                   `P strategy Low`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy High` = 'e',
-                   `P strategy High` = 'f'
-))
-
-t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
-
-#browser()
-norm <- t_growth %>% 
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
-
-Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig.
-\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\cite{sainmont_effective_2015}).
+Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig./~\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\cite{sainmont_effective_2015}).
 With increasing temperatures, fitness declines at our basic parameter settings, in opposition to growth and aerobic scope.
 At low temperatures, fitness is limited by aerobic scope, with the magnitude determined by the extend of doming in aerobic scope.
-Note that this limitation through the aerobic scope appears at higher temperatures than apparent from fig.
-\ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (fig.
-\ref{fig:size-rates}).
-Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig.
-\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for safe strategy species, and moves the fitness optimum to higher temperatures for production strategy species.
-Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for production strategists, and a slower decline of fitness with temperature.
+Note that this limitation through the aerobic scope appears at higher temperatures than apparent from fig./~\ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (fig./~\ref{fig:size-rates}).
+Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig./~\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for slow strategy species, and moves the fitness optimum to higher temperatures for fast strategy species.
+Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for fast strategists, and a slower decline of fitness with temperature.
 
-<<>>=
-ssm <- ss
-ssm$delta <- 2
+\begin{figure}
 
-ssl <- ss
-ssl$delta <- 1
+{\centering \includegraphics[width=\maxwidth]{images/fit-1}
 
-fsm <- fs
-fsm$delta <- 2
+}
 
-fsl <- fs
-fsl$delta <- 1
+\caption[Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and base parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)]{Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and base parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)}\label{fig:fit}
+\end{figure}
 
-scsa <- list(ss,ssm,ssl,fs,fsm,fsl)
-scna <- rep(unique(scenarios$Scenario),each=3)
-scza <- rep(c('High','Medium','Low'),3)
-
-gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
-goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 3)
-@
-
-<<fit, fig.cap='Fitness (R0), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for safe- (a) and production strategy (b) species at the assumed maturation-raction norm and base parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)',fig.align='center',fig.height=8>>=
-
-R0s <- bind_rows(lapply(1:length(goutr), function(x) {
-  y <- data.frame(goutr[[x]]['R0'])
-  y$Temperature <-goutr[[x]][['winfs']]$Temperature
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
-  y}))
-
-R0s <- R0s %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T))
-
-sizes = c(0.5,1,1.5)
-
-f1.1 <- ggplot(R0s%>% filter(Scenario=='M strategy')) + 
-  geom_line(aes(x=Temperature, y=R0, col=O2lim)) +
-  theme_cowplot()+
-  theme(axis.text.x = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-    scale_colour_manual(values=cols,guide='none')+
-  labs(x = ' ',
-       y='Relative fitness')
-
- f1.2 <- ggplot(R0s%>% filter(Scenario=='P strategy')) + 
-  geom_line(aes(x=Temperature, y=R0, col=O2lim)) +
-  theme_cowplot()+
-  theme(axis.text = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_colour_manual(values=cols,guide='none')+
-  labs(x = ' ',
-       y=' ')
-
-R0ss <- bind_rows(lapply(1:length(gouta), function(x) {
-  y <- data.frame(gouta[[x]]['R0'])
-  y$Temperature <-gouta[[x]][['winfs']]$Temperature
-  y$Scenario <- scna[x]
-  y$ActivityCost <- scza[x]
-  y$Dispatch <- paste(scna[x],scza[x])
-  y}))
-
-R0ss <- R0ss %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T),
-         ActivityCost = factor(ActivityCost,levels=c('Low','Medium','High')))
-
-f2.1 <- ggplot(R0ss%>% filter(Scenario=='M strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=ActivityCost,size=as.numeric(ActivityCost)/3)) +
-  theme_cowplot()+
-  theme(axis.text.x = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.8,1.2))+
-  labs(x = ' ',
-       y='Relative fitness')
-
-f2.2 <- ggplot(R0ss%>% filter(Scenario=='P strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=ActivityCost,size=as.numeric(ActivityCost)/3)) +
-  theme_cowplot()+
-  theme(axis.text = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.8,1.2))+
-  labs(x =' ',
-       y=' ')
-
-R0sss <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- data.frame(gouts[[x]]['R0'])
-   y$Temperature <-gouts[[x]][['winfs']]$Temperature
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-R0sss <- R0sss %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T),
-         Food = factor(Food,levels=c('High','Medium','Low')))
-
-f3.1 <- ggplot(R0sss %>% filter(Scenario=='M strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=Food,size=as.numeric(Food)/3)) +
-  theme_cowplot()+
-  theme(
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.8,1.2))+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative fitness')
-
-f3.2 <- ggplot(R0sss %>% filter(Scenario=='P strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=Food,size=as.numeric(Food)/3)) +
-  theme_cowplot()+
-  theme(axis.text.y = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.8,1.2))+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=' ')
-
-cowplot::plot_grid(f1.1,f1.2,f2.1,f2.2,f3.1,f3.2,ncol=2,labels = 'auto')
-
-@
-
-\section{Discussion}
+\section*{Discussion}
 
@@
 Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages.
-For instance, oxygen limitation is a more severe constraint for small individuals (fig.
-\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
+For instance, oxygen limitation is a more severe constraint for small individuals (fig./~\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
 Furthermore, changes in environmental oxygen supply, if beyond an organisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
 
-Variation in performance metrics away from temperature extremes, even if potentially correlated with aerobic scope (e.g., growth efficiency), are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
+Variation in performance metrics away from temperature extremes are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
 Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\cite{lucas_utilization_1992,priede_metabolic_1985}).
@@
 
-Importantly, fitness is predicted to decline with increasing temperature in nearly all our simulation scenarios.
-This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
-In many species, both the aerobic scope and growth efficiency peak at relatively high temperatures within the potential thermal range, yet species are generally found at temperatures lower than these optima (\cite{magnuson_thermal_1997, claireaux_influence_2000}).
-This apparent paradox can be explained by an opposing trend in fitness: fitness is predicted to decline with increasing temperature in nearly all scenarios, and leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
-The decline in fitness is caused by a decline in available energy with temperature, and a constant or increasing mortality rate.
+In many species, both the aerobic scope and growth peak at relatively high temperatures within the potential thermal range, yet species are often found at temperatures lower than these optima (\cite{magnuson_thermal_1997, claireaux_influence_2000}).
 Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\cite{claireaux_influence_2000, magnuson_thermal_1997}).
-However, in relatively homogeneous habitats such as marine ecosystems, for example, the simple negative relationship between growth and fitness across the temperature range provides a parsimonious explanation for this apparent paradox.
+In nearly all our simulation scenarios, fitness is predicted to decline with increasing temperature.
+This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.s
 
@@
 leading to increased fitness at warmer temperatures. Our
-base-parametrisation is based on the assumption that the fractional
-aerobic scope reflects the cost of maximal activity (i.e., cost of
-$\tau=1$) relative to standard metabolism. The fractional scope varies
-widely around an average of $\delta \approx 4$ (\cite[e.g.,
-][]{killen_ecological_2016}), however, this approximation may not
+base-parametrisation is based on the assumption that activity cost $k_a$ reflects the cost of maximal activity (i.e., cost of
+$\tau=1$), and has the same pay-off for all life-histories. This approximation may not
 reflect actual activity cost as swimming at MMR in fast predatory fish
@@
 
-Our prediction of constantly decreasing fitness with temperature, especially for relatively inactive species (safe strategists), contrasts with a previous species-specific eco-physiological model for cod that includes similar constraints to our model (\cite{holt_climate_2014,holt_climate_2015}), and which predicted relatively high fitness at high temperatures.
-Although this difference is potentially due to the different activity cost coefficients and foraging assumptions in our model, the product of $\delta*\tau$ is on the same order of magnitude in both models.
-Differences may also be due to key assumptions about time-scales in the model --- we assume an evolutionarily fixed maturation reaction norm that drives relative growth and reproductive output across temperatures.
-In other words, we explicitly model species responses on ecological time-scales.
-Models of Holt \& Joergensen have assumed that adaption of reproductive investment is instantaneous with changing temperatures --- species display an evolutionarily optimal maturation-reaction at any temperature (\cite{holt_climate_2014,holt_climate_2015}).
-This, however, would require foresight about future environmental conditions and related reproductive output.
-In practice this optimisation occurs through selection, and we suggest that our "short-sighted" optimisation of activity coupled with a evolutionarily stable maturation-reaction norm provides a more explicit separation of evolutionary and ecological time-scales.
-
 That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\cite{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
-Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\cite{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (safe strategy) life-history.
+Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\cite{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (slow strategy) life-history.
 Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
@@
 This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses.
-Only large individuals of the simulated production strategy species will optimally decrease activity as a result of increased temperature.
+Only large individuals of the simulated fast strategy species will optimally decrease activity as a result of increased temperature.
 In this case, additional activity will lead to comparatively small gains from feeding relative to the cost of activity and SDA, owing to the non-linearity of the functional response.
@@
 Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\cite{atkinson_temperature_1994}), without needing to evoke direct changes in ecological rates with temperature.
-This leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (fig.s \ref{fig:norms}, \ref{fig:norms_O2}).
+The physiological basis leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (figs \ref{fig:norms}, \ref{fig:norms_O2}).
 Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\cite{angilletta_temperature_2004}).
+
+In order to provide a general framework, our model setup is deliberatly minimalist, and probably under-parametrised to reflect ecological and life-history aspects of particular species, such as migrations, social behaviour or seasonal energy requirements.
+As such, this framework provides a null model to assess the diversity of possible responses in fish, and other ectotherms, to temperature in a highly simplified system.
+Nevertheless, it provides a starting point from which to explore the importance of costs and benefits of particular life-histories and thermal adaptations.
+For instance, a recent species-specific eco-physiological model for cod (\emph{Gadus morhua}) that includes similar physiological constraints to our model predicted relatively high fitness at high temperatures (\cite{holt_climate_2014,holt_climate_2015}).
+Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \textcite{holt_climate_2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive patterns could offset potential fitness declines with increasing temperatures.
+
+\section*{Conclusions}
 
@@
 
-\end{spacing}
+% \section*{Acknowledgments}
+% 
+% The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
+PN was supported by a Marsden fast-start grant by the Royal Society Te Apārangi of New Zealand.
+KHA was supported by the Centre for Ocean Life, a VKR Centre of Excellence funded by the Villum Foundation.
 
-\printbibliography
+\newpage{}
 
-\appendix
+\titleformat{\section}{\normalfont\bfseries\sffamily}{APPENDIX \thesection:}{1em}{}
+\renewcommand{\theequation}{\thesection-\arabic{equation}}
+\renewcommand{\thetable}{\thesection-\arabic{table}}
+\renewcommand{\thefigure}{\thesection-\arabic{figure}}
+\setcounter{figure}{0}  % reset counter 
+\setcounter{table}{0}  % reset counter 
+\setcounter{equation}{0}  % reset counter
 
-\section{Specification of temperature dependent oxygen availability}
-
-The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
-Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\cite{priede_metabolic_1985}).
-We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR.
-We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\cite{gnauck2013freshwater, lefrancois_influence_2003}):
-
-\begin{align}
-f_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{crit})\log(0.5)/(P50-P_{crit})}\right),\\
-\lambda(T)&=\zeta\left(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right)^\eta \times \exp\left(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right),
-\end{align}
-
-Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term describes the saturation dependence on ambient $O_2$ at temperature $T$ ($O_2(T)$).
-At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}).
-We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{crit}$ is the ambient concentration at which oxygen supply ceases.
-Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentration at 5\degree C.
-To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height (fig.
-\ref{fig:O2_fig}).
-Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature.
-
-\input{O2_fig}
-
-\section{Maturation-reaction norm}
+\section*{Maturation-reaction norm}
 \label{sec:MRN}
 
-A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig. \ref{fig:MRN}).
+A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig./~\ref{fig:MRN}).
 
-<<MRN, fig.cap='Proportion of energy allocated to reproduction, as a function of age (a) and size (b).
-With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.',fig.align='center',fig.height=6>>=
+\begin{figure}
 
-lam <- goutr[[3]]$t_growth
+{\centering \includegraphics[width=\maxwidth]{images/MRN-1}
 
-mr1 <- ggplot(lam) + 
-  geom_line(aes(x=t, y=allocs,col=Temperature,group=as.factor(Temperature))) +
-  #geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Proportion',
-       x='Age  (years)')
+}
 
-mr2 <- ggplot(lam) + 
-  geom_line(aes(x=t_length, y=allocs,col=Temperature,group=as.factor(Temperature))) +
-  #geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Proportion',
-       x='Size (cm)')
-
-cowplot::plot_grid(mr1,mr2,ncol=1,labels = 'auto')
-
-@
+\caption[Proportion of energy allocated to reproduction, as a function of age (a) and size (b)]{Proportion of energy allocated to reproduction, as a function of age (a) and size (b).
+With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.}\label{fig:MRN}
+\end{figure}
 
@@
 
-\section{Supplementary results}
+\section*{Supplementary results}
 
@@
 \centering
-<<activitys, fig.height=4,fig.width=6>>=
 
-sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,O2lim))
+\includegraphics[width=\maxwidth]{images/activitys-1}
 
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
-
-lab1 <- as_labeller(c(`M strategy Rising`  ='a',
-                   `P strategy Rising` = 'c'))
-
-lab2 <- as_labeller(c(`M strategy Rising`  ='b',
-                   `P strategy Rising` = 'd'))
-
-ggsc <- ggplot(sc_act %>% filter(O2lim=='Rising')) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
-  mutate(Dispatch = paste(Scenario,O2lim))
-
-ggso <- sco %>% filter(O2lim=='Rising') %>%
-  ggplot() + 
-   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot() +
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression(Oxygen~(mg.yr^-1)))
-
-cowplot::plot_grid(ggsc,ggso,ncol=2)
-
-@
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for safe strategy (slow life history; aandb) and production strategy (fast life-history; c, d).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; aandb) and fast strategy (fast life-history; c, d).}
 \label{fig:activity-rising}
@@
 
-<<size-act_low,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm; e--f), for a production strategy (fast life-history) species with a dome-shaped maximum metabolic rate with respect to temperature.
-',fig.align='center'>>=
+\begin{figure}
 
-scsa[[4]]$m <- 80
-scsa[[5]]$m <- 80
-scsa[[6]]$m <- 80
+{\centering \includegraphics[width=\maxwidth]{images/size-act_low-1}
 
-scenarios_d <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('P strategy'),each=3),each=int_temp)),
-                                   AC= as.factor(rep(rep(c('High','Medium','Low'),1),each=int_temp))),
-                       bind_rows(lapply(scsa[4:6], plot_data_temp)))
+}
 
-sc_actd <- gather(scenarios_d,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,AC))
+\caption[Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm]{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm; e--f), for a fast strategy (fast life-history) species with a dome-shaped maximum metabolic rate with respect to temperature.
+}\label{fig:size-act_low}
+\end{figure}
 
-laba <- as_labeller(c(`P strategy Low` ='a',
-                   `P strategy Medium`  ='b',
-                   `P strategy High` ='c'))
+\begin{figure}
 
-sc_actd$Dispatch <- factor(sc_actd$Dispatch,levels=unique(sc_actd$Dispatch)[order(unlist(laba(unique(sc_actd$Dispatch))))])
+{\centering \includegraphics[width=\maxwidth]{images/size-rates-1}
 
-ggplot(sc_actd) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = laba)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
+}
 
-@
-
-<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for safe strategy (slow life history; left column [a,c,e]) and production strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.
-Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center'>>=
-
-sc_feed <- scenarios_s %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,Size) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         M = sc(M),
-         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         `Relative M` = sc(M),
-         `Energy` = sc(`Available Energy`),
-         Fitness = sc(`Available Energy`/M)) %>%  
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,Size))
-
-sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])
-
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
-
-@
+\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\infty}\sim 30$cm) of 1.25g (5cm]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\infty}\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.
+Energy, mortality and fitness are plotted relative to their maximum over all temperatures.}\label{fig:size-rates}
+\end{figure}
 
@@
 \centering
-<<norms_O2, fig.align='center',fig.height=6>>=
 
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b',
-                   `M strategy Rising`  ='c',
-                   `P strategy Rising` = 'd'))
+{\centering \includegraphics[width=\maxwidth]{images/norms_O2-1}
 
-t_growth <- bind_rows(lapply(1:length(goutr), function(x) {
-  y <- goutr[[x]][['t_growth']] 
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
-  y}))
+}
 
-#browser()
-norm <- t_growth %>% 
-  mutate(Dispatch = paste(Scenario,O2lim)) %>%
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  #geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  #geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
 \caption{Contrasting growth responses at baseline resource availability for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
-Growth curves are shown for safe- (left column [a,c]) and production strategists (right column [b,d]).
+Growth curves are shown for slow- (left column [a,c]) and fast strategists (right column [b,d]).
 Increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.}
@@
 
-<<>>=
+\begin{figure}
 
-scsg <- lapply(scsg,function(x) {x$slope=-1;x})
+{\centering \includegraphics[width=\maxwidth]{images/norms_neg-1}
 
-goutss <- parallel::mclapply(scsg[1:3],
-                             plot_data_growth_tO2,
-                             mstar=mstar_ss,
-                             mc.cores = 3)
+}
 
-goutsf <- parallel::mclapply(scsg[4:6],
-                             plot_data_growth_tO2,
-                             mstar=mstar_fs,
-                             mc.cores = 3)
+\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_neg}
+\end{figure}
 
-gouts <- c(goutss,goutsf)
+\begin{figure}
 
-@
+{\centering \includegraphics[width=\maxwidth]{images/norms_pos-1}
 
-<<norms_neg, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
+}
 
-labla <- as_labeller(c(`M strategy Low` ='a',
-                   `P strategy Low`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy High` = 'e',
-                   `P strategy High` = 'f'
-))
-
-t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
-
-#browser()
-norm <- t_growth %>% 
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
-
-<<>>=
-
-scsg <- lapply(scsg,function(x) {x$slope=1;x})
-
-goutss <- parallel::mclapply(scsg[1:3],
-                             plot_data_growth_tO2,
-                             mstar=mstar_ss,
-                             mc.cores = 3)
-
-goutsf <- parallel::mclapply(scsg[4:6],
-                             plot_data_growth_tO2,
-                             mstar=mstar_fs,
-                             mc.cores = 3)
-
-gouts <- c(goutss,goutsf)
-
-@
-
-<<norms_pos, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for safe- (left column [a,c,e]) and production strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
-
-labla <- as_labeller(c(`M strategy Low` ='a',
-                   `P strategy Low`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy High` = 'e',
-                   `P strategy High` = 'f'
-))
-
-t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
-
-#browser()
-norm <- t_growth %>% 
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
+\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_pos}
+\end{figure}
 

### 2018-07-06 draft_model_only_for_AMNAT_bbl.Rnw
AmNat submission

--- 2018-07-06 MS_AMNat.Rnw
@@
-\documentclass[11pt]{article}
-\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
-\usepackage{fullpage}
+\documentclass[a4paper, toc=index,abstract=true]{scrartcl}
 \usepackage{gensymb}
+\usepackage{geometry}
+\usepackage{enumitem}
+\usepackage{setspace}
+\usepackage{booktabs}
+\usepackage{subfig}
+\usepackage{placeins}
+\usepackage{amsmath}
+\usepackage{pdflscape}
 \usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{amsmath}
+\usepackage{longtable}
+\usepackage[toc,page]{appendix}
+\usepackage{array,booktabs}
+\usepackage[american]{babel}
 \usepackage[authoryear,sectionbib,sort]{natbib}
-\linespread{1.7}
-\usepackage[utf8]{inputenc}
-\usepackage{lineno}
-\usepackage{titlesec}
-\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
-\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
-\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
-\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}
+%\usepackage[backend=bibtex, citestyle = amnatnat]{biblatex}%
+\usepackage{lineno, blindtext}
+%\addbibresource{Sizing-fx-of-temperature.bib}
+
+\captionsetup[table]{singlelinecheck=false}
 
 \title{Thermal performance of fish is explained by an interplay between physiology, behaviour, and ecology}
-
-% \author{Philipp Neubauer^{1,\ast}$ \\ 
-%         Ken H. Andersen$^{2,\dag}$}
-
-\date{}
+\author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
+        Ken H. Andersen\\Centre for Ocean Life
+        Danish Technical University, Lyngby, Denmark}
 
@@
 
-% \noindent{} 1. Dragonfly Data Science, PO Box 27535, Wellington 6141, New Zealand;
-% 
-% \noindent{} 2. Centre for Ocean Life, National Institute of Aquatic Resources, Technical University of Denmark, 7 Kemitorvet B-202, 2800 Kongens Lyngby, Denmark;
-
-\bigskip
-
-\textit{Manuscript elements}: Figure~1, figure~2, table~1, online appendices~A and B (including figure~A1 and figure~A2). Figure~2 is to print in color.
-
-\bigskip
-
-\textit{Keywords}: thermal performance, OCLTT, metabolic rate, climate change
-
-\bigskip
-
-\textit{Manuscript type}: Article.
-
-\bigskip
-
-\noindent{\footnotesize Prepared using the suggested \LaTeX{} template for \textit{Am.\ Nat.}}
-
-\linenumbers{}
-\modulolinenumbers[3]
-
-\newpage{}
-
-\section*{Abstract}
+\begin{spacing}{1.9}
+
+\pagenumbering{gobble}
+\begin{abstract}
 
@@
 
+\end{abstract}
+{\large Keywords:} thermal performance curves, OCLTT, metabolic rates, climate change
+
 \newpage
@@
 
-Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\citealt{deutsch_climate_2015,pinsky_marine_2013}).
-As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\citealt{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).
+Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\citealt{deutschclimate2015,pinskymarine2013}).
+As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\citealt{deutschclimate2015, stuart-smiththermal2015, parmesanglobally2003, waltherecological2002}).
 However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems.
-Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\citealt{brander_overconfidence_2013, lefevre_models_2017}).
-In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\citealt{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\citealt{brander_overconfidence_2013, lefevre_models_2017,jutfelt_oxygen-and_2018}).
-
-Although there are conceptual and model frameworks to explain aspects of thermal performance and ecological responses to temperature (\citealt{fry_effects_1947,brown_toward_2004,pauly_sound_2017,portner_oxygen-and_2010}), many of these remain controversial as they appear limited in their generality or predictive capacity (\citealt{lefevre_models_2017,jutfelt_oxygen-and_2018}).
-To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in  ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angilletta_temperature_2004,atkinson_temperature_1994}), or attack rates (\citealt{englund_temperature_2011,rall_universal_2012}) with temperature, from fundamental physiological processes.
-Instead, and as advocated by the metabolic theory of ecology (\citealt{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{angilletta_temperature_2004,vucic-pestic_warming_2011, guiet_effects_2016}).
-
-A phenomenological description that assumes a general ecological temperature response often fails to explain heterogeneity in ecological responses (\citealt{angilletta_temperature_2004,rall_universal_2012}).
-Although ecological rates seem to follow some general patterns in the response to temperature, there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}).
-This leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
-In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011,lefevre_models_2017}).
+Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\citealt{branderoverconfidence2013, lefevremodels2017}).
+In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\citealt{cheungshrinking2013}), have been criticized as overly simplistic and not in line with physiological constraints (\citealt{branderoverconfidence2013, lefevremodels2017,jutfeltoxygen-and2018}).
+
+Although there are conceptual and model frameworks to explain aspects of thermal performance and ecological responses to temperature (\citealt{fryeffects1947,browntoward2004,paulysound2017,portneroxygen-and2010}), many of these remain controversial as they appear limited in their generality or predictive capacity (\citealt{lefevremodels2017,jutfeltoxygen-and2018}).
+To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in  ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angillettatemperature2004,atkinsontemperature1994}), or attack rates (\citealt{englundtemperature2011,ralluniversal2012}) with temperature, from fundamental physiological processes.
+Instead, and as advocated by the metabolic theory of ecology (\citealt{browntoward2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{angillettatemperature2004,vucic-pesticwarming2011, guieteffects2016}).
+
+A phenomenological description that assumes a general ecological temperature response often fails to explain heterogeneity in ecological responses (\citealt{angillettatemperature2004,ralluniversal2012}).
+Although ecological rates seem to follow some general patterns in the response to temperature, there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angillettatemperature2004,englundtemperature2011,ralluniversal2012}).
+This leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guieteffects2016}).
+In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pesticwarming2011,lefevremodels2017}).
 Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.
 
-Physiologically, a long held view has been that temperature is a controlling factor while oxygen supply sets the physiological limits (\citealt{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016}).
+Physiologically, a long held view has been that temperature is a controlling factor while oxygen supply sets the physiological limits (\citealt{fryeffects1947,claireauxlinking2007,lefevreare2016}).
 How exactly temperature influences ectotherm physiological rates and limits, however, has been a matter of debate, not least because of the variable responses observed among different species.
 In most species, the standard metabolism (SM; the metabolic cost of maintenance and routine activity such as ventilation) increases near exponentially with temperature.
-A prevalent view is that the maximum metabolic rate (MMR; the metabolic rate at maximum sustained exercise) has a dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\citealt{fry_effects_1947,claireaux_linking_2007,lefevre_are_2016,portner_physiology_2008}).
+A prevalent view is that the maximum metabolic rate (MMR; the metabolic rate at maximum sustained exercise) has a dome-shaped response to temperature, whereby it can be increased (passively and actively) up to a point, but plateaus or decreases thereafter (\citealt{fryeffects1947,claireauxlinking2007,lefevreare2016,portnerphysiology2008}).
 This leads to the view of a uni-modal curve for metabolic scope (MMR minus SM; the available oxygen/energy for additional activity), and suggests that towards the upper end of this curve, organisms will, simply put, run out of oxygen.
 
-This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\citealt{portner_oxygen-and_2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
-In some species, however, maximum metabolic rate increases steadily (\citealt{lefevre_are_2016, verberk_does_2016}), suggesting that oxygen may not be the limiting factor at high temperatures.
-Indeed, it has been argued that oxygen is unlikely to determine performance for most species over most of their temperature range as oxygen limits are rarely reached during normal activity (\citealt{jutfelt_oxygen-and_2018, holt_climate_2015}).
+This view was encapsulated in the Theory of Oxygen and Capacity Limitation of Temperature (\citealt{portneroxygen-and2010}), which suggests that the decrease in metabolic scope towards extreme temperatures limits species ability to sustain core functions such as foraging and growth (i.e., functions beyond SM).
+In some species, however, maximum metabolic rate increases steadily (\citealt{lefevreare2016, verberkdoes2016}), suggesting that oxygen may not be the limiting factor at high temperatures.
+Indeed, it has been argued that oxygen is unlikely to determine performance for most species over most of their temperature range as oxygen limits are rarely reached during normal activity (\citealt{jutfeltoxygen-and2018, holtclimate2015}).
 
@@
 
-Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets (\citealt{holt_climate_2015,holt_climate_2014}).
+Our model assumes that physiology is described by two key budgets: the energy and oxygen budgets (\citealt{holtclimate2015,holtclimate2014}).
 We assume that animals will adapt activity levels to optimise available energy for growth and reproduction relative to mortality risk.
@@
 \subsection*{Model description}
-Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality (\citealt{gilliam_habitat_1987}).
+Ectotherms adjust the relative amounts of time ($\tau$) spent on metabolically costly activity and resting/hiding to optimise the net energy gain relative to mortality (\citealt{gilliamhabitat1987}).
 In the following, we refer to $\tau$ as the activity fraction for sake of generality.
@@
 
-Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazier_activity_2009,brett1965relation}, and the activity fraction.
-Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approimated by an Arrhenious scaling $c(T) = e^{E_a(T-T_0)/(bTT_0)}$, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (here 15 degrees Celsius), and $b$ is the Bolzman constant.
+Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazieractivity2009,brett1965relation}, and the activity fraction.
+Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschkepredator2002, sentisparsing2013}) and approimated by an Arrhenious scaling $c(T) = e^{E_a(T-T_0)/(bTT_0)}$, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (here 15 degrees Celsius), and $b$ is the Bolzman constant.
 Note that we only scale rates related to enzymatic activity with temperature, we do assume that ecological rates such as foraging rates or activity are a direct function of temperature.
@@
 The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
-Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\citealt{priede_metabolic_1985}).
+Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\citealt{priedemetabolic1985}).
 We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR.
-We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck2013freshwater, lefrancois_influence_2003}):
+We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck2013freshwater, lefrancoisinfluence2003}):
 
@@
 Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the $s_{O_2}(T)$ term describes the saturation dependence on ambient $O_2$ at temperature $T$ ($O_2(T)$).
-At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}).
+At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancoisinfluence2003}).
 We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{\text{crit}}$ is the ambient concentration at which oxygen supply ceases.
@@
 
-\input{O2_fig}
-
-In pour model, fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \citealt{gilliam_habitat_1987}:
+\begin{figure}
+\includegraphics[width=\linewidth]{images/O2_fig_used-1} \caption[Maximum oxygen supply relative to the maximum supply for species with a dome-shaped MOS (here $\eta$ = 3) and a continually increasing MOS ($\eta$ = 0.1) used in model scenarios discussed below]{Maximum oxygen supply relative to the maximum supply for species with a dome-shaped MOS (here $\eta$ = 3) and a continually increasing MOS ($\eta$ = 0.1) used in model scenarios discussed below.}\label{fig:O2_fig_used}
+\end{figure}
+
+In pour model, fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \citealt{gilliamhabitat1987}:
 \begin{equation}
@@
 \end{equation}
-This optimisation represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for optimisation in stable environments (\citealt{sainmont_effective_2015}).
-Mortality scales with activity fraction and weight as $w^{q-1}$ (\citealt{andersen_how_2009, hartvig_food_2011}):
+This optimisation represents a "short-sighted" fitness optimisation that does not account for future changes in conditions, and is appropriate for optimisation in stable environments (\citealt{sainmonteffective2015}).
+Mortality scales with activity fraction and weight as $w^{q-1}$ (\citealt{andersenhow2009, hartvigfood2011}):
 \begin{equation}
@@
 
-Performance itself is a vague concept that is often used without definition in the relevant literature, but it is only defined in the context of a particular physiological or demographic parameter, with potentially different thermal response curves (\citealt{jutfelt_oxygen-and_2018}).
-For instance, even though growth in ectotherms is often impacted by temperature (\citealt{angilletta_temperature_2004}), measured performance may depend strongly on what aspect of growth is measured --- whether it is the growth increment at a particular size, growth efficiency per unit intake, the attained asymptotic size, or parameters of a fitted growth curve.
+Performance itself is a vague concept that is often used without definition in the relevant literature, but it is only defined in the context of a particular physiological or demographic parameter, with potentially different thermal response curves (\citealt{jutfeltoxygen-and2018}).
+For instance, even though growth in ectotherms is often impacted by temperature (\citealt{angillettatemperature2004}), measured performance may depend strongly on what aspect of growth is measured --- whether it is the growth increment at a particular size, growth efficiency per unit intake, the attained asymptotic size, or parameters of a fitted growth curve.
 We use and compare four performance measures with broad ecological and practical implications:
@@
 Temperature affects growth via its effects on the energy budget and the investment of available (surplus) energy into reproduction and growth.
-The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}).
+The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmannprobabilistic2007}).
 We defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
@@
 The slope of maturation reaction norms is evolutionarily determined by the strength of the co-variation between growth and mortality for a given population in a given environment.
-Strongly positive co-variation leads to the relatively flat reaction norms observed for most fish populations (\citealt{marty_impact_2011}).
+Strongly positive co-variation leads to the relatively flat reaction norms observed for most fish populations (\citealt{martyimpact2011}).
 This covariation is probably the consequence of good growth conditions (e.g., from increased prey density) altering the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators).
@@
 The allocation was parametrised as 
-\[ \phi(w^*) = 1/(1+\exp(-cw^*))\],
+\[\phi(w^*) = 1/(1+\exp(-cw^*))\],
 where $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
@@
 
-\[R_0(T) = \int_0^\infty \phi(w(t),w^*)P(w(t),T)S_{0 \rightarrow t}(T) \text{d}t, \text{, where} \\
+\[R_0(T) = \int_0^\infty \phi(w(t),w^*)P(w(t),T)S_{0 \rightarrow t}(T) \text{d}t, \text{, where}\\
 S_{0 \rightarrow t}(T) = \int_0^t \exp(-M(w(t),T))\text{d}t \]
@@
 
-int_m <- 500
-int_t <- 500
-int_temp <- 30
+int_m <- 50
+int_t <- 50
+int_temp <- 10
 
@@
 Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the fast strategy, indicated by a subscript $f$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth slow strategy, indicated by a subcript $s$).
-This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
+This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnovevolutionary2013} (\citeyear{charnovevolutionary2013}).
 In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm or $w_{\infty}\sim 270$g) with defensive/sluggish versus active life-histories.
@@
 metabolic costs
-(\citealt{priede_metabolic_1985,killen_intraspecific_2010}). We assumed
+(\citealt{priedemetabolic1985,killenintraspecific2010}). We assumed
 that higher standard metabolism is due to increased digestive capacity
@@
 larger heart will also contribute to higher standard metabolism in
-active species (\citealt{priede_metabolic_1985}). In practice, we assumed
+active species (\citealt{priedemetabolic1985}). In practice, we assumed
 that approximately 50\% of the standard metabolic cost is due to gut
@@
 
-We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \citealt{salin_inadequate_2016,iftikar_mitochondria_2013}).
+We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \citealt{salininadequate2016,iftikarmitochondria2013}).
 In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig./~\ref{fig:O2_fig}).
-Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\citealt{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
+Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\citealt{salininadequate2016,iftikarmitochondria2013}) may determine upper limits to activity over some or all of a species temperature range.
 However the over-all mechanism would be the same to the one assumed here, with different untis (e.g., ATP instead of $O_2$).
@@
 
-Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig./~\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\citealt{sainmont_effective_2015}).
+Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig./~\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\citealt{sainmonteffective2015}).
 With increasing temperatures, fitness declines at our basic parameter settings, in opposition to growth and aerobic scope.
@@
 In this study, we attempt to provide a general mechanistic basis for exploring thermal sensitivities of ectotherm organisms.
-Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\citealt{pauly_sound_2017,lefevre_modelling_2017}).
+Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\citealt{paulysound2017,lefevremodelling2017}).
 We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organism response to temperature.
@@
 
-It has been argued that the OCLTT as a concept provides a basis to explain observed responses to climate change on the basis of oxygen limitation via the aerobic scope (\citealt{portner_physiology_2008,portner_oxygen-and_2010}), and simple oxygen budgets have been used to predict metabolic constraints on organismal activity due to warming ocean temperatures (\citealt{deutsch_climate_2015}).
-As a conceptual framework, however, the OCLTT is subject not only to semantic dispute but also criticism of its core concept of oxygen limitation (\citealt{jutfelt_oxygen-and_2018,lefevre_are_2016}).
-
-Our quantitative thermal impact model generalises existing eco-physiological models for particular species and stocks (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}), and allows to develop a more nuanced understanding of interactions between temperature, oxygen limitation and ecology for species with varying traits.
+It has been argued that the OCLTT as a concept provides a basis to explain observed responses to climate change on the basis of oxygen limitation via the aerobic scope (\citealt{portnerphysiology2008,portneroxygen-and2010}), and simple oxygen budgets have been used to predict metabolic constraints on organismal activity due to warming ocean temperatures (\citealt{deutschclimate2015}).
+As a conceptual framework, however, the OCLTT is subject not only to semantic dispute but also criticism of its core concept of oxygen limitation (\citealt{jutfeltoxygen-and2018,lefevreare2016}).
+
+Our quantitative thermal impact model generalises existing eco-physiological models for particular species and stocks (\citealt{hufnaglphysiological2011, holtclimate2014,holtclimate2015}), and allows to develop a more nuanced understanding of interactions between temperature, oxygen limitation and ecology for species with varying traits.
 In line with the conceptual framework of Fry's aerobic scope and the OCLTT, our model suggests that oxygen limitation can be a potentially important ecological driver, especially at extreme temperatures for species with declining MOSs in such temperature regimes.
 At the onset of this limitation, ecological parameters change drastically, and growth, mortality are strongly impacted.
-This limitation closely mimics limitations seen in wild fish (\citealt{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}).
+This limitation closely mimics limitations seen in wild fish (\citealt{myricktemperature2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrongdiel2013,claireauxphysiology1995}).
 Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages.
@@
 Variation in performance metrics away from temperature extremes are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
-Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\citealt{lucas_utilization_1992,priede_metabolic_1985}).
-Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\citealt{priede_natural_1977,priede_metabolic_1985}).
-Furthermore, as a limit for long-term performance, the MOS does not usually impose a limitation on short term energy demands, as fish can incur oxygen debt during swimming bursts during which the MOS is exceeded (\citealt{brett_metabolic_1972,priede_metabolic_1985}).
+Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holtclimate2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\citealt{lucasutilization1992,priedemetabolic1985}).
+Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\citealt{priedenatural1977,priedemetabolic1985}).
+Furthermore, as a limit for long-term performance, the MOS does not usually impose a limitation on short term energy demands, as fish can incur oxygen debt during swimming bursts during which the MOS is exceeded (\citealt{brettmetabolic1972,priedemetabolic1985}).
 A logical conclusion is that the metabolic scope is only limiting to performance at extreme temperatures where MOS is low due to impaired oxygen delivery.
 
-In many species, both the aerobic scope and growth peak at relatively high temperatures within the potential thermal range, yet species are often found at temperatures lower than these optima (\citealt{magnuson_thermal_1997, claireaux_influence_2000}).
-Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\citealt{claireaux_influence_2000, magnuson_thermal_1997}).
+In many species, both the aerobic scope and growth peak at relatively high temperatures within the potential thermal range, yet species are often found at temperatures lower than these optima (\citealt{magnusonthermal1997, claireauxinfluence2000}).
+Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\citealt{claireauxinfluence2000, magnusonthermal1997}).
 In nearly all our simulation scenarios, fitness is predicted to decline with increasing temperature.
@@
 is far more efficient than swimming of sluggish fish, such as flatfish
-(\citealt{priede_metabolic_1985}).
+(\citealt{priedemetabolic1985}).
 Such an efficiency gain may occur as a result of more efficient form or physiology, or simply by reduced drag at large size (e.g., whale-sharks), and may be a key requirement to the viability of active pelagic predatory fish in tropical waters.
 
-That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\citealt{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
-Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\citealt{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (slow strategy) life-history.
+That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\citealt{gilliamhabitat1987,sainmonteffective2015,priedenatural1977, claireauxinfluence2000,hufnaglphysiological2011}).
+Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\citealt{priedenatural1977}), an observation that is in line with predictions from our model, especially for the slow (slow strategy) life-history.
 Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
-This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\citealt{priede_metabolic_1985}).
+This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\citealt{priedemetabolic1985}).
 
 Optimal activity is predicted to increase with temperature in nearly all cases, but it is sensitive to the cost of activity - at higher cost relative to the potential pay-off, activity may even decline at high temeprature.
-Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\citealt{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
-This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses.
+Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\citealt{sswatgrowth2018,brownfeeding1989,claireauxphysiology1995, biromechanisms2007}).
+This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswatgrowth2018, biromechanisms2007}), and serves the necessity to offset increased metabolic expenses.
 Only large individuals of the simulated fast strategy species will optimally decrease activity as a result of increased temperature.
@@
 increasing or dome-shaped consumption or attack-rates with temperature
-(\citealt{biro_mechanisms_2007,englund_temperature_2011,rall_universal_2012}). Depending on the
+(\citealt{biromechanisms2007,englundtemperature2011,ralluniversal2012}). Depending on the
 strength of oxygen limitation and the development of the optimal
@@
 
-Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\citealt{atkinson_temperature_1994}), without needing to evoke direct changes in ecological rates with temperature.
+Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\citealt{atkinsontemperature1994}), without needing to evoke direct changes in ecological rates with temperature.
 The physiological basis leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (figs \ref{fig:norms}, \ref{fig:norms_O2}).
-Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\citealt{angilletta_temperature_2004}).
+Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\citealt{angillettatemperature2004}).
 
@@
 Nevertheless, it provides a starting point from which to explore the importance of costs and benefits of particular life-histories and thermal adaptations.
-For instance, a recent species-specific eco-physiological model for cod (\emph{Gadus morhua}) that includes similar physiological constraints to our model predicted relatively high fitness at high temperatures (\citealt{holt_climate_2014,holt_climate_2015}).
-Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \citet{holt_climate_2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive patterns could offset potential fitness declines with increasing temperatures.
+For instance, a recent species-specific eco-physiological model for cod (\emph{Gadus morhua}) that includes similar physiological constraints to our model predicted relatively high fitness at high temperatures (\citealt{holtclimate2014,holtclimate2015}).
+Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \citet{holtclimate2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive patterns could offset potential fitness declines with increasing temperatures.
 
@@
 
-The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheung_shrinking_2013, pauly_sound_2017}).
-We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
+The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheungshrinking2013, paulysound2017}).
+We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{branderoverconfidence2013, lefevremodels2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guieteffects2016}) and species specific eco-physiology models (\citealt{hufnaglphysiological2011, holtclimate2014,holtclimate2015}).
 In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT.
@@
 
-% \section*{Acknowledgments}
-% 
-% The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
-PN was supported by a Marsden fast-start grant by the Royal Society Te Apārangi of New Zealand.
-KHA was supported by the Centre for Ocean Life, a VKR Centre of Excellence funded by the Villum Foundation.
-
-\newpage{}
-
-\titleformat{\section}{\normalfont\bfseries\sffamily}{APPENDIX \thesection:}{1em}{}
-\renewcommand{\theequation}{\thesection-\arabic{equation}}
-\renewcommand{\thetable}{\thesection-\arabic{table}}
-\renewcommand{\thefigure}{\thesection-\arabic{figure}}
-\setcounter{figure}{0}  % reset counter 
-\setcounter{table}{0}  % reset counter 
-\setcounter{equation}{0}  % reset counter
+\end{spacing}
+
+%\printbibliography
+
+\bibliographystyle{amnatnat}
+\bibliography{Sizing-fx-of-temperature}
+
+\appendix
 
@@
 A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig./~\ref{fig:MRN}).
-
-To express a MRN that varies as a function of age, we can reparametrise the MRN as:
-\[\phi(z) = 1/(1+\exp(-(c z))) \text{, where }\\
-z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))\]
-rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
-
-\section*{Supplementary figures}
-
-\bibliographystyle{amnatnat}
-\begin{thebibliography}{55}
-\providecommand{\natexlab}[1]{#1}
-
-\bibitem[{Andersen et~al.(2009-10-01)Andersen, Farnsworth, Pedersen, Gislason,
-  and Beyer}]{andersenhow2009}
-Andersen, K.~H., K.~D. Farnsworth, M.~Pedersen, H.~Gislason, and J.~E. Beyer.
-  2009-10-01.
-\newblock How community ecology links natural mortality, growth, and production
-  of fish populations.
-\newblock {ICES} Journal of Marine Science: Journal du Conseil 66:1978--1984.
-
-\bibitem[{Angilletta et~al.(2004)Angilletta, Steury, and
-  Sears}]{angillettatemperature2004}
-Angilletta, M.~J., T.~D. Steury, and M.~W. Sears. 2004.
-\newblock Temperature, growth rate, and body size in ectotherms: Fitting pieces
-  of a life-history puzzle.
-\newblock Integrative and Comparative Biology 44:498--509.
-
-\bibitem[{Armstrong et~al.(2013)Armstrong, Schindler, Ruff, Brooks, Bentley,
-  and Torgersen}]{armstrongdiel2013}
-Armstrong, J.~B., D.~E. Schindler, C.~P. Ruff, G.~T. Brooks, K.~E. Bentley, and
-  C.~E. Torgersen. 2013.
-\newblock Diel horizontal migration in streams: juvenile fish exploit spatial
-  heterogeneity in thermal and trophic resources.
-\newblock Ecology 94:2066--2075.
-
-\bibitem[{Atkinson(1994)}]{atkinsontemperature1994}
-Atkinson, D. 1994.
-\newblock Temperature and organism size: a biological law for ectotherms?
-\newblock Advances in ecological research 25:1--1.
-
-\bibitem[{Biro et~al.(2007)Biro, Post, and Booth}]{biromechanisms2007}
-Biro, P.~A., J.~R. Post, and D.~J. Booth. 2007.
-\newblock Mechanisms for climate-induced mortality of fish populations in
-  whole-lake experiments.
-\newblock Proceedings of the National Academy of Sciences 104:9715--9719.
-
-\bibitem[{Brander et~al.(2013-08-21)Brander, Neuheimer, Andersen, and
-  Hartvig}]{branderoverconfidence2013}
-Brander, K., A.~Neuheimer, K.~H. Andersen, and M.~Hartvig. 2013-08-21.
-\newblock Overconfidence in model projections.
-\newblock {ICES} Journal of Marine Science 70:1065--1068.
-
-\bibitem[{Brett(1965)}]{brett1965relation}
-Brett, J. 1965.
-\newblock The relation of size to rate of oxygen consumption and sustained
-  swimming speed of sockeye salmon (oncorhynchus nerka).
-\newblock Journal of the Fisheries Board of Canada 22:1491--1501.
-
-\bibitem[{Brett(1972)}]{brettmetabolic1972}
-Brett, J.~R. 1972.
-\newblock The metabolic demand for oxygen in fish, particularly salmonids, and
-  a comparison with other vertebrates.
-\newblock Respiration physiology 14:151--170.
-
-\bibitem[{Brown et~al.(1989)Brown, Pepin, Methven, and
-  Somerton}]{brownfeeding1989}
-Brown, J.~A., P.~Pepin, D.~A. Methven, and D.~C. Somerton. 1989.
-\newblock The feeding, growth and behaviour of juvenile cod, gadus morhua l.,
-  in cold environments.
-\newblock Journal of Fish Biology 35:373--380.
-
-\bibitem[{Brown et~al.(2004)Brown, Gillooly, Allen, Savage, and
-  West}]{browntoward2004}
-Brown, J.~H., J.~F. Gillooly, A.~P. Allen, V.~M. Savage, and G.~B. West. 2004.
-\newblock Toward a metabolic theory of ecology.
-\newblock Ecology 85:1771--1789.
-
-\bibitem[{Charnov et~al.(2013)Charnov, Gislason, and
-  Pope}]{charnovevolutionary2013}
-Charnov, E.~L., H.~Gislason, and J.~G. Pope. 2013.
-\newblock Evolutionary assembly rules for fish life histories.
-\newblock Fish and Fisheries 14:213--224.
-
-\bibitem[{Cheung et~al.(2013)Cheung, Sarmiento, Dunne, Frölicher, Lam,
-  Palomares, Watson, and Pauly}]{cheungshrinking2013}
-Cheung, W.~W., J.~L. Sarmiento, J.~Dunne, T.~L. Frölicher, V.~W. Lam, M.~D.
-  Palomares, R.~Watson, and D.~Pauly. 2013.
-\newblock Shrinking of fishes exacerbates impacts of global ocean changes on
-  marine ecosystems.
-\newblock Nature Climate Change 3:254--258.
-
-\bibitem[{Claireaux and Lefrançois(2007)}]{claireauxlinking2007}
-Claireaux, G., and C.~Lefrançois. 2007.
-\newblock Linking environmental variability and fish performance: integration
-  through the concept of scope for activity.
-\newblock Philosophical Transactions of the Royal Society B: Biological
-  Sciences 362:2031--2041.
-
-\bibitem[{Claireaux et~al.(1995)Claireaux, Webber, Kerr, and
-  Boutilier}]{claireauxphysiology1995}
-Claireaux, G., D.~Webber, S.~Kerr, and R.~Boutilier. 1995.
-\newblock Physiology and behaviour of free-swimming atlantic cod (gadus morhua)
-  facing fluctuating temperature conditions.
-\newblock Journal of Experimental Biology 198:49--60.
-
-\bibitem[{Claireaux et~al.(2016-08-08)Claireaux, Webber, Lagardère, and
-  Kerr}]{claireauxinfluence2000}
-Claireaux, G., D.~M. Webber, J.-P. Lagardère, and S.~R. Kerr. 2016-08-08.
-\newblock Influence of water temperature and oxygenation on the aerobic
-  metabolic scope of atlantic cod (gadus morhua).
-\newblock Journal of Sea Research 44:257--265.
-
-\bibitem[{Deutsch et~al.(2015)Deutsch, Ferrel, Seibel, Pörtner, and
-  Huey}]{deutschclimate2015}
-Deutsch, C., A.~Ferrel, B.~Seibel, H.-O. Pörtner, and R.~B. Huey. 2015.
-\newblock Climate change tightens a metabolic constraint on marine habitats.
-\newblock Science 348:1132--1135.
-
-\bibitem[{Dieckmann and Heino(2007)}]{dieckmannprobabilistic2007}
-Dieckmann, U., and M.~Heino. 2007.
-\newblock Probabilistic maturation reaction norms: their history, strengths,
-  and limitations.
-\newblock Marine Ecology Progress Series 335:253--269.
-
-\bibitem[{Englund et~al.(2011)Englund, Öhlund, Hein, and
-  Diehl}]{englundtemperature2011}
-Englund, G., G.~Öhlund, C.~L. Hein, and S.~Diehl. 2011.
-\newblock Temperature dependence of the functional response.
-\newblock Ecology Letters 14:914--921.
-
-\bibitem[{Fry(1947)}]{fryeffects1947}
-Fry. 1947.
-\newblock Effects of the environment on animal activity .
-
-\bibitem[{Gilliam and Fraser(1987)}]{gilliamhabitat1987}
-Gilliam, J.~F., and D.~F. Fraser. 1987.
-\newblock Habitat selection under predation hazard: test of a model with
-  foraging minnows.
-\newblock Ecology 68:1856--1862.
-
-\bibitem[{Glazier(2009)}]{glazieractivity2009}
-Glazier, D.~S. 2009.
-\newblock Activity affects intraspecific body-size scaling of metabolic rate in
-  ectothermic animals.
-\newblock Journal of Comparative Physiology B 179:821--828.
-
-\bibitem[{Gnauck and Stra{\v{s}}kraba(2013)}]{gnauck2013freshwater}
-Gnauck, A., and M.~Stra{\v{s}}kraba. 2013.
-\newblock Freshwater ecosystems: modelling and simulation, vol.~8.
-\newblock Elsevier.
-
-\bibitem[{Guiet et~al.(2016)Guiet, Aumont, Poggiale, and
-  Maury}]{guieteffects2016}
-Guiet, J., O.~Aumont, J.-C. Poggiale, and O.~Maury. 2016.
-\newblock Effects of lower trophic level biomass and water temperature on fish
-  communities: A modelling study.
-\newblock Progress in Oceanography 146:22--37.
-
-\bibitem[{Hartvig et~al.(2011)Hartvig, Andersen, and Beyer}]{hartvigfood2011}
-Hartvig, M., K.~H. Andersen, and J.~E. Beyer. 2011.
-\newblock Food web framework for size-structured populations.
-\newblock Journal of Theoretical Biology 272:113--122.
-
-\bibitem[{Holt and Jorgensen(2014-11-04)}]{holtclimate2014}
-Holt, R.~E., and C.~Jorgensen. 2014-11-04.
-\newblock Climate warming causes life-history evolution in a model for atlantic
-  cod (gadus morhua).
-\newblock Conservation Physiology 2.
-
-\bibitem[{Holt and Jorgensen(2015)}]{holtclimate2015}
----{}---{}---. 2015.
-\newblock Climate change in fish: effects of respiratory constraints on optimal
-  life history and behaviour.
-\newblock Biology Letters 11:20141032--20141032.
-
-\bibitem[{Hufnagl and Peck(2011)}]{hufnaglphysiological2011}
-Hufnagl, M., and M.~A. Peck. 2011.
-\newblock Physiological individual-based modelling of larval atlantic herring
-  (clupea harengus) foraging and growth: insights on climate-driven
-  life-history scheduling.
-\newblock {ICES} Journal of Marine Science 68:1170--1188.
-
-\bibitem[{Iftikar and Hickey(2013)}]{iftikarmitochondria2013}
-Iftikar, F.~I., and A.~J.~R. Hickey. 2013.
-\newblock Do mitochondria limit hot fish hearts? understanding the role of
-  mitochondrial function with heat stress in notolabrus celidotus.
-\newblock {PLOS} {ONE} 8:e64120.
-
-\bibitem[{Jeschke et~al.(2002)Jeschke, Kopp, and
-  Tollrian}]{jeschkepredator2002}
-Jeschke, J.~M., M.~Kopp, and R.~Tollrian. 2002.
-\newblock Predator functional responses: discriminating between handling and
-  digesting prey.
-\newblock Ecological Monographs 72:95--112.
-
-\bibitem[{Jutfelt et~al.(2018)Jutfelt, Norin, Ern, Overgaard, Wang, {McKenzie},
-  Lefevre, Nilsson, Metcalfe, and Hickey}]{jutfeltoxygen-and2018}
-Jutfelt, F., T.~Norin, R.~Ern, J.~Overgaard, T.~Wang, D.~J. {McKenzie},
-  S.~Lefevre, G.~E. Nilsson, N.~B. Metcalfe, and A.~J. Hickey. 2018.
-\newblock Oxygen-and capacity-limited thermal tolerance: blurring ecology and
-  physiology.
-\newblock Journal of Experimental Biology 221:jeb169615.
-
-\bibitem[{Killen et~al.(2010)Killen, Atkinson, and
-  Glazier}]{killenintraspecific2010}
-Killen, S.~S., D.~Atkinson, and D.~S. Glazier. 2010.
-\newblock The intraspecific scaling of metabolic rate with body mass in fishes
-  depends on lifestyle and temperature.
-\newblock Ecology Letters 13:184--193.
-
-\bibitem[{Lefevre(2016)}]{lefevreare2016}
-Lefevre, S. 2016.
-\newblock Are global warming and ocean acidification conspiring against marine
-  ectotherms? a meta-analysis of the respiratory effects of elevated
-  temperature, high {CO}2 and their interaction.
-\newblock Conservation Physiology 4.
-
-\bibitem[{Lefevre et~al.(2017)Lefevre, {McKenzie}, and
-  Nilsson}]{lefevremodels2017}
-Lefevre, S., D.~J. {McKenzie}, and G.~E. Nilsson. 2017.
-\newblock Models projecting the fate of fish populations under climate change
-  need to be based on valid physiological mechanisms.
-\newblock Global Change Biology .
-
-\bibitem[{Lefevre et~al.(2018)Lefevre, McKenzie, and
-  Nilsson}]{lefevremodelling2017}
-Lefevre, S., D.~J. McKenzie, and G.~E. Nilsson. 2018.
-\newblock In modelling effects of global warming, invalid assumptions lead to
-  unrealistic projections.
-\newblock Global change biology 24:553--556.
-
-\bibitem[{Lefrancois and Claireaux(2003)}]{lefrancoisinfluence2003}
-Lefrancois, C., and G.~Claireaux. 2003.
-\newblock Influence of ambient oxygenation and temperature on metabolic scope
-  and scope for heart rate in the common sole solea solea.
-\newblock Marine Ecology Progress Series 259:273--284.
-
-\bibitem[{Lucas and Priede(1992)}]{lucasutilization1992}
-Lucas, M.~C., and I.~G. Priede. 1992.
-\newblock Utilization of metabolic scope in relation to feeding and activity by
-  individual and grouped zebrafish, brachydanio rerio (hamilton-buchanan).
-\newblock Journal of Fish Biology 41:175--190.
-
-\bibitem[{Magnuson and {DeStasio}(1997)}]{magnusonthermal1997}
-Magnuson, J.~J., and B.~T. {DeStasio}. 1997.
-\newblock Thermal niche of fishes and global warming.
-\newblock Pages 377--408 \emph{in} C.~Wood and D.~{McDonald}, eds. Global
-  warming: implications for freshwater and marine fish, vol.~61. Cambridge
-  University Press.
-
-\bibitem[{Marty et~al.(2011)Marty, Dieckmann, Rochet, and
-  Ernande}]{martyimpact2011}
-Marty, L., U.~Dieckmann, M.-J. Rochet, and B.~Ernande. 2011.
-\newblock Impact of environmental covariation in growth and mortality on
-  evolving maturation reaction norms.
-\newblock The American Naturalist 177:E98--E118.
-
-\bibitem[{Myrick and Cech(2000)}]{myricktemperature2000}
-Myrick, C.~A., and J.~J. Cech. 2000.
-\newblock Temperature influences on california rainbow trout physiological
-  performance.
-\newblock Fish Physiology and Biochemistry 22:245--254.
-
-\bibitem[{Parmesan and Yohe(2003)}]{parmesanglobally2003}
-Parmesan, C., and G.~Yohe. 2003.
-\newblock A globally coherent fingerprint of climate change impacts across
-  natural systems.
-\newblock Nature 421:37--42.
-
-\bibitem[{Pauly and Cheung(2017)}]{paulysound2017}
-Pauly, D., and W.~W.~L. Cheung. 2017.
-\newblock Sound physiological knowledge and principles in modeling shrinking of
-  fishes under climate change.
-\newblock Global Change Biology 24:e15--e26.
-
-\bibitem[{Pinsky et~al.(2013)Pinsky, Worm, Fogarty, Sarmiento, and
-  Levin}]{pinskymarine2013}
-Pinsky, M.~L., B.~Worm, M.~J. Fogarty, J.~L. Sarmiento, and S.~A. Levin. 2013.
-\newblock Marine taxa track local climate velocities.
-\newblock Science 341:1239--1242.
-
-\bibitem[{Priede(1977)}]{priedenatural1977}
-Priede, I.~G. 1977.
-\newblock Natural selection for energetic efficiency and the relationship
-  between activity level and mortality.
-\newblock Nature 267:610--611.
-
-\bibitem[{Priede(1985)}]{priedemetabolic1985}
----{}---{}---. 1985.
-\newblock Metabolic scope in fishes.
-\newblock Pages 33--64 \emph{in} Fish Energetics. Springer.
-
-\bibitem[{Pörtner(2010)}]{portneroxygen-and2010}
-Pörtner, H.-O. 2010.
-\newblock Oxygen-and capacity-limitation of thermal tolerance: a matrix for
-  integrating climate-related stressor effects in marine ecosystems.
-\newblock The Journal of experimental biology 213:881--893.
-
-\bibitem[{Pörtner and Farrell(2008)}]{portnerphysiology2008}
-Pörtner, H.~O., and A.~P. Farrell. 2008.
-\newblock Physiology and climate change.
-\newblock Science 322:690--692.
-
-\bibitem[{Rall et~al.(2012)Rall, Brose, Hartvig, Kalinkat, Schwarzmüller,
-  Vucic-Pestic, and Petchey}]{ralluniversal2012}
-Rall, B.~C., U.~Brose, M.~Hartvig, G.~Kalinkat, F.~Schwarzmüller,
-  O.~Vucic-Pestic, and O.~L. Petchey. 2012.
-\newblock Universal temperature and body-mass scaling of feeding rates.
-\newblock Phil. Trans. R. Soc. B 367:2923--2934.
-
-\bibitem[{Sainmont et~al.(2015-09)Sainmont, Andersen, Thygesen, Fiksen, and
-  Visser}]{sainmonteffective2015}
-Sainmont, J., K.~H. Andersen, U.~H. Thygesen, ?.~Fiksen, and A.~W. Visser.
-  2015-09.
-\newblock An effective algorithm for approximating adaptive behavior in
-  seasonal environments.
-\newblock Ecological Modelling 311:20--30.
-
-\bibitem[{Salin et~al.(2016)Salin, Auer, Anderson, Selman, and
-  Metcalfe}]{salininadequate2016}
-Salin, K., S.~K. Auer, G.~J. Anderson, C.~Selman, and N.~B. Metcalfe. 2016.
-\newblock Inadequate food intake at high temperatures is related to depressed
-  mitochondrial respiratory capacity.
-\newblock Journal of Experimental Biology 219:1356--1362.
-
-\bibitem[{Sentis et~al.(2013)Sentis, Hemptinne, and
-  Brodeur}]{sentisparsing2013}
-Sentis, A., J.-L. Hemptinne, and J.~Brodeur. 2013.
-\newblock Parsing handling time into its components: implications for responses
-  to a temperature gradient.
-\newblock Ecology 94:1675--1680.
-
-\bibitem[{Sswat et~al.(2018-01-25)Sswat, Stiasny, Jutfelt, Riebesell, and
-  Clemmesen}]{sswatgrowth2018}
-Sswat, M., M.~H. Stiasny, F.~Jutfelt, U.~Riebesell, and C.~Clemmesen.
-  2018-01-25.
-\newblock Growth performance and survival of larval atlantic herring, under the
-  combined effects of elevated temperatures and {CO}2.
-\newblock {PLOS} {ONE} 13:e0191947.
-
-\bibitem[{Stuart-Smith et~al.(2015)Stuart-Smith, Edgar, Barrett, Kininmonth,
-  and Bates}]{stuart-smiththermal2015}
-Stuart-Smith, R.~D., G.~J. Edgar, N.~S. Barrett, S.~J. Kininmonth, and A.~E.
-  Bates. 2015.
-\newblock Thermal biases and vulnerability to warming in the world’s marine
-  fauna.
-\newblock Nature 528:88--92.
-
-\bibitem[{Verberk et~al.(2016)Verberk, Overgaard, Ern, Bayley, Wang, Boardman,
-  and Terblanche}]{verberkdoes2016}
-Verberk, W. C. E.~P., J.~Overgaard, R.~Ern, M.~Bayley, T.~Wang, L.~Boardman,
-  and J.~S. Terblanche. 2016.
-\newblock Does oxygen limit thermal tolerance in arthropods? a critical review
-  of current evidence.
-\newblock Comparative Biochemistry and Physiology Part A: Molecular \&
-  Integrative Physiology 192:64--78.
-
-\bibitem[{Vucic-Pestic et~al.(2011-03-01)Vucic-Pestic, Ehnes, Rall, and
-  Brose}]{vucic-pesticwarming2011}
-Vucic-Pestic, O., R.~B. Ehnes, B.~C. Rall, and U.~Brose. 2011-03-01.
-\newblock Warming up the system: higher predator feeding rates but lower
-  energetic efficiencies.
-\newblock Global Change Biology 17:1301--1310.
-
-\bibitem[{Walther et~al.(2002)Walther, Post, Convey, Menzel, Parmesan, Beebee,
-  Fromentin, Hoegh-Guldberg, and Bairlein}]{waltherecological2002}
-Walther, G.-R., E.~Post, P.~Convey, A.~Menzel, C.~Parmesan, T.~J.~C. Beebee,
-  J.-M. Fromentin, O.~Hoegh-Guldberg, and F.~Bairlein. 2002.
-\newblock Ecological responses to recent climate change.
-\newblock Nature 416:389--395.
-
-\end{thebibliography}
-
-\subsection*{Online figure legends}
-
-\renewcommand{\thefigure}{A\arabic{figure}}
-\setcounter{figure}{0}
 
@@
 
-\renewcommand{\thefigure}{B\arabic{figure}}
-\setcounter{figure}{0}
+To express a MRN that varies as a function of age, we can reparametrise the MRN as:
+\[\phi(z) = 1/(1+\exp(-(c z))) \text{, where } \\
+z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b)) \]
+rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
+
+\section*{Supplementary results}
 

### 2018-07-06 figures/O2_fig.Rnw
AmNat submission

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(warning=F, message = FALSE,echo=F,results='asis',error=FALSE,fig.lp='fig:',fig.path='images/')
@

<<O2_fig,fig.cap='Maximum metabolic rate, determined by oxygen supply, as a function of temperature, for four different optimal temperatures (panels---see panel label for optimal temperature in degrees celsius), and increasing values of $\\eta$.', fig.width=8, fig.height=4, echo=FALSE, out.width='\\linewidth'>>=

grid <- expand.grid(eta = c(0.1,0.5,3,5),
                    Topt = c(10,15,20,25))

O2fun <- function(x) {
  ts = with(x,((26-seq(1,26,l=1000))/(26-Topt))^eta*exp(-eta*(26-seq(1,26,l=1000))/(26-Topt)))
  ts = ts/max(ts)
}

require(dplyr)
require(purrr)
require(ggplot2)
#require(cowplot)

g <- grid %>% 
  mutate(n=1:n()) %>%
  split(.$n) %>%
  map(~data.frame(eta = .$eta,
                  Topt = .$Topt,
                  O2 = O2fun(.))) %>%
  bind_rows(.id = 'n') %>%
  group_by(eta,Topt) %>%
  mutate(Temperature=seq(1,26,l=1000)) 
# 
# ggplot(g) + 
#   geom_line(aes(x = Temperature, 
#                 y = O2,
#                 linetype=factor(eta))) + 
#   theme_bw() + 
#   facet_grid(Topt~.) +
#   scale_linetype_discrete(bquote(eta)) + 
#   scale_x_continuous(limits = c(3,29),breaks = seq(4,28,4)) +
#   labs(y=expression(Relative~O[2]~supply),
#        x=expression("Temperature " ( degree*C)))

@

<<O2_fig_used,fig.cap='Maximum oxygen supply relative to the maximum supply for species with a dome-shaped MOS (here $\\eta$ = 3) and a continually increasing MOS ($\\eta$ = 0.1) used in model scenarios discussed below.', fig.width=6, fig.height=3, echo=FALSE, out.width='\\linewidth'>>=

ggplot(g %>% filter((eta==0.1 & Topt==25)|(eta==3 & Topt==20))) + 
  geom_line(aes(x = Temperature, 
                y = O2,
                linetype=factor(eta))) + 
  theme_bw() + 
  scale_linetype_discrete(bquote(eta)) + 
  scale_x_continuous(limits = c(3,29),breaks = seq(4,28,4)) +
  labs(y=expression(Relative~O[2]~supply),
       x=expression("Temperature " ( degree*C)))
  #scale_color_discrete(bquote(T[opt]), h.start = 180)

@

### 2018-07-06 model.R

@@ -307,7 +307,7 @@ model_out <- function(tau_max,
   inp <- (1-phi-beta)*f*tc*h*m^q
   out <- k*tc*m^n + tau_max*delta*k*tc*m^o
   e <-  inp -out
-  efficiency <- e/(f)
+  efficiency <- e/(f*tc*h*m^q)
   efficiency[efficiency<0] <- 0
   predation_rate <- f/phi
   

### 2019-01-16 MS_AMNat.Rnw
revisions

@@
 Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.
-The oxygen supply ($S_{O_2}c_{O_2}(T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig./~\ref{fig:O2_fig_used}).
+The oxygen supply ($S_{O_2}c_{O_2}(T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig.~\ref{fig:O2_fig_used}).
 The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
@@
 To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height.
-Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig./~\ref{fig:O2_fig}).
-
-\input{O2_fig}
+Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).
 
@@
 We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past.
-Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm (i.e., allocation to reproduction is a function of size only; fig./~\ref{fig:MRN}), although sloping reaction norms can be formulated and used in our framework (see appendix \ref{sec:MRN}).
+Consequently, we assumed that the evolved slope of the reaction norm is a fixed trait over the time-scales considered here for a particular species or population, and for simplicity and generality we assume a flat reaction norm (i.e., allocation to reproduction is a function of size only; fig.~\ref{fig:MRN}), although sloping reaction norms can be formulated and used in our framework (see appendix \ref{sec:MRN}).
 The intercept of this reaction norm was found numerically by maximising fitness ($R_0$, see below) at the reference temperature for our simulations (15\degree C), and this intercept was assumed fixed as temperatures change.
@@
 
+\subsection*{Trait based scenarios}
+
+To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
+Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the fast strategy, indicated by a subscript $f$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth slow strategy, indicated by a subcript $s$).
+This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
+In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm or $w_{\infty}\sim 270$g) with defensive/sluggish versus active life-histories.
+
+To implement this axis, we used the result that species with a more
+active, production oriented life-history (e.g., predatory pelagic
+fish) have a higher standard metabolism and lower weight scaling of
+metabolic costs
+(\citealt{priede_metabolic_1985,killen_intraspecific_2010}). We assumed
+that higher standard metabolism is due to increased digestive capacity
+(i.e., is used for gut maintenance), though high muscle mass and a
+larger heart will also contribute to higher standard metabolism in
+active species (\citealt{priede_metabolic_1985}). In practice, we assumed
+that approximately 50\% of the standard metabolic cost is due to gut
+maintenance, such that a doubling of the maximum ingestion leads to a
+50\% increase in standard metabolic cost.
+We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M_{s}(w) = (0.1+6\tau) w^{q-1}$ and $M_{f}(w) = (1+\tau) w^{q-1}$).
+Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
+Together, these assumed trait differences lead to very different ecological and bio-energetic responses of slow- and fast strategists (fig.~\ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for slow-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to food intake) at high activity levels.
+A slower increase in available energy and M with $\tau$ for fast strategists leads to a higher $\tau_{\text{opt}}$.
+
+We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \citealt{salin_inadequate_2016,iftikar_mitochondria_2013}).
+In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).
+Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\citealt{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
+However the over-all mechanism would be the same to the one assumed here, with different untis (e.g., ATP instead of $O_2$).
+
+\section*{Results}
+
+Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig.~\ref{fig:activity}).
+This adjustment is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig.~\ref{fig:size-act}).
+A similar increase in activity is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.~\ref{fig:size-act}).
+For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
+For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig.~\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
+For species with a rising MOS with temperature, oxygen is not limiting (fig.~\ref{fig:activity-rising}).
+However, larger fast strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
+This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig.~\ref{fig:size-act_low}).
+
+Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.~\ref{fig:feeding}).
+For slow strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
+Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures.
+However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS.
+Production efficiency follows a near opposite trend due to the relatively flat response in the feeding level $f$, but temperature driven increases in maximum consumption.
+
+For fast strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig.~\ref{fig:feeding}).
+Again, production efficiency peaks at relatively low temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
+Given the relatively flat mortality levels, the ratio of $P/M$ largely follows the trend in $P$.
+
+Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig.~\ref{fig:norms}).
+For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig.~\ref{fig:norms_O2}).
+This can be explained by ontogenetic shifts in temperature optima for growth (fig.~\ref{fig:size-rates}): for small individuals, available energy and growth consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals in either trait-scenario grow.
+For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
+
+Resource availability strongly modulates this growth response to temperature: low resource availability leads to strong differences in asymptotic size, whereas high food availability leads to fast growth and larger asymptotic length at high temperatures (figs.~\ref{fig:norms},\ref{fig:infs}).
+In addition, in very resource poor conditions, individuals may not grow to reproductive size in our scenario of a flat MRN.
+Over-all growth responses to temperature are not strongly affected by the assumed slope of the MRN (figs.~\ref{fig:norms_neg},\ref{fig:norms_pos}), although a negatively sloped MRN does ensure maturation in low resource environments.
+
+Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig.~\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\citealt{sainmont_effective_2015}).
+With increasing temperatures, fitness declines at our basic parameter settings, in opposition to growth and aerobic scope.
+At low temperatures, fitness is limited by aerobic scope, with the magnitude determined by the extend of doming in aerobic scope.
+Note that this limitation through the aerobic scope appears at higher temperatures than apparent from fig.~\ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (fig.~\ref{fig:size-rates}).
+Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig.~\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for slow strategy species, and moves the fitness optimum to higher temperatures for fast strategy species.
+Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for fast strategists, and a slower decline of fitness with temperature.
+
+\section*{Discussion}
+
+In this study, we attempt to provide a general mechanistic basis for exploring thermal sensitivities of ectotherm organisms.
+Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\citealt{pauly_sound_2017,lefevre_modelling_2017}).
+We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organism response to temperature.
+The general model and its parameter values are also easily adjusted to reflect particular organisms or theories.
+
+It has been argued that the OCLTT as a concept provides a basis to explain observed responses to climate change on the basis of oxygen limitation via the aerobic scope (\citealt{portner_physiology_2008,portner_oxygen-and_2010}), and simple oxygen budgets have been used to predict metabolic constraints on organismal activity due to warming ocean temperatures (\citealt{deutsch_climate_2015}).
+As a conceptual framework, however, the OCLTT is subject not only to semantic dispute but also criticism of its core concept of oxygen limitation (\citealt{jutfelt_oxygen-and_2018,lefevre_are_2016}).
+
+Our quantitative thermal impact model generalises existing eco-physiological models for particular species and stocks (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}), and allows to develop a more nuanced understanding of interactions between temperature, oxygen limitation and ecology for species with varying traits.
+In line with the conceptual framework of Fry's aerobic scope and the OCLTT, our model suggests that oxygen limitation can be a potentially important ecological driver, especially at extreme temperatures for species with declining MOSs in such temperature regimes.
+At the onset of this limitation, ecological parameters change drastically, and growth, mortality are strongly impacted.
+This limitation closely mimics limitations seen in wild fish (\citealt{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}).
+Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages.
+For instance, oxygen limitation is a more severe constraint for small individuals (fig.~\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
+Furthermore, changes in environmental oxygen supply, if beyond an organisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
+
+Variation in performance metrics away from temperature extremes are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
+Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\citealt{lucas_utilization_1992,priede_metabolic_1985}).
+Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\citealt{priede_natural_1977,priede_metabolic_1985}).
+Furthermore, as a limit for long-term performance, the MOS does not usually impose a limitation on short term energy demands, as fish can incur oxygen debt during swimming bursts during which the MOS is exceeded (\citealt{brett_metabolic_1972,priede_metabolic_1985}).
+A logical conclusion is that the metabolic scope is only limiting to performance at extreme temperatures where MOS is low due to impaired oxygen delivery.
+
+In many species, both the aerobic scope and growth peak at relatively high temperatures within the potential thermal range, yet species are often found at temperatures lower than these optima (\citealt{magnuson_thermal_1997, claireaux_influence_2000}).
+Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\citealt{claireaux_influence_2000, magnuson_thermal_1997}).
+In nearly all our simulation scenarios, fitness is predicted to decline with increasing temperature.
+This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.s
+
+Resource availability imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
+Changes in prey availability thus influence individual temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal activity level.
+In low-food environments, changing energetic demands with temperature are not easily adjusted for, and any adjustment demands higher energetic costs and mortality risk.
+This environment-driven change in costs of temperature adjustments leads to the strong modulation of the growth response, as well as changing gradients in fitness with temperature in these environments.
+In particular, in low-food environments, asymptotic size is strongly reduced at high temperatures, whereas this is not necessarily the case in high-food environments.
+Increased growth and mortality changes in such environments then combine to produce a more strongly domed fitness curve than in environments where food supply is not limiting.
+
+Our model prediction of declining fitness with temperature is
+particularly sensitive to activity costs, with low activity costs
+leading to increased fitness at warmer temperatures. Our
+base-parametrisation is based on the assumption that activity cost $k_a$ reflects the cost of maximal activity (i.e., cost of
+$\tau=1$), and has the same pay-off for all life-histories. This approximation may not
+reflect actual activity cost as swimming at MMR in fast predatory fish
+is far more efficient than swimming of sluggish fish, such as flatfish
+(\citealt{priede_metabolic_1985}).
+Such an efficiency gain may occur as a result of more efficient form or physiology, or simply by reduced drag at large size (e.g., whale-sharks), and may be a key requirement to the viability of active pelagic predatory fish in tropical waters.
+
+That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\citealt{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
+Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\citealt{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (slow strategy) life-history.
+Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
+This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\citealt{priede_metabolic_1985}).
+
+Optimal activity is predicted to increase with temperature in nearly all cases, but it is sensitive to the cost of activity - at higher cost relative to the potential pay-off, activity may even decline at high temeprature.
+Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\citealt{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
+This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses.
+Only large individuals of the simulated fast strategy species will optimally decrease activity as a result of increased temperature.
+In this case, additional activity will lead to comparatively small gains from feeding relative to the cost of activity and SDA, owing to the non-linearity of the functional response.
+
+Taken together, the physiological processes and optimisation described in our model provide a mechanistic underpinning for observations about changes of ecological rates, such as
+increasing or dome-shaped consumption or attack-rates with temperature
+(\citealt{biro_mechanisms_2007,englund_temperature_2011,rall_universal_2012}). Depending on the
+strength of oxygen limitation and the development of the optimal
+activity level over the range of temperatures considered, attack rates
+and feeding rates may appear to be steadily increasing via increased
+optimal activity, or dome-shaped from oxygen limitation or dome-shaped
+optimal activity.
+Thus, rather than assuming \emph{ad hoc} changes in ecological rates in response to temperature that may not be transferable between species and traits, the change in these rates may be mechanistically described in terms of optimal ecological adjustments to physiological constraints.
+
+Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\citealt{atkinson_temperature_1994}), without needing to evoke direct changes in ecological rates with temperature.
+The physiological basis leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (figs \ref{fig:norms}, \ref{fig:norms_O2}).
+Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\citealt{angilletta_temperature_2004}).
+
+In order to provide a general framework, our model setup is deliberatly minimalist, and probably under-parametrised to reflect ecological and life-history aspects of particular species, such as migrations, social behaviour or seasonal energy requirements.
+As such, this framework provides a null model to assess the diversity of possible responses in fish, and other ectotherms, to temperature in a highly simplified system.
+Nevertheless, it provides a starting point from which to explore the importance of costs and benefits of particular life-histories and thermal adaptations.
+For instance, a recent species-specific eco-physiological model for cod (\emph{Gadus morhua}) that includes similar physiological constraints to our model predicted relatively high fitness at high temperatures (\citealt{holt_climate_2014,holt_climate_2015}).
+Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \citet{holt_climate_2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive patterns could offset potential fitness declines with increasing temperatures.
+
+\section*{Conclusions}
+
+The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheung_shrinking_2013, pauly_sound_2017}).
+We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
+In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT.
+Predictions from the OCLTT are both contributing to patterns in fitness and ecological rates shown here, but are also only part of the picture, and we suggest that future improvements of predictive frameworks should center on model critisism and improvements, and leave behind semantic discussions about conceptual constructs that are difficult to explicitly link to data.
+
+% \section*{Acknowledgments}
+% 
+% The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
+PN was supported by a Marsden fast-start grant by the Royal Society Te Apārangi of New Zealand.
+KHA was supported by the Centre for Ocean Life, a VKR Centre of Excellence funded by the Villum Foundation.
+
+\newpage{}
+
+\titleformat{\section}{\normalfont\bfseries\sffamily}{APPENDIX \thesection:}{1em}{}
+
+\section*{Maturation-reaction norm}
+\label{sec:MRN}
+
+A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig.~\ref{fig:MRN}).
+
+To express a MRN that varies as a function of age, we can reparametrise the MRN as:
+\[\phi(z) = 1/(1+\exp(-(c z))) \text{, where }\\
+z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))\]
+rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
+
+\section*{Supplementary figures}
+
+\bibliographystyle{amnatnat}
+\begin{thebibliography}{55}
+\providecommand{\natexlab}[1]{#1}
+
+\bibitem[{Andersen et~al.(2009)Andersen, Farnsworth, Pedersen, Gislason,
+  and Beyer}]{andersen_how_2009}
+Andersen, K.~H., K.~D. Farnsworth, M.~Pedersen, H.~Gislason, and J.~E. Beyer.
+  2009.
+\newblock How community ecology links natural mortality, growth, and production
+  of fish populations.
+\newblock {ICES} Journal of Marine Science: Journal du Conseil 66:1978--1984.
+
+\bibitem[{Angilletta et~al.(2004)Angilletta, Steury, and
+  Sears}]{angilletta_temperature_2004}
+Angilletta, M.~J., T.~D. Steury, and M.~W. Sears. 2004.
+\newblock Temperature, growth rate, and body size in ectotherms: Fitting pieces
+  of a life-history puzzle.
+\newblock Integrative and Comparative Biology 44:498--509.
+
+\bibitem[{Armstrong et~al.(2013)Armstrong, Schindler, Ruff, Brooks, Bentley,
+  and Torgersen}]{armstrong_diel_2013}
+Armstrong, J.~B., D.~E. Schindler, C.~P. Ruff, G.~T. Brooks, K.~E. Bentley, and
+  C.~E. Torgersen. 2013.
+\newblock Diel horizontal migration in streams: juvenile fish exploit spatial
+  heterogeneity in thermal and trophic resources.
+\newblock Ecology 94:2066--2075.
+
+\bibitem[{Atkinson(1994)}]{atkinson_temperature_1994}
+Atkinson, D. 1994.
+\newblock Temperature and organism size: a biological law for ectotherms?
+\newblock Advances in ecological research 25:1--1.
+
+\bibitem[{Biro et~al.(2007)Biro, Post, and Booth}]{biromechanisms2007}
+Biro, P.~A., J.~R. Post, and D.~J. Booth. 2007.
+\newblock Mechanisms for climate-induced mortality of fish populations in
+  whole-lake experiments.
+\newblock Proceedings of the National Academy of Sciences 104:9715--9719.
+
+\bibitem[{Brander et~al.(2013)Brander, Neuheimer, Andersen, and
+  Hartvig}]{brander_overconfidence_2013}
+Brander, K., A.~Neuheimer, K.~H. Andersen, and M.~Hartvig. 2013.
+\newblock Overconfidence in model projections.
+\newblock {ICES} Journal of Marine Science 70:1065--1068.
+
+\bibitem[{Brett(1965)}]{brett_1965_relation}
+Brett, J. 1965.
+\newblock The relation of size to rate of oxygen consumption and sustained
+  swimming speed of sockeye salmon (oncorhynchus nerka).
+\newblock Journal of the Fisheries Board of Canada 22:1491--1501.
+
+\bibitem[{Brett(1972)}]{brettmetabolic1972}
+Brett, J.~R. 1972.
+\newblock The metabolic demand for oxygen in fish, particularly salmonids, and
+  a comparison with other vertebrates.
+\newblock Respiration physiology 14:151--170.
+
+\bibitem[{Brown et~al.(1989)Brown, Pepin, Methven, and
+  Somerton}]{brown_feeding_1989}
+Brown, J.~A., P.~Pepin, D.~A. Methven, and D.~C. Somerton. 1989.
+\newblock The feeding, growth and behaviour of juvenile cod, gadus morhua l.,
+  in cold environments.
+\newblock Journal of Fish Biology 35:373--380.
+
+\bibitem[{Brown et~al.(2004)Brown, Gillooly, Allen, Savage, and
+  West}]{brown_toward_2004}
+Brown, J.~H., J.~F. Gillooly, A.~P. Allen, V.~M. Savage, and G.~B. West. 2004.
+\newblock Toward a metabolic theory of ecology.
+\newblock Ecology 85:1771--1789.
+
+\bibitem[{Charnov et~al.(2013)Charnov, Gislason, and
+  Pope}]{charnov_evolutionary_2013}
+Charnov, E.~L., H.~Gislason, and J.~G. Pope. 2013.
+\newblock Evolutionary assembly rules for fish life histories.
+\newblock Fish and Fisheries 14:213--224.
+
+\bibitem[{Cheung et~al.(2013)Cheung, Sarmiento, Dunne, Frölicher, Lam,
+  Palomares, Watson, and Pauly}]{cheung_shrinking_2013}
+Cheung, W.~W., J.~L. Sarmiento, J.~Dunne, T.~L. Frölicher, V.~W. Lam, M.~D.
+  Palomares, R.~Watson, and D.~Pauly. 2013.
+\newblock Shrinking of fishes exacerbates impacts of global ocean changes on
+  marine ecosystems.
+\newblock Nature Climate Change 3:254--258.
+
+\bibitem[{Claireaux and Lefrançois(2007)}]{claireaux_linking_2007}
+Claireaux, G., and C.~Lefrançois. 2007.
+\newblock Linking environmental variability and fish performance: integration
+  through the concept of scope for activity.
+\newblock Philosophical Transactions of the Royal Society B: Biological
+  Sciences 362:2031--2041.
+
+\bibitem[{Claireaux et~al.(1995)Claireaux, Webber, Kerr, and
+  Boutilier}]{claireaux_physiology_1995}
+Claireaux, G., D.~Webber, S.~Kerr, and R.~Boutilier. 1995.
+\newblock Physiology and behaviour of free-swimming atlantic cod (gadus morhua)
+  facing fluctuating temperature conditions.
+\newblock Journal of Experimental Biology 198:49--60.
+
+\bibitem[{Claireaux et~al.(2016-08-08)Claireaux, Webber, Lagardère, and
+  Kerr}]{claireaux_influence_2000}
+Claireaux, G., D.~M. Webber, J.-P. Lagardère, and S.~R. Kerr. 2016-08-08.
+\newblock Influence of water temperature and oxygenation on the aerobic
+  metabolic scope of atlantic cod (gadus morhua).
+\newblock Journal of Sea Research 44:257--265.
+
+\bibitem[{Deutsch et~al.(2015)Deutsch, Ferrel, Seibel, Pörtner, and
+  Huey}]{deutsch_climate_2015}
+Deutsch, C., A.~Ferrel, B.~Seibel, H.-O. Pörtner, and R.~B. Huey. 2015.
+\newblock Climate change tightens a metabolic constraint on marine habitats.
+\newblock Science 348:1132--1135.
+
+\bibitem[{Dieckmann and Heino(2007)}]{dieckmann_probabilistic_2007}
+Dieckmann, U., and M.~Heino. 2007.
+\newblock Probabilistic maturation reaction norms: their history, strengths,
+  and limitations.
+\newblock Marine Ecology Progress Series 335:253--269.
+
+\bibitem[{Englund et~al.(2011)Englund, Öhlund, Hein, and
+  Diehl}]{englund_temperature_2011}
+Englund, G., G.~Öhlund, C.~L. Hein, and S.~Diehl. 2011.
+\newblock Temperature dependence of the functional response.
+\newblock Ecology Letters 14:914--921.
+
+\bibitem[{Fry(1947)}]{fry_effects_1947}
+Fry. 1947.
+\newblock Effects of the environment on animal activity .
+
+\bibitem[{Gilliam and Fraser(1987)}]{gilliamhabitat1987}
+Gilliam, J.~F., and D.~F. Fraser. 1987.
+\newblock Habitat selection under predation hazard: test of a model with
+  foraging minnows.
+\newblock Ecology 68:1856--1862.
+
+\bibitem[{Glazier(2009)}]{glazier_activity_2009}
+Glazier, D.~S. 2009.
+\newblock Activity affects intraspecific body-size scaling of metabolic rate in
+  ectothermic animals.
+\newblock Journal of Comparative Physiology B 179:821--828.
+
+\bibitem[{Gnauck and Stra{\v{s}}kraba(2013)}]{gnauck_2013_freshwater}
+Gnauck, A., and M.~Stra{\v{s}}kraba. 2013.
+\newblock Freshwater ecosystems: modelling and simulation, vol.~8.
+\newblock Elsevier.
+
+\bibitem[{Guiet et~al.(2016)Guiet, Aumont, Poggiale, and
+  Maury}]{guiet_effects_2016}
+Guiet, J., O.~Aumont, J.-C. Poggiale, and O.~Maury. 2016.
+\newblock Effects of lower trophic level biomass and water temperature on fish
+  communities: A modelling study.
+\newblock Progress in Oceanography 146:22--37.
+
+\bibitem[{Hartvig et~al.(2011)Hartvig, Andersen, and Beyer}]{hartvig_food_2011}
+Hartvig, M., K.~H. Andersen, and J.~E. Beyer. 2011.
+\newblock Food web framework for size-structured populations.
+\newblock Journal of Theoretical Biology 272:113--122.
+
+\bibitem[{Holt and Jorgensen(2014)}]{holt_climate_2014}
+Holt, R.~E., and C.~Jorgensen. 2014.
+\newblock Climate warming causes life-history evolution in a model for atlantic
+  cod (gadus morhua).
+\newblock Conservation Physiology 2.
+
+\bibitem[{Holt and Jorgensen(2015)}]{holt_climate_2015}
+Holt, R.~E., and C.~Jorgensen. 2015.
+\newblock Climate change in fish: effects of respiratory constraints on optimal
+  life history and behaviour.
+\newblock Biology Letters 11:20141032--20141032.
+
+\bibitem[{Hufnagl and Peck(2011)}]{hufnagl_physiological_2011}
+Hufnagl, M., and M.~A. Peck. 2011.
+\newblock Physiological individual-based modelling of larval atlantic herring
+  (clupea harengus) foraging and growth: insights on climate-driven
+  life-history scheduling.
+\newblock {ICES} Journal of Marine Science 68:1170--1188.
+
+\bibitem[{Iftikar and Hickey(2013)}]{iftikar_mitochondria_2013}
+Iftikar, F.~I., and A.~J.~R. Hickey. 2013.
+\newblock Do mitochondria limit hot fish hearts? understanding the role of
+  mitochondrial function with heat stress in notolabrus celidotus.
+\newblock {PLOS} {ONE} 8:e64120.
+
+\bibitem[{Jeschke et~al.(2002)Jeschke, Kopp, and
+  Tollrian}]{jeschke_predator_2002}
+Jeschke, J.~M., M.~Kopp, and R.~Tollrian. 2002.
+\newblock Predator functional responses: discriminating between handling and
+  digesting prey.
+\newblock Ecological Monographs 72:95--112.
+
+\bibitem[{Jutfelt et~al.(2018)Jutfelt, Norin, Ern, Overgaard, Wang, {McKenzie},
+  Lefevre, Nilsson, Metcalfe, and Hickey}]{jutfelt_oxygen-and_2018}
+Jutfelt, F., T.~Norin, R.~Ern, J.~Overgaard, T.~Wang, D.~J. {McKenzie},
+  S.~Lefevre, G.~E. Nilsson, N.~B. Metcalfe, and A.~J. Hickey. 2018.
+\newblock Oxygen-and capacity-limited thermal tolerance: blurring ecology and
+  physiology.
+\newblock Journal of Experimental Biology 221:jeb169615.
+
+\bibitem[{Killen et~al.(2010)Killen, Atkinson, and
+  Glazier}]{killen_intraspecific_2010}
+Killen, S.~S., D.~Atkinson, and D.~S. Glazier. 2010.
+\newblock The intraspecific scaling of metabolic rate with body mass in fishes
+  depends on lifestyle and temperature.
+\newblock Ecology Letters 13:184--193.
+
+\bibitem[{Lefevre(2016)}]{lefevre_are_2016}
+Lefevre, S. 2016.
+\newblock Are global warming and ocean acidification conspiring against marine
+  ectotherms? a meta-analysis of the respiratory effects of elevated
+  temperature, high {CO}2 and their interaction.
+\newblock Conservation Physiology 4.
+
+\bibitem[{Lefevre et~al.(2017)Lefevre, {McKenzie}, and
+  Nilsson}]{lefevre_models_2017}
+Lefevre, S., D.~J. {McKenzie}, and G.~E. Nilsson. 2017.
+\newblock Models projecting the fate of fish populations under climate change
+  need to be based on valid physiological mechanisms.
+\newblock Global Change Biology .
+
+\bibitem[{Lefevre et~al.(2018)Lefevre, McKenzie, and
+  Nilsson}]{lefevre_modelling_2017}
+Lefevre, S., D.~J. McKenzie, and G.~E. Nilsson. 2018.
+\newblock In modelling effects of global warming, invalid assumptions lead to
+  unrealistic projections.
+\newblock Global change biology 24:553--556.
+
+\bibitem[{Lefrancois and Claireaux(2003)}]{lefrancois_influence_2003}
+Lefrancois, C., and G.~Claireaux. 2003.
+\newblock Influence of ambient oxygenation and temperature on metabolic scope
+  and scope for heart rate in the common sole solea solea.
+\newblock Marine Ecology Progress Series 259:273--284.
+
+\bibitem[{Lucas and Priede(1992)}]{lucas_utilization_1992}
+Lucas, M.~C., and I.~G. Priede. 1992.
+\newblock Utilization of metabolic scope in relation to feeding and activity by
+  individual and grouped zebrafish, brachydanio rerio (hamilton-buchanan).
+\newblock Journal of Fish Biology 41:175--190.
+
+\bibitem[{Magnuson and {DeStasio}(1997)}]{magnuson_thermal_1997}
+Magnuson, J.~J., and B.~T. {DeStasio}. 1997.
+\newblock Thermal niche of fishes and global warming.
+\newblock Pages 377--408 \emph{in} C.~Wood and D.~{McDonald}, eds. Global
+  warming: implications for freshwater and marine fish, vol.~61. Cambridge
+  University Press.
+
+\bibitem[{Marty et~al.(2011)Marty, Dieckmann, Rochet, and
+  Ernande}]{marty_impact_2011}
+Marty, L., U.~Dieckmann, M.-J. Rochet, and B.~Ernande. 2011.
+\newblock Impact of environmental covariation in growth and mortality on
+  evolving maturation reaction norms.
+\newblock The American Naturalist 177:E98--E118.
+
+\bibitem[{Myrick and Cech(2000)}]{myrick_temperature_2000}
+Myrick, C.~A., and J.~J. Cech. 2000.
+\newblock Temperature influences on california rainbow trout physiological
+  performance.
+\newblock Fish Physiology and Biochemistry 22:245--254.
+
+\bibitem[{Parmesan and Yohe(2003)}]{parmesan_globally_2003}
+Parmesan, C., and G.~Yohe. 2003.
+\newblock A globally coherent fingerprint of climate change impacts across
+  natural systems.
+\newblock Nature 421:37--42.
+
+\bibitem[{Pauly and Cheung(2017)}]{pauly_sound_2017}
+Pauly, D., and W.~W.~L. Cheung. 2017.
+\newblock Sound physiological knowledge and principles in modeling shrinking of
+  fishes under climate change.
+\newblock Global Change Biology 24:e15--e26.
+
+\bibitem[{Pinsky et~al.(2013)Pinsky, Worm, Fogarty, Sarmiento, and
+  Levin}]{pinsky_marine_2013}
+Pinsky, M.~L., B.~Worm, M.~J. Fogarty, J.~L. Sarmiento, and S.~A. Levin. 2013.
+\newblock Marine taxa track local climate velocities.
+\newblock Science 341:1239--1242.
+
+\bibitem[{Priede(1977)}]{priede_natural_1977}
+Priede, I.~G. 1977.
+\newblock Natural selection for energetic efficiency and the relationship
+  between activity level and mortality.
+\newblock Nature 267:610--611.
+
+\bibitem[{Priede(1985)}]{priede_metabolic_1985}
+---{}---{}---. 1985.
+\newblock Metabolic scope in fishes.
+\newblock Pages 33--64 \emph{in} Fish Energetics. Springer.
+
+\bibitem[{Pörtner(2010)}]{portner_oxygen-and_2010}
+Pörtner, H.-O. 2010.
+\newblock Oxygen-and capacity-limitation of thermal tolerance: a matrix for
+  integrating climate-related stressor effects in marine ecosystems.
+\newblock The Journal of experimental biology 213:881--893.
+
+\bibitem[{Pörtner and Farrell(2008)}]{portnerphysiology2008}
+Pörtner, H.~O., and A.~P. Farrell. 2008.
+\newblock Physiology and climate change.
+\newblock Science 322:690--692.
+
+\bibitem[{Rall et~al.(2012)Rall, Brose, Hartvig, Kalinkat, Schwarzmüller,
+  Vucic-Pestic, and Petchey}]{rall_universal_2012}
+Rall, B.~C., U.~Brose, M.~Hartvig, G.~Kalinkat, F.~Schwarzmüller,
+  O.~Vucic-Pestic, and O.~L. Petchey. 2012.
+\newblock Universal temperature and body-mass scaling of feeding rates.
+\newblock Phil. Trans. R. Soc. B 367:2923--2934.
+
+\bibitem[{Sainmont et~al.(2015-09)Sainmont, Andersen, Thygesen, Fiksen, and
+  Visser}]{sainmont_effective_2015}
+Sainmont, J., K.~H. Andersen, U.~H. Thygesen, ?.~Fiksen, and A.~W. Visser.
+  2015-09.
+\newblock An effective algorithm for approximating adaptive behavior in
+  seasonal environments.
+\newblock Ecological Modelling 311:20--30.
+
+\bibitem[{Salin et~al.(2016)Salin, Auer, Anderson, Selman, and
+  Metcalfe}]{salin_inadequate_2016}
+Salin, K., S.~K. Auer, G.~J. Anderson, C.~Selman, and N.~B. Metcalfe. 2016.
+\newblock Inadequate food intake at high temperatures is related to depressed
+  mitochondrial respiratory capacity.
+\newblock Journal of Experimental Biology 219:1356--1362.
+
+\bibitem[{Sentis et~al.(2013)Sentis, Hemptinne, and
+  Brodeur}]{sentis_parsing_2013}
+Sentis, A., J.-L. Hemptinne, and J.~Brodeur. 2013.
+\newblock Parsing handling time into its components: implications for responses
+  to a temperature gradient.
+\newblock Ecology 94:1675--1680.
+
+\bibitem[{Sswat et~al.(2018)Sswat, Stiasny, Jutfelt, Riebesell, and
+  Clemmesen}]{sswat_growth_2018}
+Sswat, M., M.~H. Stiasny, F.~Jutfelt, U.~Riebesell, and C.~Clemmesen.
+  2018.
+\newblock Growth performance and survival of larval atlantic herring, under the
+  combined effects of elevated temperatures and {CO}2.
+\newblock {PLOS} {ONE} 13:e0191947.
+
+\bibitem[{Stuart-Smith et~al.(2015)Stuart-Smith, Edgar, Barrett, Kininmonth,
+  and Bates}]{stuart-smith_thermal_2015}
+Stuart-Smith, R.~D., G.~J. Edgar, N.~S. Barrett, S.~J. Kininmonth, and A.~E.
+  Bates. 2015.
+\newblock Thermal biases and vulnerability to warming in the world’s marine
+  fauna.
+\newblock Nature 528:88--92.
+
+\bibitem[{Verberk et~al.(2016)Verberk, Overgaard, Ern, Bayley, Wang, Boardman,
+  and Terblanche}]{verberk_does_2016}
+Verberk, W. C. E.~P., J.~Overgaard, R.~Ern, M.~Bayley, T.~Wang, L.~Boardman,
+  and J.~S. Terblanche. 2016.
+\newblock Does oxygen limit thermal tolerance in arthropods? a critical review
+  of current evidence.
+\newblock Comparative Biochemistry and Physiology Part A: Molecular \&
+  Integrative Physiology 192:64--78.
+
+\bibitem[{Vucic-Pestic et~al.(2011-03-01)Vucic-Pestic, Ehnes, Rall, and
+  Brose}]{vucic-pestic_warming_2011}
+Vucic-Pestic, O., R.~B. Ehnes, B.~C. Rall, and U.~Brose. 2011-03-01.
+\newblock Warming up the system: higher predator feeding rates but lower
+  energetic efficiencies.
+\newblock Global Change Biology 17:1301--1310.
+
+\bibitem[{Walther et~al.(2002)Walther, Post, Convey, Menzel, Parmesan, Beebee,
+  Fromentin, Hoegh-Guldberg, and Bairlein}]{walther_ecological_2002}
+Walther, G.-R., E.~Post, P.~Convey, A.~Menzel, C.~Parmesan, T.~J.~C. Beebee,
+  J.-M. Fromentin, O.~Hoegh-Guldberg, and F.~Bairlein. 2002.
+\newblock Ecological responses to recent climate change.
+\newblock Nature 416:389--395.
+
+\end{thebibliography}
+
+\newpage{}
+
+\section*{Tables}
+\renewcommand{\thetable}{\arabic{table}}
+\setcounter{table}{0}
+
+\begin{table}
+{\small
+\caption{Parameters of the constrained activity model for two scenarios: slow strategy and fast strategy species.
+For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
+Values in brackets for $\gamma$ are alternative resource availability scenarios.}
+\label{tab:parameters}
+\begin{tabular}{llcc}
+ \multirow{2}{*}{Description} &  \multirow{2}{*}{Symbol (unit)} & \multicolumn{2}{r}{Value} \\
+ \cmidrule{3-4}
+ & & slow strategy  & fast strategy \\
+
+\hline
+\addlinespace
+\multicolumn{4}{c}{\textbf{Biomass Metabolism}} \\
+Specific dynamic action & $\beta$ & \multicolumn{2}{c}{0.15} \\
+Egestion and excretion & $\phi$ & \multicolumn{2}{c}{0.25}  \\
+Coeff. for std.~metabolism  & $k$ (g$^{1-n}\cdot$y$^{-1}$)  & 1 &  1.5 \\
+Coeff. for act.~metabolism  & $k$ (g$ \cdot$y$^{-1}$)  & 4 &  2 \\
+Exponent for std.~metabolism & $n$ & 0.88 & 0.75  \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Feeding ecology}}\\
+Coeff. for Encountered food & $\gamma\Theta$ (g$^{1-p} \cdot$y$^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
+Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
+Coeff. for Maximum consumption rate & $h$ (g$^{1-q}\cdot$y$^{-1}$) & 30 & 60  \\
+Exponent for max.~consumption $h$ & $q$ & \multicolumn{2}{c}{0.8} \\
+Coeff. for constant mortality & $M$ (g$\cdot$y$^{-1}$) & 0.1  & 1  \\
+Coeff. for activity related mortality & $\rho$(y$^{-1}$) & 6 & 1\\
+Exponent for mortality & $\nu$ & \multicolumn{2}{c}{0.2} \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Temperature}}\\
+Reference temperature  & $T_{\text{ref}}$ (°C)& \multicolumn{2}{c}{15} \\
+Activation energy & $E_a$ & \multicolumn{2}{c}{0.52} \\
+Temperature at maximum MOS & $T_{\text{max}}$ & \multicolumn{2}{c}{20/25}\\
+Temperature range & $T^-_{\text{lethal}}$--$T^+_{\text{lethal}}$ & \multicolumn{2}{c}{5--26} \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Reaction norm}}\\
+
+Slope &  & \multicolumn{2}{c}{0}\\
+Reaction & $c$ & \multicolumn{2}{c}{0.5} \\
+
+\addlinespace
+\multicolumn{4}{c}{\textbf{Oxygen budget}} \\
+Critical $O_2$ & $P_{\text{crit}}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{2}\\
+Dissolved $O_2$ at $0.5\times f_{\text{max}}(O_2)$  & $P_{50}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{4} \\
+Doming for $O_2$ supply & $\eta$ & \multicolumn{2}{c}{3/0.1}\\
+Level of $O_2$ supply  & $\zeta$ (g$\cdot$y$^{-1}$) &  0.5 & 1\\
+
+\hline
+\end{tabular}
+}
+\end{table}
+
+\newpage{}
+
+\section*{Figure legends}
+
+\begin{figure}
+%\includegraphics[width=\linewidth]{images/O2_fig_used-1} 
+\caption[Maximum oxygen supply relative to the maximum supply for species with a dome-shaped MOS (here $\eta$ = 3) and a continually increasing MOS ($\eta$ = 0.1) used in model scenarios discussed below]{Maximum oxygen supply relative to the maximum supply for species with a dome-shaped MOS (here $\eta$ = 3) and a continually increasing MOS ($\eta$ = 0.1) used in model scenarios discussed below.}\label{fig:O2_fig_used}
+\end{figure}
+
 << setup,echo=FALSE,include=F>>=
-knitr::opts_chunk$set(echo = F, message = F,cache=T,autodep = T)
+knitr::opts_chunk$set(echo = F,warning = F, message = F,cache=T,autodep = T)
 
@@
          Fitness = sc(`Available Energy`/M)) %>% 
-  tidyr::gather(Rate,value,Energy,Efficiency,`Relative M`,Fitness) %>%
+  tidyr::gather(Rate,value,Energy,Efficiency,Fitness) %>%
   mutate(Rate = factor(Rate,levels = c('Energy','Efficiency','Fitness')),
@@
         plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
+  scale_linetype_manual('',values=c(1:3))+
+  scale_color_manual('',values = cols)+
    labs(x = expression('Activity ' (tau)),
@@
 
-\subsection*{Trait based scenarios}
-
-To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
-Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the fast strategy, indicated by a subscript $f$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth slow strategy, indicated by a subcript $s$).
-This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
-In other words, this axis contrasts species of similar size (here $L_{\infty}\sim 30$cm or $w_{\infty}\sim 270$g) with defensive/sluggish versus active life-histories.
-
-To implement this axis, we used the result that species with a more
-active, production oriented life-history (e.g., predatory pelagic
-fish) have a higher standard metabolism and lower weight scaling of
-metabolic costs
-(\citealt{priede_metabolic_1985,killen_intraspecific_2010}). We assumed
-that higher standard metabolism is due to increased digestive capacity
-(i.e., is used for gut maintenance), though high muscle mass and a
-larger heart will also contribute to higher standard metabolism in
-active species (\citealt{priede_metabolic_1985}). In practice, we assumed
-that approximately 50\% of the standard metabolic cost is due to gut
-maintenance, such that a doubling of the maximum ingestion leads to a
-50\% increase in standard metabolic cost.
-We further assumed that such active species have a less effective refuge from predators and therefore have a higher constant mortality, but lower mortality related to activity (i.e., $M_{s}(w) = (0.1+6\tau) w^{q-1}$ and $M_{f}(w) = (1+\tau) w^{q-1}$).
-Exact parameter values for these trait scenarios are given in Table \ref{tab:parameters}.
-Together, these assumed trait differences lead to very different ecological and bio-energetic responses of slow- and fast strategists (fig./~\ref{fig:scenarios}), with $\tau_{\text{opt}}$ found at lower activity levels for slow-strategists, as high activity induces exceedingly high mortality and decreasing energy efficiency (i.e., available energy relative to food intake) at high activity levels.
-A slower increase in available energy and M with $\tau$ for fast strategists leads to a higher $\tau_{\text{opt}}$.
-
-We further contrasted species with oxygen limitation at high temperatures (i.e., species with a uni-modal metabolic scope) with species that do not experience oxygen limitation at high temperatures (at least not up to a lethal temperature, where death may be induced by sudden failure to deliver oxygen to vital organs, or failure of bio-chemical pathways at high temperature \citealt{salin_inadequate_2016,iftikar_mitochondria_2013}).
-In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig./~\ref{fig:O2_fig}).
-Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\citealt{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
-However the over-all mechanism would be the same to the one assumed here, with different untis (e.g., ATP instead of $O_2$).
-
-\begin{table}
-\caption{Parameters of the constrained activity model for two scenarios: slow strategy and fast strategy species.
-For parameters with dual values (i.e., x/y), the former reflects species with a domed maximum oxygen supply (MOS) with respect to temperature, whereas the latter corresponds to species with a continuously increasing MOS.
-Values in brackets for $\gamma$ are alternative resource availability scenarios.}
-\label{tab:parameters}
-\begin{tabular}{llcc}
- \multirow{2}{*}{Description} &  \multirow{2}{*}{Symbol (unit)} & \multicolumn{2}{r}{Value} \\
- \cmidrule{3-4}
- & & slow strategy  & fast strategy \\
-
-\hline
-\addlinespace
-\multicolumn{4}{c}{\textbf{Biomass Metabolism}} \\
-Specific dynamic action & $\beta$ & \multicolumn{2}{c}{0.15} \\
-Egestion and excretion & $\phi$ & \multicolumn{2}{c}{0.25}  \\
-Coeff. for std.~metabolism  & $k$ (g$^{1-n}\cdot$y$^{-1}$)  & 1 &  1.5 \\
-Coeff. for act.~metabolism  & $k$ (g$ \cdot$y$^{-1}$)  & 4 &  2 \\
-Exponent for std.~metabolism & $n$ & 0.88 & 0.75  \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Feeding ecology}}\\
-Coeff. for Encountered food & $\gamma\Theta$ (g$^{1-p} \cdot$y$^{-1}$)& \multicolumn{2}{c}{60 (40/80)} \\
-Exponent for clearance rate $\gamma$ & $p$ & \multicolumn{2}{c}{0.8}  \\
-Coeff. for Maximum consumption rate & $h$ (g$^{1-q}\cdot$y$^{-1}$) & 30 & 60  \\
-Exponent for max.~consumption $h$ & $q$ & \multicolumn{2}{c}{0.8} \\
-Coeff. for constant mortality & $M$ (g$\cdot$y$^{-1}$) & 0.1  & 1  \\
-Coeff. for activity related mortality & $\rho$(y$^{-1}$) & 6 & 1\\
-Exponent for mortality & $\nu$ & \multicolumn{2}{c}{0.2} \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Temperature}}\\
-Reference temperature  & $T_{\text{ref}}$ (°C)& \multicolumn{2}{c}{15} \\
-Activation energy & $E_a$ & \multicolumn{2}{c}{0.52} \\
-Temperature at maximum MOS & $T_{\text{max}}$ & \multicolumn{2}{c}{20/25}\\
-Temperature range & $T^-_{\text{lethal}}$--$T^+_{\text{lethal}}$ & \multicolumn{2}{c}{5--26} \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Reaction norm}}\\
-
-Slope &  & \multicolumn{2}{c}{0}\\
-Reaction & $c$ & \multicolumn{2}{c}{0.5} \\
-
-\addlinespace
-\multicolumn{4}{c}{\textbf{Oxygen budget}} \\
-Critical $O_2$ & $P_{\text{crit}}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{2}\\
-Dissolved $O_2$ at $0.5\times f_{\text{max}}(O_2)$  & $P_{50}$ (mg$\cdot$L$^{-1}$) & \multicolumn{2}{c}{4} \\
-Doming for $O_2$ supply & $\eta$ & \multicolumn{2}{c}{3/0.1}\\
-Level of $O_2$ supply  & $\zeta$ (g$\cdot$y$^{-1}$) &  0.5 & 1\\
-
-\hline
-\end{tabular}
-\end{table}
-
-\section*{Results}
-
-Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig./~\ref{fig:activity}).
-This adjustment is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig./~\ref{fig:size-act}).
-A similar increase in activity is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig./~\ref{fig:size-act}).
-For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
-For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig./~\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
-For species with a rising MOS with temperature, oxygen is not limiting (fig./~\ref{fig:activity-rising}).
-However, larger fast strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
-This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig./~\ref{fig:size-act_low}).
-
 \begin{figure}
 \centering
-<<activity, fig.height=4,fig.width=6>>=
+<<activity, fig.height=6,fig.width=7>>=
 
@@
 lab1 <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'c'))
-
-lab2 <- as_labeller(c(`M strategy Domed`  ='b',
+                   `P strategy Domed` = 'b'))
+
+lab2 <- as_labeller(c(`M strategy Domed`  ='c',
                    `P strategy Domed` = 'd'))
@@
   theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
+  scale_color_manual(values = cols)+
+  scale_linetype()+
+  facet_wrap(~Dispatch,ncol = 2,labeller = lab1)+
   theme(strip.text = element_text(hjust = 0),
@@
   theme_cowplot() +
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
+  scale_color_manual(values = cols)+
+  scale_linetype()+
+  facet_wrap(~Dispatch,ncol = 2,labeller = lab2)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-cowplot::plot_grid(ggsc,ggso,ncol=2)
-
-@
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; a \& b) and fast strategy (fast life-history; c \& d).}
+cowplot::plot_grid(ggsc,ggso,ncol=1)
+
+@
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (top row [a,b]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (bottom row [c,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; a \& c) and fast strategy (fast life-history; b \& d).}
 \label{fig:activity}
@@
   theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
+  scale_color_manual(values = cols)+
+  scale_linetype()+
   facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
@@
 
-Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig./~\ref{fig:feeding}).
-For slow strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
-Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures.
-However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS.
-Production efficiency follows a near opposite trend due to the relatively flat response in the feeding level $f$, but temperature driven increases in maximum consumption.
-
-For fast strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig./~\ref{fig:feeding}).
-Again, production efficiency peaks at relatively low temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
-Given the relatively flat mortality levels, the ratio of $P/M$ largely follows the trend in $P$.
-
 <<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
 Responses are shown for slow  and fast strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center',fig.height=5,fig.width=6>>=
+Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center',fig.height=4,fig.width=7>>=
 
@@
   theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=1)+
+  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
   theme(strip.text = element_text(hjust = 0.05),
@@
         plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1))+
-  scale_color_manual(values = cols)+
+  scale_linetype_manual('',values=c(1:4,1))+
+  scale_color_manual('',values = cols)+
   labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
-
-@
-
-Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig./~\ref{fig:norms}).
-For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig./~\ref{fig:norms_O2}).
-This can be explained by ontogenetic shifts in temperature optima for growth (fig./~\ref{fig:size-rates}): for small individuals, available energy and growth consistently peak at high temperatures, but this peak rapidly moves to lower temperatures as individuals in either trait-scenario grow.
-For large individuals, growth is optimised at relatively low temperatures, leading to larger asymptotic size at lower temperatures.
-
-Resource availability strongly modulates this growth response to temperature: low resource availability leads to strong differences in asymptotic size, whereas high food availability leads to fast growth and larger asymptotic length at high temperatures (figs./~\ref{fig:norms},\ref{fig:infs}).
-In addition, in very resource poor conditions, individuals may not grow to reproductive size in our scenario of a flat MRN.
-Over-all growth responses to temperature are not strongly affected by the assumed slope of the MRN (figs.
-\ref{fig:norms_neg},\ref{fig:norms_pos}), although a negatively sloped MRN does ensure maturation in low resource environments.
+       y='Relative rate') + theme(legend.position = "top")
+
+@
 
@@
 
-Over-all fitness consequences mirror trends in the ratio of $P/M$ (fig./~\ref{fig:fit}a), which can be seen as a short sighted approximation to over-all fitness optimisation (\citealt{sainmont_effective_2015}).
-With increasing temperatures, fitness declines at our basic parameter settings, in opposition to growth and aerobic scope.
-At low temperatures, fitness is limited by aerobic scope, with the magnitude determined by the extend of doming in aerobic scope.
-Note that this limitation through the aerobic scope appears at higher temperatures than apparent from fig./~\ref{fig:activity}, reflecting stronger limitation of oxygen on growth during early life (fig./~\ref{fig:size-rates}).
-Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig./~\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for slow strategy species, and moves the fitness optimum to higher temperatures for fast strategy species.
-Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for fast strategists, and a slower decline of fitness with temperature.
-
 <<>>=
@@
   mutate(R0 = R0/max(R0, na.rm=T),
-         Food = factor(Food,levels=c('High','Medium','Low')))
+         Food = factor(Food,levels=c('Low','Medium','High')))
 
 f3.1 <- ggplot(R0sss %>% filter(Scenario=='M strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=Food,size=as.numeric(Food)/3)) +
+  geom_line(aes(x=Temperature, y=log(R0),group=Food,size=as.numeric(Food)/3)) +
   theme_cowplot()+
@@
 @
-
-\section*{Discussion}
-
-In this study, we attempt to provide a general mechanistic basis for exploring thermal sensitivities of ectotherm organisms.
-Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\citealt{pauly_sound_2017,lefevre_modelling_2017}).
-We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organism response to temperature.
-The general model and its parameter values are also easily adjusted to reflect particular organisms or theories.
-
-It has been argued that the OCLTT as a concept provides a basis to explain observed responses to climate change on the basis of oxygen limitation via the aerobic scope (\citealt{portner_physiology_2008,portner_oxygen-and_2010}), and simple oxygen budgets have been used to predict metabolic constraints on organismal activity due to warming ocean temperatures (\citealt{deutsch_climate_2015}).
-As a conceptual framework, however, the OCLTT is subject not only to semantic dispute but also criticism of its core concept of oxygen limitation (\citealt{jutfelt_oxygen-and_2018,lefevre_are_2016}).
-
-Our quantitative thermal impact model generalises existing eco-physiological models for particular species and stocks (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}), and allows to develop a more nuanced understanding of interactions between temperature, oxygen limitation and ecology for species with varying traits.
-In line with the conceptual framework of Fry's aerobic scope and the OCLTT, our model suggests that oxygen limitation can be a potentially important ecological driver, especially at extreme temperatures for species with declining MOSs in such temperature regimes.
-At the onset of this limitation, ecological parameters change drastically, and growth, mortality are strongly impacted.
-This limitation closely mimics limitations seen in wild fish (\citealt{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}).
-Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages.
-For instance, oxygen limitation is a more severe constraint for small individuals (fig./~\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
-Furthermore, changes in environmental oxygen supply, if beyond an organisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
-
-Variation in performance metrics away from temperature extremes are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
-Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\citealt{lucas_utilization_1992,priede_metabolic_1985}).
-Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\citealt{priede_natural_1977,priede_metabolic_1985}).
-Furthermore, as a limit for long-term performance, the MOS does not usually impose a limitation on short term energy demands, as fish can incur oxygen debt during swimming bursts during which the MOS is exceeded (\citealt{brett_metabolic_1972,priede_metabolic_1985}).
-A logical conclusion is that the metabolic scope is only limiting to performance at extreme temperatures where MOS is low due to impaired oxygen delivery.
-
-In many species, both the aerobic scope and growth peak at relatively high temperatures within the potential thermal range, yet species are often found at temperatures lower than these optima (\citealt{magnuson_thermal_1997, claireaux_influence_2000}).
-Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\citealt{claireaux_influence_2000, magnuson_thermal_1997}).
-In nearly all our simulation scenarios, fitness is predicted to decline with increasing temperature.
-This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.s
-
-Resource availability imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
-Changes in prey availability thus influence individual temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal activity level.
-In low-food environments, changing energetic demands with temperature are not easily adjusted for, and any adjustment demands higher energetic costs and mortality risk.
-This environment-driven change in costs of temperature adjustments leads to the strong modulation of the growth response, as well as changing gradients in fitness with temperature in these environments.
-In particular, in low-food environments, asymptotic size is strongly reduced at high temperatures, whereas this is not necessarily the case in high-food environments.
-Increased growth and mortality changes in such environments then combine to produce a more strongly domed fitness curve than in environments where food supply is not limiting.
-
-Our model prediction of declining fitness with temperature is
-particularly sensitive to activity costs, with low activity costs
-leading to increased fitness at warmer temperatures. Our
-base-parametrisation is based on the assumption that activity cost $k_a$ reflects the cost of maximal activity (i.e., cost of
-$\tau=1$), and has the same pay-off for all life-histories. This approximation may not
-reflect actual activity cost as swimming at MMR in fast predatory fish
-is far more efficient than swimming of sluggish fish, such as flatfish
-(\citealt{priede_metabolic_1985}).
-Such an efficiency gain may occur as a result of more efficient form or physiology, or simply by reduced drag at large size (e.g., whale-sharks), and may be a key requirement to the viability of active pelagic predatory fish in tropical waters.
-
-That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\citealt{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
-Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\citealt{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (slow strategy) life-history.
-Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
-This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\citealt{priede_metabolic_1985}).
-
-Optimal activity is predicted to increase with temperature in nearly all cases, but it is sensitive to the cost of activity - at higher cost relative to the potential pay-off, activity may even decline at high temeprature.
-Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\citealt{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
-This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses.
-Only large individuals of the simulated fast strategy species will optimally decrease activity as a result of increased temperature.
-In this case, additional activity will lead to comparatively small gains from feeding relative to the cost of activity and SDA, owing to the non-linearity of the functional response.
-
-Taken together, the physiological processes and optimisation described in our model provide a mechanistic underpinning for observations about changes of ecological rates, such as
-increasing or dome-shaped consumption or attack-rates with temperature
-(\citealt{biro_mechanisms_2007,englund_temperature_2011,rall_universal_2012}). Depending on the
-strength of oxygen limitation and the development of the optimal
-activity level over the range of temperatures considered, attack rates
-and feeding rates may appear to be steadily increasing via increased
-optimal activity, or dome-shaped from oxygen limitation or dome-shaped
-optimal activity.
-Thus, rather than assuming \emph{ad hoc} changes in ecological rates in response to temperature that may not be transferable between species and traits, the change in these rates may be mechanistically described in terms of optimal ecological adjustments to physiological constraints.
-
-Similarly, our model provides a mechanistic basis for the temperature-size rule in ectotherms (\citealt{atkinson_temperature_1994}), without needing to evoke direct changes in ecological rates with temperature.
-The physiological basis leads to heterogeneous predictions about growth trajectories over ranges of temperature, with various degrees of nesting (i.e., non-crossing) and crossing of growth trajectories possible depending on ecological conditions (e.g., food availability) and physiological traits (figs \ref{fig:norms}, \ref{fig:norms_O2}).
-Due to its reliance on physiological traits and their interaction with ecological variables, our model provides a multi-variate framework to predict heterogeneous temperature impacts on size and growth (\citealt{angilletta_temperature_2004}).
-
-In order to provide a general framework, our model setup is deliberatly minimalist, and probably under-parametrised to reflect ecological and life-history aspects of particular species, such as migrations, social behaviour or seasonal energy requirements.
-As such, this framework provides a null model to assess the diversity of possible responses in fish, and other ectotherms, to temperature in a highly simplified system.
-Nevertheless, it provides a starting point from which to explore the importance of costs and benefits of particular life-histories and thermal adaptations.
-For instance, a recent species-specific eco-physiological model for cod (\emph{Gadus morhua}) that includes similar physiological constraints to our model predicted relatively high fitness at high temperatures (\citealt{holt_climate_2014,holt_climate_2015}).
-Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \citet{holt_climate_2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive patterns could offset potential fitness declines with increasing temperatures.
-
-\section*{Conclusions}
-
-The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheung_shrinking_2013, pauly_sound_2017}).
-We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
-In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT.
-Predictions from the OCLTT are both contributing to patterns in fitness and ecological rates shown here, but are also only part of the picture, and we suggest that future improvements of predictive frameworks should center on model critisism and improvements, and leave behind semantic discussions about conceptual constructs that are difficult to explicitly link to data.
-
-% \section*{Acknowledgments}
-% 
-% The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
-PN was supported by a Marsden fast-start grant by the Royal Society Te Apārangi of New Zealand.
-KHA was supported by the Centre for Ocean Life, a VKR Centre of Excellence funded by the Villum Foundation.
-
-\newpage{}
-
-\titleformat{\section}{\normalfont\bfseries\sffamily}{APPENDIX \thesection:}{1em}{}
-\renewcommand{\theequation}{\thesection-\arabic{equation}}
-\renewcommand{\thetable}{\thesection-\arabic{table}}
-\renewcommand{\thefigure}{\thesection-\arabic{figure}}
-\setcounter{figure}{0}  % reset counter 
-\setcounter{table}{0}  % reset counter 
-\setcounter{equation}{0}  % reset counter
-
-\section*{Maturation-reaction norm}
-\label{sec:MRN}
-
-A flat maturation reaction norm (MRN) leads to a logistic allocation to reproduction that is only dependent on size and independent of age (fig./~\ref{fig:MRN}).
-
-To express a MRN that varies as a function of age, we can reparametrise the MRN as:
-\[\phi(z) = 1/(1+\exp(-(c z))) \text{, where }\\
-z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))\]
-rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
-
-\section*{Supplementary figures}
-
-\bibliographystyle{amnatnat}
-\begin{thebibliography}{55}
-\providecommand{\natexlab}[1]{#1}
-
-\bibitem[{Andersen et~al.(2009-10-01)Andersen, Farnsworth, Pedersen, Gislason,
-  and Beyer}]{andersenhow2009}
-Andersen, K.~H., K.~D. Farnsworth, M.~Pedersen, H.~Gislason, and J.~E. Beyer.
-  2009-10-01.
-\newblock How community ecology links natural mortality, growth, and production
-  of fish populations.
-\newblock {ICES} Journal of Marine Science: Journal du Conseil 66:1978--1984.
-
-\bibitem[{Angilletta et~al.(2004)Angilletta, Steury, and
-  Sears}]{angillettatemperature2004}
-Angilletta, M.~J., T.~D. Steury, and M.~W. Sears. 2004.
-\newblock Temperature, growth rate, and body size in ectotherms: Fitting pieces
-  of a life-history puzzle.
-\newblock Integrative and Comparative Biology 44:498--509.
-
-\bibitem[{Armstrong et~al.(2013)Armstrong, Schindler, Ruff, Brooks, Bentley,
-  and Torgersen}]{armstrongdiel2013}
-Armstrong, J.~B., D.~E. Schindler, C.~P. Ruff, G.~T. Brooks, K.~E. Bentley, and
-  C.~E. Torgersen. 2013.
-\newblock Diel horizontal migration in streams: juvenile fish exploit spatial
-  heterogeneity in thermal and trophic resources.
-\newblock Ecology 94:2066--2075.
-
-\bibitem[{Atkinson(1994)}]{atkinsontemperature1994}
-Atkinson, D. 1994.
-\newblock Temperature and organism size: a biological law for ectotherms?
-\newblock Advances in ecological research 25:1--1.
-
-\bibitem[{Biro et~al.(2007)Biro, Post, and Booth}]{biromechanisms2007}
-Biro, P.~A., J.~R. Post, and D.~J. Booth. 2007.
-\newblock Mechanisms for climate-induced mortality of fish populations in
-  whole-lake experiments.
-\newblock Proceedings of the National Academy of Sciences 104:9715--9719.
-
-\bibitem[{Brander et~al.(2013-08-21)Brander, Neuheimer, Andersen, and
-  Hartvig}]{branderoverconfidence2013}
-Brander, K., A.~Neuheimer, K.~H. Andersen, and M.~Hartvig. 2013-08-21.
-\newblock Overconfidence in model projections.
-\newblock {ICES} Journal of Marine Science 70:1065--1068.
-
-\bibitem[{Brett(1965)}]{brett1965relation}
-Brett, J. 1965.
-\newblock The relation of size to rate of oxygen consumption and sustained
-  swimming speed of sockeye salmon (oncorhynchus nerka).
-\newblock Journal of the Fisheries Board of Canada 22:1491--1501.
-
-\bibitem[{Brett(1972)}]{brettmetabolic1972}
-Brett, J.~R. 1972.
-\newblock The metabolic demand for oxygen in fish, particularly salmonids, and
-  a comparison with other vertebrates.
-\newblock Respiration physiology 14:151--170.
-
-\bibitem[{Brown et~al.(1989)Brown, Pepin, Methven, and
-  Somerton}]{brownfeeding1989}
-Brown, J.~A., P.~Pepin, D.~A. Methven, and D.~C. Somerton. 1989.
-\newblock The feeding, growth and behaviour of juvenile cod, gadus morhua l.,
-  in cold environments.
-\newblock Journal of Fish Biology 35:373--380.
-
-\bibitem[{Brown et~al.(2004)Brown, Gillooly, Allen, Savage, and
-  West}]{browntoward2004}
-Brown, J.~H., J.~F. Gillooly, A.~P. Allen, V.~M. Savage, and G.~B. West. 2004.
-\newblock Toward a metabolic theory of ecology.
-\newblock Ecology 85:1771--1789.
-
-\bibitem[{Charnov et~al.(2013)Charnov, Gislason, and
-  Pope}]{charnovevolutionary2013}
-Charnov, E.~L., H.~Gislason, and J.~G. Pope. 2013.
-\newblock Evolutionary assembly rules for fish life histories.
-\newblock Fish and Fisheries 14:213--224.
-
-\bibitem[{Cheung et~al.(2013)Cheung, Sarmiento, Dunne, Frölicher, Lam,
-  Palomares, Watson, and Pauly}]{cheungshrinking2013}
-Cheung, W.~W., J.~L. Sarmiento, J.~Dunne, T.~L. Frölicher, V.~W. Lam, M.~D.
-  Palomares, R.~Watson, and D.~Pauly. 2013.
-\newblock Shrinking of fishes exacerbates impacts of global ocean changes on
-  marine ecosystems.
-\newblock Nature Climate Change 3:254--258.
-
-\bibitem[{Claireaux and Lefrançois(2007)}]{claireauxlinking2007}
-Claireaux, G., and C.~Lefrançois. 2007.
-\newblock Linking environmental variability and fish performance: integration
-  through the concept of scope for activity.
-\newblock Philosophical Transactions of the Royal Society B: Biological
-  Sciences 362:2031--2041.
-
-\bibitem[{Claireaux et~al.(1995)Claireaux, Webber, Kerr, and
-  Boutilier}]{claireauxphysiology1995}
-Claireaux, G., D.~Webber, S.~Kerr, and R.~Boutilier. 1995.
-\newblock Physiology and behaviour of free-swimming atlantic cod (gadus morhua)
-  facing fluctuating temperature conditions.
-\newblock Journal of Experimental Biology 198:49--60.
-
-\bibitem[{Claireaux et~al.(2016-08-08)Claireaux, Webber, Lagardère, and
-  Kerr}]{claireauxinfluence2000}
-Claireaux, G., D.~M. Webber, J.-P. Lagardère, and S.~R. Kerr. 2016-08-08.
-\newblock Influence of water temperature and oxygenation on the aerobic
-  metabolic scope of atlantic cod (gadus morhua).
-\newblock Journal of Sea Research 44:257--265.
-
-\bibitem[{Deutsch et~al.(2015)Deutsch, Ferrel, Seibel, Pörtner, and
-  Huey}]{deutschclimate2015}
-Deutsch, C., A.~Ferrel, B.~Seibel, H.-O. Pörtner, and R.~B. Huey. 2015.
-\newblock Climate change tightens a metabolic constraint on marine habitats.
-\newblock Science 348:1132--1135.
-
-\bibitem[{Dieckmann and Heino(2007)}]{dieckmannprobabilistic2007}
-Dieckmann, U., and M.~Heino. 2007.
-\newblock Probabilistic maturation reaction norms: their history, strengths,
-  and limitations.
-\newblock Marine Ecology Progress Series 335:253--269.
-
-\bibitem[{Englund et~al.(2011)Englund, Öhlund, Hein, and
-  Diehl}]{englundtemperature2011}
-Englund, G., G.~Öhlund, C.~L. Hein, and S.~Diehl. 2011.
-\newblock Temperature dependence of the functional response.
-\newblock Ecology Letters 14:914--921.
-
-\bibitem[{Fry(1947)}]{fryeffects1947}
-Fry. 1947.
-\newblock Effects of the environment on animal activity .
-
-\bibitem[{Gilliam and Fraser(1987)}]{gilliamhabitat1987}
-Gilliam, J.~F., and D.~F. Fraser. 1987.
-\newblock Habitat selection under predation hazard: test of a model with
-  foraging minnows.
-\newblock Ecology 68:1856--1862.
-
-\bibitem[{Glazier(2009)}]{glazieractivity2009}
-Glazier, D.~S. 2009.
-\newblock Activity affects intraspecific body-size scaling of metabolic rate in
-  ectothermic animals.
-\newblock Journal of Comparative Physiology B 179:821--828.
-
-\bibitem[{Gnauck and Stra{\v{s}}kraba(2013)}]{gnauck2013freshwater}
-Gnauck, A., and M.~Stra{\v{s}}kraba. 2013.
-\newblock Freshwater ecosystems: modelling and simulation, vol.~8.
-\newblock Elsevier.
-
-\bibitem[{Guiet et~al.(2016)Guiet, Aumont, Poggiale, and
-  Maury}]{guieteffects2016}
-Guiet, J., O.~Aumont, J.-C. Poggiale, and O.~Maury. 2016.
-\newblock Effects of lower trophic level biomass and water temperature on fish
-  communities: A modelling study.
-\newblock Progress in Oceanography 146:22--37.
-
-\bibitem[{Hartvig et~al.(2011)Hartvig, Andersen, and Beyer}]{hartvigfood2011}
-Hartvig, M., K.~H. Andersen, and J.~E. Beyer. 2011.
-\newblock Food web framework for size-structured populations.
-\newblock Journal of Theoretical Biology 272:113--122.
-
-\bibitem[{Holt and Jorgensen(2014-11-04)}]{holtclimate2014}
-Holt, R.~E., and C.~Jorgensen. 2014-11-04.
-\newblock Climate warming causes life-history evolution in a model for atlantic
-  cod (gadus morhua).
-\newblock Conservation Physiology 2.
-
-\bibitem[{Holt and Jorgensen(2015)}]{holtclimate2015}
----{}---{}---. 2015.
-\newblock Climate change in fish: effects of respiratory constraints on optimal
-  life history and behaviour.
-\newblock Biology Letters 11:20141032--20141032.
-
-\bibitem[{Hufnagl and Peck(2011)}]{hufnaglphysiological2011}
-Hufnagl, M., and M.~A. Peck. 2011.
-\newblock Physiological individual-based modelling of larval atlantic herring
-  (clupea harengus) foraging and growth: insights on climate-driven
-  life-history scheduling.
-\newblock {ICES} Journal of Marine Science 68:1170--1188.
-
-\bibitem[{Iftikar and Hickey(2013)}]{iftikarmitochondria2013}
-Iftikar, F.~I., and A.~J.~R. Hickey. 2013.
-\newblock Do mitochondria limit hot fish hearts? understanding the role of
-  mitochondrial function with heat stress in notolabrus celidotus.
-\newblock {PLOS} {ONE} 8:e64120.
-
-\bibitem[{Jeschke et~al.(2002)Jeschke, Kopp, and
-  Tollrian}]{jeschkepredator2002}
-Jeschke, J.~M., M.~Kopp, and R.~Tollrian. 2002.
-\newblock Predator functional responses: discriminating between handling and
-  digesting prey.
-\newblock Ecological Monographs 72:95--112.
-
-\bibitem[{Jutfelt et~al.(2018)Jutfelt, Norin, Ern, Overgaard, Wang, {McKenzie},
-  Lefevre, Nilsson, Metcalfe, and Hickey}]{jutfeltoxygen-and2018}
-Jutfelt, F., T.~Norin, R.~Ern, J.~Overgaard, T.~Wang, D.~J. {McKenzie},
-  S.~Lefevre, G.~E. Nilsson, N.~B. Metcalfe, and A.~J. Hickey. 2018.
-\newblock Oxygen-and capacity-limited thermal tolerance: blurring ecology and
-  physiology.
-\newblock Journal of Experimental Biology 221:jeb169615.
-
-\bibitem[{Killen et~al.(2010)Killen, Atkinson, and
-  Glazier}]{killenintraspecific2010}
-Killen, S.~S., D.~Atkinson, and D.~S. Glazier. 2010.
-\newblock The intraspecific scaling of metabolic rate with body mass in fishes
-  depends on lifestyle and temperature.
-\newblock Ecology Letters 13:184--193.
-
-\bibitem[{Lefevre(2016)}]{lefevreare2016}
-Lefevre, S. 2016.
-\newblock Are global warming and ocean acidification conspiring against marine
-  ectotherms? a meta-analysis of the respiratory effects of elevated
-  temperature, high {CO}2 and their interaction.
-\newblock Conservation Physiology 4.
-
-\bibitem[{Lefevre et~al.(2017)Lefevre, {McKenzie}, and
-  Nilsson}]{lefevremodels2017}
-Lefevre, S., D.~J. {McKenzie}, and G.~E. Nilsson. 2017.
-\newblock Models projecting the fate of fish populations under climate change
-  need to be based on valid physiological mechanisms.
-\newblock Global Change Biology .
-
-\bibitem[{Lefevre et~al.(2018)Lefevre, McKenzie, and
-  Nilsson}]{lefevremodelling2017}
-Lefevre, S., D.~J. McKenzie, and G.~E. Nilsson. 2018.
-\newblock In modelling effects of global warming, invalid assumptions lead to
-  unrealistic projections.
-\newblock Global change biology 24:553--556.
-
-\bibitem[{Lefrancois and Claireaux(2003)}]{lefrancoisinfluence2003}
-Lefrancois, C., and G.~Claireaux. 2003.
-\newblock Influence of ambient oxygenation and temperature on metabolic scope
-  and scope for heart rate in the common sole solea solea.
-\newblock Marine Ecology Progress Series 259:273--284.
-
-\bibitem[{Lucas and Priede(1992)}]{lucasutilization1992}
-Lucas, M.~C., and I.~G. Priede. 1992.
-\newblock Utilization of metabolic scope in relation to feeding and activity by
-  individual and grouped zebrafish, brachydanio rerio (hamilton-buchanan).
-\newblock Journal of Fish Biology 41:175--190.
-
-\bibitem[{Magnuson and {DeStasio}(1997)}]{magnusonthermal1997}
-Magnuson, J.~J., and B.~T. {DeStasio}. 1997.
-\newblock Thermal niche of fishes and global warming.
-\newblock Pages 377--408 \emph{in} C.~Wood and D.~{McDonald}, eds. Global
-  warming: implications for freshwater and marine fish, vol.~61. Cambridge
-  University Press.
-
-\bibitem[{Marty et~al.(2011)Marty, Dieckmann, Rochet, and
-  Ernande}]{martyimpact2011}
-Marty, L., U.~Dieckmann, M.-J. Rochet, and B.~Ernande. 2011.
-\newblock Impact of environmental covariation in growth and mortality on
-  evolving maturation reaction norms.
-\newblock The American Naturalist 177:E98--E118.
-
-\bibitem[{Myrick and Cech(2000)}]{myricktemperature2000}
-Myrick, C.~A., and J.~J. Cech. 2000.
-\newblock Temperature influences on california rainbow trout physiological
-  performance.
-\newblock Fish Physiology and Biochemistry 22:245--254.
-
-\bibitem[{Parmesan and Yohe(2003)}]{parmesanglobally2003}
-Parmesan, C., and G.~Yohe. 2003.
-\newblock A globally coherent fingerprint of climate change impacts across
-  natural systems.
-\newblock Nature 421:37--42.
-
-\bibitem[{Pauly and Cheung(2017)}]{paulysound2017}
-Pauly, D., and W.~W.~L. Cheung. 2017.
-\newblock Sound physiological knowledge and principles in modeling shrinking of
-  fishes under climate change.
-\newblock Global Change Biology 24:e15--e26.
-
-\bibitem[{Pinsky et~al.(2013)Pinsky, Worm, Fogarty, Sarmiento, and
-  Levin}]{pinskymarine2013}
-Pinsky, M.~L., B.~Worm, M.~J. Fogarty, J.~L. Sarmiento, and S.~A. Levin. 2013.
-\newblock Marine taxa track local climate velocities.
-\newblock Science 341:1239--1242.
-
-\bibitem[{Priede(1977)}]{priedenatural1977}
-Priede, I.~G. 1977.
-\newblock Natural selection for energetic efficiency and the relationship
-  between activity level and mortality.
-\newblock Nature 267:610--611.
-
-\bibitem[{Priede(1985)}]{priedemetabolic1985}
----{}---{}---. 1985.
-\newblock Metabolic scope in fishes.
-\newblock Pages 33--64 \emph{in} Fish Energetics. Springer.
-
-\bibitem[{Pörtner(2010)}]{portneroxygen-and2010}
-Pörtner, H.-O. 2010.
-\newblock Oxygen-and capacity-limitation of thermal tolerance: a matrix for
-  integrating climate-related stressor effects in marine ecosystems.
-\newblock The Journal of experimental biology 213:881--893.
-
-\bibitem[{Pörtner and Farrell(2008)}]{portnerphysiology2008}
-Pörtner, H.~O., and A.~P. Farrell. 2008.
-\newblock Physiology and climate change.
-\newblock Science 322:690--692.
-
-\bibitem[{Rall et~al.(2012)Rall, Brose, Hartvig, Kalinkat, Schwarzmüller,
-  Vucic-Pestic, and Petchey}]{ralluniversal2012}
-Rall, B.~C., U.~Brose, M.~Hartvig, G.~Kalinkat, F.~Schwarzmüller,
-  O.~Vucic-Pestic, and O.~L. Petchey. 2012.
-\newblock Universal temperature and body-mass scaling of feeding rates.
-\newblock Phil. Trans. R. Soc. B 367:2923--2934.
-
-\bibitem[{Sainmont et~al.(2015-09)Sainmont, Andersen, Thygesen, Fiksen, and
-  Visser}]{sainmonteffective2015}
-Sainmont, J., K.~H. Andersen, U.~H. Thygesen, ?.~Fiksen, and A.~W. Visser.
-  2015-09.
-\newblock An effective algorithm for approximating adaptive behavior in
-  seasonal environments.
-\newblock Ecological Modelling 311:20--30.
-
-\bibitem[{Salin et~al.(2016)Salin, Auer, Anderson, Selman, and
-  Metcalfe}]{salininadequate2016}
-Salin, K., S.~K. Auer, G.~J. Anderson, C.~Selman, and N.~B. Metcalfe. 2016.
-\newblock Inadequate food intake at high temperatures is related to depressed
-  mitochondrial respiratory capacity.
-\newblock Journal of Experimental Biology 219:1356--1362.
-
-\bibitem[{Sentis et~al.(2013)Sentis, Hemptinne, and
-  Brodeur}]{sentisparsing2013}
-Sentis, A., J.-L. Hemptinne, and J.~Brodeur. 2013.
-\newblock Parsing handling time into its components: implications for responses
-  to a temperature gradient.
-\newblock Ecology 94:1675--1680.
-
-\bibitem[{Sswat et~al.(2018-01-25)Sswat, Stiasny, Jutfelt, Riebesell, and
-  Clemmesen}]{sswatgrowth2018}
-Sswat, M., M.~H. Stiasny, F.~Jutfelt, U.~Riebesell, and C.~Clemmesen.
-  2018-01-25.
-\newblock Growth performance and survival of larval atlantic herring, under the
-  combined effects of elevated temperatures and {CO}2.
-\newblock {PLOS} {ONE} 13:e0191947.
-
-\bibitem[{Stuart-Smith et~al.(2015)Stuart-Smith, Edgar, Barrett, Kininmonth,
-  and Bates}]{stuart-smiththermal2015}
-Stuart-Smith, R.~D., G.~J. Edgar, N.~S. Barrett, S.~J. Kininmonth, and A.~E.
-  Bates. 2015.
-\newblock Thermal biases and vulnerability to warming in the world’s marine
-  fauna.
-\newblock Nature 528:88--92.
-
-\bibitem[{Verberk et~al.(2016)Verberk, Overgaard, Ern, Bayley, Wang, Boardman,
-  and Terblanche}]{verberkdoes2016}
-Verberk, W. C. E.~P., J.~Overgaard, R.~Ern, M.~Bayley, T.~Wang, L.~Boardman,
-  and J.~S. Terblanche. 2016.
-\newblock Does oxygen limit thermal tolerance in arthropods? a critical review
-  of current evidence.
-\newblock Comparative Biochemistry and Physiology Part A: Molecular \&
-  Integrative Physiology 192:64--78.
-
-\bibitem[{Vucic-Pestic et~al.(2011-03-01)Vucic-Pestic, Ehnes, Rall, and
-  Brose}]{vucic-pesticwarming2011}
-Vucic-Pestic, O., R.~B. Ehnes, B.~C. Rall, and U.~Brose. 2011-03-01.
-\newblock Warming up the system: higher predator feeding rates but lower
-  energetic efficiencies.
-\newblock Global Change Biology 17:1301--1310.
-
-\bibitem[{Walther et~al.(2002)Walther, Post, Convey, Menzel, Parmesan, Beebee,
-  Fromentin, Hoegh-Guldberg, and Bairlein}]{waltherecological2002}
-Walther, G.-R., E.~Post, P.~Convey, A.~Menzel, C.~Parmesan, T.~J.~C. Beebee,
-  J.-M. Fromentin, O.~Hoegh-Guldberg, and F.~Bairlein. 2002.
-\newblock Ecological responses to recent climate change.
-\newblock Nature 416:389--395.
-
-\end{thebibliography}
 
@@
 \centering
-<<activitys, fig.height=4,fig.width=6>>=
+<<activitys, fig.height=6,fig.width=7>>=
 
@@
 lab1 <- as_labeller(c(`M strategy Rising`  ='a',
-                   `P strategy Rising` = 'c'))
-
-lab2 <- as_labeller(c(`M strategy Rising`  ='b',
+                   `P strategy Rising` = 'b'))
+
+lab2 <- as_labeller(c(`M strategy Rising`  ='c',
                    `P strategy Rising` = 'd'))
@@
   scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
+  facet_wrap(~Dispatch,ncol = 2,labeller = lab1)+
   theme(strip.text = element_text(hjust = 0),
@@
   scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
+  facet_wrap(~Dispatch,ncol = 2,labeller = lab2)+
   theme(strip.text = element_text(hjust = 0),
@@
 
-cowplot::plot_grid(ggsc,ggso,ncol=2)
+cowplot::plot_grid(ggsc,ggso,ncol=1)
 

### 2019-01-16 Cons_physio_revision.tex
revisions pt2

--- 2019-01-16 MS_AMNat.Rnw
@@
-\documentclass[11pt]{article}
+\documentclass[11pt]{article}\usepackage[]{graphicx}\usepackage[]{color,soul}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+\usepackage{placeins}
+\usepackage{alltt}
 \usepackage[sc]{mathpazo} %Like Palatino with extensive math support
@@
 \usepackage[authoryear,sectionbib,sort]{natbib}
-\linespread{1.7}
+\linespread{2}
 \usepackage[utf8]{inputenc}
@@
 \titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
-\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}
+\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{References}
 
@@
 
-% \author{Philipp Neubauer^{1,\ast}$ \\ 
-%         Ken H. Andersen$^{2,\dag}$}
+ \author{Philipp Neubauer^{1,\ast}$ \\ 
+         Ken H. Andersen$^{2}$}
 
 \date{}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-% \noindent{} 1. Dragonfly Data Science, PO Box 27535, Wellington 6141, New Zealand;
+\noindent{} 1. Dragonfly Data Science, PO Box 27535, Wellington 6141, New Zealand;\\
 % 
-% \noindent{} 2. Centre for Ocean Life, National Institute of Aquatic Resources, Technical University of Denmark, 7 Kemitorvet B-202, 2800 Kongens Lyngby, Denmark;
+\noindent{} 2. Centre for Ocean Life, National Institute of Aquatic Resources, Technical University of Denmark, 7 Kemitorvet B 202, 2800 Kongens Lyngby, Denmark;\\
 
@@
 
-\textit{Manuscript elements}: Figure~1, figure~2, table~1, online appendices~A and B (including figure~A1 and figure~A2). Figure~2 is to print in color.
+\noindent{} * Corresponding author's contact: \\
+email: neubauer.phil@gmail.com 
+Tel: +64 4 385 9285\\
 
@@
 
-\textit{Keywords}: thermal performance, OCLTT, metabolic rate, climate change
-
-\bigskip
-
-\textit{Manuscript type}: Article.
-
-\bigskip
-
-\noindent{\footnotesize Prepared using the suggested \LaTeX{} template for \textit{Am.\ Nat.}}
+Summary: Although a number of theories exist, there is currently little consensus on drivers of thermal performance in ectotherms, and fish in particular.
+We present a general size and trait based model that shows that thermal performance can be explained by an interplay of physiological, ecological, and behavioural constraints.
 
@@
 Whether or not oxygen limitations via the metabolic scope, or a lack thereof, have major ecological consequences remains a highly contested question.
-Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of metabolic rates, oxygen limitation, and environmental conditions on ecotherm performance.
+Here, we propose a general size and trait-based model of energy and oxygen budgets to determine the relative influence of metabolic rates, oxygen limitation, and environmental conditions on ectotherm performance.
 We show that oxygen limitation is not necessary to explain performance variation with temperature.
@@
 Furthermore, our model reveals that fitness trends with temperature can oppose trends in growth, suggesting a potential explanation for the paradox that species often occur at lower temperatures than their growth-optimum.
-Our model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on the performance of fish and other ectotherms, and act as a null model for contrasting temperature impacts on species with different metabolic and ecological traits.
+Our model provides a mechanistic underpinning that can provide general and realistic predictions about temperature impacts on the performance of fish and other ectotherms, and function as a null model for contrasting temperature impacts on species with different metabolic and ecological traits.
+
+\textit{Keywords}: thermal performance, OCLTT, metabolic rate, climate change
 
@@
 As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\citealt{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).
+\hl{Such predictions of changes in species ecology based on physiological function are important to ensure appropriate policy and management response to changing environments and expected effects on organisms}\cite{mckenzieconservation2016, pattersonperspective2016}.
 However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems.
 Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\citealt{brander_overconfidence_2013, lefevre_models_2017}).
-In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\citealt{cheung_shrinking_2013}), have been criticized as overly simplistic and not in line with physiological constraints (\citealt{brander_overconfidence_2013, lefevre_models_2017,jutfelt_oxygen-and_2018}).
+In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\citealt{cheung_shrinking_2013}).
+\hl{Such changes in fish growth and size would have downstream implications for fisheries stock assessment (e.g., by changing population productivity) and management tools such as size limits}.
+However, these predictions have been criticized as overly simplistic and not in line with physiological constraints (\citealt{brander_overconfidence_2013, lefevre_models_2017}).
 
@@
 To our knowledge, no general theoretical framework exists to quantitatively explain and predict changes in  ecological rates, such as observed change in growth and asymptotic size \cite[e.g., the temerature-size rule in ectotherms;][]{angilletta_temperature_2004,atkinson_temperature_1994}), or attack rates (\citealt{englund_temperature_2011,rall_universal_2012}) with temperature, from fundamental physiological processes.
-Instead, and as advocated by the metabolic theory of ecology (\citealt{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers (\cite[e.g., ][]{angilletta_temperature_2004,vucic-pestic_warming_2011, guiet_effects_2016}).
+Instead, and as advocated by the metabolic theory of ecology (\citealt{brown_toward_2004}), ecological theory often treats ecological rates as being directly temperature dependent, without a direct link to the underlying physiological drivers \cite[e.g., ][]{angilletta_temperature_2004,vucic-pestic_warming_2011, guiet_effects_2016}.
 
 A phenomenological description that assumes a general ecological temperature response often fails to explain heterogeneity in ecological responses (\citealt{angilletta_temperature_2004,rall_universal_2012}).
-Although ecological rates seem to follow some general patterns in the response to temperature, there is also significant heterogeneity between species and trait groups (\cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}).
-This leads to difficulties with extrapolation across species or other model components (\cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}).
-In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures (\cite[e.g., ][]{vucic-pestic_warming_2011,lefevre_models_2017}).
-Since the primary effect of temperature of organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.
+Although ecological rates seem to follow some general patterns in the response to temperature, there is also significant heterogeneity between species and trait groups \cite[e.g., ][]{angilletta_temperature_2004,englund_temperature_2011,rall_universal_2012}.
+This leads to difficulties with extrapolation across species or other model components \cite[e.g., fish in marine ecosystem models; ][]{guiet_effects_2016}.
+In this case, a deeper understanding of the underlying drivers of thermal responses may be necessary in order to derive general predictions about ecological responses to changing temperatures \cite[e.g., ][]{vucic-pestic_warming_2011,lefevre_models_2017}.
+Since the primary effect of temperature on organisms is on individual physiology, a general model to explain ecological response should be grounded in physiology.
 
@@
 \end{align}
-where the feeding level $[0:1]$ is given by a Holling type II function response:
+
+\hl{ For supply, $h c(T) w^q$ is the maximum consumption rate, and $f(w,T)$ is the feeding level as a fraction between 0 and 1.
+The supply is discounted by the loss due to specific dynamic action  $\beta$ (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.}
+
+The feeding level is given by a Holling type II functional response:
 \begin{align}
@@
 \end{align}
-where $h c(T) w^q$ is the maximum consumption rate.
-The feeding level is determined by the fraction of time spent foraging $\tau$ (henceforth the activity fraction), foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times prey availability $\Theta$) and maximum consumption $h c(T) w^q$.
-The supply is discounted by the loss due to specific dynamic action  $\beta$ (SDA, or heat increment; the energy spent absorbing food), and $\phi$ is the fraction of food excreted and egested.
-
-Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazier_activity_2009,brett1965relation}, and the activity fraction.
-Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approimated by an Arrhenious scaling $c(T) = e^{E_a(T-T_0)/(bTT_0)}$, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (here 15 degrees Celsius), and $b$ is the Bolzman constant.
-Note that we only scale rates related to enzymatic activity with temperature, we do assume that ecological rates such as foraging rates or activity are a direct function of temperature.
+
+The feeding level is therefore determined by the fraction of time spent foraging $\tau$ (henceforth the activity fraction), foraging rate $\gamma w^p \Theta$ (search rate $\gamma w^p$ times food resource availability $\Theta$) and maximum consumption $h c(T) w^q$.
+
+Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazier_activity_2009,brett_1965_relation}, and the activity fraction.
+Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approximated by an Arrhenius scaling $c(T) = e^{E_a(T-T_0)/(b\cdot T\cdot T_0)}$ \cite{gilloolyeffects2001}, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (such that c(T)=1 at 15\degree C), and $b$ is the Boltzmann constant.
+Note that we only scale rates related to enzymatic activity with temperature, we do not assume that ecological rates such as foraging rates or activity are a direct function of temperature.
 Rather, they are modulated by an individual's behavioural response to temperature driven physiological changes.
@@
   P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
-        &= S_{O_2}c_{O_2}(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
+        &= S_{O_2}(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
 \end{align}
 Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.
-The oxygen supply ($S_{O_2}c_{O_2}(T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig.~\ref{fig:O2_fig_used}).
-The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and is usually termed the maximum metabolic rate (MMR).
+The oxygen supply ($S_{O_2}(w,T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig.~\ref{fig:O2_fig_used}).
+The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and corresponds to the maximum metabolic rate (MMR) in our model.
 Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\citealt{priede_metabolic_1985}).
-We use MMR and oxygen supply interchangeably, although maximum oxygen demand (i.e., at full activity) may be lower than the MMR.
-We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck2013freshwater, lefrancois_influence_2003}):
+\hl{ In our model, MMR and maximum oxygen supply are equivalent as we do not explicitly model contributions from anaerobic metabolism, such as during burst swimming or hypoxia.
+During such events, the actual metabolic rate may be higher than oxygen consumption alone would suggest, however such states cannot usually be sustained (and therefore fall outside of the sustained MMR defined here).} We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck_2013_freshwater, lefrancois_influence_2003}):
 
 \begin{align}
-s_{O_2}(T)&=\lambda(T)\left(1-e^{(O_2(T)-P_{\text{crit}})\log(0.5)/(P\text{50}-P_{\text{crit}})}\right),\\
+S_{O_2}(T)&=\lambda(T)\left(1-e^{(C_{O_2}(T)-C_{O_2}^{\text{crit}})\log(0.5)/(C_{O_2}^\text{50}-C_{O_2}^{\text{crit}})}\right),\\
 \lambda(T)&=\zeta\left(\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right)^\eta \times \exp\left(-\eta\frac{T_{\text{max}}-T}{T_{\text{max}}-T_{\text{opt}}}\right),
@@
 
-Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the $s_{O_2}(T)$ term describes the saturation dependence on ambient $O_2$ at temperature $T$ ($O_2(T)$).
-At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function (\cite[e.g.,][]{lefrancois_influence_2003}).
-We specify $P_{50}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $P_{\text{crit}}$ is the ambient concentration at which oxygen supply ceases.
-Ambient oxygen levels are assumed to decline with temperature as $l*\exp(-0.01851*(T-5)$, with $l$ the ambient oxygen concentration at 5\degree C.
-To specify $\lambda(T)$, we use $T_{\text{max}}$ the lethal temperature for the species, $T_{\text{opt}}$ the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height.
+\hl{ Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term in $S_{O_2}(T)$ term describes the dependence on ambient $O_2$ concentrations at temperature $T$ ($O_2(T)$).} At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function \cite[e.g.,][]{lefrancois_influence_2003}.
+\hl{We specify $C_{O_2}^{\text{50}}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $C_{O_2}^{\text{crit}}$ is the ambient concentration at which oxygen supply ceases.
+Ambient oxygen concentration levels are assumed to decline with temperature according to a curve that approximates declines of dissolved oxygen in saltwater at 35 PSU as $l\cdot e^{-0.01851*(T-5)}$, with $l$ the oxygen concentration at 5\degree C.} To specify $\lambda(T)$, we define $T_{\text{max}}$ as the lethal temperature for the species, and $T_{\text{opt}}$ as the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height.
 Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).
 
-In pour model, fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \citealt{gilliam_habitat_1987}:
+In our model, fish will adjust their activity fraction $\tau$ to maximise fitness. We use Gilliam's rule as a fitness proxy \citealt{gilliam_habitat_1987}:
 \begin{equation}
@@
   \label{eq:M}
-  M(w) = (\rho+\eta\tau) w^{q-1},
+  M(w) = (\rho+\mu\tau) w^{q-1},
 \end{equation}
-$\rho$ is mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism.
+$\rho$ is the base mortality at mass $w=1$ and $\tau=0$, that is, with no activity beyond that covered by standard metabolism, and $\mu$ is the coefficient for activity related mortality.
 Activity is limited by available oxygen, such that the aerobic scope $P_{O_2}$ is not allowed to be negative over the time scales considered.
@@
 
+That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\citealt{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
+Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\citealt{priede_natural_1977}).
+
 \subsection*{Defining performance metrics}
@@
 Temperature affects growth via its effects on the energy budget and the investment of available (surplus) energy into reproduction and growth.
-The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions (\cite[e.g., ][]{dieckmann_probabilistic_2007}).
+The change in allocation to reproduction with size and age in variable environmental conditions is described by the maturation reaction norm, which is generally defined as the probability of maturing at a certain age under different growth conditions \cite[e.g., ][]{dieckmann_probabilistic_2007}.
 We defined the reaction norm as the mid-point of a logistic allocation function that determines investment in reproduction as a function of age and size.
@@
 Strongly positive co-variation leads to the relatively flat reaction norms observed for most fish populations (\citealt{marty_impact_2011}).
-This covariation is probably the consequence of good growth conditions (e.g., from increased prey density) altering the baseline mortality $\rho$ and the risk of foraging $\eta$ (e.g., by attracting predators).
+This covariation is probably the consequence of good growth conditions (e.g., from increased food resources) altering the baseline mortality $\rho$ and the risk of foraging $\mu$ (e.g., by attracting predators).
 We did not explicitly model these interactions here (aside from the dependence of mortality on $\tau$), but rather assumed that reaction norms evolved over regimes of relatively stable temperature and growth variation in the past.
@@
 Fitness consequences for particular life-history strategies (trait combinations, see below) at different temperatures can be investigated if one considers the time-scales in the model to be short relative to evolutionary time-scales (i.e., if the model represents ecological time-scales).
-On these time-scales, we assume that adaptive responses are negligible.
-We investigate over-all fitness with respect to temperature by calculating $R_0$ for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
-$R_0$ was calculated as
-
-\[R_0(T) = \int_0^\infty \phi(w(t),w^*)P(w(t),T)S_{0 \rightarrow t}(T) \text{d}t, \text{, where} \\
-S_{0 \rightarrow t}(T) = \int_0^t \exp(-M(w(t),T))\text{d}t \]
-
-\subsection*{Trait based scenarios}
-
-To ensure a level of generality, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
-Specifically, we aimed to contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the fast strategy, indicated by a subscript $f$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth slow strategy, indicated by a subcript $s$).
+On these time-scales, we assume that adaptive responses are negligible \cite[see, however, ][]{moffett_local_2018, sandblom_plastic_2016}.
+We investigate over-all fitness with respect to temperature by calculating $R_0$, the lifetime reproductive output, for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
+$R_0$ is the appropriate measure of fitness when density dependence mainly operates early in life \cite{kozlowskican2004}, as is often assumed for fish \cite{andersenwhen2017, lorenzendensity2018}, and was calculated as
+
+\begin{align}
+R_0(T) &= \int_0^\infty \phi(w(t),w^*)P(w(t),T)S_{0 \rightarrow t}(T) \text{d}t \text{, where} \\
+S_{0 \rightarrow t}(T) &= \int_0^t \exp(-M(w(t),T))\text{d}t, 
+\end{align}
+
+\hl{is survival to age $t$, which is found by integrating over instantaneous survival ($exp(-M(w(t),T))$) from age zero to $t$, where $M$ depends on weight-at-age ($w(t)$) and temperature $T$ via temperature driven activity.
+Fitness is the the integral over energy allocated to reproduction at age $t$ and corresponding weight $w(t)$, $\phi(w(t),w^*)P(w(t),T)$ (the reproductive output), and the probability of surviving to age $t$.}
+
+\subsection*{Trait-based scenarios}
+
+To ensure a level of generality \hl{beyond existing, species-specific eco-physiological models, we explored ecological impacts of optimised behaviour at different temperatures in a trait-based context.
+In doing so, we hoped to bridge the existing gap between detailed species-specific models, and general, largely conceptual theory describing temperature impacts.}
+Specifically, we contrast species along a gradient of life-history that, at the one end, maximises production (energy acquisition; henceforth called the fast strategy, indicated by a subscript $f$) at the cost of increased metabolism and mortality, and at the opposing end minimises mortality and metabolic costs at the expense of production (henceforth slow strategy, indicated by a subscript $s$).
 This axis leads to an approximately constant ratio of production to mortality, and corresponds to a line of equal size in the life-history space proposed by \citeauthor{charnov_evolutionary_2013} (\citeyear{charnov_evolutionary_2013}).
@@
 larger heart will also contribute to higher standard metabolism in
-active species (\citealt{priede_metabolic_1985}). In practice, we assumed
-that approximately 50\% of the standard metabolic cost is due to gut
-maintenance, such that a doubling of the maximum ingestion leads to a
+active species (\citealt{priede_metabolic_1985}). \hl{In practice, we assumed
+that approximately 50\% of the standard metabolic cost is due supporting organs associated with feeding activity alone}, such that a doubling of the maximum ingestion leads to a
 50\% increase in standard metabolic cost.
@@
 In practice, this was achieved as described above by setting the maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).
-Note that, although we assume here that limitations over the temperature range are due to oxygen availibility, other limiting mechanisms, such as the respiratory control ratio (\citealt{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
-However the over-all mechanism would be the same to the one assumed here, with different untis (e.g., ATP instead of $O_2$).
+Note that, although we assume here that limitations over the temperature range are due to oxygen availability, other limiting mechanisms, such as the respiratory control ratio (\citealt{salin_inadequate_2016,iftikar_mitochondria_2013}) may determine upper limits to activity over some or all of a species temperature range.
+However the overall mechanism would be the same to the one assumed here, with different units (e.g., ATP instead of $O_2$).
+
+Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
+This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\citealt{priede_metabolic_1985}).
 
@@
 
-Increasing metabolic demands with temperature lead species to adjust activity levels in order to optimise energy gains relative to mortality risk (fig.~\ref{fig:activity}).
-This adjustment is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which show a consistent increase in activity over-all sizes for the simulated life-history (fig.~\ref{fig:size-act}).
-A similar increase in activity is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.~\ref{fig:size-act}).
-For these individuals, the increasing activity and metabolic demands lead to an active metabolic rate that is close to their MMR.
+Increasing metabolic demands at higher temperatures leads to increased activity levels in order to optimise energy gains relative to mortality risk (fig.~\ref{fig:activity}).
+This difference in activity level is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which consistently show higher activity over all sizes for the simulated life-history (fig.~\ref{fig:size-act}).
+A similarly higher activity lelve is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.~\ref{fig:size-act}).
+For these individuals, the higher activity levels and metabolic demands lead to an active metabolic rate that is close to their MMR.
 For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig.~\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature.
 For species with a rising MOS with temperature, oxygen is not limiting (fig.~\ref{fig:activity-rising}).
-However, larger fast strategy individuals are predicted to show a slightly dome-shaped adjustment in activity levels at intermediate sizes, and a slightly decreasing activity level in response to temperature at large sizes, despite available aerobic scope for activity.
-This adjsutment is a function of metabolic activity costs assumed here - at smaller metabolic costs per activity, activity adjustment are strictly increasing (fig.~\ref{fig:size-act_low}).
+However, larger fast strategy individuals are predicted to show a slightly dome-shaped relationship between activity levels and temperature at intermediate sizes, and slightly decreasing activity levels in response to temperature at large sizes, despite available aerobic scope for activity.
+\hl{This adjustment is a function of metabolic activity costs assumed here - if we assume smaller metabolic costs for activity, activity levels are always higher at higher temperature} (fig.~\ref{fig:size-act_low}).
 
 Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.~\ref{fig:feeding}).
-For slow strategy species, the increases in activity levels lead to relatively stable feeding levels, but a substantial increase in mortality coupled with a slow increase in available energy leads to an over-all decline in the ratio of $P$ to $M$.
+For slow strategy species, higher activity levels at warmer tmeperatures lead to relatively stable feeding levels, but a substantially higher mortality coupled with slightly increased available energy leads to an over-all decline in the ratio of $P$ to $M$.
 Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures.
@@
 For fast strategists, the relatively modest response in activity levels at all but the smallest sizes leads to a decline in feeding levels, which causes a largely dome-shaped response of available energy and growth efficiency to warmer temperatures (fig.~\ref{fig:feeding}).
-Again, production efficiency peaks at relatively low temperatures, but in this scenario available energy $P$ peaks at much lower temperatures.
+Again, production efficiency peaks at relatively low temperatures, but for fast life histories, available energy $P$ peaks at much lower temperatures.
 Given the relatively flat mortality levels, the ratio of $P/M$ largely follows the trend in $P$.
 
-Simulated growth curves illustrate the ontogenetic consequences of increasing temperatures (fig.~\ref{fig:norms}).
+Simulated growth curves illustrate the ontogenetic consequences of higher temperatures (fig.~\ref{fig:norms}).
 For both trait scenarios, fastest growth occurred at relatively high temperatures, with declining growth for oxygen limited species at the highest temperatures (fig.~\ref{fig:norms_O2}).
@@
 Fitness trends with temperature are strongly dependent on metabolic costs of activity (fig.~\ref{fig:fit}b), and changing the activity cost to lower values attenuates the decline in fitness with temperature for slow strategy species, and moves the fitness optimum to higher temperatures for fast strategy species.
-Similarly, increased food availibility leads to changes in fitness optima, with higher optimum temperatures, especially for fast strategists, and a slower decline of fitness with temperature.
+Similarly, increased food availability leads to changes in fitness optima, with higher optimum temperatures, especially for fast strategists, and a slower decline of fitness with temperature.
 
@@
 In this study, we attempt to provide a general mechanistic basis for exploring thermal sensitivities of ectotherm organisms.
-Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has resolved about the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\citealt{pauly_sound_2017,lefevre_modelling_2017}).
+Much of the recent debate about the validity of projected climate change impact on ectotherms, and fish in particular, has revolved around the validity of particular concepts, such as the OCLTT and projections based on the gill-oxygen limitation theory (\citealt{pauly_sound_2017,lefevre_modelling_2017}).
 We attempted to go beyond this debate by developing a model that allows for general insights about the temperature response in ectotherms, while being specific enough to mechanistically articulate aspects of physiology and ecology that are fundamental to organism response to temperature.
@@
 In line with the conceptual framework of Fry's aerobic scope and the OCLTT, our model suggests that oxygen limitation can be a potentially important ecological driver, especially at extreme temperatures for species with declining MOSs in such temperature regimes.
-At the onset of this limitation, ecological parameters change drastically, and growth, mortality are strongly impacted.
-This limitation closely mimics limitations seen in wild fish (\citealt{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function (\cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}).
+At the onset of this limitation, ecological parameters change drastically, and both growth and mortality are strongly impacted.
+This limitation closely mimics limitations seen in wild fish (\citealt{myrick_temperature_2000}), and is in line with observations that fish often seek specific water temperatures to optimise metabolic function \cite[e.g., ][]{armstrong_diel_2013,claireaux_physiology_1995}.
 Fitness, however, appears to be limited through the metabolic scope primarily via limitations at temperature extremes and impact on particular life-history stages.
 For instance, oxygen limitation is a more severe constraint for small individuals (fig.~\ref{fig:size-rates}), and thereby can limit growth performance early in life, impacting over-all fitness.
-Furthermore, changes in environmental oxygen supply, if beyond an organisms ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
+Furthermore, changes in environmental oxygen supply, if beyond an organism's ability to compensate via passive or active compensation mechanisms, will induce an over-all lower aerobic scope and lead to an earlier onset of oxygen limitation, but such scenarios do not change the qualitative predictions from our model.
 
 Variation in performance metrics away from temperature extremes are primarily affected by the interaction of temperature driven metabolic demands with optimal feeding behaviour.
-Predictions from our model, in line with metabolic experiments and species specific physiological predictions (\cite[e.g., ][]{holt_climate_2014}), suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\citealt{lucas_utilization_1992,priede_metabolic_1985}).
+Predictions from our model, in line with metabolic experiments and species specific physiological predictions \cite[e.g., ][]{holt_climate_2014}, suggest that routine activity, including normal swimming behaviour, feeding, and digestion usually lead to routine metabolic rates that are well below the MOS, even in fish with high metabolism (\citealt{lucas_utilization_1992,priede_metabolic_1985}).
 Strenuous swimming activity, for example, usually only makes up a small proportion of the standard energy budget in fish (\citealt{priede_natural_1977,priede_metabolic_1985}).
@@
 In many species, both the aerobic scope and growth peak at relatively high temperatures within the potential thermal range, yet species are often found at temperatures lower than these optima (\citealt{magnuson_thermal_1997, claireaux_influence_2000}).
-Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\citealt{claireaux_influence_2000, magnuson_thermal_1997}).
-In nearly all our simulation scenarios, fitness is predicted to decline with increasing temperature.
-This decline with temperature leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.s
-
-Resource availability imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available prey.
-Changes in prey availability thus influence individual temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal activity level.
+Previous explanations of this niche-occupation paradox involved environmental factors that narrow the thermal niche or behaviour that optimises thermal performance across available habitats (\citealt{claireaux_influence_2000, magnuson_thermal_1997, martin_why_2008}).
+In nearly all our simulation scenarios, fitness is predicted to decline with increasing temperature, \hl{and our model therefore provides a complementary explanation to those based on behavioural thermo-regulation in variable environments} (\cite[e.g., ][]{martin_why_2008}).
+This decline with temperature also leads to a parsimonious explanation for the relationship between growth performance and fitness at varying temperatures.
+
+Resource availability imposes a strong environmental constraint on organisms, with all aspects from optimal activity levels, mortality and available energy for growth ultimately influenced by available food resources.
+Changes in food resource availability thus influence individual temperature response directly via available energy, and indirectly, through altered energetic requirements to procure food and changes in mortality due to changes in the optimal activity level.
 In low-food environments, changing energetic demands with temperature are not easily adjusted for, and any adjustment demands higher energetic costs and mortality risk.
@@
 leading to increased fitness at warmer temperatures. Our
-base-parametrisation is based on the assumption that activity cost $k_a$ reflects the cost of maximal activity (i.e., cost of
+default parametrisation is based on the assumption that activity cost $k_a$ reflects the cost of maximal activity (i.e., cost of
 $\tau=1$), and has the same pay-off for all life-histories. This approximation may not
@@
 
-That fish behave optimally to maximise food acquisition relative to mortality risk and energetic requirements is a standard hypothesis and assumption in ecological models (\citealt{gilliam_habitat_1987,sainmont_effective_2015,priede_natural_1977, claireaux_influence_2000,hufnagl_physiological_2011}).
-Indeed, heightened mortality risk may be a key driver of fish spending very little time \emph{in vivo} at metabolic regimes that approach the MOS (\citealt{priede_natural_1977}), an observation that is in line with predictions from our model, especially for the slow (slow strategy) life-history.
-Our scenarios were parametrised to allow for excess metabolic scope beyond maximum foraging activity (i.e., $\tau=1$).
-This assumption is in line with observations that the aerobic scope often exceeds energetic requirements from swimming alone, and is adapted to provide oxygen for digestion (SDA), the oxygen demand of which can be as high or higher than that of locomotion alone (\citealt{priede_metabolic_1985}).
-
-Optimal activity is predicted to increase with temperature in nearly all cases, but it is sensitive to the cost of activity - at higher cost relative to the potential pay-off, activity may even decline at high temeprature.
+Optimal activity is predicted to be higher at warmer temperature in nearly all cases, but this finding is sensitive to the cost of activity - at higher cost relative to the potential pay-off, activity may even decline at high temperatures.
 Predictions of increased activity are supported by many observations in experimental and field conditions for both larval and adult fish (\citealt{sswat_growth_2018,brown_feeding_1989,claireaux_physiology_1995, biro_mechanisms_2007}).
-This increase of activity often occurs despite increased mortality (\cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}), and serves the necessity to offset increased metabolic expenses.
+This increase of activity often occurs despite increased mortality \cite[e.g., ][]{sswat_growth_2018, biro_mechanisms_2007}, and serves the necessity to offset increased metabolic expenses.
 Only large individuals of the simulated fast strategy species will optimally decrease activity as a result of increased temperature.
@@
 
-In order to provide a general framework, our model setup is deliberatly minimalist, and probably under-parametrised to reflect ecological and life-history aspects of particular species, such as migrations, social behaviour or seasonal energy requirements.
+In order to provide a general framework, our model setup is deliberately minimalist, and probably under-parametrised to reflect ecological and life-history aspects of particular species, such as migrations, social behaviour or seasonal energy requirements.
 As such, this framework provides a null model to assess the diversity of possible responses in fish, and other ectotherms, to temperature in a highly simplified system.
@@
 For instance, a recent species-specific eco-physiological model for cod (\emph{Gadus morhua}) that includes similar physiological constraints to our model predicted relatively high fitness at high temperatures (\citealt{holt_climate_2014,holt_climate_2015}).
-Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \citet{holt_climate_2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive patterns could offset potential fitness declines with increasing temperatures.
+Although this difference is potentially due to the different activity cost coefficients, foraging assumptions and species specific parametrisations in their model, differences may also be due to key assumptions about optimal reproduction: the model of  \citet{holt_climate_2014} assumed that reproductive investment is instantaneously optimised in a changing climate, pointing to the possibility that adaptation of reproductive strategies could offset potential fitness declines with increasing temperatures.
 
@@
 The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheung_shrinking_2013, pauly_sound_2017}).
-We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models (\cite[e.g., ][]{guiet_effects_2016}) and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
+We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models \cite[e.g., ][]{guiet_effects_2016} and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}).
 In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT.
 Predictions from the OCLTT are both contributing to patterns in fitness and ecological rates shown here, but are also only part of the picture, and we suggest that future improvements of predictive frameworks should center on model critisism and improvements, and leave behind semantic discussions about conceptual constructs that are difficult to explicitly link to data.
-
-% \section*{Acknowledgments}
-% 
-% The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
-PN was supported by a Marsden fast-start grant by the Royal Society Te Apārangi of New Zealand.
-KHA was supported by the Centre for Ocean Life, a VKR Centre of Excellence funded by the Villum Foundation.
+\hl{Improved eco-physiological models will provide a more robust basis for incorporating eco-physiology into tactical management and strategic conservation planning} \cite{mckenzieconservation2016, pattersonperspective2016}.
+
+\section*{Funding}
+
+This work was supported by a Marsden fast-start grant [grant number DFG-1401 to PN] by the Royal Society Te Apārangi of New Zealand and the Centre for Ocean Life, a VKR Centre of Excellence funded by the Villum Foundation.
+
+ \section*{Acknowledgments}
+
+ The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
 
@@
 
-\section*{Maturation-reaction norm}
+\section*{Appendix A: Maturation-reaction norm}
 \label{sec:MRN}
@@
 To express a MRN that varies as a function of age, we can reparametrise the MRN as:
-\[\phi(z) = 1/(1+\exp(-(c z))) \text{, where }\\
-z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))\]
+\begin{align}
+\phi(z) = 1/(1+\exp(-(c z))) \text{, where }\\
+z(t, w_t) = (w_t-w^*)\times \text{cos}(\text{atan}(b))-t\times \text{sin}(\text{atan}(b))
+\end{align}
+
 rotates the coordinate system about the slope $b$ of the reaction norm, $t$ is the age, $w$ is the mass, $w^*$ is the intercept of the reaction norm, and $c$ determines how rapidly energy allocation shifts from somatic growth to reproduction.
 
-\section*{Supplementary figures}
+\newpage
 
@@
 \begin{thebibliography}{55}
+\linespread{1.5}
 \providecommand{\natexlab}[1]{#1}
@@
 
+\bibitem[{Andersen et~al.(2017)Andersen, Jacobsen, Jansen, and
+  Beyer}]{andersenwhen2017}
+Andersen, K.~H., N.~S. Jacobsen, T.~Jansen, and J.~E. Beyer. 2017
+\newblock When in life does density dependence occur in fish populations?
+\newblock Fish and Fisheries 18:656--667.
+
 \bibitem[{Angilletta et~al.(2004)Angilletta, Steury, and
@@
 
-\bibitem[{Biro et~al.(2007)Biro, Post, and Booth}]{biromechanisms2007}
+\bibitem[{Biro et~al.(2007)Biro, Post, and Booth}]{biro_mechanisms_2007}
 Biro, P.~A., J.~R. Post, and D.~J. Booth. 2007.
@@
 
-\bibitem[{Brett(1972)}]{brettmetabolic1972}
+\bibitem[{Brett(1972)}]{brett_metabolic_1972}
 Brett, J.~R. 1972.
@@
 
-\bibitem[{Claireaux et~al.(2016-08-08)Claireaux, Webber, Lagardère, and
+\bibitem[{Claireaux et~al.(2000)Claireaux, Webber, Lagardère, and
   Kerr}]{claireaux_influence_2000}
-Claireaux, G., D.~M. Webber, J.-P. Lagardère, and S.~R. Kerr. 2016-08-08.
+Claireaux, G., D.~M. Webber, J.-P. Lagardère, and S.~R. Kerr. 2000.
 \newblock Influence of water temperature and oxygenation on the aerobic
@@
 
-\bibitem[{Gilliam and Fraser(1987)}]{gilliamhabitat1987}
+\bibitem[{Gilliam and Fraser(1987)}]{gilliam_habitat_1987}
 Gilliam, J.~F., and D.~F. Fraser. 1987.
@@
 \newblock Ecology 68:1856--1862.
+
+\bibitem[{Gillooly et~al.(2001)Gillooly, Brown, West, Savage, and
+  Charnov}]{gilloolyeffects2001}
+Gillooly, J.~F., J.~H. Brown, G.~B. West, V.~M. Savage, and E.~L. Charnov. 2001.
+\newblock Effects of size and temperature on metabolic rate 
+\newblock Science 293:2248--2251.
 
@@
 \bibitem[{Jutfelt et~al.(2018)Jutfelt, Norin, Ern, Overgaard, Wang, {McKenzie},
-  Lefevre, Nilsson, Metcalfe, and Hickey}]{jutfelt_oxygen-and_2018}
+  Lefevre, Nilsson, Metcalfe, Hickey, Brijs, Speers-Roesch, Roche, Gamperl, Raby, Morgan, Esbaugh, Gr{\"a}ns, Axelsson, Ekstr{\"o}m, Sandblom, Binning, Hicks, Seebacher, J{\o}rgensen, Killen, Schulte, and Clark}]{jutfelt_oxygen-and_2018}
 Jutfelt, F., T.~Norin, R.~Ern, J.~Overgaard, T.~Wang, D.~J. {McKenzie},
-  S.~Lefevre, G.~E. Nilsson, N.~B. Metcalfe, and A.~J. Hickey. 2018.
+  S.~Lefevre, G.~E.
+Nilsson, N.~B.
+Metcalfe, A.~J.R.
+Hickey, J.~Brijs, B.~Speers-Roesch, D.~G.
+Roche, A.~K.
+Gamperl, G.~D.
+Raby, R.~Morgan, A.~J.
+Esbaugh, A.~Gr{\"a}ns, M.~Axelsson, A.~Ekstr{\"o}m, E.~Sandblom, S.~A.
+Binning, J.~W.
+Hicks, F.~Seebacher, C.~J{\o}rgensen, S.~S.
+Killen, P.~M.
+Schulte, and T.~D.
+Clark.
+2018.
 \newblock Oxygen-and capacity-limited thermal tolerance: blurring ecology and
@@
 
+\bibitem[{Kozlowski et~al.(2004)Kozlowski, Czarnoleski, and
+  Danko}]{kozlowskican2004}
+Kozlowski, J., M.~Czarnoleski, and M.~Danko. 2004.
+\newblock Can optimal resource allocation models explain why ectotherms grow
+  larger in cold?
+\newblock Integrative and Comparative Biology 44:480--493.
+
 \bibitem[{Lefevre(2016)}]{lefevre_are_2016}
@@
 
+\bibitem[{Lorenzen and Camp(2018)}]{lorenzendensity2018}
+Lorenzen, K., and E.~V. Camp. 2018
+\newblock Density-dependence in the life history of fishes: When is a fish
+  recruited? 
+\newblock Fisheries research, in press.
+
 \bibitem[{Magnuson and {DeStasio}(1997)}]{magnuson_thermal_1997}
@@
 
+\bibitem[{Martin and Huey(2008)}]{martin_why_2008}
+Martin, T. L., and R. B. Huey. 2008.
+\newblock Why “suboptimal” is optimal: Jensen’s inequality and ectotherm thermal preferences. 
+\newblock The American Naturalist 171(3):102--118.
+
 \bibitem[{Marty et~al.(2011)Marty, Dieckmann, Rochet, and
@@
 
+\bibitem[{{McKenzie} et~al.(2016){McKenzie}, Axelsson, Chabot, Claireaux, Cooke,
+  Corner, De~Boeck, Domenici, Guerreiro, Hamer, Jørgensen, Killen, Lefevre,
+  Marras, Michaelidis, Nilsson, Peck, Perez-Ruzafa, Rijnsdorp, Shiels,
+  Steffensen, Svendsen, Svendsen, Teal, van~der Meer, Wang, Wilson, Wilson, and
+  Metcalfe}]{mckenzieconservation2016}
+{McKenzie}, D.~J., M.~Axelsson, D.~Chabot, G.~Claireaux, S.~J. Cooke, R.~A.
+  Corner, G.~De~Boeck, P.~Domenici, P.~M. Guerreiro, B.~Hamer, C.~Jørgensen,
+  S.~S. Killen, S.~Lefevre, S.~Marras, B.~Michaelidis, G.~E. Nilsson, M.~A.
+  Peck, A.~Perez-Ruzafa, A.~D. Rijnsdorp, H.~A. Shiels, J.~F. Steffensen, J.~C.
+  Svendsen, M.~B.~S. Svendsen, L.~R. Teal, J.~van~der Meer, T.~Wang, J.~M.
+  Wilson, R.~W. Wilson, and J.~D. Metcalfe. 2016.
+\newblock Conservation physiology of marine fishes: state of the art and
+  prospects for policy. 
+\newblock Conservation Physiology 4:cow046.
+
+\bibitem[{Moffett et~al.(2018)Moffett, Fryxell, Palkovacs, Kinnison, and Simon}]{moffett_local_2018}
+Moffett, E. R., D.~C. Fryxell, E.~P. Palkovacs, M.~T. Kinnison, and K.~S. Simon.
+\newblock Local adaptation reduces the metabolic cost of environmental warming.
+\newblock Ecology 99(10):2318--2326.
+
 \bibitem[{Myrick and Cech(2000)}]{myrick_temperature_2000}
@@
 
+\bibitem[{Patterson et~al.(2016)Patterson, Cooke, Hinch, Robinson, Young, Farrell,
+  and Miller}]{pattersonperspective2016}
+Patterson, D.~A., S.~J. Cooke, S.~G. Hinch, K.~A. Robinson, N.~Young, A.~P.
+  Farrell, and K.~M. Miller. 2016
+\newblock A perspective on physiological studies supporting the provision of
+  scientific advice for the management of fraser river sockeye salmon (
+  \textit{Oncorhynchus nerka} )
+\newblock Conservation Physiology 4:cow026.
+
 \bibitem[{Pauly and Cheung(2017)}]{pauly_sound_2017}
@@
 
-\bibitem[{Pörtner(2010)}]{portner_oxygen-and_2010}
-Pörtner, H.-O. 2010.
+\bibitem[{P{\"o}rtner(2010)}]{portner_oxygen-and_2010}
+P{\"o}rtner, H.-O. 2010.
 \newblock Oxygen-and capacity-limitation of thermal tolerance: a matrix for
@@
 
-\bibitem[{Pörtner and Farrell(2008)}]{portnerphysiology2008}
-Pörtner, H.~O., and A.~P. Farrell. 2008.
+\bibitem[{P{\"o}rtner and Farrell(2008)}]{portner_physiology_2008}
+P{\"o}rtner, H.~O., and A.~P. Farrell. 2008.
 \newblock Physiology and climate change.
@@
   Visser}]{sainmont_effective_2015}
-Sainmont, J., K.~H. Andersen, U.~H. Thygesen, ?.~Fiksen, and A.~W. Visser.
+Sainmont, J., K.~H. Andersen, U.~H. Thygesen, O.~Fiksen, and A.~W. Visser.
   2015-09.
@@
 \newblock Journal of Experimental Biology 219:1356--1362.
+
+\bibitem[{Sandblom et~al.(2016)Sandblom, Clark, Gräns, Ekström, Brijs, Sundström, Odelström, Adill, Aho and Jutfelt}]{sandblom_plastic_2016}
+Sandblom, E., T.~D. Clark, A.~Gräns,  A.~Ekström, J.~Brijs, L.~F. Sundström, A.~Odelström, A.~Adill, T.~Aho, and F.~Jutfelt. 2016.
+\newblock Physiological constraints to climate warming in fish follow principles of plastic floors and concrete ceilings. 
+\newblock Nature Communications 7: 11447.
 
@@
 
-\bibitem[{Vucic-Pestic et~al.(2011-03-01)Vucic-Pestic, Ehnes, Rall, and
+\bibitem[{Vucic-Pestic et~al.(2011)Vucic-Pestic, Ehnes, Rall, and
   Brose}]{vucic-pestic_warming_2011}
-Vucic-Pestic, O., R.~B. Ehnes, B.~C. Rall, and U.~Brose. 2011-03-01.
+Vucic-Pestic, O., R.~B. Ehnes, B.~C. Rall, and U.~Brose. 2011.
 \newblock Warming up the system: higher predator feeding rates but lower
@@
 \begin{table}
-{\small
+{\scriptsize
 \caption{Parameters of the constrained activity model for two scenarios: slow strategy and fast strategy species.
@@
 Exponent for max.~consumption $h$ & $q$ & \multicolumn{2}{c}{0.8} \\
-Coeff. for constant mortality & $M$ (g$\cdot$y$^{-1}$) & 0.1  & 1  \\
-Coeff. for activity related mortality & $\rho$(y$^{-1}$) & 6 & 1\\
+Coeff. for constant mortality & $\rho$ (g$\cdot$y$^{-1}$) & 0.1  & 1  \\
+Coeff. for activity related mortality & $\mu$(y$^{-1}$) & 6 & 1\\
 Exponent for mortality & $\nu$ & \multicolumn{2}{c}{0.2} \\
@@
 
+\FloatBarrier
 \newpage{}
-
-\section*{Figure legends}
-
-\begin{figure}
-%\includegraphics[width=\linewidth]{images/O2_fig_used-1} 
+\section*{Figures}
+
+\begin{figure}[!ht]
+\includegraphics[width=\linewidth]{images/O2_fig_used-1} 
 \caption[Maximum oxygen supply relative to the maximum supply for species with a dome-shaped MOS (here $\eta$ = 3) and a continually increasing MOS ($\eta$ = 0.1) used in model scenarios discussed below]{Maximum oxygen supply relative to the maximum supply for species with a dome-shaped MOS (here $\eta$ = 3) and a continually increasing MOS ($\eta$ = 0.1) used in model scenarios discussed below.}\label{fig:O2_fig_used}
@@
 
-<< setup,echo=FALSE,include=F>>=
-knitr::opts_chunk$set(echo = F,warning = F, message = F,cache=T,autodep = T)
-
-require(dplyr)
-require(tidyr)
-require(rlang)
-require(cowplot)
-
-source('model.R')
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
-
-@
-
-<<Scenarios>>=
-
-int_m <- 500
-int_t <- 500
-int_temp <- 30
-
-# Sluggish small
-ss <- list(c=0.3,
-           beta=0.1,
-           delta=4,
-           Ea=0.52, 
-           gamma=60, 
-           h=30, 
-           k=1,
-           lO=0.5, 
-           m=10, 
-           n=0.88, 
-           o=1,
-           O2crit=2, 
-           omega=0.25, 
-           p=0.8,
-           P50=4.2, 
-           phi=0.25, 
-           q=0.8,
-           shape=3,
-           temp=seq(5,26,l=int_temp),
-           Topt=20, 
-           temp_ref=15,
-           slope=0,
-           tmax=20,
-           tr=0.5,
-           M=0.1,
-           v=6,
-           lm=int_m,
-           nu=0.8-1,
-           dt=int_t,
-           min_m=-2,
-           max_m= 3
-)
-
-# fast small0.8-1
-fs <- ss
-fs$lO <- 1
-fs$k <- 1.5
-fs$h <- 60
-fs$v <- 1
-fs$M <- 1
-fs$nu<- 0.8-1
-fs$n <- 0.75
-fs$delta <- 4
-fs$o <- 1
-fs$p <- 0.8
-fs$q <- 0.8
-fs$tmax <- 10
-
-fl <- fs
-fl$shape <- 0.1
-fl$Topt <- 25
-
-sl <- ss
-sl$shape <- 0.1
-sl$Topt <- 25
-
-ffl <- fs
-ffl$gamma <- 20
-
-fsl <- ss
-fsl$gamma <- 20
-
-ffh <- fs
-ffl$gamma <- 80
-
-fsh <- ss
-fsl$gamma <- 80
-
-scs <- list(ss,fs,sl,fl)
-fscs <- list(fsh,ffh,fsl,ffl)
-
-baseline <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
-                                  Food = as.factor(rep(c('High','Low'),each=int_temp*2))),
-                       bind_rows(lapply(fscs, get_model_out,seq(0.05,1,l=int_temp))))
-
-scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
-                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
-                       bind_rows(lapply(scs, plot_data_temp)))
-
-scn <- rep(unique(scenarios$Scenario),2)
-scz <- rep(unique(scenarios$O2lim),each=2)
-
-@
-
-<<scenarios,fig.cap='Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\\degree C) for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/scenarios-1} 
+}
+\caption[Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\degree C) for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g)]{Available energy $P$ (Blue solid line), efficiency (green dashed line), and the ratio of $P$ to $M$ (orange dotted line) are impacted as a function of changing activity at constant temperature ($T=15$\degree C) for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g).
 Responses are shown for slow- (a) and fast strategy (b).
-All rates are plotted relative to their maximum for each trait scenario, the optimal activity level $\\tau^*$ is indicated by the dotted vertical line.',fig.align='center',fig.height=3,fig.width=6>>=
-
-lab <- as_labeller(c(
-                   `M strategy Low`  ='a',
-                   `P strategy Low` = 'b'))
-
-sc_bl <- baseline  %>%
-  filter(Food == 'Low') %>% 
-  group_by(Scenario) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=sc(`Feeding level`),
-         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         `Relative M` = sc(M),
-         `Energy` = sc(`Available Energy`),
-         Fitness = sc(`Available Energy`/M)) %>% 
-  tidyr::gather(Rate,value,Energy,Efficiency,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Energy','Efficiency','Fitness')),
-         Dispatch = paste(Scenario,Food))
-
-tstar <- baseline  %>%
-  filter(Food == 'Low') %>%
-  group_by(Scenario, Food) %>%
-  mutate(`Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         Fitness = sc(`Available Energy`/M)) %>% 
-  summarise(tstar = tau[which.max(Fitness)]) %>%
-  mutate(Dispatch = paste(Scenario,Food))
-
-ggplot() + 
-  geom_line(aes(x=tau, y=value, linetype=Rate,col=Rate,group=Rate),data=sc_bl) +
-  geom_vline(aes(xintercept=tstar),linetype=3,data=tstar) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
-  theme(strip.text = element_text(hjust = 0.05),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual('',values=c(1:3))+
-  scale_color_manual('',values = cols)+
-   labs(x = expression('Activity ' (tau)),
-       y='Relative rate')
-
-@
-
-\begin{figure}
+All rates are plotted relative to their maximum for each trait scenario, the optimal activity level $\tau^*$ is indicated by the dotted vertical line.}\label{fig:scenarios}
+\end{figure}
+
+\begin{figure}[!ht]
 \centering
-<<activity, fig.height=6,fig.width=7>>=
-
-sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,O2lim))
-
-lab1 <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b'))
-
-lab2 <- as_labeller(c(`M strategy Domed`  ='c',
-                   `P strategy Domed` = 'd'))
-
-ggsc <- ggplot(sc_act %>% filter(O2lim=='Domed')) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols)+
-  scale_linetype()+
-  facet_wrap(~Dispatch,ncol = 2,labeller = lab1)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
-  mutate(Dispatch = paste(Scenario,O2lim))
-
-ggso <- sco %>% filter(O2lim=='Domed') %>%
-  ggplot() + 
-   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot() +
-  scale_color_manual(values = cols)+
-  scale_linetype()+
-  facet_wrap(~Dispatch,ncol = 2,labeller = lab2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression(Oxygen~(mg.yr^-1)))
-
-cowplot::plot_grid(ggsc,ggso,ncol=1)
-
-@
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (top row [a,b]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (bottom row [c,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; a \& c) and fast strategy (fast life-history; b \& d).}
+\includegraphics[width=\maxwidth]{figure/activity-1}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (top row [a,b]) at increasing temperatures for a 10g fish with a dome-shaped MOS with increasing temperature (maximum at 20\degree C), with corresponding oxygen demand (bottom row [c,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow life-history (a \& c) and fast life-history (b \& d).}
 \label{fig:activity}
@@
 
-<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\\infty}\\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=
-
-ssm <- ss
-ssm$m <- 1.25
-
-ssl <- ss
-ssl$m <- 80
-
-fsm <- fs
-fsm$m <- 1.25
-
-fsl <- fs
-fsl$m <- 80
-
-scss <- list(ssm,ss,ssl,fsm,fs,fsl)
-
-scenarios_s <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('M strategy','P strategy'),each=3),each=int_temp)),
-                                  Size = as.factor(rep(rep(c('Small','Medium','Large'),2),each=int_temp))),
-                       bind_rows(lapply(scss, plot_data_temp)))
-
-sc_acts <- gather(scenarios_s,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,Size))
-
-laba <- as_labeller(c(`M strategy Small` ='a',
-                   `P strategy Small`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy Large` = 'e',
-                   `P strategy Large` = 'f'
-))
-
-sc_acts$Dispatch <- factor(sc_acts$Dispatch,levels=unique(sc_acts$Dispatch)[order(unlist(laba(unique(sc_acts$Dispatch))))])
-
-ggplot(sc_acts) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols)+
-  scale_linetype()+
-  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-@
-
-<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\\infty}\\sim 30$cm) at 10cm length (10g).
+\begin{figure}[!ht]
+{\centering 
+  \includegraphics[width=\maxwidth]{figure/size-act-1} 
+}
+\caption[Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\infty}\sim 30$cm at 1.25g (5cm]{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures through ontogeny for a for fish with a $L_{\infty}\sim 30$cm at 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.}\label{fig:size-act}
+\end{figure}
+
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/feeding-1} 
+}
+\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g)]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish ($L_{\infty}\sim 30$cm) at 10cm length (10g).
 Responses are shown for slow  and fast strategy (a and b, respectively), for species with and without oxygen limitation (left and right columns, respectively).
-Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center',fig.height=4,fig.width=7>>=
-
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b'))
-
-sc_feed <- scenarios %>% filter(O2lim=='Domed') %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,O2lim) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         M=sc(M),
-         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         `Relative M` = sc(M),
-         `Energy` = sc(`Available Energy`),
-         Fitness = sc(`Available Energy`/M)) %>% 
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,O2lim))
-
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
-  theme(strip.text = element_text(hjust = 0.05),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual('',values=c(1:4,1))+
-  scale_color_manual('',values = cols)+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate') + theme(legend.position = "top")
-
-@
-
-<<calc-gouts>>=
-
-ssgl <- ss
-ssgl$gamma <- 40
-
-ssgh <- ss
-ssgh$gamma <- 80
-
-fsgl <- fs
-fsgl$gamma <- 40
-
-fsgh <- fs
-fsgh$gamma <- 80
-
-scsg <- list(ssgl,ss,ssgh,fsgl,fs,fsgh)
-
-mstar_ss <- plot_data_growth_tO2(ss)$mstar
-mstar_fs <- plot_data_growth_tO2(fs)$mstar
-
-#mstar_ss <- 18
-#mstar_fs <- 18
-
-goutss <- parallel::mclapply(list(ssgl,ss,ssgh),
-                             plot_data_growth_tO2,
-                             mstar=mstar_ss,
-                             mc.cores = 3)
-
-goutsf <- parallel::mclapply(list(fsgl,fs,fsgh),
-                             plot_data_growth_tO2,
-                             mstar=mstar_fs,
-                             mc.cores = 3)
-
-gouts <- c(goutss,goutsf)
-
-@
-
-<<norms, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Energy, mortality and fitness are plotted relative to their maximum over all temperatures.}\label{fig:feeding}
+\end{figure}
+
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/norms-1} 
+}
+\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
 Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
-
-labla <- as_labeller(c(`M strategy Low` ='a',
-                   `P strategy Low`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy High` = 'e',
-                   `P strategy High` = 'f'
-))
-
-t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
-
-#browser()
-norm <- t_growth %>% 
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
-
-<<infs, fig.cap='Interactive effects of food availibility and temperature of the asymptotic size ($L_{\\infty}$), with increasing linewidth showing increasing prey availibility for a) slow and b) fast life-history species.',fig.align='center',fig.width=6,fig.height=3>>=
-
-infs <- t_growth %>% 
-  mutate(Food = factor(Food, levels=c('Low','Medium','High'))) %>%
-  group_by(Scenario, Food,Temperature) %>%
-  summarise(lmax = max(t_length)) %>%
-  mutate(wmax = wl(lmax))
-
-size <- tidyr::gather(infs,size,value,-Scenario, -Food,-Temperature)
-
-labls <- as_labeller(c(`M strategy` ='a',
-                   `P strategy`  ='b'))
-
-ggplot() +
-  geom_line(aes(x=Temperature, y=value,size=as.numeric(Food),group=Food),data=size%>% filter(size=='lmax')) +
-  theme_cowplot()+
-  scale_linetype_discrete(guide='none') +
-  facet_wrap(~Scenario,labeller = labls) + 
-  scale_size(guide='none',range = c(0.6,1.4))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0.05),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = expression(L[infinity]~(cm)),
-       x=expression("Mean temperature " ( degree*C)))
-
-@
-
-<<>>=
-ssm <- ss
-ssm$delta <- 2
-
-ssl <- ss
-ssl$delta <- 1
-
-fsm <- fs
-fsm$delta <- 2
-
-fsl <- fs
-fsl$delta <- 1
-
-scsa <- list(ss,ssm,ssl,fs,fsm,fsl)
-scna <- rep(unique(scenarios$Scenario),each=3)
-scza <- rep(c('High','Medium','Low'),3)
-
-gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)
-goutr <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 3)
-@
-
-<<fit, fig.cap='Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and base parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)',fig.align='center',fig.height=8>>=
-
-R0s <- bind_rows(lapply(1:length(goutr), function(x) {
-  y <- data.frame(goutr[[x]]['R0'])
-  y$Temperature <-goutr[[x]][['winfs']]$Temperature
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
-  y}))
-
-R0s <- R0s %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T))
-
-sizes = c(0.5,1,1.5)
-
-f1.1 <- ggplot(R0s%>% filter(Scenario=='M strategy')) + 
-  geom_line(aes(x=Temperature, y=R0, col=O2lim)) +
-  theme_cowplot()+
-  theme(axis.text.x = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-    scale_colour_manual(values=cols,guide='none')+
-  labs(x = ' ',
-       y='Relative fitness')
-
- f1.2 <- ggplot(R0s%>% filter(Scenario=='P strategy')) + 
-  geom_line(aes(x=Temperature, y=R0, col=O2lim)) +
-  theme_cowplot()+
-  theme(axis.text = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_colour_manual(values=cols,guide='none')+
-  labs(x = ' ',
-       y=' ')
-
-R0ss <- bind_rows(lapply(1:length(gouta), function(x) {
-  y <- data.frame(gouta[[x]]['R0'])
-  y$Temperature <-gouta[[x]][['winfs']]$Temperature
-  y$Scenario <- scna[x]
-  y$ActivityCost <- scza[x]
-  y$Dispatch <- paste(scna[x],scza[x])
-  y}))
-
-R0ss <- R0ss %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T),
-         ActivityCost = factor(ActivityCost,levels=c('Low','Medium','High')))
-
-f2.1 <- ggplot(R0ss%>% filter(Scenario=='M strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=ActivityCost,size=as.numeric(ActivityCost)/3)) +
-  theme_cowplot()+
-  theme(axis.text.x = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.6,1.4))+
-  labs(x = ' ',
-       y='Relative fitness')
-
-f2.2 <- ggplot(R0ss%>% filter(Scenario=='P strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=ActivityCost,size=as.numeric(ActivityCost)/3)) +
-  theme_cowplot()+
-  theme(axis.text = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.6,1.4))+
-  labs(x =' ',
-       y=' ')
-
-R0sss <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- data.frame(gouts[[x]]['R0'])
-   y$Temperature <-gouts[[x]][['winfs']]$Temperature
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-R0sss <- R0sss %>% group_by(Dispatch) %>%
-  mutate(R0 = R0/max(R0, na.rm=T),
-         Food = factor(Food,levels=c('Low','Medium','High')))
-
-f3.1 <- ggplot(R0sss %>% filter(Scenario=='M strategy')) + 
-  geom_line(aes(x=Temperature, y=log(R0),group=Food,size=as.numeric(Food)/3)) +
-  theme_cowplot()+
-  theme(
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.6,1.4))+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative fitness')
-
-f3.2 <- ggplot(R0sss %>% filter(Scenario=='P strategy')) + 
-  geom_line(aes(x=Temperature, y=R0,group=Food,size=as.numeric(Food)/3)) +
-  theme_cowplot()+
-  theme(axis.text.y = element_text(colour = 'white'),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_size(guide='none',range = c(0.6,1.4))+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=' ')
-
-cowplot::plot_grid(f1.1,f1.2,f2.1,f2.2,f3.1,f3.2,ncol=2,labels = 'auto')
-
-@
-
-\subsection*{Online figure legends}
-
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms}
+\end{figure}
+
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/infs-1} 
+}
+\caption[Interactive effects of food availibility and temperature on the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing food resource availibility for a) slow and b) fast life-history species]{Interactive effects of food availibility and temperature of the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing food resource availibility for a) slow and b) fast life-history species.}\label{fig:infs}
+\end{figure}
+
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=0.8\maxwidth]{figure/fit-1} 
+}
+\caption[Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)]{Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)}\label{fig:fit}
+\end{figure}
+
+\FloatBarrier
+\newpage
+\subsection*{Supplementary Figures}
 \renewcommand{\thefigure}{A\arabic{figure}}
@@
 
-<<MRN, fig.cap='Proportion of energy allocated to reproduction, as a function of age (a) and size (b).
-With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.',fig.align='center',fig.height=6>>=
-
-lam <- goutr[[3]]$t_growth
-
-mr1 <- ggplot(lam) + 
-  geom_line(aes(x=t, y=allocs,col=Temperature,group=as.factor(Temperature))) +
-  #geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Proportion',
-       x='Age  (years)')
-
-mr2 <- ggplot(lam) + 
-  geom_line(aes(x=t_length, y=allocs,col=Temperature,group=as.factor(Temperature))) +
-  #geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Proportion',
-       x='Size (cm)')
-
-cowplot::plot_grid(mr1,mr2,ncol=1,labels = 'auto')
-
-@
-
-\renewcommand{\thefigure}{B\arabic{figure}}
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/MRN-1} 
+}
+\caption[Proportion of energy allocated to reproduction, as a function of age (a) and size (b)]{Proportion of energy allocated to reproduction, as a function of age (a) and size (b).
+With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.}\label{fig:MRN}
+\end{figure}
+
+\renewcommand{\thefigure}{S\arabic{figure}}
 \setcounter{figure}{0}
-
-\begin{figure}
+\begin{figure}[!ht]
 \centering
-<<activitys, fig.height=6,fig.width=7>>=
-
-sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,O2lim))
-
-cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')
-
-lab1 <- as_labeller(c(`M strategy Rising`  ='a',
-                   `P strategy Rising` = 'b'))
-
-lab2 <- as_labeller(c(`M strategy Rising`  ='c',
-                   `P strategy Rising` = 'd'))
-
-ggsc <- ggplot(sc_act %>% filter(O2lim=='Rising')) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 2,labeller = lab1)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
-  mutate(Dispatch = paste(Scenario,O2lim))
-
-ggso <- sco %>% filter(O2lim=='Rising') %>%
-  ggplot() + 
-   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
-  theme_cowplot() +
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 2,labeller = lab2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression(Oxygen~(mg.yr^-1)))
-
-cowplot::plot_grid(ggsc,ggso,ncol=1)
-
-@
+\includegraphics[width=\maxwidth]{figure/activitys-1} 
 \caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; aandb) and fast strategy (fast life-history; c, d).}
@@
 
-<<size-act_low,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm; e--f), for a fast strategy (fast life-history) species with a dome-shaped maximum metabolic rate with respect to temperature.
-',fig.align='center'>>=
-
-scsa[[4]]$m <- 80
-scsa[[5]]$m <- 80
-scsa[[6]]$m <- 80
-
-scenarios_d <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('P strategy'),each=3),each=int_temp)),
-                                   AC= as.factor(rep(rep(c('High','Medium','Low'),1),each=int_temp))),
-                       bind_rows(lapply(scsa[4:6], plot_data_temp)))
-
-sc_actd <- gather(scenarios_d,Activity,value,Optimum, Limit,Realised) %>%
-  mutate(Activity = relevel(as.factor(Activity), "Realised"),
-         Dispatch = paste(Scenario,AC))
-
-labal <- as_labeller(c(`P strategy Low` ='a',
-                   `P strategy Medium`  ='b',
-                   `P strategy High` ='c'))
-
-sc_actd$Dispatch <- factor(sc_actd$Dispatch,levels=unique(sc_actd$Dispatch)[order(unlist(labal(unique(sc_actd$Dispatch))))])
-
-ggplot(sc_actd) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
-  theme_cowplot()+
-  scale_color_manual(values = cols,guide='none')+
-  scale_linetype(guide='none')+
-  facet_wrap(~Dispatch,ncol = 1,labeller = labal)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank()) + 
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y=expression('Activity ' (tau)))
-
-@
-
-<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\\infty}\\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.
-Energy, mortality and fitness are plotted relative to their maximum over all temperatures.',fig.align='center'>>=
-
-sc_feed <- scenarios_s %>%
-  #filter(!grepl('large',Scenario)) %>% 
-  group_by(Scenario,Size) %>%
-  mutate(Consumption=sc(Consumption),
-         Efficiency=sc(Efficiency),
-         Feeding=`Feeding level`,
-         M = sc(M),
-         `Available Energy` = ifelse(`C for growth`<0,0,`C for growth`),
-         `Relative M` = sc(M),
-         `Energy` = sc(`Available Energy`),
-         Fitness = sc(`Available Energy`/M)) %>%  
-  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
-  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
-         Dispatch = paste(Scenario,Size))
-
-sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])
-
-ggplot(sc_feed) + 
-  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
-  theme(strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  scale_linetype_manual(values=c(1:4,1),guide='none')+
-  scale_color_manual(values = cols,guide='none')+
-  labs(x = expression("Mean temperature " ( degree*C)),
-       y='Relative rate')
-
-@
-
-\begin{figure}
-\centering
-<<norms_O2, fig.align='center',fig.height=6>>=
-
-lab <- as_labeller(c(`M strategy Domed`  ='a',
-                   `P strategy Domed` = 'b',
-                   `M strategy Rising`  ='c',
-                   `P strategy Rising` = 'd'))
-
-t_growth <- bind_rows(lapply(1:length(goutr), function(x) {
-  y <- goutr[[x]][['t_growth']] 
-  y$Scenario <- scn[x]
-  y$O2lim <- scz[x]
-  y$Dispatch <- paste(scn[x],scz[x])
-  y}))
-
-#browser()
-norm <- t_growth %>% 
-  mutate(Dispatch = paste(Scenario,O2lim)) %>%
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  #geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  #geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/size-act_low-1} 
+}
+\caption[Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm]{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels at increasing temperatures through ontogeny for a for fish nearly grown fish of 80g (20cm; e--f), for a fast strategy (fast life-history) species with a dome-shaped maximum metabolic rate with respect to temperature.
+}\label{fig:size-act_low}
+\end{figure}
+
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/size-rates-1} 
+}
+\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\infty}\sim 30$cm) of 1.25g (5cm]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish ($L_{\infty}\sim 30$cm) of 1.25g (5cm; a--b); 10g (10cm; c--d) and 80g (20cm; e--f ), for slow strategy (slow life history; left column [a,c,e]) and fast strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.
+Energy, mortality and fitness are plotted relative to their maximum over all temperatures.}\label{fig:size-rates}
+\end{figure}
+
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/norms_O2-1} 
+}
 \caption{Contrasting growth responses at baseline resource availability for species with dome-shaped MOS (top row [a,b]) and increasing MOS with temperature (bottom row [c,d]).
@@
 
-<<>>=
-
-scsg <- lapply(scsg,function(x) {x$slope=-1;x})
-
-goutss <- parallel::mclapply(scsg[1:3],
-                             plot_data_growth_tO2,
-                             mstar=mstar_ss,
-                             mc.cores = 3)
-
-goutsf <- parallel::mclapply(scsg[4:6],
-                             plot_data_growth_tO2,
-                             mstar=mstar_fs,
-                             mc.cores = 3)
-
-gouts <- c(goutss,goutsf)
-
-@
-
-<<norms_neg, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/norms_neg-1} 
+}
+\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
 Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
-
-labla <- as_labeller(c(`M strategy Low` ='a',
-                   `P strategy Low`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy High` = 'e',
-                   `P strategy High` = 'f'
-))
-
-t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
-
-#browser()
-norm <- t_growth %>% 
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
-
-<<>>=
-
-scsg <- lapply(scsg,function(x) {x$slope=1;x})
-
-goutss <- parallel::mclapply(scsg[1:3],
-                             plot_data_growth_tO2,
-                             mstar=mstar_ss,
-                             mc.cores = 3)
-
-goutsf <- parallel::mclapply(scsg[4:6],
-                             plot_data_growth_tO2,
-                             mstar=mstar_fs,
-                             mc.cores = 3)
-
-gouts <- c(goutss,goutsf)
-
-@
-
-<<norms_pos, fig.cap='On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_neg}
+\end{figure}
+
+\begin{figure}[!ht]
+{\centering 
+\includegraphics[width=\maxwidth]{figure/norms_pos-1} 
+}
+\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
 Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.',fig.align='center',fig.width=6>>=
-
-labla <- as_labeller(c(`M strategy Low` ='a',
-                   `P strategy Low`  ='b',
-                   `M strategy Medium` ='c',
-                   `P strategy Medium` = 'd',
-                   `M strategy High` = 'e',
-                   `P strategy High` = 'f'
-))
-
-t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
-  y <- gouts[[x]][['t_growth']] 
-  y$Scenario <- rep(c('M strategy','P strategy'),each=3)[x]
-  y$Food<- rep(c('Low','Medium','High'),2)[x]
-  y$Dispatch <- paste(rep(c('M strategy','P strategy'),each=3)[x],rep(c('Low','Medium','High'),2)[x])
-  y}))
-
-t_growth$Dispatch <- factor(t_growth$Dispatch, levels = levels(as.factor(t_growth$Dispatch))[c(2,5,3,6,1,4)])
-
-#browser()
-norm <- t_growth %>% 
-  group_by(Dispatch,Temperature) %>%
-  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
-            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
-            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
-            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])
-
-ggplot() +
-  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
-  geom_point(aes(x=ts, y=m),data=norm) +
-  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
-  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
-  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
-  theme_cowplot()+
-  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = labla)+
-  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
-  theme(legend.text = element_text(size=8),
-        legend.title = element_text(size=9),
-        strip.text = element_text(hjust = 0),
-        strip.background = element_blank(),
-        panel.background = element_blank(),
-        plot.background = element_blank())+
-  coord_cartesian()+
-  labs(y = 'Length (cm)',
-       x='Age  (years)')
-
-@
+Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_pos}
+\end{figure}
 

### 2019-01-31 Cons_physio_revision.tex
revised submission

@@
 As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\citealt{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).
-\hl{Such predictions of changes in species ecology based on physiological function are important to ensure appropriate policy and management response to changing environments and expected effects on organisms}\cite{mckenzieconservation2016, pattersonperspective2016}.
+\hl{Such predictions of changes in species ecology based on physiological function are important to ensure appropriate policy and management response to changing environments and expected effects on organisms}(\citealt{mckenzieconservation2016, pattersonperspective2016}).
 However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems.
@@
 Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazier_activity_2009,brett_1965_relation}, and the activity fraction.
-Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approximated by an Arrhenius scaling $c(T) = e^{E_a(T-T_0)/(b\cdot T\cdot T_0)}$ \cite{gilloolyeffects2001}, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (such that c(T)=1 at 15\degree C), and $b$ is the Boltzmann constant.
+Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approximated by an Arrhenius scaling $c(T) = e^{E_a(T-T_0)/(b\cdot T\cdot T_0)}$ (\citealt{gilloolyeffects2001}), where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (such that c(T)=1 at 15\degree C), and $b$ is the Boltzmann constant.
 Note that we only scale rates related to enzymatic activity with temperature, we do not assume that ecological rates such as foraging rates or activity are a direct function of temperature.
@@
 \hl{ In our model, MMR and maximum oxygen supply are equivalent as we do not explicitly model contributions from anaerobic metabolism, such as during burst swimming or hypoxia.
-During such events, the actual metabolic rate may be higher than oxygen consumption alone would suggest, however such states cannot usually be sustained (and therefore fall outside of the sustained MMR defined here).} We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck_2013_freshwater, lefrancois_influence_2003}):
+During such events, the actual metabolic rate may be higher than oxygen consumption alone would suggest, however such states cannot usually be sustained (and therefore fall outside of the sustained MMR defined here).} We assume that oxygen supply, \hl{taken as the aggregated process of oxygen delivery from diffusion across respiratory organ membranes (e.g., gills) to delivery for cellular metabolism,} is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck_2013_freshwater, lefrancois_influence_2003}):
 
@@
 Ambient oxygen concentration levels are assumed to decline with temperature according to a curve that approximates declines of dissolved oxygen in saltwater at 35 PSU as $l\cdot e^{-0.01851*(T-5)}$, with $l$ the oxygen concentration at 5\degree C.} To specify $\lambda(T)$, we define $T_{\text{max}}$ as the lethal temperature for the species, and $T_{\text{opt}}$ as the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height.
-Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).
+\hl{Note that the simulated increase in the aggregated oxygen supply includes potential increases in oxygen delivery via increased diffusive (passive) supply at higher temperatures} (\citealt{verberk_oxygen_2011}) \hl{as well as increased active delivery of oxygen made possible by increased heart rates at higher temperatures} \cite[e.g.,][]{lefrancois_influence_2003}.
+With the above formulation, we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).
 
@@
 \item Production efficiency, here defined as available energy for both growth and reproduction, relative to the food consumption (i.e., $\frac{P(w,T)}{f(w,T)h c(T) w^q)}$.
-\item The dimensionless ratio of $\frac{P}{Mw}$, which is analogous to the short-sighted fitness aproximation (Gilliam's rule) used above.
+\item The dimensionless ratio of $\frac{P}{Mw}$, which is analogous to the short-sighted fitness approximation (Gilliam's rule) used above.
 \item Fitness integrated over an individual's lifetime, defined as $R_0$ (see below).
@@
 We investigate over-all fitness with respect to temperature by calculating $R_0$, the lifetime reproductive output, for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here.
-$R_0$ is the appropriate measure of fitness when density dependence mainly operates early in life \cite{kozlowskican2004}, as is often assumed for fish \cite{andersenwhen2017, lorenzendensity2018}, and was calculated as
+$R_0$ is the appropriate measure of fitness when density dependence mainly operates early in life (\citealt{kozlowskican2004}), as is often assumed for fish (\citealt{andersenwhen2017, lorenzendensity2018}), and was calculated as
 
@@
 This difference in activity level is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which consistently show higher activity over all sizes for the simulated life-history (fig.~\ref{fig:size-act}).
-A similarly higher activity lelve is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.~\ref{fig:size-act}).
+A similarly higher activity level is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.~\ref{fig:size-act}).
 For these individuals, the higher activity levels and metabolic demands lead to an active metabolic rate that is close to their MMR.
@@
 Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.~\ref{fig:feeding}).
-For slow strategy species, higher activity levels at warmer tmeperatures lead to relatively stable feeding levels, but a substantially higher mortality coupled with slightly increased available energy leads to an over-all decline in the ratio of $P$ to $M$.
+For slow strategy species, higher activity levels at warmer temperatures lead to relatively stable feeding levels, but a substantially higher mortality coupled with slightly increased available energy leads to an over-all decline in the ratio of $P$ to $M$.
 Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures.
@@
 Predictions from the OCLTT are both contributing to patterns in fitness and ecological rates shown here, but are also only part of the picture, and we suggest that future improvements of predictive frameworks should center on model critisism and improvements, and leave behind semantic discussions about conceptual constructs that are difficult to explicitly link to data.
-\hl{Improved eco-physiological models will provide a more robust basis for incorporating eco-physiology into tactical management and strategic conservation planning} \cite{mckenzieconservation2016, pattersonperspective2016}.
+\hl{Improved eco-physiological models will provide a more robust basis for incorporating eco-physiology into tactical management and strategic conservation planning} (\citealt{mckenzieconservation2016, pattersonperspective2016}).
 
@@
 The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.
+We also thank Christian Jørgensen and three anonymous reviewers, who provided helpful reviews that greatly clarified the manuscript.
 
@@
 \bibliographystyle{amnatnat}
-\begin{thebibliography}{55}
+\begin{thebibliography}{62}
 \linespread{1.5}
@@
 
+\bibitem[{Verberk et~al.(2011)Verberk, Bilton, Calosi, and
+  Spicer}]{verberk_oxygen_2011}
+Verberk, W.~C., D.~T. Bilton, P.~Calosi, and J.~I. Spicer. 2011
+\newblock Oxygen supply in aquatic ectotherms: partial pressure and solubility
+  together explain biodiversity and size patterns 92:1565--1572.
+
 \bibitem[{Verberk et~al.(2016)Verberk, Overgaard, Ern, Bayley, Wang, Boardman,
@@
 \caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms}
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availability from top (a/b) to bottom (e/f).
+Baseline resource availability assumed in all other simulations is that shown in panels c and d.}\label{fig:norms}
 \end{figure}
@@
 }
-\caption[Interactive effects of food availibility and temperature on the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing food resource availibility for a) slow and b) fast life-history species]{Interactive effects of food availibility and temperature of the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing food resource availibility for a) slow and b) fast life-history species.}\label{fig:infs}
+\caption[Interactive effects of food availability and temperature on the asymptotic size ($L_{\infty}$), with increasing line width showing increasing food resource availability for a) slow and b) fast life-history species]{Interactive effects of food availability and temperature of the asymptotic size ($L_{\infty}$), with increasing line width showing increasing food resource availability for a) slow and b) fast life-history species.}\label{fig:infs}
 \end{figure}
@@
 }
-\caption[Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)]{Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)}\label{fig:fit}
+\caption[Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (left column) and fast strategy (right column) species at the assumed maturation-reaction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing line width, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing line width)]{Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (left column) and fast strategy (right column) species at the assumed maturation-reaction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing line width, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing line width)}\label{fig:fit}
 \end{figure}
@@
 \includegraphics[width=\maxwidth]{figure/activitys-1} 
-\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; aandb) and fast strategy (fast life-history; c, d).}
+\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; a and b) and fast strategy (fast life-history; c, d).}
 \label{fig:activity-rising}
@@
 \caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_neg}
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availability from top (a/b) to bottom (e/f).
+Baseline resource availability assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_neg}
 \end{figure}
@@
 \caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.
-Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f).
-Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_pos}
+Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availability from top (a/b) to bottom (e/f).
+Baseline resource availability assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_pos}
 \end{figure}
